### 2020-09-14 manuscript/manuscript.Rmd
initial commit

---
title: Categorical Predictor Embeddings in Actuarial Modeling
authors:
  - name: Kevin Kuo 
    affiliation: RStudio and Kasa AI
    email: kevin@kasa.ai
  - name: Ronald Richman
    affiliation: QED Actuaries and Consultants
    email: ronaldrichman@gmail.com
abstract: |
  Enter the text of your abstract here.
keywords:
  - blah
  - blee
  - bloo
  - these are optional and can be removed
bibliography: references.bib
output: rticles::arxiv_article
---

# Introduction

Categorical data are modelled by actuaries in many different contexts, from pricing of insurance products to reserving for the liabilities generated by these products. Sometimes, these data are modelled in an explicit manner, for example, when building models that apply across multiple categories, a form of dummy coding is usually used. For example, when building models to price the frequency of motor insurance claims, claim experience relating to different types of motor vehicle will often be modelled by including a (single) factor within models that modifies the relative frequency predicted for each type of vehicle. In other cases, modelling is performed for each category separately, thus the categorical data is used within the modelling in an implicit manner, for example, common practice is to estimate reserves for different lines of business separately, meaning to say, with no parameters being shared across each of the reserving models.

Recently, several studies of insurance problems have applied an alternative approach, originally from the natural language processing literature [@Bengio2003] and now applied to diverse types of machine learning problem [@Guo2016], known as **categorical embeddings**. Instead of trying to capture the differences between categories using a single factor, the categorical embedding approach rather maps each category to a low-dimensional numeric vector, which is then used within the model as a new predictor variable.

This approach to modelling categorical data has several advantages over more traditional treatments of categorical data. Using categorical embeddings instead of traditional techniques has been shown to increase predictive accuracy of models, for example, see [@Richman2018] in the context of pricing. Models incorporating categorical embeddings can be pre-calibrated to traditional actuarial models, increasing the speed with which these models can be calibrated and leading to models with better explainability [@wuthrich2019yes]. Finally, the similarity between the vectors learned for different categories can be inspected, sometimes leading to insights into the workings of models, see, for example, [@Kuo2019].

On the other hand, several open questions about the use of embeddings within actuarial work remain, which we aim to address in this study. First, hyperparameter settings for embeddings, such as the dimensions of the embedding layer and the use of regularization techniques such as dropout or normalization, that achieve optimal predictive performance has not yet been studied in detail in the actuarial literature. In this work, we aim to study how embeddings using different settings perform in the context of a large-scale predictive modelling problem, and give guidance on the process that can be followed to determine this in other problems. Although neural network have been shown to achieve excellent predictive accuracy on actuarial tasks, many actuaries still prefer to use GLM models for pricing tasks, thus, the issue of whether transferring embeddings to GLM models can achieve better performance is considered in this paper. Traditional actuarial techniques such as credibility theory have been used to work with some types of categorical data, but no study has been performed whether this can be applied within embeddings; here, we investigate whether performance is enhanced by applying credibility theory on embeddings relating to categorical variables with many labels. Whereas embedding layers are usually considered in the context of categorical data,the option exists to quantize numerical data and model it using embeddings, however, the results of doing so have not been investigated. Finally, in the past several years, a new type of neural network architecture based on attention [@Vaswani2017] has been successfully used on embeddings in the field of natural language processing and we incorporate attention based models into our predictive modelling example.

In this work, we utilize the recently released National Flood Insurance Program (NFIP) dataset [@FederalEmergencyManagementAgency2019] which provides exposure information for policies written under the NFIP since XXXXDateXXXX, as well as the claims data relating to these exposures. We refer the reader to Appendix \ref{NFIP_eda} for an exploratory analysis of this dataset.

The rest of this manuscript is organized as follows. Section \ref{lit_review} reviews recent applications of embeddings in the actuarial literature. Section \ref{defns} provides the notation used in the paper and defines GLMs, neural networks and related modelling concepts. In Section \ref{modelling}, we provide initial models for the NFIP dataset and consider the influence of hyperparameter choices on the results of the neural network model. Section \ref{tl} considers how successfully the embeddings used in the neural network model can be transferred to a GLM model of the same data. Extensions to the modelling approach are considered in Section \ref{extend} and we focus on attention based models in Section \ref{attention}. The interpretability of embedding layers is addressed in Section \ref{interpretation}. Finally, Section \ref{Conclusions} provides a discussion of the results of this paper and considers avenues for future research.

(TODO: link to github repo)

# Literature Review {#lit_review}

Categorical data are usually modelled within GLMs and other predictive models using indicator variables which capture the effect of each level of the category, see, for example, Section 2 in [@Goldburd], using one of two main encoding schemes: dummy-coding and one-hot encoding. Dummy-coding, used in the popular \texttt{R} statistical software, assigns one level of the category as a baseline, for which an indicator variable is not calibrated, and the rest of the levels are assigned indicator variables, thus, producing estimates within the model of how the effects of each level differ from the baselines. One-hot encoding, often used in machine learning, is similar to dummy-coding, but assigns indicator variables to each level, in other words, calibrates an extra indicator variable compared with dummy-coding.

A different approach to modelling categorical data is credibility theory (see [@Buhlmann2006] for an overview), which, in the context of rating, can be applied to derive premiums that reflect the experience of a particular policyholder, by estimating premiums as a weighted average between the premium produced using the collective experience (i.e. of all policyholders) and the premium produced using the experience of the particular policyholder. The weight used in this average is called a credibility factor and is calculated with reference to te variability of the policyholder experience relative to the variability of the group experience. In this context, the implicit categorical variable is the policyholder under consideration.

Generalized Linear Mixed Models (GLMMs) are an extension of GLMs that are designed for modelling categorical data using a principle very similar to that of credibility theory [@Klinker2010]. Instead of calibrating indicator variables for each level of the category, GLMMs estimate effects for each of these levels as a combination of the overall group mean and the experience in each level of the category.

Embedding layers represent a different approach to the problem of modelling categorical data that was recently introduced in an actuarial context. Note that in the next section, we reflect on similarities between the conventional approaches discussed above and embedding layers. [@Richman2018] reviewed the concept of embedding layers and connected the sharing of information across categories to the familiar concept of credibility theory. In that work, two applications of embedding layers were demonstrated. The first of these was in a Property and Casualty (P&C) pricing context, it was shown that the out-of-sample accuracy of a neural network trained to predict claims frequencies on motor third party liability was enhanced by modelling the categorical variables within this dataset using embedding layers. Second, a neural network with embedding layers was used to model all of the mortality rates in the Human Mortality Database, where the differences in population mortality across countries and the differences in mortality at different ages were modelled with embedding layers, again producing more accurate out of sample performance than the other models tested.

Contemporaneous with that work is the DeepTriangle model of [@Kuo2019], which applied recurrent neural networks to the problem of Incurred but not Reported (IBNR) loss reserving, to model jointly the paid and incurred losses in the Schedule P dataset. Embedding layers were used to capture the effect of differences in reserving delays and loss ratios for each company in the Schedule P dataset. Evaluating the results of the DeepTriangle method showed that the out of sample performance of the model (tested against the lower triangles in the Schedule P dataset) exceeded that of traditional IBNR reserving techniques.

Many other applications of embeddings have subsequently appeared in the actuarial literature. Within mortality forecasting, [@Richman2019d] and [@Richman2020] both apply embeddings layers to model and forecast mortality rates on a large scale. [@wuthrich2019yes] discussed how embeddings can be calibrated using GLM techniques and then incorporated into a combined actuarial neural network, with subsequent contributions in P&C pricing by [@schelldorfer2019nesting] and in IBNR reserving by [@Gabrielli2019c] and [@Gabrielli2019]. Other applications in IBNR reserving are in [@Kuo2020] and [@Delong2020a] who use embedding layers to model individual claims development.

# Definitions {#defns}

In this study, we are concerned with regression modelling, which is the task of predicting an unknown outcome $y$ on the basis of information about that outcome contained in predictor variables, or features, stored in a matrix $X$. For simplicity, we only consider the case of univariate outcomes, i.e., $y \in \mathbb{R}^1$. The outcomes and the rows of the predictor variable matrix are indexed by $i \in \{1 \dots I\}$, where $i$ represents a particular observation of $(y_i, \mathbf{x}_i)$, where bold indicates that we are now dealing with a vector. The columns of the predictor variables are indexed by $j \in \{1 \dots J\}$, where $j$ represents a particular predictor variable, of which $J$ have been observed, thus, we use the notation $X_j$ to represent the $j$th predictor variable and $X \in \mathbb{R}^J$. Formally, we look to build regression models that map from the predictor variables $\mathbf{x}_i$ to the outcome $y$ using a function $f$ of the form:

$$
\mathbf{f} : \mathbb{R}^J \mapsto \mathbb{R}^1, \quad \quad \mathbf{x_i} \mapsto  \mathbf f{(\mathbf{x_i})} = y. 
$$

The predictor variables that we consider here are comprised of two types: continuous variables, taking on numerical values and represented by the matrix $X_{num}$ with $J^{num}$ columns, and categorical variables, which take on discrete values indicating one of several possible categories, represented by the matrix $X_{cat}$ with $J^{cat}$ columns, such that $J^{num} + J^{cat} = J$.

A categorical variable $X_j, j \in J_{cat}$ takes as its value only one of a finite number of labels. Let the set of labels be $\mathcal{P}^j = \{p^j_1, p^j_2,\dots, p^j_{n_{\mathcal{P}^j}} \}$, where $n_\mathcal{P}^j = |\mathcal{P}^j|$ is the cardinality or number of levels, in $\mathcal{P}^j$. One-hot encoding maps each value $x_{i,j}$ of $X_j$ to $n_\mathcal{P}^j$ indicator variables, which take a value of $1$ if the label of $x_{i,j}$ corresponds to the level of the indicator variable, and $0$ otherwise.

# Modelling the NFIP Data {#modelling}

# Transfer Learning {#tl}

How can embedding layers be used in GLM models? (Potential uses of embedding layers as a feature engineering technique for GLM) Transfer learned embeddings to GLM - backprop on NN and use as preprocessing Train GLM on embedding layers - backprop on 1 layer NN

# Extending the model {#extend}

Investigate approaches for using embedding layers for numeric variables, or numeric variables that were captured as categorical variables (Can the modelling of numerical variables benefit from the application of embedding layers?) How should this best be done? CatBoost - cut into 256 groups smoothness Map numeric to a dense layer and use that as embedding - basis expansion Add a distribution to the embeddings Can insights from credibility theory lead to enhanced embeddings? Take credibility mixture over embeddings Cluster embeddings PCA of embeddings

# Attention based modelling {#attention}

Can we get some lift by adding attention layers? TabNet model Transformer model

# Interpretations {#interpretation}

Extracting and interpreting trained embeddings, including visualization techniques Can we explain the learned embeddings using a GLM? distance to water etc Rainfall Density Distance to coast

# Conclusions {#Conclusions}

Conclusions

### 2020-09-29 manuscript/manuscript.Rmd

@@
 
-# Modelling the NFIP Data {#modelling}
+# A Minimalist Neural Network {#modelling}
+
+In this section, we describe, fit, and evaluate both a minimalist neural network architecture utilizing embeddings and a traditional GLM.
+The working example for our experiments is as follows: Given a set of claims characteristics, we predict the losses paid on the property coverage of the policy.
+In the rest of this section, we describe the dataset we use, describe formally the models being considered, and discuss results.
+
+## NFIP data
+
+The data we use comes from the National Flood Insurance Program (NFIP) and is made available by the OpenFEMA initiative of the Federal Emergency Management Agency (FEMA) (TODO: cite).
+Two datasets are made available by OpenFEMA: A policies dataset with exposure information, and a claims dataset with claims transactions, including paid amounts.
+Because there is no way to associate records of the two datasets, we are limited to fitting severity models on the claims dataset.
+While the complete dataset contains over two million transactions, for the purposes of our experiments we limit ourselves to data from 2000 to August 2019, which amounts to approximately 1.4 million claims.
+The dataset can be downloaded from Cellar (TODO: link).
+The dataset includes a rich variety of variables, from occupancy type to coarse coordinates.
+For our models, we work with a few selected variables that represent continuous and discrete variables of low and high cardinalities, which we list in Table \ref{tab:variables}.
+
+| Variable                                 | Type                                     |
+|------------------------------------------|------------------------------------------|
+| Building insurance coverage              | Numeric                                  |
+| Basement enclosure type                  | Categorical                              |
+| Number of floors in the insured building | Categorical (binned in original dataset) |
+| Flood zone                               | Categorical (high cardinality)           |
+| Primary residence                        | Categorical (binary indicator)           |
+
+: \label{tab:variables} Variables used in modeling.
+
+## Severity GLM
+
+asdf
+
+## Neural net
+
+asdf
+
+## Performance evaluation framework and results
+
+asdf
+
+# Interpretations {#interpretation}
+
+Extracting and interpreting trained embeddings, including visualization techniques Can we explain the learned embeddings using a GLM? distance to water etc Rainfall Density Distance to coast
 
@@
 
-# Interpretations {#interpretation}
-
-Extracting and interpreting trained embeddings, including visualization techniques Can we explain the learned embeddings using a GLM? distance to water etc Rainfall Density Distance to coast
-
 # Conclusions {#Conclusions}

### 2020-09-29 manuscript/manuscript.Rmd
Added definitions

--- 2020-09-14 manuscript/manuscript.Rmd
@@
 
+We will use mainly use GLMs and neural networks to approximate the function $f(.)$.
+
 The predictor variables that we consider here are comprised of two types: continuous variables, taking on numerical values and represented by the matrix $X_{num}$ with $J^{num}$ columns, and categorical variables, which take on discrete values indicating one of several possible categories, represented by the matrix $X_{cat}$ with $J^{cat}$ columns, such that $J^{num} + J^{cat} = J$.
+
+## Categorical data modeling
 
@@
 One-hot encoding maps each value $x_{i,j}$ of $X_j$ to $n_\mathcal{P}^j$ indicator variables, which take a value of $1$ if the label of $x_{i,j}$ corresponds to the level of the indicator variable, and $0$ otherwise.
+One-hot encoding is often used in the machine learning community while the statistical community often favors dummy coding, which, instead of assigning $n_p^j$ indicator variables, assigns one of the levels of the categories as a baseline, and maps all of the other $n_p^j -1$ variables to indicator variables.
+
+The approach that we focus on in this study is to use embeddings, which map each level of the categorical data to a low dimensional vector of parameters that is learned together with the rest of the GLM or neural network that is used for the modeling problem.
+Formally, an embedding is
+
+$$
+z_\mathcal{P^j} : \mathcal{P^j} \to \mathbb{R}^{q_\mathcal{P^j} }, \quad \quad p^j \mapsto  z_\mathcal{P^j}(p),
+$$
+
+where $q_\mathcal{P^j}$ is the dimension of the embedding for the $j$th categorical variable and $z_\mathcal{P^j}(.)$ is an function that maps from the particular element of the labels $p$ to the embedding space.
+This function is left implicit, meaning to say, we allow the embeddings to be derived during the process of fitting the model and do not attempt to specify exactly how the embeddings can be derived from the input data.
+
+## GLMs and Neural Networks
 

### 2020-09-29 manuscript/manuscript.Rmd
add table
add table

@@
 One-hot encoding maps each value $x_{i,j}$ of $X_j$ to $n_\mathcal{P}^j$ indicator variables, which take a value of $1$ if the label of $x_{i,j}$ corresponds to the level of the indicator variable, and $0$ otherwise.
+An example of one-hot encoding is shown in Table \ref{tab:onehot}.
+
+```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
+require(dplyr)
+require(cellar)
+require(recipes)
+require(data.table)
+
+# nfip = cellar_pull("nfip_claims", vintage = NULL)
+# 
+# states = nfip %>% select(state) %>% unique()
+# 
+# states %>% fwrite("manuscript/states.csv")
+
+states= fread("../manuscript/states.csv")
+
+sample_dat = sample_n(states,5) %>% arrange(state)
+
+rec = recipe(~state, data = sample_dat)
+
+dummies <- rec %>% step_dummy(state)
+dummies <- prep(dummies, training = sample_dat)
+
+dummy_data <- bake(dummies, new_data =sample_dat)
+
+cbind(sample_dat, dummy_data) %>% knitr::kable(label = "tab:onehot", caption = "Example one-hot encoding of the state variable")
+```
+
 One-hot encoding is often used in the machine learning community while the statistical community often favors dummy coding, which, instead of assigning $n_p^j$ indicator variables, assigns one of the levels of the categories as a baseline, and maps all of the other $n_p^j -1$ variables to indicator variables.
@@
 
++------------------------------------------+------------------------------------------+
 | Variable                                 | Type                                     |
-|------------------------------------------|------------------------------------------|
++==========================================+==========================================+
 | Building insurance coverage              | Numeric                                  |
++------------------------------------------+------------------------------------------+
 | Basement enclosure type                  | Categorical                              |
++------------------------------------------+------------------------------------------+
 | Number of floors in the insured building | Categorical (binned in original dataset) |
++------------------------------------------+------------------------------------------+
 | Flood zone                               | Categorical (high cardinality)           |
++------------------------------------------+------------------------------------------+
 | Primary residence                        | Categorical (binary indicator)           |
++------------------------------------------+------------------------------------------+
 

### 2020-09-29 manuscript/manuscript.tex
add table
add table

\documentclass{article}

\usepackage{arxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}

\title{Categorical Predictor Embeddings in Actuarial Modeling}

\author{
    Kevin Kuo
   \\
    RStudio and Kasa AI \\
   \\
  \texttt{\href{mailto:kevin@kasa.ai}{\nolinkurl{kevin@kasa.ai}}} \\
   \And
    Ronald Richman
   \\
    QED Actuaries and Consultants \\
   \\
  \texttt{\href{mailto:ronaldrichman@gmail.com}{\nolinkurl{ronaldrichman@gmail.com}}} \\
  }

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}%
  {\setlength{\parindent}{0pt}%
  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
  {\par}

\begin{document}
\maketitle

\def\tightlist{}

\begin{abstract}
Enter the text of your abstract here.
\end{abstract}

\keywords{
    blah
   \and
    blee
   \and
    bloo
   \and
    these are optional and can be removed
  }

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Categorical data are modelled by actuaries in many different contexts,
from pricing of insurance products to reserving for the liabilities
generated by these products. Sometimes, these data are modelled in an
explicit manner, for example, when building models that apply across
multiple categories, a form of dummy coding is usually used. For
example, when building models to price the frequency of motor insurance
claims, claim experience relating to different types of motor vehicle
will often be modelled by including a (single) factor within models that
modifies the relative frequency predicted for each type of vehicle. In
other cases, modelling is performed for each category separately, thus
the categorical data is used within the modelling in an implicit manner,
for example, common practice is to estimate reserves for different lines
of business separately, meaning to say, with no parameters being shared
across each of the reserving models.

Recently, several studies of insurance problems have applied an
alternative approach, originally from the natural language processing
literature (Bengio et al. 2003) and now applied to diverse types of
machine learning problem (Guo and Berkhahn 2016), known as
\textbf{categorical embeddings}. Instead of trying to capture the
differences between categories using a single factor, the categorical
embedding approach rather maps each category to a low-dimensional
numeric vector, which is then used within the model as a new predictor
variable.

This approach to modelling categorical data has several advantages over
more traditional treatments of categorical data. Using categorical
embeddings instead of traditional techniques has been shown to increase
predictive accuracy of models, for example, see (Richman 2018) in the
context of pricing. Models incorporating categorical embeddings can be
pre-calibrated to traditional actuarial models, increasing the speed
with which these models can be calibrated and leading to models with
better explainability (Wüthrich and Merz 2019). Finally, the similarity
between the vectors learned for different categories can be inspected,
sometimes leading to insights into the workings of models, see, for
example, (Kuo 2019).

On the other hand, several open questions about the use of embeddings
within actuarial work remain, which we aim to address in this study.
First, hyperparameter settings for embeddings, such as the dimensions of
the embedding layer and the use of regularization techniques such as
dropout or normalization, that achieve optimal predictive performance
has not yet been studied in detail in the actuarial literature. In this
work, we aim to study how embeddings using different settings perform in
the context of a large-scale predictive modelling problem, and give
guidance on the process that can be followed to determine this in other
problems. Although neural network have been shown to achieve excellent
predictive accuracy on actuarial tasks, many actuaries still prefer to
use GLM models for pricing tasks, thus, the issue of whether
transferring embeddings to GLM models can achieve better performance is
considered in this paper. Traditional actuarial techniques such as
credibility theory have been used to work with some types of categorical
data, but no study has been performed whether this can be applied within
embeddings; here, we investigate whether performance is enhanced by
applying credibility theory on embeddings relating to categorical
variables with many labels. Whereas embedding layers are usually
considered in the context of categorical data,the option exists to
quantize numerical data and model it using embeddings, however, the
results of doing so have not been investigated. Finally, in the past
several years, a new type of neural network architecture based on
attention (Vaswani et al. 2017) has been successfully used on embeddings
in the field of natural language processing and we incorporate attention
based models into our predictive modelling example.

In this work, we utilize the recently released National Flood Insurance
Program (NFIP) dataset (Federal Emergency Management Agency 2019) which
provides exposure information for policies written under the NFIP since
XXXXDateXXXX, as well as the claims data relating to these exposures. We
refer the reader to Appendix \ref{NFIP_eda} for an exploratory analysis
of this dataset.

The rest of this manuscript is organized as follows. Section
\ref{lit_review} reviews recent applications of embeddings in the
actuarial literature. Section \ref{defns} provides the notation used in
the paper and defines GLMs, neural networks and related modelling
concepts. In Section \ref{modelling}, we provide initial models for the
NFIP dataset and consider the influence of hyperparameter choices on the
results of the neural network model. Section \ref{tl} considers how
successfully the embeddings used in the neural network model can be
transferred to a GLM model of the same data. Extensions to the modelling
approach are considered in Section \ref{extend} and we focus on
attention based models in Section \ref{attention}. The interpretability
of embedding layers is addressed in Section \ref{interpretation}.
Finally, Section \ref{Conclusions} provides a discussion of the results
of this paper and considers avenues for future research.

(TODO: link to github repo)

\hypertarget{lit_review}{%
\section{Literature Review}\label{lit_review}}

Categorical data are usually modelled within GLMs and other predictive
models using indicator variables which capture the effect of each level
of the category, see, for example, Section 2 in (Goldburd et al. 2020),
using one of two main encoding schemes: dummy-coding and one-hot
encoding. Dummy-coding, used in the popular \texttt{R} statistical
software, assigns one level of the category as a baseline, for which an
indicator variable is not calibrated, and the rest of the levels are
assigned indicator variables, thus, producing estimates within the model
of how the effects of each level differ from the baselines. One-hot
encoding, often used in machine learning, is similar to dummy-coding,
but assigns indicator variables to each level, in other words,
calibrates an extra indicator variable compared with dummy-coding.

A different approach to modelling categorical data is credibility theory
(see (Bühlmann and Gisler 2005) for an overview), which, in the context
of rating, can be applied to derive premiums that reflect the experience
of a particular policyholder, by estimating premiums as a weighted
average between the premium produced using the collective experience
(i.e.~of all policyholders) and the premium produced using the
experience of the particular policyholder. The weight used in this
average is called a credibility factor and is calculated with reference
to te variability of the policyholder experience relative to the
variability of the group experience. In this context, the implicit
categorical variable is the policyholder under consideration.

Generalized Linear Mixed Models (GLMMs) are an extension of GLMs that
are designed for modelling categorical data using a principle very
similar to that of credibility theory (Klinker 2010). Instead of
calibrating indicator variables for each level of the category, GLMMs
estimate effects for each of these levels as a combination of the
overall group mean and the experience in each level of the category.

Embedding layers represent a different approach to the problem of
modelling categorical data that was recently introduced in an actuarial
context. Note that in the next section, we reflect on similarities
between the conventional approaches discussed above and embedding
layers. (Richman 2018) reviewed the concept of embedding layers and
connected the sharing of information across categories to the familiar
concept of credibility theory. In that work, two applications of
embedding layers were demonstrated. The first of these was in a Property
and Casualty (P\&C) pricing context, it was shown that the out-of-sample
accuracy of a neural network trained to predict claims frequencies on
motor third party liability was enhanced by modelling the categorical
variables within this dataset using embedding layers. Second, a neural
network with embedding layers was used to model all of the mortality
rates in the Human Mortality Database, where the differences in
population mortality across countries and the differences in mortality
at different ages were modelled with embedding layers, again producing
more accurate out of sample performance than the other models tested.

Contemporaneous with that work is the DeepTriangle model of (Kuo 2019),
which applied recurrent neural networks to the problem of Incurred but
not Reported (IBNR) loss reserving, to model jointly the paid and
incurred losses in the Schedule P dataset. Embedding layers were used to
capture the effect of differences in reserving delays and loss ratios
for each company in the Schedule P dataset. Evaluating the results of
the DeepTriangle method showed that the out of sample performance of the
model (tested against the lower triangles in the Schedule P dataset)
exceeded that of traditional IBNR reserving techniques.

Many other applications of embeddings have subsequently appeared in the
actuarial literature. Within mortality forecasting, (Richman and
Wüthrich 2019) and (Perla et al. 2020) both apply embeddings layers to
model and forecast mortality rates on a large scale. (Wüthrich and Merz
2019) discussed how embeddings can be calibrated using GLM techniques
and then incorporated into a combined actuarial neural network, with
subsequent contributions in P\&C pricing by (Schelldorfer and Wüthrich
2019) and in IBNR reserving by (Gabrielli 2019) and (Gabrielli, Richman,
and Wüthrich 2019). Other applications in IBNR reserving are in (Kuo
2020) and (Delong, Lindholm, and Wuthrich 2020) who use embedding layers
to model individual claims development.

\hypertarget{defns}{%
\section{Definitions}\label{defns}}

In this study, we are concerned with regression modelling, which is the
task of predicting an unknown outcome \(y\) on the basis of information
about that outcome contained in predictor variables, or features, stored
in a matrix \(X\). For simplicity, we only consider the case of
univariate outcomes, i.e., \(y \in \mathbb{R}^1\). The outcomes and the
rows of the predictor variable matrix are indexed by
\(i \in \{1 \dots I\}\), where \(i\) represents a particular observation
of \((y_i, \mathbf{x}_i)\), where bold indicates that we are now dealing
with a vector. The columns of the predictor variables are indexed by
\(j \in \{1 \dots J\}\), where \(j\) represents a particular predictor
variable, of which \(J\) have been observed, thus, we use the notation
\(X_j\) to represent the \(j\)th predictor variable and
\(X \in \mathbb{R}^J\). Formally, we look to build regression models
that map from the predictor variables \(\mathbf{x}_i\) to the outcome
\(y\) using a function \(f\) of the form:

\[
\mathbf{f} : \mathbb{R}^J \mapsto \mathbb{R}^1, \quad \quad \mathbf{x_i} \mapsto  \mathbf f{(\mathbf{x_i})} = y. 
\]

We will use mainly use GLMs and neural networks to approximate the
function \(f(.)\).

The predictor variables that we consider here are comprised of two
types: continuous variables, taking on numerical values and represented
by the matrix \(X_{num}\) with \(J^{num}\) columns, and categorical
variables, which take on discrete values indicating one of several
possible categories, represented by the matrix \(X_{cat}\) with
\(J^{cat}\) columns, such that \(J^{num} + J^{cat} = J\).

\hypertarget{categorical-data-modeling}{%
\subsection{Categorical data modeling}\label{categorical-data-modeling}}

A categorical variable \(X_j, j \in J_{cat}\) takes as its value only
one of a finite number of labels. Let the set of labels be
\(\mathcal{P}^j = \{p^j_1, p^j_2,\dots, p^j_{n_{\mathcal{P}^j}} \}\),
where \(n_\mathcal{P}^j = |\mathcal{P}^j|\) is the cardinality or number
of levels, in \(\mathcal{P}^j\). One-hot encoding maps each value
\(x_{i,j}\) of \(X_j\) to \(n_\mathcal{P}^j\) indicator variables, which
take a value of \(1\) if the label of \(x_{i,j}\) corresponds to the
level of the indicator variable, and \(0\) otherwise. An example of
one-hot encoding is shown in Table \ref{tab:onehot}.

\begin{longtable}[]{@{}lrrrr@{}}
\caption{Example one-hot encoding of the state variable}\tabularnewline
\toprule
state & state\_KS & state\_OK & state\_UT & state\_WA\tabularnewline
\midrule
\endfirsthead
\toprule
state & state\_KS & state\_OK & state\_UT & state\_WA\tabularnewline
\midrule
\endhead
CO & 0 & 0 & 0 & 0\tabularnewline
KS & 1 & 0 & 0 & 0\tabularnewline
OK & 0 & 1 & 0 & 0\tabularnewline
UT & 0 & 0 & 1 & 0\tabularnewline
WA & 0 & 0 & 0 & 1\tabularnewline
\bottomrule
\end{longtable}

One-hot encoding is often used in the machine learning community while
the statistical community often favors dummy coding, which, instead of
assigning \(n_p^j\) indicator variables, assigns one of the levels of
the categories as a baseline, and maps all of the other \(n_p^j -1\)
variables to indicator variables.

The approach that we focus on in this study is to use embeddings, which
map each level of the categorical data to a low dimensional vector of
parameters that is learned together with the rest of the GLM or neural
network that is used for the modeling problem. Formally, an embedding is

\[
z_\mathcal{P^j} : \mathcal{P^j} \to \mathbb{R}^{q_\mathcal{P^j} }, \quad \quad p^j \mapsto  z_\mathcal{P^j}(p),
\]

where \(q_\mathcal{P^j}\) is the dimension of the embedding for the
\(j\)th categorical variable and \(z_\mathcal{P^j}(.)\) is an function
that maps from the particular element of the labels \(p\) to the
embedding space. This function is left implicit, meaning to say, we
allow the embeddings to be derived during the process of fitting the
model and do not attempt to specify exactly how the embeddings can be
derived from the input data.

\hypertarget{glms-and-neural-networks}{%
\subsection{GLMs and Neural Networks}\label{glms-and-neural-networks}}

\hypertarget{modelling}{%
\section{A Minimalist Neural Network}\label{modelling}}

In this section, we describe, fit, and evaluate both a minimalist neural
network architecture utilizing embeddings and a traditional GLM. The
working example for our experiments is as follows: Given a set of claims
characteristics, we predict the losses paid on the property coverage of
the policy. In the rest of this section, we describe the dataset we use,
describe formally the models being considered, and discuss results.

\hypertarget{nfip-data}{%
\subsection{NFIP data}\label{nfip-data}}

The data we use comes from the National Flood Insurance Program (NFIP)
and is made available by the OpenFEMA initiative of the Federal
Emergency Management Agency (FEMA) (TODO: cite). Two datasets are made
available by OpenFEMA: A policies dataset with exposure information, and
a claims dataset with claims transactions, including paid amounts.
Because there is no way to associate records of the two datasets, we are
limited to fitting severity models on the claims dataset. While the
complete dataset contains over two million transactions, for the
purposes of our experiments we limit ourselves to data from 2000 to
August 2019, which amounts to approximately 1.4 million claims. The
dataset can be downloaded from Cellar (TODO: link). The dataset includes
a rich variety of variables, from occupancy type to coarse coordinates.
For our models, we work with a few selected variables that represent
continuous and discrete variables of low and high cardinalities, which
we list in Table \ref{tab:variables}.

\begin{longtable}[]{@{}ll@{}}
\caption{\label{tab:variables} Variables used in
modeling.}\tabularnewline
\toprule
\begin{minipage}[b]{0.47\columnwidth}\raggedright
Variable\strut
\end{minipage} & \begin{minipage}[b]{0.47\columnwidth}\raggedright
Type\strut
\end{minipage}\tabularnewline
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{0.47\columnwidth}\raggedright
Variable\strut
\end{minipage} & \begin{minipage}[b]{0.47\columnwidth}\raggedright
Type\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.47\columnwidth}\raggedright
Building insurance coverage\strut
\end{minipage} & \begin{minipage}[t]{0.47\columnwidth}\raggedright
Numeric\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.47\columnwidth}\raggedright
Basement enclosure type\strut
\end{minipage} & \begin{minipage}[t]{0.47\columnwidth}\raggedright
Categorical\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.47\columnwidth}\raggedright
Number of floors in the insured building\strut
\end{minipage} & \begin{minipage}[t]{0.47\columnwidth}\raggedright
Categorical (binned in original dataset)\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.47\columnwidth}\raggedright
Flood zone\strut
\end{minipage} & \begin{minipage}[t]{0.47\columnwidth}\raggedright
Categorical (high cardinality)\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.47\columnwidth}\raggedright
Primary residence\strut
\end{minipage} & \begin{minipage}[t]{0.47\columnwidth}\raggedright
Categorical (binary indicator)\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{severity-glm}{%
\subsection{Severity GLM}\label{severity-glm}}

asdf

\hypertarget{neural-net}{%
\subsection{Neural net}\label{neural-net}}

asdf

\hypertarget{performance-evaluation-framework-and-results}{%
\subsection{Performance evaluation framework and
results}\label{performance-evaluation-framework-and-results}}

asdf

\hypertarget{interpretation}{%
\section{Interpretations}\label{interpretation}}

Extracting and interpreting trained embeddings, including visualization
techniques Can we explain the learned embeddings using a GLM? distance
to water etc Rainfall Density Distance to coast

\hypertarget{tl}{%
\section{Transfer Learning}\label{tl}}

How can embedding layers be used in GLM models? (Potential uses of
embedding layers as a feature engineering technique for GLM) Transfer
learned embeddings to GLM - backprop on NN and use as preprocessing
Train GLM on embedding layers - backprop on 1 layer NN

\hypertarget{extend}{%
\section{Extending the model}\label{extend}}

Investigate approaches for using embedding layers for numeric variables,
or numeric variables that were captured as categorical variables (Can
the modelling of numerical variables benefit from the application of
embedding layers?) How should this best be done? CatBoost - cut into 256
groups smoothness Map numeric to a dense layer and use that as embedding
- basis expansion Add a distribution to the embeddings Can insights from
credibility theory lead to enhanced embeddings? Take credibility mixture
over embeddings Cluster embeddings PCA of embeddings

\hypertarget{attention}{%
\section{Attention based modelling}\label{attention}}

Can we get some lift by adding attention layers? TabNet model
Transformer model

\hypertarget{Conclusions}{%
\section{Conclusions}\label{Conclusions}}

Conclusions

\hypertarget{refs}{}
\begin{cslreferences}
\leavevmode\hypertarget{ref-Bengio2003}{}%
Bengio, Yoshua, Réjean Ducharme, Pascal Vincent, and Christian Jauvin.
2003. ``A Neural Probabilistic Language Model.'' \emph{Journal of
Machine Learning Research} 3 (6): 1137--55.
\url{https://doi.org/10.1162/153244303322533223}.

\leavevmode\hypertarget{ref-Buhlmann2006}{}%
Bühlmann, Hans, and Alois Gisler. 2005. \emph{A Course in Credibility
Theory and its Applications}. Springer Science \& Business Media.
\url{https://doi.org/10.1080/03461230600889660}.

\leavevmode\hypertarget{ref-Delong2020a}{}%
Delong, Lukasz, Mathias Lindholm, and Mario V. Wuthrich. 2020.
``Collective Reserving using Individual Claims Data.'' \emph{SSRN
Electronic Journal}, May. \url{https://doi.org/10.2139/ssrn.3582398}.

\leavevmode\hypertarget{ref-FederalEmergencyManagementAgency2019}{}%
Federal Emergency Management Agency. 2019. ``FIMA NFIP Redacted Claims
Data Set.''
\url{https://www.fema.gov/media-library/assets/documents/180376\%20https://www.fema.gov/media-library/assets/documents/180374}.

\leavevmode\hypertarget{ref-Gabrielli2019c}{}%
Gabrielli, Andrea. 2019. ``A Neural Network Boosted Double
over-Dispersed Poisson Claims Reserving Model.'' \emph{SSRN Electronic
Journal}, April. \url{https://doi.org/10.2139/ssrn.3365517}.

\leavevmode\hypertarget{ref-Gabrielli2019}{}%
Gabrielli, Andrea, Ronald Richman, and Mario V. Wüthrich. 2019. ``Neural
network embedding of the over-dispersed Poisson reserving model.''
\emph{Scandinavian Actuarial Journal}.
\url{https://doi.org/10.1080/03461238.2019.1633394}.

\leavevmode\hypertarget{ref-Goldburd}{}%
Goldburd, Mark, Anand Khare, Dan Tevet, and Dmitriy Guller. 2020.
\emph{Generalized Linear Models for Insurance Rating}. Second Edi.
Casualty Actuarial Society. \url{www.casact.org}.

\leavevmode\hypertarget{ref-Guo2016}{}%
Guo, Cheng, and Felix Berkhahn. 2016. ``Entity Embeddings of Categorical
Variables.'' \emph{arXiv} arXiv:1604.
\url{http://arxiv.org/abs/1604.06737}.

\leavevmode\hypertarget{ref-Klinker2010}{}%
Klinker, Fred. 2010. ``Generalized Linear Mixed Models for Ratemaking: A
Means of Introducing Credibility into a Generalized Linear Model
Setting.'' \emph{Casualty Actuarial Society E-Forum, Winter 2011 Volume
2} 2 (1): 1--25.
\url{http://scholar.google.com/scholar?hl=en\%7B/\&\%7DbtnG=Search\%7B/\&\%7Dq=intitle:Generalized+Linear+Mixed+Models+for+Ratemaking+:+A+Means+of+Introducing+Credibility+into+a+Generalized+Linear+Model+Setting\%7B/\#\%7D0}.

\leavevmode\hypertarget{ref-Kuo2019}{}%
Kuo, Kevin. 2019. ``Deeptriangle: A deep learning approach to loss
reserving.'' \emph{Risks} 7 (3).
\url{https://doi.org/10.3390/risks7030097}.

\leavevmode\hypertarget{ref-Kuo2020}{}%
---------. 2020. ``Individual Claims Forecasting with Bayesian Mixture
Density Networks,'' March. \url{http://arxiv.org/abs/2003.02453}.

\leavevmode\hypertarget{ref-Richman2020}{}%
Perla, Francesca, Ronald Richman, Salvatore Scognamiglio, and Mario V.
Wüthrich. 2020. ``Time-Series Forecasting of Mortality Rates using Deep
Learning.'' \emph{SSRN Electronic Journal}.

\leavevmode\hypertarget{ref-Richman2018}{}%
Richman, R. 2018. ``AI in Actuarial Science.'' \emph{SSRN Electronic
Journal}, October. \url{https://doi.org/10.2139/ssrn.3218082}.

\leavevmode\hypertarget{ref-Richman2019d}{}%
Richman, R, and Mario V. Wüthrich. 2019. ``A neural network extension of
the Lee-Carter model to multiple populations.'' \emph{Annals of
Actuarial Science}. \url{https://doi.org/10.1017/S1748499519000071}.

\leavevmode\hypertarget{ref-schelldorfer2019nesting}{}%
Schelldorfer, Jürg, and Mario V. Wüthrich. 2019. ``Nesting Classical
Actuarial Models into Neural Networks.'' \emph{SSRN Electronic Journal}.
\url{https://doi.org/10.2139/ssrn.3320525}.

\leavevmode\hypertarget{ref-Vaswani2017}{}%
Vaswani, Ashish, Noam Shazeer, Niki Parmar, Jakob Uszkoreit, Llion
Jones, Aidan N Gomez, Łukasz Kaiser, and Illia Polosukhin. 2017.
``Attention is all you need.'' In \emph{Advances in Neural Information
Processing Systems}, 2017-Decem:5999--6009.
\url{http://arxiv.org/abs/1706.03762v5}.

\leavevmode\hypertarget{ref-wuthrich2019yes}{}%
Wüthrich, Mario V, and Michael Merz. 2019. ``Yes, we CANN!'' \emph{ASTIN
Bulletin: The Journal of the IAA} 49 (1): 1--3.
\end{cslreferences}

\bibliographystyle{unsrt}
\bibliography{references.bib}

\end{document}

### 2020-10-13 manuscript/manuscript.Rmd
more stuff in modeling section

--- 2020-09-29 manuscript/manuscript.Rmd
@@
 
-## GLMs and Neural Networks
-
-# A Minimalist Neural Network {#modelling}
+## Predictive Modeling with GLM and a Minimalist Neural Network
 
@@
 
-asdf
+We fit a GLM with the following specifications:
 
-## Neural net
+-   Target variable: Amount paid on building claim
 
-asdf
+-   Predictors: *Log* of **building insurance coverage**, **basement enclosure type**, **number of floors in the insured building**, *prefix* of **flood zone**, and ***primary residence***.
+
+-   Link function: log
+
+-   Distribution: gamma
+
+We take the log of the continuous predictor **building insurance coverage** following (cite cas glm monograph), which allows the scale of the predictor to match that of the target variable.
+Because the **flood zone** variable in the original data contains 60 levels, we take the prefix of the zone code, which corresponds to the level of risk as determined by FEMA (source?).
+For example, *A01*, *A02*, and so on are recoded as simply *A*.
+
+A log link together with the gamma distribution is a standard choice for severity modeling, which provides a multiplicative structure where the response is positive.
+
+## A Simple Neural Network
+
+(Note: this section is WIP doesn't match up w/ code, which is also WIP) For the neural net, we utilize the same responsible variable, amount paid on building claim.
+We normalize the numeric variable ***building insurance coverage***, one-hot encode the **primary residence** variable, and apply embedding layers of dimension one to the rest of the categorical variables.
+We then connect the embeddings and the normalized variable to a single output unit with softplus activation, where the softplus function is defined to be
+
+\begin{equation}
+x \mapsto \log(1 + e^x).
+\end{equation}
+
+Figure (todo: add figure) exhibits the architecture of our simple neural network.
 
@@
 
-asdf
+To evaluate these baseline models and other models in this paper, we perform 10-fold cross validation and compare the root mean square error (RMSE) on the predicted and actual paid amounts.
 

### 2020-11-17 manuscript/manuscript.Rmd
Added NN section

@@
 output: rticles::arxiv_article 
+extra_dependencies: ["amsmath"]
+
 ---
@@
 Section \ref{lit_review} reviews recent applications of embeddings in the actuarial literature.
-Section \ref{defns} provides the notation used in the paper and defines GLMs, neural networks and related modelling concepts.
+Section \ref{defns} provides the notation used in the paper and defines GLMs, neural networks and related modelling concepts, including embeddings and attention.
 In Section \ref{modelling}, we provide initial models for the NFIP dataset and consider the influence of hyperparameter choices on the results of the neural network model.
@@
 
-We will use mainly use GLMs and neural networks to approximate the function $f(.)$.
+In this study, will use mainly use GLMs and neural networks to approximate the function $f(.)$.
 
@@
 One-hot encoding maps each value $x_{i,j}$ of $X_j$ to $n_\mathcal{P}^j$ indicator variables, which take a value of $1$ if the label of $x_{i,j}$ corresponds to the level of the indicator variable, and $0$ otherwise.
-An example of one-hot encoding is shown in Table \ref{tab:onehot}.
+An example of one-hot encoding is shown in Table \ref{onehot}.
 
@@
 
-# nfip = cellar_pull("nfip_claims", vintage = NULL)
-# 
-# states = nfip %>% select(state) %>% unique()
-# 
-# states %>% fwrite("manuscript/states.csv")
+states= fread("../manuscript/states.csv")
+set.seed(42)
+sample_dat = sample_n(states,5) %>% arrange(state)
+
+rec = recipe(~state, data = sample_dat)
+
+dummies <- rec %>% step_dummy(state, one_hot =T)
+dummies <- prep(dummies, training = sample_dat)
+
+dummy_data <- bake(dummies, new_data =sample_dat)
+
+cbind(sample_dat, dummy_data) %>% knitr::kable(label = "onehot", caption = "Example one-hot encoding of the state variable")
+```
+
+One-hot encoding is often used in the machine learning community while the statistical community often favors dummy coding, which, instead of assigning $n_p^j$ indicator variables, assigns one of the levels of the categories as a baseline, and maps all of the other $n_p^j -1$ variables to indicator variables.
+An example of dummy encoding is shown in Table \ref{dummy}.
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
 
 states= fread("../manuscript/states.csv")
+set.seed(42)
 
@@
 
-dummies <- rec %>% step_dummy(state)
+dummies <- rec %>% step_dummy(state, one_hot =F)
 dummies <- prep(dummies, training = sample_dat)
@@
 
-cbind(sample_dat, dummy_data) %>% knitr::kable(label = "tab:onehot", caption = "Example one-hot encoding of the state variable")
+cbind(sample_dat, dummy_data) %>% knitr::kable(label = "dummy", caption = "Example dummy encoding of the state variable")
+
 ```
 
-One-hot encoding is often used in the machine learning community while the statistical community often favors dummy coding, which, instead of assigning $n_p^j$ indicator variables, assigns one of the levels of the categories as a baseline, and maps all of the other $n_p^j -1$ variables to indicator variables.
+After encoding the categorical data in this manner, most regression models such as GLMs will then fit coefficients for each level of the category in the table (if a tree based model is used, such as decision tree, then splits in the tree may occur depending on the presence, or not, of the categorical variable for the data).
+If one-hot encoding has been used, $n_\mathcal{P}^j$ coefficients will be fit, compared to $n_\mathcal{P}^j - 1$ coefficients in the case of dummy coding.
 
-The approach that we focus on in this study is to use embeddings, which map each level of the categorical data to a low dimensional vector of parameters that is learned together with the rest of the GLM or neural network that is used for the modeling problem.
+These coefficients represent the effect that each level of the categorical variable will have on the outcome.
+In the case that there are no other variables available in the dataset, then the coefficients will reflect the average value of the outcomes for that level of the categorical variable.
+For example, suppose that the categorical variable is a policyholder identifier, and the outcomes are the value of claims in different years, then the coefficients will reflect the average annual claims for each policyholder based on the experience.
+In other words, both of these encoding schemes give full credibility to the data available for each category, thus, even if a relatively small amount of data is available for a specific policyholder, the coefficient that is calibrated will only reflect that data.
+On the other hand, a foundational technique within actuarial work is the application of credibility methods, which are used for experience rating and other applications.
+These techniques provide an estimate that reflects not only the experience of the individual policyholder but also that of the collective, based on an estimate of how credible the data for each individual is.
+While we have described the application of credibility in a simple univariate context, it is also possible to apply credibility considerations within GLMs.
+using models known as Generalized Linear Mixed Models or GLMMs, and we refer to [@Klinker2010] for more details.
+
+Having described traditional approaches for modeling categorical data, we now turn to neural networks, and discuss embedding layers for categorical data modeling, which we define in more detail in the section on neural networks.
+
+## Neural Networks
+
+Neural networks are flexible machine learning models that have recently been applied to a number of problems with Property and Casualty (P&C) insurance.
+Here, we provide a brief overview of these models, and refer the reader to [@Richman2018] for a more detailed overview.
+Neural networks are characterized by multiple layers of non-linear regression functions that are used to learn a new representation of the data input to the network that is then used to make predictions.
+Here we focus on the most common type of neural networks, which are fully connected networks (FCNs), which provide as the output of each set of non-linear functions to the subsequent layer of functions.
+Formally, a $K$-layer neural network is:
+
+\begin{equation} 
+\label{NN}
+\begin{split}
+z^1 &= \sigma(a_1.X+ b_1) \\
+z^2 &= \sigma(a_2.z^1+ b_2) \\
+\vdots \\
+z^K &= \sigma(a_{K}.z^{K-1}+ b_{K}) \\
+\hat{y} &= \sigma(a_{K+1}.z^{K}+ b_{K+1}),
+\end{split}
+\end{equation}
+
+where the regression parameters (weights) for each layer $$k \in [1;K]$$ are represented by the matrices $a_k$ and the intercept terms are represented by $b_k$.
+Whereas the calculation inside each of the layers is nothing more than linear regression, $\sigma$ represents the non-linear part of each layer.
+Choices for $\sigma$ are often the tanh function or the rectified linear unit (ReLu) $max(0,x)$.
+The parameters of the network are estimated ('trained') as follows.
+First a loss function $L(.,.)$ is specified for the network that measures the difference between the observed data $y$ and the predictions of the network $\hat{y}$, for example, the Mean Squared Error ($(y - \hat{y})^2$).
+Then, the parameters of the network are changed such that the loss decreases (formally, this is done using the technique of backpropagation).Finally, training is stopped once the predictive performance of the network on unseen data is suitably good.
+
+If $K$ is set equal to $1$, then Equation \ref{NN} reduced to nothing more than a GLM.
+A neural network with $K=2$ is called a shallow neural network and for $K \geq 2$, the network is called a deep neural network.
+The matrix $X$ of data input to the network can be composed of both continuous variables as well as categorical variables, which can be pre-processed using one-hot or dummy encoding.
+As mentioned above, a different option is to use encodings, which we discuss in more detail next.
+
+### Embeddings
+Common issues with the traditional encoding schemes for categorical data occur when the number of levels for each variable is very large.
+Often, in these cases, models do not converge quickly, and the very large matrices that result from applying these schemes often cause computational difficulties.
+Besides for these practical issues, a deeper issue is that one-hot or dummy encoded data assumes that each category is entirely independent of the rest of the categories, in other words, there are no similarities between categories that could enable more robust estimation of models.
+In technical terms, this is because the columns of the matrices created by one-hot encoding are all orthogonal to each other.
+(These arguments appear in a similar form in [@Guo2016].) Solutions to these problems are provided by embedding layers.
+
+An embedding layer is a neural network component which maps each level of the categorical data to a low dimensional vector of parameters that is learned together with the rest of the GLM or neural network that is used for the modeling problem.
 Formally, an embedding is
@@
 where $q_\mathcal{P^j}$ is the dimension of the embedding for the $j$th categorical variable and $z_\mathcal{P^j}(.)$ is an function that maps from the particular element of the labels $p$ to the embedding space.
+Equation \ref{eq:embedding} states that an embedding maps a level of a categrical variable to a numerical vector.
 This function is left implicit, meaning to say, we allow the embeddings to be derived during the process of fitting the model and do not attempt to specify exactly how the embeddings can be derived from the input data.
+In Table \ref{embed} we show an example of two dimensional embeddings for the state variables, where these have been generated randomly.
 
-## Predictive Modeling with GLM and a Minimalist Neural Network
+```{r, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
+states= fread("../manuscript/states.csv")
+set.seed(42)
+
+sample_dat = sample_n(states,5) %>% arrange(state)
+
+sample_dat = sample_n(states,5) %>% arrange(state)
+
+data.frame(sample_dat, dimension1 = rnorm(5),dimension2 = rnorm(5)) %>% knitr::kable(label = "", caption = "Example (random) embeddings of the state variable")
+
+```
+
+When applying embeddings in a data modeling context using neural networks, the values of the embeddings will be calibrated during the same fitting process that calibrates the parameters of the neural network.
+
+### Attention {#attention}
+
+# Predictive Modeling with GLM and a Minimalist Neural Network
 
@@
 
-\begin{equation}
-x \mapsto \log(1 + e^x).
-\end{equation}
+\\begin{equation} x \\mapsto \\log(1 + e\^x). \\end{equation}
 
@@
 
-# Attention based modelling {#attention}
+# Attention based modelling
 

### 2020-11-17 manuscript/manuscript.tex
Added NN section

@@
 the paper and defines GLMs, neural networks and related modelling
-concepts. In Section \ref{modelling}, we provide initial models for the
-NFIP dataset and consider the influence of hyperparameter choices on the
-results of the neural network model. Section \ref{tl} considers how
-successfully the embeddings used in the neural network model can be
-transferred to a GLM model of the same data. Extensions to the modelling
-approach are considered in Section \ref{extend} and we focus on
-attention based models in Section \ref{attention}. The interpretability
-of embedding layers is addressed in Section \ref{interpretation}.
-Finally, Section \ref{Conclusions} provides a discussion of the results
-of this paper and considers avenues for future research.
+concepts, including embeddings and attention. In Section
+\ref{modelling}, we provide initial models for the NFIP dataset and
+consider the influence of hyperparameter choices on the results of the
+neural network model. Section \ref{tl} considers how successfully the
+embeddings used in the neural network model can be transferred to a GLM
+model of the same data. Extensions to the modelling approach are
+considered in Section \ref{extend} and we focus on attention based
+models in Section \ref{attention}. The interpretability of embedding
+layers is addressed in Section \ref{interpretation}. Finally, Section
+\ref{Conclusions} provides a discussion of the results of this paper and
+considers avenues for future research.
 
@@
 
-We will use mainly use GLMs and neural networks to approximate the
-function \(f(.)\).
+In this study, will use mainly use GLMs and neural networks to
+approximate the function \(f(.)\).
 
@@
 level of the indicator variable, and \(0\) otherwise. An example of
-one-hot encoding is shown in Table \ref{tab:onehot}.
+one-hot encoding is shown in Table \ref{onehot}.
 
-\begin{longtable}[]{@{}lrrrr@{}}
+\begin{longtable}[]{@{}lrrrrr@{}}
 \caption{Example one-hot encoding of the state variable}\tabularnewline
 \toprule
-state & state\_KS & state\_OK & state\_UT & state\_WA\tabularnewline
+state & state\_CA & state\_MD & state\_ND & state\_UT &
+state\_WA\tabularnewline
 \midrule
@@
 \toprule
-state & state\_KS & state\_OK & state\_UT & state\_WA\tabularnewline
+state & state\_CA & state\_MD & state\_ND & state\_UT &
+state\_WA\tabularnewline
 \midrule
 \endhead
-CO & 0 & 0 & 0 & 0\tabularnewline
-KS & 1 & 0 & 0 & 0\tabularnewline
-OK & 0 & 1 & 0 & 0\tabularnewline
-UT & 0 & 0 & 1 & 0\tabularnewline
-WA & 0 & 0 & 0 & 1\tabularnewline
+CA & 1 & 0 & 0 & 0 & 0\tabularnewline
+MD & 0 & 1 & 0 & 0 & 0\tabularnewline
+ND & 0 & 0 & 1 & 0 & 0\tabularnewline
+UT & 0 & 0 & 0 & 1 & 0\tabularnewline
+WA & 0 & 0 & 0 & 0 & 1\tabularnewline
 \bottomrule
@@
 the categories as a baseline, and maps all of the other \(n_p^j -1\)
-variables to indicator variables.
+variables to indicator variables. An example of dummy encoding is shown
+in Table \ref{dummy}.
 
-The approach that we focus on in this study is to use embeddings, which
-map each level of the categorical data to a low dimensional vector of
-parameters that is learned together with the rest of the GLM or neural
-network that is used for the modeling problem. Formally, an embedding is
+\begin{longtable}[]{@{}lrrrr@{}}
+\caption{Example dummy encoding of the state variable}\tabularnewline
+\toprule
+state & state\_MD & state\_ND & state\_UT & state\_WA\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+state & state\_MD & state\_ND & state\_UT & state\_WA\tabularnewline
+\midrule
+\endhead
+CA & 0 & 0 & 0 & 0\tabularnewline
+MD & 1 & 0 & 0 & 0\tabularnewline
+ND & 0 & 1 & 0 & 0\tabularnewline
+UT & 0 & 0 & 1 & 0\tabularnewline
+WA & 0 & 0 & 0 & 1\tabularnewline
+\bottomrule
+\end{longtable}
+
+After encoding the categorical data in this manner, most regression
+models such as GLMs will then fit coefficients for each level of the
+category in the table (if a tree based model is used, such as decision
+tree, then splits in the tree may occur depending on the presence, or
+not, of the categorical variable for the data). If one-hot encoding has
+been used, \(n_\mathcal{P}^j\) coefficients will be fit, compared to
+\(n_\mathcal{P}^j - 1\) coefficients in the case of dummy coding.
+
+These coefficients represent the effect that each level of the
+categorical variable will have on the outcome. In the case that there
+are no other variables available in the dataset, then the coefficients
+will reflect the average value of the outcomes for that level of the
+categorical variable. For example, suppose that the categorical variable
+is a policyholder identifier, and the outcomes are the value of claims
+in different years, then the coefficients will reflect the average
+annual claims for each policyholder based on the experience. In other
+words, both of these encoding schemes give full credibility to the data
+available for each category, thus, even if a relatively small amount of
+data is available for a specific policyholder, the coefficient that is
+calibrated will only reflect that data. On the other hand, a
+foundational technique within actuarial work is the application of
+credibility methods, which are used for experience rating and other
+applications. These techniques provide an estimate that reflects not
+only the experience of the individual policyholder but also that of the
+collective, based on an estimate of how credible the data for each
+individual is. While we have described the application of credibility in
+a simple univariate context, it is also possible to apply credibility
+considerations within GLMs. using models known as Generalized Linear
+Mixed Models or GLMMs, and we refer to (Klinker 2010) for more details.
+
+Having described traditional approaches for modeling categorical data,
+we now turn to neural networks, and discuss embedding layers for
+categorical data modeling, which we define in more detail in the section
+on neural networks.
+
+\hypertarget{neural-networks}{%
+\subsection{Neural Networks}\label{neural-networks}}
+
+Neural networks are flexible machine learning models that have recently
+been applied to a number of problems with Property and Casualty (P\&C)
+insurance. Here, we provide a brief overview of these models, and refer
+the reader to (Richman 2018) for a more detailed overview. Neural
+networks are characterized by multiple layers of non-linear regression
+functions that are used to learn a new representation of the data input
+to the network that is then used to make predictions. Here we focus on
+the most common type of neural networks, which are fully connected
+networks (FCNs), which provide as the output of each set of non-linear
+functions to the subsequent layer of functions. Formally, a \(K\)-layer
+neural network is:
+
+\begin{equation} 
+\label{NN}
+\begin{split}
+z^1 &= \sigma(a_1.X+ b_1) \\
+z^2 &= \sigma(a_2.z^1+ b_2) \\
+\vdots \\
+z^K &= \sigma(a_{K}.z^{K-1}+ b_{K}) \\
+\hat{y} &= \sigma(a_{K+1}.z^{K}+ b_{K+1}),
+\end{split}
+\end{equation}
+
+where the regression parameters (weights) for each layer \[k \in [1;K]\]
+are represented by the matrices \(a_k\) and the intercept terms are
+represented by \(b_k\). Whereas the calculation inside each of the
+layers is nothing more than linear regression, \(\sigma\) represents the
+non-linear part of each layer. Choices for \(\sigma\) are often the tanh
+function or the rectified linear unit (ReLu) \(max(0,x)\). The
+parameters of the network are estimated (`trained') as follows. First a
+loss function \(L(.,.)\) is specified for the network that measures the
+difference between the observed data \(y\) and the predictions of the
+network \(\hat{y}\), for example, the Mean Squared Error
+(\((y - \hat{y})^2\)). Then, the parameters of the network are changed
+such that the loss decreases (formally, this is done using the technique
+of backpropagation).Finally, training is stopped once the predictive
+performance of the network on unseen data is suitably good.
+
+If \(K\) is set equal to \(1\), then Equation \ref{NN} reduced to
+nothing more than a GLM. A neural network with \(K=2\) is called a
+shallow neural network and for \(K \geq 2\), the network is called a
+deep neural network. The matrix \(X\) of data input to the network can
+be composed of both continuous variables as well as categorical
+variables, which can be pre-processed using one-hot or dummy encoding.
+As mentioned above, a different option is to use encodings, which we
+discuss in more detail next.
+
+\hypertarget{embeddings}{%
+\subsubsection{Embeddings}\label{embeddings}}
+
+Common issues with the traditional encoding schemes for categorical data
+occur when the number of levels for each variable is very large. Often,
+in these cases, models do not converge quickly, and the very large
+matrices that result from applying these schemes often cause
+computational difficulties. Besides for these practical issues, a deeper
+issue is that one-hot or dummy encoded data assumes that each category
+is entirely independent of the rest of the categories, in other words,
+there are no similarities between categories that could enable more
+robust estimation of models. In technical terms, this is because the
+columns of the matrices created by one-hot encoding are all orthogonal
+to each other. (These arguments appear in a similar form in (Guo and
+Berkhahn 2016).) Solutions to these problems are provided by embedding
+layers.
+
+An embedding layer is a neural network component which maps each level
+of the categorical data to a low dimensional vector of parameters that
+is learned together with the rest of the GLM or neural network that is
+used for the modeling problem. Formally, an embedding is
 
@@
 that maps from the particular element of the labels \(p\) to the
-embedding space. This function is left implicit, meaning to say, we
-allow the embeddings to be derived during the process of fitting the
-model and do not attempt to specify exactly how the embeddings can be
-derived from the input data.
+embedding space. Equation \ref{eq:embedding} states that an embedding
+maps a level of a categrical variable to a numerical vector. This
+function is left implicit, meaning to say, we allow the embeddings to be
+derived during the process of fitting the model and do not attempt to
+specify exactly how the embeddings can be derived from the input data.
+In Table \ref{embed} we show an example of two dimensional embeddings
+for the state variables, where these have been generated randomly.
 
-\hypertarget{glms-and-neural-networks}{%
-\subsection{GLMs and Neural Networks}\label{glms-and-neural-networks}}
+\begin{longtable}[]{@{}lrr@{}}
+\caption{Example (random) embeddings of the state
+variable}\tabularnewline
+\toprule
+state & dimension1 & dimension2\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+state & dimension1 & dimension2\tabularnewline
+\midrule
+\endhead
+CO & 1.5115220 & 2.2866454\tabularnewline
+DC & -0.0946590 & -1.3888607\tabularnewline
+ME & 2.0184237 & -0.2787888\tabularnewline
+PA & -0.0627141 & -0.1333213\tabularnewline
+UT & 1.3048697 & 0.6359504\tabularnewline
+\bottomrule
+\end{longtable}
 
-\hypertarget{modelling}{%
-\section{A Minimalist Neural Network}\label{modelling}}
+When applying embeddings in a data modeling context using neural
+networks, the values of the embeddings will be calibrated during the
+same fitting process that calibrates the parameters of the neural
+network.
+
+\hypertarget{attention}{%
+\subsubsection{Attention}\label{attention}}
+
+\hypertarget{predictive-modeling-with-glm-and-a-minimalist-neural-network}{%
+\section{Predictive Modeling with GLM and a Minimalist Neural
+Network}\label{predictive-modeling-with-glm-and-a-minimalist-neural-network}}
 
@@
 
-asdf
+We fit a GLM with the following specifications:
 
-\hypertarget{neural-net}{%
-\subsection{Neural net}\label{neural-net}}
+\begin{itemize}
+\item
+  Target variable: Amount paid on building claim
+\item
+  Predictors: \emph{Log} of \textbf{building insurance coverage},
+  \textbf{basement enclosure type}, \textbf{number of floors in the
+  insured building}, \emph{prefix} of \textbf{flood zone}, and
+  \textbf{\emph{primary residence}}.
+\item
+  Link function: log
+\item
+  Distribution: gamma
+\end{itemize}
 
-asdf
+We take the log of the continuous predictor \textbf{building insurance
+coverage} following (cite cas glm monograph), which allows the scale of
+the predictor to match that of the target variable. Because the
+\textbf{flood zone} variable in the original data contains 60 levels, we
+take the prefix of the zone code, which corresponds to the level of risk
+as determined by FEMA (source?). For example, \emph{A01}, \emph{A02},
+and so on are recoded as simply \emph{A}.
+
+A log link together with the gamma distribution is a standard choice for
+severity modeling, which provides a multiplicative structure where the
+response is positive.
+
+\hypertarget{a-simple-neural-network}{%
+\subsection{A Simple Neural Network}\label{a-simple-neural-network}}
+
+(Note: this section is WIP doesn't match up w/ code, which is also WIP)
+For the neural net, we utilize the same responsible variable, amount
+paid on building claim. We normalize the numeric variable
+\textbf{\emph{building insurance coverage}}, one-hot encode the
+\textbf{primary residence} variable, and apply embedding layers of
+dimension one to the rest of the categorical variables. We then connect
+the embeddings and the normalized variable to a single output unit with
+softplus activation, where the softplus function is defined to be
+
+\textbackslash begin\{equation\} x \textbackslash mapsto
+\textbackslash log(1 + e\^{}x). \textbackslash end\{equation\}
+
+Figure (todo: add figure) exhibits the architecture of our simple neural
+network.
 
@@
 
-asdf
+To evaluate these baseline models and other models in this paper, we
+perform 10-fold cross validation and compare the root mean square error
+(RMSE) on the predicted and actual paid amounts.
 
@@
 
-\hypertarget{attention}{%
-\section{Attention based modelling}\label{attention}}
+\hypertarget{attention-based-modelling}{%
+\section{Attention based modelling}\label{attention-based-modelling}}
 

### 2021-02-02 manuscript/manuscript.Rmd
clean up a bit

@@
 bibliography: references.bib
-output: rticles::arxiv_article 
+output:
+  bookdown::pdf_book:
+    base_format: rticles::arxiv_article
 extra_dependencies: ["amsmath"]
@@
 
-Categorical data are modelled by actuaries in many different contexts, from pricing of insurance products to reserving for the liabilities generated by these products.
-Sometimes, these data are modelled in an explicit manner, for example, when building models that apply across multiple categories, a form of dummy coding is usually used.
-For example, when building models to price the frequency of motor insurance claims, claim experience relating to different types of motor vehicle will often be modelled by including a (single) factor within models that modifies the relative frequency predicted for each type of vehicle.
-In other cases, modelling is performed for each category separately, thus the categorical data is used within the modelling in an implicit manner, for example, common practice is to estimate reserves for different lines of business separately, meaning to say, with no parameters being shared across each of the reserving models.
+Categorical data are modelled by actuaries in many different contexts, from pricing of insurance products to reserving 
+for the liabilities generated by these products. Sometimes, these data are modelled in an explicit manner, for example, 
+when building models that apply across multiple categories, a form of dummy coding is usually used. For example, when 
+building models to price the frequency of motor insurance claims, claim experience relating to different types of motor
+vehicle will often be modelled by including a (single) factor within models that modifies the relative frequency 
+predicted for each type of vehicle. In other cases, modelling is performed for each category separately, thus the 
+categorical data is used within the modelling in an implicit manner, for example, common practice is to estimate 
+reserves for different lines of business separately, meaning to say, with no parameters being shared across each of the
+reserving models.
 
-Recently, several studies of insurance problems have applied an alternative approach, originally from the natural language processing literature [@Bengio2003] and now applied to diverse types of machine learning problem [@Guo2016], known as **categorical embeddings**.
-Instead of trying to capture the differences between categories using a single factor, the categorical embedding approach rather maps each category to a low-dimensional numeric vector, which is then used within the model as a new predictor variable.
+Recently, several studies of insurance problems have applied an alternative approach, originally from the natural 
+known as **categorical embeddings**. Instead of trying to capture the differences between categories using a single 
+factor, the categorical embedding approach rather maps each category to a low-dimensional numeric vector, which is then
+used within the model as a new predictor variable.
 
 This approach to modelling categorical data has several advantages over more traditional treatments of categorical data.
-Using categorical embeddings instead of traditional techniques has been shown to increase predictive accuracy of models, for example, see [@Richman2018] in the context of pricing.
-Models incorporating categorical embeddings can be pre-calibrated to traditional actuarial models, increasing the speed with which these models can be calibrated and leading to models with better explainability [@wuthrich2019yes].
-Finally, the similarity between the vectors learned for different categories can be inspected, sometimes leading to insights into the workings of models, see, for example, [@Kuo2019].
+Using categorical embeddings instead of traditional techniques has been shown to increase predictive accuracy of 
+models, for example, see [@Richman2018] in the context of pricing. Models incorporating categorical embeddings can be
+pre-calibrated to traditional actuarial models, increasing the speed with which these models can be calibrated and 
+leading to models with better explainability [@wuthrich2019yes]. Finally, the similarity between the vectors learned 
+for different categories can be inspected, sometimes leading to insights into the workings of models, see, for example,
+[@Kuo2019].
 
-On the other hand, several open questions about the use of embeddings within actuarial work remain, which we aim to address in this study.
-First, hyperparameter settings for embeddings, such as the dimensions of the embedding layer and the use of regularization techniques such as dropout or normalization, that achieve optimal predictive performance has not yet been studied in detail in the actuarial literature.
-In this work, we aim to study how embeddings using different settings perform in the context of a large-scale predictive modelling problem, and give guidance on the process that can be followed to determine this in other problems.
-Although neural network have been shown to achieve excellent predictive accuracy on actuarial tasks, many actuaries still prefer to use GLM models for pricing tasks, thus, the issue of whether transferring embeddings to GLM models can achieve better performance is considered in this paper.
-Traditional actuarial techniques such as credibility theory have been used to work with some types of categorical data, but no study has been performed whether this can be applied within embeddings; here, we investigate whether performance is enhanced by applying credibility theory on embeddings relating to categorical variables with many labels.
-Whereas embedding layers are usually considered in the context of categorical data,the option exists to quantize numerical data and model it using embeddings, however, the results of doing so have not been investigated.
-Finally, in the past several years, a new type of neural network architecture based on attention [@Vaswani2017] has been successfully used on embeddings in the field of natural language processing and we incorporate attention based models into our predictive modelling example.
+On the other hand, several open questions about the use of embeddings within actuarial work remain, which we aim to 
+address in this study. First, hyperparameter settings for embeddings, such as the dimensions of the embedding layer and
+the use of regularization techniques such as dropout or normalization, that achieve optimal predictive performance has
+not yet been studied in detail in the actuarial literature. In this work, we aim to study how embeddings using 
+different settings perform in the context of a large-scale predictive modelling problem, and give guidance on the 
+process that can be followed to determine this in other problems. Although neural network have been shown to achieve
+excellent predictive accuracy on actuarial tasks, many actuaries still prefer to use GLM models for pricing tasks, 
+thus, the issue of whether transferring embeddings to GLM models can achieve better performance is considered in this
+paper. Traditional actuarial techniques such as credibility theory have been used to work with some types of 
+categorical data, but no study has been performed whether this can be applied within embeddings; here, we investigate
+whether performance is enhanced by applying credibility theory on embeddings relating to categorical variables with
+many labels. Whereas embedding layers are usually considered in the context of categorical data,the option exists to
+quantize numerical data and model it using embeddings, however, the results of doing so have not been investigated.
+Finally, in the past several years, a new type of neural network architecture based on attention [@Vaswani2017] has
+been successfully used on embeddings in the field of natural language processing and we incorporate attention 
+based models into our predictive modelling example.
 
-In this work, we utilize the recently released National Flood Insurance Program (NFIP) dataset [@FederalEmergencyManagementAgency2019] which provides exposure information for policies written under the NFIP since XXXXDateXXXX, as well as the claims data relating to these exposures.
-We refer the reader to Appendix \ref{NFIP_eda} for an exploratory analysis of this dataset.
+In this work, we utilize the recently released National Flood Insurance Program (NFIP) dataset 
+[@FederalEmergencyManagementAgency2019] which provides exposure information for policies written under the NFIP since 
+XXXXDateXXXX, as well as the claims data relating to these exposures. We refer the reader to Appendix \ref{NFIP_eda} for
+an exploratory analysis of this dataset.
 
-The rest of this manuscript is organized as follows.
-Section \ref{lit_review} reviews recent applications of embeddings in the actuarial literature.
-Section \ref{defns} provides the notation used in the paper and defines GLMs, neural networks and related modelling concepts, including embeddings and attention.
-In Section \ref{modelling}, we provide initial models for the NFIP dataset and consider the influence of hyperparameter choices on the results of the neural network model.
-Section \ref{tl} considers how successfully the embeddings used in the neural network model can be transferred to a GLM model of the same data.
-Extensions to the modelling approach are considered in Section \ref{extend} and we focus on attention based models in Section \ref{attention}.
-The interpretability of embedding layers is addressed in Section \ref{interpretation}.
-Finally, Section \ref{Conclusions} provides a discussion of the results of this paper and considers avenues for future research.
+The rest of this manuscript is organized as follows. Section \ref{lit_review} reviews recent applications of embeddings
+in the actuarial literature. Section \ref{defns} provides the notation used in the paper and defines GLMs, neural 
+networks and related modelling concepts, including embeddings and attention. In Section \ref{modelling}, we provide 
+initial models for the NFIP dataset and consider the influence of hyperparameter choices on the results of the neural 
+network model. Section \ref{tl} considers how successfully the embeddings used in the neural network model can be 
+transferred to a GLM model of the same data. Extensions to the modelling approach are considered in Section \ref{extend} 
+and we focus on attention based models in Section \ref{attention}. The interpretability of embedding layers is addressed
+in Section \ref{interpretation}. Finally, Section \ref{Conclusions} provides a discussion of the results of this paper
+and considers avenues for future research.
 
@@
 
-Categorical data are usually modelled within GLMs and other predictive models using indicator variables which capture the effect of each level of the category, see, for example, Section 2 in [@Goldburd], using one of two main encoding schemes: dummy-coding and one-hot encoding.
-Dummy-coding, used in the popular \texttt{R} statistical software, assigns one level of the category as a baseline, for which an indicator variable is not calibrated, and the rest of the levels are assigned indicator variables, thus, producing estimates within the model of how the effects of each level differ from the baselines.
-One-hot encoding, often used in machine learning, is similar to dummy-coding, but assigns indicator variables to each level, in other words, calibrates an extra indicator variable compared with dummy-coding.
+Categorical data are usually modelled within GLMs and other predictive models using indicator variables which capture 
+the effect of each level of the category, see, for example, Section 2 in [@Goldburd], using one of two main encoding 
+schemes: dummy-coding and one-hot encoding. Dummy-coding, used in the popular \texttt{R} statistical software, assigns 
+one level of the category as a baseline, for which an indicator variable is not calibrated, and the rest of the levels 
+are assigned indicator variables, thus, producing estimates within the model of how the effects of each level differ 
+from the baselines. One-hot encoding, often used in machine learning, is similar to dummy-coding, but assigns 
+indicator variables to each level, in other words, calibrates an extra indicator variable compared with dummy-coding.
 
-A different approach to modelling categorical data is credibility theory (see [@Buhlmann2006] for an overview), which, in the context of rating, can be applied to derive premiums that reflect the experience of a particular policyholder, by estimating premiums as a weighted average between the premium produced using the collective experience (i.e.
-of all policyholders) and the premium produced using the experience of the particular policyholder.
-The weight used in this average is called a credibility factor and is calculated with reference to te variability of the policyholder experience relative to the variability of the group experience.
-In this context, the implicit categorical variable is the policyholder under consideration.
+A different approach to modelling categorical data is credibility theory (see [@Buhlmann2006] for an overview), which, 
+in the context of rating, can be applied to derive premiums that reflect the experience of a particular policyholder, by 
+estimating premiums as a weighted average between the premium produced using the collective experience (i.e. of all 
+policyholders) and the premium produced using the experience of the particular policyholder. The weight used in this 
+average is called a credibility factor and is calculated with reference to te variability of the policyholder experience 
+relative to the variability of the group experience. In this context, the implicit categorical variable is the 
+policyholder under consideration.
 
-Generalized Linear Mixed Models (GLMMs) are an extension of GLMs that are designed for modelling categorical data using a principle very similar to that of credibility theory [@Klinker2010].
-Instead of calibrating indicator variables for each level of the category, GLMMs estimate effects for each of these levels as a combination of the overall group mean and the experience in each level of the category.
+Generalized Linear Mixed Models (GLMMs) are an extension of GLMs that are designed for modelling categorical data using 
+a principle very similar to that of credibility theory [@Klinker2010]. Instead of calibrating indicator variables for 
+each level of the category, GLMMs estimate effects for each of these levels as a combination of the overall group mean 
+and the experience in each level of the category.
 
-Embedding layers represent a different approach to the problem of modelling categorical data that was recently introduced in an actuarial context.
-Note that in the next section, we reflect on similarities between the conventional approaches discussed above and embedding layers.
-[@Richman2018] reviewed the concept of embedding layers and connected the sharing of information across categories to the familiar concept of credibility theory.
-In that work, two applications of embedding layers were demonstrated.
-The first of these was in a Property and Casualty (P&C) pricing context, it was shown that the out-of-sample accuracy of a neural network trained to predict claims frequencies on motor third party liability was enhanced by modelling the categorical variables within this dataset using embedding layers.
-Second, a neural network with embedding layers was used to model all of the mortality rates in the Human Mortality Database, where the differences in population mortality across countries and the differences in mortality at different ages were modelled with embedding layers, again producing more accurate out of sample performance than the other models tested.
+Embedding layers represent a different approach to the problem of modelling categorical data that was recently 
+introduced in an actuarial context. Note that in the next section, we reflect on similarities between the conventional 
+approaches discussed above and embedding layers. [@Richman2018] reviewed the concept of embedding layers and connected 
+the sharing of information across categories to the familiar concept of credibility theory. In that work, two 
+applications of embedding layers were demonstrated. The first of these was in a Property and Casualty (P&C) pricing 
+context, it was shown that the out-of-sample accuracy of a neural network trained to predict claims frequencies on motor 
+third party liability was enhanced by modelling the categorical variables within this dataset using embedding layers. 
+Second, a neural network with embedding layers was used to model all of the mortality rates in the Human Mortality 
+Database, where the differences in population mortality across countries and the differences in mortality at different 
+ages were modelled with embedding layers, again producing more accurate out of sample performance than the other models 
+tested.
 
-Contemporaneous with that work is the DeepTriangle model of [@Kuo2019], which applied recurrent neural networks to the problem of Incurred but not Reported (IBNR) loss reserving, to model jointly the paid and incurred losses in the Schedule P dataset.
-Embedding layers were used to capture the effect of differences in reserving delays and loss ratios for each company in the Schedule P dataset.
-Evaluating the results of the DeepTriangle method showed that the out of sample performance of the model (tested against the lower triangles in the Schedule P dataset) exceeded that of traditional IBNR reserving techniques.
+Contemporaneous with that work is the DeepTriangle model of [@Kuo2019], which applied recurrent neural networks to the 
+problem of Incurred but not Reported (IBNR) loss reserving, to model jointly the paid and incurred losses in the 
+Schedule P dataset. Embedding layers were used to capture the effect of differences in reserving delays and loss ratios 
+for each company in the Schedule P dataset. Evaluating the results of the DeepTriangle method showed that the out of 
+sample performance of the model (tested against the lower triangles in the Schedule P dataset) exceeded that of 
+traditional IBNR reserving techniques.
 
-Many other applications of embeddings have subsequently appeared in the actuarial literature.
-Within mortality forecasting, [@Richman2019d] and [@Richman2020] both apply embeddings layers to model and forecast mortality rates on a large scale.
-[@wuthrich2019yes] discussed how embeddings can be calibrated using GLM techniques and then incorporated into a combined actuarial neural network, with subsequent contributions in P&C pricing by [@schelldorfer2019nesting] and in IBNR reserving by [@Gabrielli2019c] and [@Gabrielli2019].
-Other applications in IBNR reserving are in [@Kuo2020] and [@Delong2020a] who use embedding layers to model individual claims development.
+Many other applications of embeddings have subsequently appeared in the actuarial literature. Within mortality 
+forecasting, [@Richman2019d] and [@Richman2020] both apply embeddings layers to model and forecast mortality rates on a 
+large scale. [@wuthrich2019yes] discussed how embeddings can be calibrated using GLM techniques and then incorporated 
+into a combined actuarial neural network, with subsequent contributions in P&C pricing by [@schelldorfer2019nesting] and 
+in IBNR reserving by [@Gabrielli2019c] and [@Gabrielli2019]. Other applications in IBNR reserving are in [@Kuo2020] and 
+[@Delong2020a] who use embedding layers to model individual claims development.
 
@@
 
-In this study, we are concerned with regression modelling, which is the task of predicting an unknown outcome $y$ on the basis of information about that outcome contained in predictor variables, or features, stored in a matrix $X$.
-For simplicity, we only consider the case of univariate outcomes, i.e., $y \in \mathbb{R}^1$.
-The outcomes and the rows of the predictor variable matrix are indexed by $i \in \{1 \dots I\}$, where $i$ represents a particular observation of $(y_i, \mathbf{x}_i)$, where bold indicates that we are now dealing with a vector.
-The columns of the predictor variables are indexed by $j \in \{1 \dots J\}$, where $j$ represents a particular predictor variable, of which $J$ have been observed, thus, we use the notation $X_j$ to represent the $j$th predictor variable and $X \in \mathbb{R}^J$.
-Formally, we look to build regression models that map from the predictor variables $\mathbf{x}_i$ to the outcome $y$ using a function $f$ of the form:
+In this study, we are concerned with regression modelling, which is the task of predicting an unknown outcome $y$ on the 
+basis of information about that outcome contained in predictor variables, or features, stored in a matrix $X$. For 
+simplicity, we only consider the case of univariate outcomes, i.e., $y \in \mathbb{R}^1$. The outcomes and the rows of 
+the predictor variable matrix are indexed by $i \in \{1 \dots I\}$, where $i$ represents a particular observation of 
+$(y_i, \mathbf{x}_i)$, where bold indicates that we are now dealing with a vector. The columns of the predictor 
+variables are indexed by $j \in \{1 \dots J\}$, where $j$ represents a particular predictor variable, of which $J$ have 
+been observed, thus, we use the notation $X_j$ to represent the $j$th predictor variable and $X \in \mathbb{R}^J$. 
+Formally, we look to build regression models that map from the predictor variables $\mathbf{x}_i$ to the outcome $y$ 
+using a function $f$ of the form:
 
@@
 
-The predictor variables that we consider here are comprised of two types: continuous variables, taking on numerical values and represented by the matrix $X_{num}$ with $J^{num}$ columns, and categorical variables, which take on discrete values indicating one of several possible categories, represented by the matrix $X_{cat}$ with $J^{cat}$ columns, such that $J^{num} + J^{cat} = J$.
+The predictor variables that we consider here are comprised of two types: continuous variables, taking on numerical 
+values and represented by the matrix $X_{num}$ with $J^{num}$ columns, and categorical variables, which take on 
+discrete values indicating one of several possible categories, represented by the matrix $X_{cat}$ with $J^{cat}$ 
+columns, such that $J^{num} + J^{cat} = J$.
 
@@
 
-A categorical variable $X_j, j \in J_{cat}$ takes as its value only one of a finite number of labels.
-Let the set of labels be $\mathcal{P}^j = \{p^j_1, p^j_2,\dots, p^j_{n_{\mathcal{P}^j}} \}$, where $n_\mathcal{P}^j = |\mathcal{P}^j|$ is the cardinality or number of levels, in $\mathcal{P}^j$.
-One-hot encoding maps each value $x_{i,j}$ of $X_j$ to $n_\mathcal{P}^j$ indicator variables, which take a value of $1$ if the label of $x_{i,j}$ corresponds to the level of the indicator variable, and $0$ otherwise.
-An example of one-hot encoding is shown in Table \ref{onehot}.
+A categorical variable $X_j, j \in J_{cat}$ takes as its value only one of a finite number of labels. Let the set of 
+labels be $\mathcal{P}^j = \{p^j_1, p^j_2,\dots, p^j_{n_{\mathcal{P}^j}} \}$, where $n_\mathcal{P}^j = |\mathcal{P}^j|$ 
+is the cardinality or number of levels, in $\mathcal{P}^j$. One-hot encoding maps each value $x_{i,j}$ of $X_j$ to 
+$n_\mathcal{P}^j$ indicator variables, which take a value of $1$ if the label of $x_{i,j}$ corresponds to the level of 
+the indicator variable, and $0$ otherwise. An example of one-hot encoding is shown in Table \ref{onehot}.
 
@@
 
-cbind(sample_dat, dummy_data) %>% knitr::kable(label = "onehot", caption = "Example one-hot encoding of the state variable")
+cbind(sample_dat, dummy_data) %>%
+  knitr::kable(label = "onehot", caption = "Example one-hot encoding of the state variable")
 ```
 
-One-hot encoding is often used in the machine learning community while the statistical community often favors dummy coding, which, instead of assigning $n_p^j$ indicator variables, assigns one of the levels of the categories as a baseline, and maps all of the other $n_p^j -1$ variables to indicator variables.
-An example of dummy encoding is shown in Table \ref{dummy}.
+One-hot encoding is often used in the machine learning community while the statistical community often favors dummy 
+coding, which, instead of assigning $n_p^j$ indicator variables, assigns one of the levels of the categories as a 
+baseline, and maps all of the other $n_p^j -1$ variables to indicator variables. An example of dummy encoding is shown 
+in Table \ref{dummy}.
 
@@
 
-cbind(sample_dat, dummy_data) %>% knitr::kable(label = "dummy", caption = "Example dummy encoding of the state variable")
+cbind(sample_dat, dummy_data) %>%
+  knitr::kable(label = "dummy", caption = "Example dummy encoding of the state variable")
 
@@
 
-After encoding the categorical data in this manner, most regression models such as GLMs will then fit coefficients for each level of the category in the table (if a tree based model is used, such as decision tree, then splits in the tree may occur depending on the presence, or not, of the categorical variable for the data).
-If one-hot encoding has been used, $n_\mathcal{P}^j$ coefficients will be fit, compared to $n_\mathcal{P}^j - 1$ coefficients in the case of dummy coding.
+After encoding the categorical data in this manner, most regression models such as GLMs will then fit coefficients for 
+each level of the category in the table (if a tree based model is used, such as decision tree, then splits in the tree 
+may occur depending on the presence, or not, of the categorical variable for the data). If one-hot encoding has been 
+used, $n_\mathcal{P}^j$ coefficients will be fit, compared to $n_\mathcal{P}^j - 1$ coefficients in the case of dummy 
+coding.
 
-These coefficients represent the effect that each level of the categorical variable will have on the outcome.
-In the case that there are no other variables available in the dataset, then the coefficients will reflect the average value of the outcomes for that level of the categorical variable.
-For example, suppose that the categorical variable is a policyholder identifier, and the outcomes are the value of claims in different years, then the coefficients will reflect the average annual claims for each policyholder based on the experience.
-In other words, both of these encoding schemes give full credibility to the data available for each category, thus, even if a relatively small amount of data is available for a specific policyholder, the coefficient that is calibrated will only reflect that data.
-On the other hand, a foundational technique within actuarial work is the application of credibility methods, which are used for experience rating and other applications.
-These techniques provide an estimate that reflects not only the experience of the individual policyholder but also that of the collective, based on an estimate of how credible the data for each individual is.
-While we have described the application of credibility in a simple univariate context, it is also possible to apply credibility considerations within GLMs.
-using models known as Generalized Linear Mixed Models or GLMMs, and we refer to [@Klinker2010] for more details.
+These coefficients represent the effect that each level of the categorical variable will have on the outcome. In the 
+case that there are no other variables available in the dataset, then the coefficients will reflect the average value of 
+the outcomes for that level of the categorical variable. For example, suppose that the categorical variable is a 
+policyholder identifier, and the outcomes are the value of claims in different years, then the coefficients will reflect 
+the average annual claims for each policyholder based on the experience. In other words, both of these encoding schemes 
+give full credibility to the data available for each category, thus, even if a relatively small amount of data is 
+available for a specific policyholder, the coefficient that is calibrated will only reflect that data. On the other 
+hand, a foundational technique within actuarial work is the application of credibility methods, which are used for 
+experience rating and other applications. These techniques provide an estimate that reflects not only the experience of 
+the individual policyholder but also that of the collective, based on an estimate of how credible the data for each 
+individual is. While we have described the application of credibility in a simple univariate context, it is also 
+possible to apply credibility considerations within GLMs. using models known as Generalized Linear Mixed Models or 
+GLMMs, and we refer to [@Klinker2010] for more details.
 
-Having described traditional approaches for modeling categorical data, we now turn to neural networks, and discuss embedding layers for categorical data modeling, which we define in more detail in the section on neural networks.
+Having described traditional approaches for modeling categorical data, we now turn to neural networks, and discuss 
+embedding layers for categorical data modeling, which we define in more detail in the section on neural networks.
 
@@
 
-Neural networks are flexible machine learning models that have recently been applied to a number of problems with Property and Casualty (P&C) insurance.
-Here, we provide a brief overview of these models, and refer the reader to [@Richman2018] for a more detailed overview.
-Neural networks are characterized by multiple layers of non-linear regression functions that are used to learn a new representation of the data input to the network that is then used to make predictions.
-Here we focus on the most common type of neural networks, which are fully connected networks (FCNs), which provide as the output of each set of non-linear functions to the subsequent layer of functions.
-Formally, a $K$-layer neural network is:
+Neural networks are flexible machine learning models that have recently been applied to a number of problems with 
+Property and Casualty (P&C) insurance. Here, we provide a brief overview of these models, and refer the reader to 
+[@Richman2018] for a more detailed overview. Neural networks are characterized by multiple layers of non-linear 
+regression functions that are used to learn a new representation of the data input to the network that is then used to 
+make predictions. Here we focus on the most common type of neural networks, which are fully connected networks (FCNs), 
+which provide as the output of each set of non-linear functions to the subsequent layer of functions. Formally, a 
+$K$-layer neural network is:
 
@@
 
-where the regression parameters (weights) for each layer $$k \in [1;K]$$ are represented by the matrices $a_k$ and the intercept terms are represented by $b_k$.
-Whereas the calculation inside each of the layers is nothing more than linear regression, $\sigma$ represents the non-linear part of each layer.
-Choices for $\sigma$ are often the tanh function or the rectified linear unit (ReLu) $max(0,x)$.
-The parameters of the network are estimated ('trained') as follows.
-First a loss function $L(.,.)$ is specified for the network that measures the difference between the observed data $y$ and the predictions of the network $\hat{y}$, for example, the Mean Squared Error ($(y - \hat{y})^2$).
-Then, the parameters of the network are changed such that the loss decreases (formally, this is done using the technique of backpropagation).Finally, training is stopped once the predictive performance of the network on unseen data is suitably good.
+where the regression parameters (weights) for each layer $$k \in [1;K]$$ are represented by the matrices $a_k$ and the 
+intercept terms are represented by $b_k$. Whereas the calculation inside each of the layers is nothing more than linear 
+regression, $\sigma$ represents the non-linear part of each layer. Choices for $\sigma$ are often the tanh function or 
+the rectified linear unit (ReLu) $max(0,x)$. The parameters of the network are estimated ('trained') as follows. First a 
+loss function $L(.,.)$ is specified for the network that measures the difference between the observed data $y$ and the 
+predictions of the network $\hat{y}$, for example, the Mean Squared Error ($(y - \hat{y})^2$). Then, the parameters of 
+the network are changed such that the loss decreases (formally, this is done using the technique of backpropagation).
+Finally, training is stopped once the predictive performance of the network on unseen data is suitably good.
 
-If $K$ is set equal to $1$, then Equation \ref{NN} reduced to nothing more than a GLM.
-A neural network with $K=2$ is called a shallow neural network and for $K \geq 2$, the network is called a deep neural network.
-The matrix $X$ of data input to the network can be composed of both continuous variables as well as categorical variables, which can be pre-processed using one-hot or dummy encoding.
-As mentioned above, a different option is to use encodings, which we discuss in more detail next.
+If $K$ is set equal to $1$, then Equation \ref{NN} reduced to nothing more than a GLM. A neural network with $K=2$ is 
+called a shallow neural network and for $K \geq 2$, the network is called a deep neural network. The matrix $X$ of data 
+input to the network can be composed of both continuous variables as well as categorical variables, which can be 
+pre-processed using one-hot or dummy encoding. As mentioned above, a different option is to use encodings, which we 
+discuss in more detail next.
 
 ### Embeddings
-Common issues with the traditional encoding schemes for categorical data occur when the number of levels for each variable is very large.
-Often, in these cases, models do not converge quickly, and the very large matrices that result from applying these schemes often cause computational difficulties.
-Besides for these practical issues, a deeper issue is that one-hot or dummy encoded data assumes that each category is entirely independent of the rest of the categories, in other words, there are no similarities between categories that could enable more robust estimation of models.
-In technical terms, this is because the columns of the matrices created by one-hot encoding are all orthogonal to each other.
-(These arguments appear in a similar form in [@Guo2016].) Solutions to these problems are provided by embedding layers.
 
-An embedding layer is a neural network component which maps each level of the categorical data to a low dimensional vector of parameters that is learned together with the rest of the GLM or neural network that is used for the modeling problem.
-Formally, an embedding is
+Common issues with the traditional encoding schemes for categorical data occur when the number of levels for each 
+variable is very large. Often, in these cases, models do not converge quickly, and the very large matrices that result 
+from applying these schemes often cause computational difficulties. Besides for these practical issues, a deeper issue 
+is that one-hot or dummy encoded data assumes that each category is entirely independent of the rest of the categories, 
+in other words, there are no similarities between categories that could enable more robust estimation of models. In 
+technical terms, this is because the columns of the matrices created by one-hot encoding are all orthogonal to each 
+other. (These arguments appear in a similar form in [@Guo2016].) Solutions to these problems are provided by embedding 
+layers.
+
+An embedding layer is a neural network component which maps each level of the categorical data to a low dimensional 
+vector of parameters that is learned together with the rest of the GLM or neural network that is used for the modeling 
+problem. Formally, an embedding is
 
@@
 
-where $q_\mathcal{P^j}$ is the dimension of the embedding for the $j$th categorical variable and $z_\mathcal{P^j}(.)$ is an function that maps from the particular element of the labels $p$ to the embedding space.
-Equation \ref{eq:embedding} states that an embedding maps a level of a categrical variable to a numerical vector.
-This function is left implicit, meaning to say, we allow the embeddings to be derived during the process of fitting the model and do not attempt to specify exactly how the embeddings can be derived from the input data.
-In Table \ref{embed} we show an example of two dimensional embeddings for the state variables, where these have been generated randomly.
+where $q_\mathcal{P^j}$ is the dimension of the embedding for the $j$th categorical variable and $z_\mathcal{P^j}(.)$ is 
+a function that maps from the particular element of the labels $p$ to the embedding space. Equation \ref{eq:embedding} 
+states that an embedding maps a level of a categrical variable to a numerical vector. This function is left implicit, 
+meaning to say, we allow the embeddings to be derived during the process of fitting the model and do not attempt to 
+specify exactly how the embeddings can be derived from the input data. In Table \ref{embed} we show an example of two 
+dimensional embeddings for the state variables, where these have been generated randomly.
 
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
-states= fread("../manuscript/states.csv")
+states <- fread("../manuscript/states.csv")
 set.seed(42)
 
-sample_dat = sample_n(states,5) %>% arrange(state)
+sample_dat <- sample_n(states, 5) %>%
+  arrange(state)
 
-sample_dat = sample_n(states,5) %>% arrange(state)
+sample_dat <- sample_n(states, 5) %>%
+  arrange(state)
 
-data.frame(sample_dat, dimension1 = rnorm(5),dimension2 = rnorm(5)) %>% knitr::kable(label = "", caption = "Example (random) embeddings of the state variable")
-
+data.frame(sample_dat, dimension1 = rnorm(5), dimension2 = rnorm(5)) %>%
+  knitr::kable(label = "", caption = "Example (random) embeddings of the state variable")
 ```
 
-When applying embeddings in a data modeling context using neural networks, the values of the embeddings will be calibrated during the same fitting process that calibrates the parameters of the neural network.
+When applying embeddings in a data modeling context using neural networks, the values of the embeddings will be 
+calibrated during the same fitting process that calibrates the parameters of the neural network.
 
@@
 
-In this section, we describe, fit, and evaluate both a minimalist neural network architecture utilizing embeddings and a traditional GLM.
-The working example for our experiments is as follows: Given a set of claims characteristics, we predict the losses paid on the property coverage of the policy.
-In the rest of this section, we describe the dataset we use, describe formally the models being considered, and discuss results.
+In this section, we describe, fit, and evaluate both a GLM and a minimalist neural network architecture utilizing
+embeddings. While this paper focuses on embeddings in neural networks, we begin with a GLM to provide a common frame of 
+reference since most actuaries are familiar with the technique. The working example for our experiments is as follows: 
+Given a set of claims characteristics, we predict the losses paid on the property coverage of the policy. In the rest of 
+this section, we describe the dataset we use, describe formally the models being considered, and discuss results.
 
@@
 
-The data we use comes from the National Flood Insurance Program (NFIP) and is made available by the OpenFEMA initiative of the Federal Emergency Management Agency (FEMA) (TODO: cite).
-Two datasets are made available by OpenFEMA: A policies dataset with exposure information, and a claims dataset with claims transactions, including paid amounts.
-Because there is no way to associate records of the two datasets, we are limited to fitting severity models on the claims dataset.
-While the complete dataset contains over two million transactions, for the purposes of our experiments we limit ourselves to data from 2000 to August 2019, which amounts to approximately 1.4 million claims.
-The dataset can be downloaded from Cellar (TODO: link).
-The dataset includes a rich variety of variables, from occupancy type to coarse coordinates.
-For our models, we work with a few selected variables that represent continuous and discrete variables of low and high cardinalities, which we list in Table \ref{tab:variables}.
+The data we use comes from the National Flood Insurance Program (NFIP) and is made available by the OpenFEMA initiative 
+of the Federal Emergency Management Agency (FEMA)[^9]. Two datasets are made available by OpenFEMA: A policies dataset 
+with exposure information, and a claims dataset with claims transactions, including paid amounts. Because there is no 
+way to associate records of the two datasets, we are limited to fitting severity models on the claims dataset. While the 
+complete dataset contains over two million transactions, for the purposes of our experiments we limit ourselves to data 
+from 2000 to August 2019, which amounts to approximately 1.4 million claims. The dataset can be downloaded from 
+Cellar[^10] The dataset includes a rich variety of variables, from occupancy type to coarse coordinates. For our models, 
+we work with a few selected variables that represent continuous and discrete variables of low and high cardinalities, 
+which we list in Table \@ref(tab:variables)
 
-| Variable                                 | Type                                     |
-|------------------------------------------|------------------------------------------|
-| Building insurance coverage              | Numeric                                  |
-| Basement enclosure type                  | Categorical                              |
-| Number of floors in the insured building | Categorical (binned in original dataset) |
-| Flood zone                               | Categorical (high cardinality)           |
-| Primary residence                        | Categorical (binary indicator)           |
+[^9]: https://www.fema.gov/about/reports-and-data/openfema
+[^10]: https://cellar.kasa.ai
 
-: \label{tab:variables} Variables used in modeling.
+```{r variables, results='asis', echo = FALSE}
+library(magrittr)
+variables <- tibble::tribble(
+  ~Variable, ~Type,
+  "Building insurance coverage", "Numeric",
+  "Basement enclosure type", "Categorical",
+  "Number of floors in the insured building", "Categorical (binned in original dataset)",
+  "Flood zone", "Categorical (high cardinality)",
+  "Primary residence", "Categorical (binary indicator)"
+)
+knitr::kable(
+  variables,
+  caption = "Predicator variables.",
+  booktabs = TRUE,
+  table.env = "table",
+  escape = FALSE,
+  linesep = ""
+) %>%
+  kableExtra::kable_styling(latex_options = "hold_position")
+```
 
@@
 
-We fit a GLM with the following specifications:
+While GLMs are commonplace and well-studied in the actuarial literature, there are still plenty of decisions to be made
+in the modeling process; see, for example, @Goldburd for an in-depth discussion. For our purpose of establishing a
+baseline model, we proceed with what we perceive as reasonable decisions around feature engineering and model structure, outlined below:
 
 -   Target variable: Amount paid on building claim
-
 -   Predictors: *Log* of **building insurance coverage**, **basement enclosure type**, **number of floors in the insured building**, *prefix* of **flood zone**, and ***primary residence***.
-
 -   Link function: log
-
 -   Distribution: gamma
 
-We take the log of the continuous predictor **building insurance coverage** following (cite cas glm monograph), which allows the scale of the predictor to match that of the target variable.
-Because the **flood zone** variable in the original data contains 60 levels, we take the prefix of the zone code, which corresponds to the level of risk as determined by FEMA (source?).
-For example, *A01*, *A02*, and so on are recoded as simply *A*.
+We take the log of the continuous predictor **building insurance coverage**, which allows the scale of the predictor to 
+match that of the target variable. Because the **flood zone** variable in the original data contains 60 levels, we take 
+the prefix of the zone code, which corresponds to the level of risk as determined by FEMA [^8]. For example, *A01*, 
+*A02*, and so on are recoded as simply *A*.
 
-A log link together with the gamma distribution is a standard choice for severity modeling, which provides a multiplicative structure where the response is positive.
+[^8]: https://www.floodsmart.gov/flood-map-zone/find-yours
+
+A log link together with the gamma distribution is a standard choice for severity modeling, which provides a 
+multiplicative structure where the response is positive.
 
@@
 
-(Note: this section is WIP doesn't match up w/ code, which is also WIP) For the neural net, we utilize the same responsible variable, amount paid on building claim.
-We normalize the numeric variable ***building insurance coverage***, one-hot encode the **primary residence** variable, and apply embedding layers of dimension one to the rest of the categorical variables.
-We then connect the embeddings and the normalized variable to a single output unit with softplus activation, where the softplus function is defined to be
+For the neural net, we utilize the same response variable, amount paid on building claim. We perform the following 
+transformations on the predictor variables:
 
-\\begin{equation} x \\mapsto \\log(1 + e\^x). \\end{equation}
+- Normalize the numeric variable ***building insurance coverage*** (center by mean and scale by standard deviation), 
+- One-hot encode the **primary residence** variable, and 
+- Apply embedding layers of dimension one to the rest of the categorical variables.
 
-Figure (todo: add figure) exhibits the architecture of our simple neural network.
+In terms of architecture, we connect the embeddings and the normalized numeric variable to a single output unit with 
+softplus activation, where the softplus function is defined to be
+
+$$
+x \mapsto \log(1 + e^x). 
+$$
+
+Figure \@ref(fig:nn-1) exhibits the architecture of our simple neural network.
+
+```{r nn-1, echo = FALSE, fig.cap = "blahblah", out.width = "80%", fig.align = "center"}
+knitr::include_graphics("images/nn.png")
+```
 
@@
 
-To evaluate these baseline models and other models in this paper, we perform 10-fold cross validation and compare the root mean square error (RMSE) on the predicted and actual paid amounts.
+To evaluate these baseline models and other models in this paper, we perform 10-fold cross validation and compare the 
+root mean square error (RMSE) on the predicted and actual paid amounts.
 
@@
 
-Extracting and interpreting trained embeddings, including visualization techniques Can we explain the learned embeddings using a GLM? distance to water etc Rainfall Density Distance to coast
+Extracting and interpreting trained embeddings, including visualization techniques Can we explain the learned 
+embeddings using a GLM? distance to water etc Rainfall Density Distance to coast
 
@@
 
-How can embedding layers be used in GLM models?
-(Potential uses of embedding layers as a feature engineering technique for GLM) Transfer learned embeddings to GLM - backprop on NN and use as preprocessing Train GLM on embedding layers - backprop on 1 layer NN
+How can embedding layers be used in GLM models? (Potential uses of embedding layers as a feature engineering technique 
+for GLM) Transfer learned embeddings to GLM - backprop on NN and use as preprocessing Train GLM on embedding layers - 
+backprop on 1 layer NN
 
@@
 
-Investigate approaches for using embedding layers for numeric variables, or numeric variables that were captured as categorical variables (Can the modelling of numerical variables benefit from the application of embedding layers?) How should this best be done?
-CatBoost - cut into 256 groups smoothness Map numeric to a dense layer and use that as embedding - basis expansion Add a distribution to the embeddings Can insights from credibility theory lead to enhanced embeddings?
+Investigate approaches for using embedding layers for numeric variables, or numeric variables that were captured as 
+categorical variables (Can the modelling of numerical variables benefit from the application of embedding layers?) How 
+should this best be done? CatBoost - cut into 256 groups smoothness Map numeric to a dense layer and use that as 
+embedding - basis expansion Add a distribution to the embeddings Can insights from credibility theory lead to enhanced embeddings?
 Take credibility mixture over embeddings Cluster embeddings PCA of embeddings

### 2021-02-03 R/tabnet.R
tabnet starter script

@@ -1,0 +1,50 @@
+library(tabnet)
+library(tidyverse)
+library(recipes)
+library(rsample)
+
+# Download data
+claims <- cellar::cellar_pull("nfip_claims") %>%
+  filter(year_of_loss > 2000)
+
+# Basic feature engineering
+small_data <- claims %>%
+  filter(amount_paid_on_building_claim > 0,
+         total_building_insurance_coverage > 0) %>%
+  sample_n(10000) %>%
+  select(amount_paid_on_building_claim, total_building_insurance_coverage,
+         reported_zip_code, state, primary_residence, basement_enclosure_crawlspace_type,
+         condominium_indicator, number_of_floors_in_the_insured_building, occupancy_type,
+         community_rating_system_discount, flood_zone)
+
+
+rec <- recipe(
+    amount_paid_on_building_claim ~ total_building_insurance_coverage + community_rating_system_discount +
+        basement_enclosure_crawlspace_type + number_of_floors_in_the_insured_building + flood_zone + occupancy_type,
+    data = small_data
+) %>%
+    step_normalize(all_numeric(), -all_outcomes()) %>%
+    step_unknown(all_nominal(), -all_outcomes())
+
+fit <- tabnet_fit(rec, small_data, epochs = 1)
+
+# example: extract embedding weights
+fit$fit$network$parameters$embedder.embeddings.2.weight
+
+# example: prediction
+predict(fit, small_data %>% sample_n(100))
+
+ex_fit <- tabnet_explain(fit, small_data)
+
+# example: attention masks visualization
+ex_fit$masks %>% 
+  imap_dfr(~mutate(
+    .x, 
+    step = sprintf("Step %d", .y),
+    rowname = row_number()
+  )) %>% 
+  pivot_longer(-c(rowname, step), names_to = "variable", values_to = "m_agg") %>% 
+  ggplot(aes(x = rowname, y = variable, fill = m_agg)) +
+  geom_tile() +
+  scale_fill_viridis_c() +
+  facet_wrap(~step)

### 2021-02-03 manuscript/manuscript.Rmd
more stuff

@@
 
+(maybe include a second nn with actual hidden layers?)
+
 ## Performance evaluation framework and results
 
-To evaluate these baseline models and other models in this paper, we perform 10-fold cross validation and compare the 
+To evaluate these baseline models and other models in this paper, we perform 10-fold 
+cross validation and compare the 
 root mean square error (RMSE) on the predicted and actual paid amounts.
+(somehwere we should say we're not doing a kaggle competition here and the performance metrics are really meant
+to show that the models aren't complete shit)
+(maybe a couple boxplots showing metrics for baseline models)
 
@@
 
+Description of tabnet, talk about how it's related to embeddings, show some plots 
+like \@ref(fig:masks) etc.
+
+```{r masks, echo = FALSE, fig.cap = "blahblah", out.width = "100%", fig.align = "center"}
+knitr::include_graphics("images/masks.png")
+```
+
 # Conclusions {#Conclusions}

### 2021-02-03 manuscript/manuscript.Rmd
edits

@@
 
-Extracting and interpreting trained embeddings, including visualization techniques Can we explain the learned 
-embeddings using a GLM? distance to water etc Rainfall Density Distance to coast
+- model explainability is important in insurance
+- the more we can learn about how we arrive at our models the better
+- cite some existing work on explainable models in actuarial literature to show people care
+- refer back to some definitions from previous sections
+- show some embedding weights from our models - 1d line plot
+- (need a multidimensional embedding for this) do some pca/tsne
+- stress that relationship of embedding weights to response variable may be nonlinear depending on architecture
 
@@
 
-How can embedding layers be used in GLM models? (Potential uses of embedding layers as a feature engineering technique 
-for GLM) Transfer learned embeddings to GLM - backprop on NN and use as preprocessing Train GLM on embedding layers - 
-backprop on 1 layer NN
+- get weights from NN and use in place of categorical variables in GLM?
+- train GLM using backprop w/ embedding layer (OK maybe this ought to be absorbed in the modeling section and we add this as a separate model?)
 

### 2021-03-09 R/cv-model-torch.R
embeddings in glm

@@ -7,7 +7,7 @@ source("R/model-utils.R")
 source("R/data-loading.R")
 
 categorical_cols <- c(
-    "state", "primary_residence", "basement_enclosure_crawlspace_type",
+    "primary_residence", "basement_enclosure_crawlspace_type",
     "condominium_indicator", "number_of_floors_in_the_insured_building",
     "occupancy_type", "flood_zone"
 )
@@ -25,18 +25,19 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
     analysis_data <- analysis(splits)
     assessment_data <- assessment(splits)
 
-    rec <- recipe(amount_paid_on_building_claim ~ .,
+    rec_nn <- recipe(amount_paid_on_building_claim ~ .,
         data = analysis_data %>%
             select(-loss_proportion, -reported_zip_code)
     ) %>%
+        step_log(total_building_insurance_coverage) %>%
         step_normalize(all_numeric(), -all_outcomes()) %>%
         step_novel(all_nominal()) %>%
         # step_unknown(all_nominal(), new_level = "missing") %>%
         step_integer(all_nominal(), strict = TRUE, zero_based = TRUE) %>%
         prep(strings_as_factors = TRUE)
 
-    ds <- flood_dataset(juice(rec), categorical_cols, numeric_cols, response_col, env)
-    baked_test_data <- bake(rec, assessment_data)
+    ds <- flood_dataset(juice(rec_nn), categorical_cols, numeric_cols, response_col, env)
+    baked_test_data <- bake(rec_nn, assessment_data)
     test_ds <- flood_dataset(baked_test_data, categorical_cols, numeric_cols)
     train_indx <- sample(length(ds), 0.8 * length(ds))
     valid_indx <- seq_len(length(ds)) %>% setdiff(train_indx)
@@ -49,17 +50,20 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 
     model <- trivial_net(env$cardinalities, length(numeric_cols), function(x) 1)
 
-    optimizer <- optim_adam(model$parameters, lr = learning_rate)
+    optimizer <- optim_adam(model$parameters, lr = learning_rate, weight_decay = 0)
+    # optimizer <- optim_rmsprop(model$parameters, lr = 0.1)
 
     train_loop(model, train_dl, valid_dl, epochs, optimizer)
+
[…]

### 2021-03-09 R/data-loading.R

@@ -9,7 +9,7 @@ small_data <- claims %>%
     sample_n(10000) %>%
     select(
         amount_paid_on_building_claim, total_building_insurance_coverage,
-        reported_zip_code, state, primary_residence, basement_enclosure_crawlspace_type,
+        reported_zip_code, primary_residence, basement_enclosure_crawlspace_type,
         condominium_indicator, number_of_floors_in_the_insured_building, occupancy_type,
         community_rating_system_discount, flood_zone
     ) %>%

### 2021-03-09 R/model-utils.R

@@ -7,7 +7,7 @@ flood_dataset <- dataset(
             `+`(1L) %>%
             torch_tensor()
         if (!is.null(env)) {
-            assign("cardinalities", sapply(df[categorical_cols], function(x) max(x) + 3), envir = env)
+            assign("cardinalities", sapply(df[categorical_cols], function(x) max(x) + 2), envir = env)
         }
         self$xnum <- df[numeric_cols] %>%
             as.matrix() %>%
@@ -74,7 +74,8 @@ trivial_net <- nn_module(
         all <- torch_cat(list(embedded, xnum$to(dtype = torch_float())), dim = 2)
         all %>%
             self$output() %>%
-            nnf_softplus()
+            torch_exp()
+            # nnf_softplus()
     }
 )
 
@@ -100,6 +101,53 @@ simple_net <- nn_module(
             nnf_softplus()
     } 
 )
+
+train_loop_alternate <- function(model, train_dl, valid_dl, epochs, optimizer) {
+    for (epoch in seq_len(epochs)) {
+        model$train()
+        train_losses <- c()
+
+        odd_epoch <- epoch %% 2 == 1
+
+        for (p in model$embedder$parameters) {
+            p$requires_grad_(odd_epoch)
+        }
+
+        for (p in model$output$parameters) {
+            p$requires_grad_(!odd_epoch)
+        }
+
+        for (b in enumerate(train_dl)) {
+            optimizer$zero_grad()
+            output <- model(b$x[[1]], b$x[[2]])
+            loss <- nnf_mse_loss(output, b$y)
+            loss$backward()
+
+            # if (odd_epoch) {
+            #     nn_utils_clip_grad_value_(model$embedder$parameters, 1)
+            # } else {
+            #     nn_utils_clip_grad_value_(model$output$parameters, 1)
+            # }
+
+            optimizer$step()
+            train_losses <- c(train_losses, loss$item())
+        }
+
+        model$eval()
+        valid_losses <- c()
+
+        for (b in enumerate(valid_dl)) {
+            output <- model(b$x[[1]], b$x[[2]])
+            loss <- nnf_mse_loss(output, b$y)
+            valid_losses <- c(valid_losses, loss$item())
+        }
+
+        cat(sprintf(
+            "Loss at epoch %d: training: %3f, validation: %3f\n", epoch,
[…]

### 2021-03-09 R/cv-model-torch.R
add mlp

@@ -59,6 +59,16 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 
     preds_nn <- get_preds(model, test_dl)
 
+    model2 <- simple_net(env$cardinalities, length(numeric_cols), units = 64, 
+                         fn_embedding_dim = function(x) ceiling(x / 2)
+    )
+
+    optimizer <- optim_adam(model$parameters, lr = learning_rate, weight_decay = 0)
+
+    train_loop(model2, train_dl, valid_dl, epochs, optimizer)
+
+    preds_nn2 <- get_preds(model2, test_dl)
+
     form <- amount_paid_on_building_claim ~ total_building_insurance_coverage +
         basement_enclosure_crawlspace_type + number_of_floors_in_the_insured_building +
         occupancy_type + flood_zone + primary_residence + condominium_indicator + community_rating_system_discount
@@ -101,6 +111,7 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 
     list(
         model_nn = model,
+        model_nn2 = model2,
         rec_nn = rec_nn,
         model_glm = model_glm,
         rec_glm = rec_glm,
@@ -108,18 +119,20 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
         rec_glm2 = rec_glm2,
         actuals = actuals,
         preds_nn = preds_nn,
+        preds_nn2 = preds_nn2,
         preds_glm = preds_glm,
         preds_glm2 = preds_glm2
     )
 }
 
 cv_results <- cvfolds$splits %>%
-    lapply(function(x) model_analyze_assess(x, 0.05, 5, 1100))
+    lapply(function(x) model_analyze_assess(x, 0.1, 5, 1100))
 
 cv_results %>%
     map(function(x) {
         list(
             rmse_nn = sqrt(sum((x$actuals - x$preds_nn)^2) / length(x$actuals)),
+            rmse_nn2 = sqrt(sum((x$actuals - x$preds_nn2)^2) / length(x$actuals)), 
             rmse_glm = sqrt(sum((x$actuals - x$preds_glm)^2) / length(x$actuals)),
             rmse_glm2 = sqrt(sum((x$actuals - x$preds_glm2) ^ 2) / length(x$actuals))
         )

### 2021-03-09 R/model-utils.R

@@ -189,9 +189,12 @@ get_preds <- function(model, dl) {
 
 replace_unseen_level_weights_ <- function(embeddings) {
     for (emb in as.list(embeddings)) {
-        emb_dim <- dim(emb$weight)[[1]]
-        median_wt <- torch_median(emb$weight[1:(emb_dim - 1),])
-        emb$weight[emb_dim, 1] <- median_wt
+        emb_num_lvls <- dim(emb$weight)[[1]]
+        emb_dim <- dim(emb$weight)[[2]]
+        for (j in seq_len(emb_dim)) {
+            median_wt <- torch_median(emb$weight[1:(emb_num_lvls - 1), j])
+            emb$weight[emb_num_lvls, j] <- median_wt
+        }
     }
 
     embeddings

### 2021-03-09 R/cv-model-torch.R
formatting

@@ -59,11 +59,12 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 
     preds_nn <- get_preds(model, test_dl)
 
-    model2 <- simple_net(env$cardinalities, length(numeric_cols), units = 64, 
-                         fn_embedding_dim = function(x) ceiling(x / 2)
+    model2 <- simple_net(env$cardinalities, length(numeric_cols),
+        units = 64,
+        fn_embedding_dim = function(x) ceiling(x / 2)
     )
 
-    optimizer <- optim_adam(model$parameters, lr = learning_rate, weight_decay = 0)
+    optimizer <- optim_adam(model2$parameters, lr = learning_rate, weight_decay = 0)
 
     train_loop(model2, train_dl, valid_dl, epochs, optimizer)
 
@@ -126,14 +127,14 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 }
 
 cv_results <- cvfolds$splits %>%
-    lapply(function(x) model_analyze_assess(x, 0.1, 5, 1100))
+    lapply(function(x) model_analyze_assess(x, 0.1, 20, 1100))
 
 cv_results %>%
     map(function(x) {
         list(
             rmse_nn = sqrt(sum((x$actuals - x$preds_nn)^2) / length(x$actuals)),
-            rmse_nn2 = sqrt(sum((x$actuals - x$preds_nn2)^2) / length(x$actuals)), 
+            rmse_nn2 = sqrt(sum((x$actuals - x$preds_nn2)^2) / length(x$actuals)),
             rmse_glm = sqrt(sum((x$actuals - x$preds_glm)^2) / length(x$actuals)),
-            rmse_glm2 = sqrt(sum((x$actuals - x$preds_glm2) ^ 2) / length(x$actuals))
+            rmse_glm2 = sqrt(sum((x$actuals - x$preds_glm2)^2) / length(x$actuals))
         )
     })

### 2021-03-09 R/model-utils.R

@@ -75,7 +75,7 @@ trivial_net <- nn_module(
         all %>%
             self$output() %>%
             torch_exp()
-            # nnf_softplus()
+        # nnf_softplus()
     }
 )
 
@@ -95,11 +95,11 @@ simple_net <- nn_module(
         embedded <- self$embedder(xcat)
         all <- torch_cat(list(embedded, xnum$to(dtype = torch_float())), dim = 2)
         all %>%
-            self$fc()  %>% 
-            nnf_relu() %>% 
+            self$fc() %>%
+            nnf_relu() %>%
             self$output() %>%
             nnf_softplus()
-    } 
+    }
 )
 
 train_loop_alternate <- function(model, train_dl, valid_dl, epochs, optimizer) {
@@ -146,7 +146,7 @@ train_loop_alternate <- function(model, train_dl, valid_dl, epochs, optimizer) {
             "Loss at epoch %d: training: %3f, validation: %3f\n", epoch,
             mean(train_losses), mean(valid_losses)
         ))
-    }    
+    }
 }
 
 train_loop <- function(model, train_dl, valid_dl, epochs, optimizer) {
@@ -202,12 +202,12 @@ replace_unseen_level_weights_ <- function(embeddings) {
 
 map_cats_to_embeddings <- function(data, keys) {
     for (v in names(keys)) {
-        mapping_table <- keys[[v]] %>% 
+        mapping_table <- keys[[v]] %>%
             select(value, embedding) %>%
             rename(!!v := value)
         data <- data %>%
-            left_join(mapping_table, by = v) %>% 
-            select(-!!v) %>% 
+            left_join(mapping_table, by = v) %>%
+            select(-!!v) %>%
             rename(!!v := embedding)
     }
 
@@ -215,18 +215,19 @@ map_cats_to_embeddings <- function(data, keys) {
 }
 
 key_with_embeddings <- function(embeddings, key) {
-    Map(function(embedder, key) {
-    # key$integer
-    embedding <- key$integer %>% 
-      `+`(1L)  %>% 
-      torch_tensor(dtype = torch_int()) %>% 
-      embedder() %>% 
-      as.numeric()
-    key[["embedding"]] <- embedding
-    key
-},
-    as.list(embeddings),
-    key
-) %>% 
-    setNames(names(key))
+    Map(
+        function(embedder, key) {
+            # key$integer
+            embedding <- key$integer %>%
+                `+`(1L) %>%
+                torch_tensor(dtype = torch_int()) %>%
[…]

### 2021-03-09 R/cv-model-torch.R
fewer variables

@@ -8,7 +8,7 @@ source("R/data-loading.R")
 
 categorical_cols <- c(
     "primary_residence", "basement_enclosure_crawlspace_type",
-    "condominium_indicator", "number_of_floors_in_the_insured_building",
+    "number_of_floors_in_the_insured_building",
     "occupancy_type", "flood_zone"
 )
 
@@ -17,8 +17,8 @@ response_col <- "amount_paid_on_building_claim"
 
 
 cvfolds <- small_data %>%
-    rsample::vfold_cv(v = 2)
-cvfolds
+    rsample::vfold_cv(v = 5)
+# cvfolds
 
 model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_size = 5000, ...) {
     env <- new.env()
@@ -72,7 +72,7 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 
     form <- amount_paid_on_building_claim ~ total_building_insurance_coverage +
         basement_enclosure_crawlspace_type + number_of_floors_in_the_insured_building +
-        occupancy_type + flood_zone + primary_residence + condominium_indicator + community_rating_system_discount
+        occupancy_type + flood_zone + primary_residence + community_rating_system_discount
 
     rec_glm <- recipe(form,
         data = analysis_data
@@ -127,7 +127,7 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 }
 
 cv_results <- cvfolds$splits %>%
-    lapply(function(x) model_analyze_assess(x, 0.1, 20, 1100))
+    lapply(function(x) model_analyze_assess(x, 0.01, 1, 1100))
 
 cv_results %>%
     map(function(x) {

### 2021-03-09 R/data-loading.R

@@ -10,7 +10,8 @@ small_data <- claims %>%
     select(
         amount_paid_on_building_claim, total_building_insurance_coverage,
         reported_zip_code, primary_residence, basement_enclosure_crawlspace_type,
-        condominium_indicator, number_of_floors_in_the_insured_building, occupancy_type,
+        # condominium_indicator, 
+        number_of_floors_in_the_insured_building, occupancy_type,
         community_rating_system_discount, flood_zone
     ) %>%
     filter(across(everything(), ~!is.na(.x))) %>% 

### 2021-03-09 manuscript/manuscript.Rmd
start writing

@@
 
-# Predictive Modeling with GLM and a Minimalist Neural Network
+# Predictive Modeling with Embeddings
 
-In this section, we describe, fit, and evaluate both a GLM and a minimalist neural network architecture utilizing
-embeddings. While this paper focuses on embeddings in neural networks, we begin with a GLM to provide a common frame of 
-reference since most actuaries are familiar with the technique. The working example for our experiments is as follows: 
-Given a set of claims characteristics, we predict the losses paid on the property coverage of the policy. In the rest of 
-this section, we describe the dataset we use, describe formally the models being considered, and discuss results.
+In this section, we walk through a simple predictive modeling exercise in order to illustrate the application of 
+embeddings. First, we pose a supervised regression problem, based on flood insurance claims severity. We then describe, 
+fit, and evaluate GLMs and neural networks utilizing embeddings for this problem. Finally, we discuss visualization 
+techniques for model interpretation. As we proceed, we also incorporate practical technical guidance on modeling
+procedure.
 
-## NFIP data
+## Problem Description and Data
+
+The working example for our experiments is as follows: Given a set of claim characteristics, we predict the losses paid 
+on the property coverage of the policy.
 
@@
 
-```{r variables, results='asis', echo = FALSE}
+```{r variables, results='asis', message=FALSE, echo = FALSE}
 library(magrittr)
@@
 
-## Severity GLM
+## Models
 
+1. A GLM with gamma distribution and log link function
+2. A linear model with categorical embeddings and an exponential output activation
+3. A GLM with the categorical predictors replaced by the trained embeddings from Model 2.
+4. A multilayer perceptron regression model
+
+### Model 1: Simple GLM
+
+While this paper focuses on embeddings in neural networks, we begin with a GLM to provide a common frame of 
+reference since most actuaries are familiar with the technique. 
 While GLMs are commonplace and well-studied in the actuarial literature, there are still plenty of decisions to be made
@@
 
-## A Simple Neural Network
+### Model 2: Linear Model with Embeddings
 
@@
 
-# Interpretations {#interpretation}
+## Interpretations {#interpretation}
 
@@
 - stress that relationship of embedding weights to response variable may be nonlinear depending on architecture
-
-# Transfer Learning {#tl}
-
-- get weights from NN and use in place of categorical variables in GLM?
-- train GLM using backprop w/ embedding layer (OK maybe this ought to be absorbed in the modeling section and we add this as a separate model?)
 

### 2021-03-09 manuscript/manuscript.Rmd
edits

@@
 The working example for our experiments is as follows: Given a set of claim characteristics, we predict the losses paid 
-on the property coverage of the policy.
-
-The data we use comes from the National Flood Insurance Program (NFIP) and is made available by the OpenFEMA initiative 
+on the property coverage of the policy. The data we use comes from the National Flood Insurance Program (NFIP) and is 
+made available by the OpenFEMA initiative 
 of the Federal Emergency Management Agency (FEMA)[^9]. Two datasets are made available by OpenFEMA: A policies dataset 
@@
   "Building insurance coverage", "Numeric",
+  "Community Rating System Discount", "Numeric",
   "Basement enclosure type", "Categorical",
+  "Occupancy Type", "Categorical",
   "Number of floors in the insured building", "Categorical (binned in original dataset)",
@@
 
+The response variable we take from the dataset is "Amount Paid on Building Claim", which is a numeric variable.
+
 ## Models
@@
 2. A linear model with categorical embeddings and an exponential output activation
-3. A GLM with the categorical predictors replaced by the trained embeddings from Model 2.
+3. A GLM with the categorical predictors replaced by the trained embeddings from Model 2
 4. A multilayer perceptron regression model

### 2021-03-10 manuscript/manuscript.Rmd
glm

@@
 
-1. A GLM with gamma distribution and log link function
-2. A linear model with categorical embeddings and an exponential output activation
-3. A GLM with the categorical predictors replaced by the trained embeddings from Model 2
-4. A multilayer perceptron regression model
+In this subsection, we develop the following models:
+
+1. A GLM with gamma distribution and log link function,
+2. A linear model with categorical embeddings and an exponential output activation,
+3. A GLM with the categorical predictors replaced by the trained embeddings from Model 2, and
+4. A multilayer perceptron model with categorical embeddings.
+
+These model architectures are relatively uncomplicated by today's standards, and are so chosen to better highlight the
+embedding components. Later, in Section X (TODO), we will investigate more involved architectures utilizing embeddings
+that represent the state of the art for modeling tabular data.
 
@@
 reference since most actuaries are familiar with the technique. 
-While GLMs are commonplace and well-studied in the actuarial literature, there are still plenty of decisions to be made
-in the modeling process; see, for example, @Goldburd for an in-depth discussion. For our purpose of establishing a
-baseline model, we proceed with what we perceive as reasonable decisions around feature engineering and model structure, outlined below:
+Although GLMs are commonplace and well-studied in the actuarial literature, there are still plenty of decisions to 
+be made in the modeling process; see, for example, @Goldburd for an in-depth discussion. For our purpose of 
+establishing a baseline, we proceed with what we perceive as reasonable decisions around feature engineering and model structure, outlined below:
 
 -   Target variable: Amount paid on building claim
--   Predictors: *Log* of **building insurance coverage**, **basement enclosure type**, **number of floors in the insured building**, *prefix* of **flood zone**, and ***primary residence***.
--   Link function: log
+-   Predictors:
+    - $\log$ `building_insurance_coverage`
+    - `basement_enclosure_type`, 
+    - `number_of_floors_in_the_insured_building`
+    - *prefix* of `flood_zone`
+    - `primary_residence`
+-   Link function: $\log$
 -   Distribution: gamma
 
-We take the log of the continuous predictor **building insurance coverage**, which allows the scale of the predictor to 
-match that of the target variable. Because the **flood zone** variable in the original data contains 60 levels, we take 
-the prefix of the zone code, which corresponds to the level of risk as determined by FEMA [^8]. For example, *A01*, 
-*A02*, and so on are recoded as simply *A*.
+We take the log of the continuous predictor `building_insurance_coverage`, which allows the scale of the predictor to 
+match that of the target variable. Because the `flood_zone` variable in the original data contains 60 levels, we take 
+the prefix of the zone code, which corresponds to the level of risk as determined by FEMA [^8]. For example, `"A01"`, 
+`"A02"`, and so on are recoded as simply `"A"`.
 

### 2021-03-10 R/model-utils.R
remove trivial model

@@ -59,31 +59,11 @@ embedding_module <- nn_module(
     }
 )
 
-trivial_net <- nn_module(
-    "baseline_net",
-    initialize = function(cardinalities,
-                          num_numerical,
-                          fn_embedding_dim = function(x) ceiling(x / 2)) {
-        self$embedder <- embedding_module(cardinalities, fn_embedding_dim)
-        sum_embedding_dim <- sapply(cardinalities, fn_embedding_dim) %>%
-            sum()
-        self$output <- nn_linear(sum_embedding_dim + num_numerical, 1)
-    },
-    forward = function(xcat, xnum) {
-        embedded <- self$embedder(xcat)
-        all <- torch_cat(list(embedded, xnum$to(dtype = torch_float())), dim = 2)
-        all %>%
-            self$output() %>%
-            torch_exp()
-        # nnf_softplus()
-    }
-)
-
 simple_net <- nn_module(
-    "mlp",
+    "simple_net",
     initialize = function(cardinalities,
                           num_numerical,
-                          units = 64,
+                          units = 16,
                           fn_embedding_dim = function(x) ceiling(x / 2)) {
         self$embedder <- embedding_module(cardinalities, fn_embedding_dim)
         sum_embedding_dim <- sapply(cardinalities, fn_embedding_dim) %>%

### 2021-03-10 R/cv-model-torch.R
update main script

@@ -48,7 +48,7 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
     valid_dl <- valid_ds %>% dataloader(batch_size = batch_size, shuffle = TRUE)
     test_dl <- test_ds %>% dataloader(batch_size = batch_size, shuffle = FALSE)
 
-    model <- trivial_net(env$cardinalities, length(numeric_cols), function(x) 1)
+    model <- simple_net(env$cardinalities, length(numeric_cols), units = 16, fn_embedding_dim = function(x) 1)
 
     optimizer <- optim_adam(model$parameters, lr = learning_rate, weight_decay = 0)
     # optimizer <- optim_rmsprop(model$parameters, lr = 0.1)
@@ -60,13 +60,15 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
     preds_nn <- get_preds(model, test_dl)
 
     model2 <- simple_net(env$cardinalities, length(numeric_cols),
-        units = 64,
+        units = 16,
         fn_embedding_dim = function(x) ceiling(x / 2)
     )
 
     optimizer <- optim_adam(model2$parameters, lr = learning_rate, weight_decay = 0)
 
     train_loop(model2, train_dl, valid_dl, epochs, optimizer)
+
+    replace_unseen_level_weights_(model2$embedder$embeddings)
 
     preds_nn2 <- get_preds(model2, test_dl)
 

### 2021-03-10 manuscript/manuscript.Rmd
edits

@@
 1. A GLM with gamma distribution and log link function,
-2. A linear model with categorical embeddings and an exponential output activation,
-3. A GLM with the categorical predictors replaced by the trained embeddings from Model 2, and
-4. A multilayer perceptron model with categorical embeddings.
+2. A neural network with unidimensional categorical embeddings,
+3. A GLM with the categorical predictors replaced by the trained embeddings from Model 2,
+4. A neural network with multidimensional categorical embeddings.
 
@@
 
-### Model 1: Simple GLM
+### Model 1: GLM
 
@@
 
-### Model 2: Linear Model with Embeddings
+### Model 2: Neural Network with Unidimensional Embeddings
 
-For the neural net, we utilize the same response variable, amount paid on building claim. We perform the following 
-transformations on the predictor variables:
-
-- Normalize the numeric variable ***building insurance coverage*** (center by mean and scale by standard deviation), 
-- One-hot encode the **primary residence** variable, and 
-- Apply embedding layers of dimension one to the rest of the categorical variables.
-
-In terms of architecture, we connect the embeddings and the normalized numeric variable to a single output unit with 
-softplus activation, where the softplus function is defined to be
+For Model 2, we build a feedforward neural network. The categorical inputs go through one-dimensional embedding
+layers where they are each mapped to a scalar. The embeddings are then concatenated with the numeric predictors, which
+have been normalized in data pre-processing, before being sent to a single linear layer of 16 units. A ReLU activation
+is then applied to the outputs before they are sent to a final linear layer resulting in a scalar. To constrain
+predictions to be positive, we apply softplus activation, which is defined to be
 
@@
 
-```{r nn-1, echo = FALSE, fig.cap = "blahblah", out.width = "80%", fig.align = "center"}
+```{r nn-1, echo = FALSE, fig.cap = "blahblah", out.width = "90%", fig.align = "center"}
 knitr::include_graphics("images/nn.png")
@@
 
-(maybe include a second nn with actual hidden layers?)
+### Model 3: GLM with Neural Network Embeddings
+
+### Model 4: Neural Network with Multidimensional Embeddings
 

### 2021-03-10 R/cv-model-torch.R
more edits

@@ -29,7 +29,7 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
         data = analysis_data %>%
             select(-loss_proportion, -reported_zip_code)
     ) %>%
-        step_log(total_building_insurance_coverage) %>%
+        # step_log(total_building_insurance_coverage) %>%
         step_normalize(all_numeric(), -all_outcomes()) %>%
         step_novel(all_nominal()) %>%
         # step_unknown(all_nominal(), new_level = "missing") %>%

### 2021-03-10 manuscript/manuscript.Rmd

@@
 layers where they are each mapped to a scalar. The embeddings are then concatenated with the numeric predictors, which
-have been normalized in data pre-processing, before being sent to a single linear layer of 16 units. A ReLU activation
-is then applied to the outputs before they are sent to a final linear layer resulting in a scalar. To constrain
+have been normalized in data pre-processing, before being sent to a hidden linear layer of 16 units. A ReLU (TODO: reference an equation in prev. section) activation
+is then applied to the outputs before they are sent to a final output layer resulting in a scalar. To constrain
 predictions to be positive, we apply softplus activation, which is defined to be
@@
 
-```{r nn-1, echo = FALSE, fig.cap = "blahblah", out.width = "90%", fig.align = "center"}
+```{r nn-1, echo = FALSE, fig.cap = "Architecture of Models 2 and 4.", out.width = "90%", fig.align = "center"}
 knitr::include_graphics("images/nn.png")
@@
 
+With a single hidden layer, this architecture is the simplest nontrivial neural network; without the hidden layer and
+corresponding ReLU activation, we would actually recover a GLM structure where the link function is the output activation. 
+The choice of one for the embedding dimension is also due to simplicity: it is easily interpretable as the representation
+of each factor level as a point on the real number line, also, the trained embeddings are easily incorporated into a GLM
+which we will see in Model 3. In practice, the embedding dimension is a hyperparameter one can tune, for example via
+cross validation, and can vary for each variable. However, we also note that the choice of one for the 
+embedding output dimension is not an unreasonable one, especially when the cardinalities of the categorical variables
+are not unusually large.
+
 ### Model 3: GLM with Neural Network Embeddings
+
+For Model 3, we return to the GLM, but now we replace the categorical variables with the trained embeddings from Model
+2. In other words, our model now contains only continuous variables, and each categorical factor is represented as a
+scalar value and obtains its own coefficient. (TODO: insert formal eqn for mean)
 
@@
 
-## Performance evaluation framework and results
+## Model Training and Results
 

### 2021-03-10 manuscript/manuscript.Rmd
latex header

@@
     base_format: rticles::arxiv_article
-extra_dependencies: ["amsmath"]
+header-includes: |
+    \usepackage{amsmath}
+    \usepackage{mathtools}
+    \DeclarePairedDelimiter\ceil{\lceil}{\rceil}
 
@@
 
-## Categorical data modeling
+## Categorical data modeling {#catdata}
 
@@
 
+Model 4 is architecturally identical to Model 2, with the only difference being the number of embedding dimensions:
+instead of mapping factor levels to real numbers, we map them to a point in Euclidean space, where the dimension of the space is the ceiling
+of the factor's cardinality divided by two. Formally, in the notation of Section \ref{catdata},
+$q_{\mathcal{P}^j}=\ceil{n^j_{\mathcal{P}}/2}$ for variable $X_j$.
+
 ## Model Training and Results

### 2021-03-10 R/embedding-extract.R
viz scratch

@@ -1,10 +1,10 @@
-model
-level_integer_mappings <- rec$steps[[3]]$key %>%
+model <- cv_results[[1]]$model_nn2
+level_integer_mappings <- cv_results[[1]]$rec_nn$steps[[4]]$key %>%
     lapply(function(x) mutate(x, integer = as.integer(integer + 1L)))
 
 embeddings <- model$embedder$embeddings %>%
-    (function(x) lapply(1:length(cat_cols), function(i) x[[i]])) %>%
-    setNames(cat_cols) %>%
+    (function(x) lapply(1:length(categorical_cols), function(i) x[[i]])) %>%
+    setNames(categorical_cols) %>%
     purrr::imap(function(m, v) {
         outputs <- level_integer_mappings[[v]]$integer %>%
             torch_tensor() %>%
@@ -17,7 +17,7 @@ embeddings <- model$embedder$embeddings %>%
         )
     })
 
-embeddings$flood_zone %>%
+embeddings$condominium_indicator %>%
   ggplot() +
   geom_vline(xintercept = 0, linetype = "dashed") +
   geom_text(aes(-0.5, e1, label = round(e1, 2))) +
@@ -38,3 +38,30 @@ embeddings$state %>%
     ggplot() +
     geom_point(aes(e1, e2)) +
     geom_text(aes(e1, e2, label = level))
+
+embeddings$flood_zone %>% dim()
+
+lbls <- embeddings$flood_zone$level
+wts <- embeddings$flood_zone %>%
+    select(starts_with("e")) %>%
+    as.matrix()
+pca <- prcomp(wts, center = TRUE, scale. = TRUE, rank = 3)$x[, c("PC1", "PC2", "PC3")] %>%
+    as.data.frame()
+
+library(ggrepel)
+
+ggplot(data = pca, aes(x = PC1, y = PC2)) +
+    geom_point()
+
+rayshader::plot_gg(ggp)
+
+pca %>%
+    as.data.frame() %>%
+    mutate(class = lbls) %>%
+    mutate(prefix = substr(lbls, 1, 1))  %>%  
+  ggplot(aes(x = PC1, y = PC2, color = prefix)) +
+  geom_point() +
+  geom_label_repel(aes(label = class)) + 
+  coord_cartesian(xlim = c(-2, 2), ylim = c(-2, 2)) +
+  theme(aspect.ratio = 1) +
+  theme_classic()

### 2021-03-10 manuscript/manuscript.Rmd
Added Attention and fixed LaTeX

--- 2021-03-10 manuscript/manuscript.Rmd
@@
     base_format: rticles::arxiv_article
-extra_dependencies: ["amsmath"]
+extra_dependencies: ["amsmath", "bm"]
 
@@
 ### Attention {#attention}
+Attention mechanisms have been widely applied within the deep learning literature to give more flexibility to RNNs [@Bahdanau2015a] and subsequently as a replacement for FCNs in the so-called Transformer architecture, which is now widely used in natural language processing [@Vaswani2017a], and, more recently, has been applied to computer vision and tabular modelling tasks.
+Attention mechanisms allow deep neural nets to choose covariates entering the model in a flexible manner; these types of applications are demonstrated in, for example, [@Vaswani2017a].
+In this section we provide an introduction to attention mechanisms and then discuss applications of attention to modeling tabular data .
+
+An attention mechanism is a mapping:
+
+  ```{=tex}
+\begin{equation}
+A: \mathbb{R}^{q \times (q \times d) \times (q \times d)} \to \mathbb{R}^q, ~~
+  (\mathbf{q}, K, V) ~\mapsto ~ \mathbf{v} = A(\mathbf{q}, K, V),
+\label{eq:attention}
+\end{equation}
+```
+where $\mathbf{q} \in \mathbb{R}^q$ is a query vector, $K \in \mathbb{R}^{q \times d}$ is a matrix of key vectors, $V \in \mathbb{R}^{q \times d}$ is a matrix of value vectors and $\mathbf{v} \in \mathbb{R}^q$, the output of the attention mechanism, is a new vector of values.
+Several different options for the mapping \eqref{eq:attention} exist in the literature; here we first describe the self-attention mechanism used in [@Vaswani2017a].
+In more detail, consider that $V$ is a matrix of covariates relating to a regression problem, which can be composed of embeddings of the same dimension for several categorical variables.
+We wish to apply the attention mechanism to $V$ to estimate the most important of these embeddings for the regression problem.
+To do this, we formulate the query vector $\mathbf{q}$ which contains information about the regression problem at hand; this is usually done by passing $L$ through a FCN.
+Similarly, the matrix $K$ contains the relevance of each row of $L$ for the regression problem and is also usually derived by passing each row of $L$ through another FCN.
+Finally, the matrix $V$ can be set equal to $L$ or alternatively, can be derived as a transformation of $L$ using a third FCN.
+The first step of the attention mechanism is to derive a vector $\mathbf{a}$ of attention scores:
+
+  ```{=tex}
+\begin{equation}
+\mathbb{R}^{(1 \times q) \times (q \times d)} \to \mathbb{R}^{1 \times d}, ~~
+  (\bold{q}, K) ~\mapsto ~ \mathbf{a} = \langle \mathbf{q}, K^T \mathbb{R}angle.
+\label{eq:attention_scores}
+\end{equation}
+```
+The attention scores are then normalized using a soft max function i.e.
+
+```{=tex}
+\begin{equation}
+a^*_i = \frac{e^{(a_i)}}{\sum_{n=1}^{d} e^{(a_n)}}.
+\end{equation}
+```
+Finally, a linear combination of $V$ is formed:
+
+  ```{=tex}
+\begin{equation}
+\mathbb{R}^{(1 \times d) \times (d \times q)} \to \mathbb{R}^{1 \times q}, ~~
+  (\mathbf{a^*}, V) ~\mapsto ~ \mathbf{v} = \langle \mathbf{a^*}, V \mathbb{R}angle.
+\label{eq:attention_output}
+\end{equation}
+```
 

### 2021-03-10 manuscript/manuscript.Rmd
Fix equation

@@
 extra_dependencies: ["amsmath", "bm"]
-
 ---
@@
 
-Categorical data are modelled by actuaries in many different contexts, from pricing of insurance products to reserving 
-for the liabilities generated by these products. Sometimes, these data are modelled in an explicit manner, for example, 
-when building models that apply across multiple categories, a form of dummy coding is usually used. For example, when 
-building models to price the frequency of motor insurance claims, claim experience relating to different types of motor
-vehicle will often be modelled by including a (single) factor within models that modifies the relative frequency 
-predicted for each type of vehicle. In other cases, modelling is performed for each category separately, thus the 
-categorical data is used within the modelling in an implicit manner, for example, common practice is to estimate 
-reserves for different lines of business separately, meaning to say, with no parameters being shared across each of the
-reserving models.
+Categorical data are modelled by actuaries in many different contexts, from pricing of insurance products to reserving for the liabilities generated by these products.
+Sometimes, these data are modelled in an explicit manner, for example, when building models that apply across multiple categories, a form of dummy coding is usually used.
+For example, when building models to price the frequency of motor insurance claims, claim experience relating to different types of motor vehicle will often be modelled by including a (single) factor within models that modifies the relative frequency predicted for each type of vehicle.
+In other cases, modelling is performed for each category separately, thus the categorical data is used within the modelling in an implicit manner, for example, common practice is to estimate reserves for different lines of business separately, meaning to say, with no parameters being shared across each of the reserving models.
 
-Recently, several studies of insurance problems have applied an alternative approach, originally from the natural 
-known as **categorical embeddings**. Instead of trying to capture the differences between categories using a single 
-factor, the categorical embedding approach rather maps each category to a low-dimensional numeric vector, which is then
-used within the model as a new predictor variable.
+Recently, several studies of insurance problems have applied an alternative approach, originally from the natural known as **categorical embeddings**.
+Instead of trying to capture the differences between categories using a single factor, the categorical embedding approach rather maps each category to a low-dimensional numeric vector, which is then used within the model as a new predictor variable.
 
 This approach to modelling categorical data has several advantages over more traditional treatments of categorical data.
-Using categorical embeddings instead of traditional techniques has been shown to increase predictive accuracy of 
-models, for example, see [@Richman2018] in the context of pricing. Models incorporating categorical embeddings can be
-pre-calibrated to traditional actuarial models, increasing the speed with which these models can be calibrated and 
-leading to models with better explainability [@wuthrich2019yes]. Finally, the similarity between the vectors learned 
-for different categories can be inspected, sometimes leading to insights into the workings of models, see, for example,
-[@Kuo2019].
+Using categorical embeddings instead of traditional techniques has been shown to increase predictive accuracy of models, for example, see [@Richman2018] in the context of pricing.
+Models incorporating categorical embeddings can be pre-calibrated to traditional actuarial models, increasing the speed with which these models can be calibrated and leading to models with better explainability [@wuthrich2019yes].
+Finally, the similarity between the vectors learned for different categories can be inspected, sometimes leading to insights into the workings of models, see, for example, [@Kuo2019].
 
-On the other hand, several open questions about the use of embeddings within actuarial work remain, which we aim to 
-address in this study. First, hyperparameter settings for embeddings, such as the dimensions of the embedding layer and
-the use of regularization techniques such as dropout or normalization, that achieve optimal predictive performance has
-not yet been studied in detail in the actuarial literature. In this work, we aim to study how embeddings using 
-different settings perform in the context of a large-scale predictive modelling problem, and give guidance on the 
-process that can be followed to determine this in other problems. Although neural network have been shown to achieve
-excellent predictive accuracy on actuarial tasks, many actuaries still prefer to use GLM models for pricing tasks, 
-thus, the issue of whether transferring embeddings to GLM models can achieve better performance is considered in this
-paper. Traditional actuarial techniques such as credibility theory have been used to work with some types of 
-categorical data, but no study has been performed whether this can be applied within embeddings; here, we investigate
-whether performance is enhanced by applying credibility theory on embeddings relating to categorical variables with
-many labels. Whereas embedding layers are usually considered in the context of categorical data,the option exists to
-quantize numerical data and model it using embeddings, however, the results of doing so have not been investigated.
-Finally, in the past several years, a new type of neural network architecture based on attention [@Vaswani2017] has
-been successfully used on embeddings in the field of natural language processing and we incorporate attention 
-based models into our predictive modelling example.
+On the other hand, several open questions about the use of embeddings within actuarial work remain, which we aim to address in this study.
+First, hyperparameter settings for embeddings, such as the dimensions of the embedding layer and the use of regularization techniques such as dropout or normalization, that achieve optimal predictive performance has not yet been studied in detail in the actuarial literature.
+In this work, we aim to study how embeddings using different settings perform in the context of a large-scale predictive modelling problem, and give guidance on the process that can be followed to determine this in other problems.
+Although neural network have been shown to achieve excellent predictive accuracy on actuarial tasks, many actuaries still prefer to use GLM models for pricing tasks, thus, the issue of whether transferring embeddings to GLM models can achieve better performance is considered in this paper.
+Traditional actuarial techniques such as credibility theory have been used to work with some types of categorical data, but no study has been performed whether this can be applied within embeddings; here, we investigate whether performance is enhanced by applying credibility theory on embeddings relating to categorical variables with many labels.
+Whereas embedding layers are usually considered in the context of categorical data,the option exists to quantize numerical data and model it using embeddings, however, the results of doing so have not been investigated.
+Finally, in the past several years, a new type of neural network architecture based on attention [@Vaswani2017] has been successfully used on embeddings in the field of natural language processing and we incorporate attention based models into our predictive modelling example.
 
-In this work, we utilize the recently released National Flood Insurance Program (NFIP) dataset 
-[@FederalEmergencyManagementAgency2019] which provides exposure information for policies written under the NFIP since 
-XXXXDateXXXX, as well as the claims data relating to these exposures. We refer the reader to Appendix \ref{NFIP_eda} for
-an exploratory analysis of this dataset.
+In this work, we utilize the recently released National Flood Insurance Program (NFIP) dataset [@FederalEmergencyManagementAgency2019] which provides exposure information for policies written under the NFIP since XXXXDateXXXX, as well as the claims data relating to these exposures.
+We refer the reader to Appendix \ref{NFIP_eda} for an exploratory analysis of this dataset.
 
-The rest of this manuscript is organized as follows. Section \ref{lit_review} reviews recent applications of embeddings
-in the actuarial literature. Section \ref{defns} provides the notation used in the paper and defines GLMs, neural 
-networks and related modelling concepts, including embeddings and attention. In Section \ref{modelling}, we provide 
-initial models for the NFIP dataset and consider the influence of hyperparameter choices on the results of the neural 
-network model. Section \ref{tl} considers how successfully the embeddings used in the neural network model can be 
-transferred to a GLM model of the same data. Extensions to the modelling approach are considered in Section \ref{extend} 
-and we focus on attention based models in Section \ref{attention}. The interpretability of embedding layers is addressed
-in Section \ref{interpretation}. Finally, Section \ref{Conclusions} provides a discussion of the results of this paper
-and considers avenues for future research.
+The rest of this manuscript is organized as follows.
+Section \ref{lit_review} reviews recent applications of embeddings in the actuarial literature.
+Section \ref{defns} provides the notation used in the paper and defines GLMs, neural networks and related modelling concepts, including embeddings and attention.
+In Section \ref{modelling}, we provide initial models for the NFIP dataset and consider the influence of hyperparameter choices on the results of the neural network model.
+Section \ref{tl} considers how successfully the embeddings used in the neural network model can be transferred to a GLM model of the same data.
+Extensions to the modelling approach are considered in Section \ref{extend} and we focus on attention based models in Section \ref{attention}.
+The interpretability of embedding layers is addressed in Section \ref{interpretation}.
+Finally, Section \ref{Conclusions} provides a discussion of the results of this paper and considers avenues for future research.
 
@@
 
-Categorical data are usually modelled within GLMs and other predictive models using indicator variables which capture 
-the effect of each level of the category, see, for example, Section 2 in [@Goldburd], using one of two main encoding 
-schemes: dummy-coding and one-hot encoding. Dummy-coding, used in the popular \texttt{R} statistical software, assigns 
-one level of the category as a baseline, for which an indicator variable is not calibrated, and the rest of the levels 
-are assigned indicator variables, thus, producing estimates within the model of how the effects of each level differ 
-from the baselines. One-hot encoding, often used in machine learning, is similar to dummy-coding, but assigns 
-indicator variables to each level, in other words, calibrates an extra indicator variable compared with dummy-coding.
+Categorical data are usually modelled within GLMs and other predictive models using indicator variables which capture the effect of each level of the category, see, for example, Section 2 in [@Goldburd], using one of two main encoding schemes: dummy-coding and one-hot encoding.
+Dummy-coding, used in the popular \texttt{R} statistical software, assigns one level of the category as a baseline, for which an indicator variable is not calibrated, and the rest of the levels are assigned indicator variables, thus, producing estimates within the model of how the effects of each level differ from the baselines.
+One-hot encoding, often used in machine learning, is similar to dummy-coding, but assigns indicator variables to each level, in other words, calibrates an extra indicator variable compared with dummy-coding.
 
-A different approach to modelling categorical data is credibility theory (see [@Buhlmann2006] for an overview), which, 
-in the context of rating, can be applied to derive premiums that reflect the experience of a particular policyholder, by 
-estimating premiums as a weighted average between the premium produced using the collective experience (i.e. of all 
-policyholders) and the premium produced using the experience of the particular policyholder. The weight used in this 
-average is called a credibility factor and is calculated with reference to te variability of the policyholder experience 
-relative to the variability of the group experience. In this context, the implicit categorical variable is the 
-policyholder under consideration.
+A different approach to modelling categorical data is credibility theory (see [@Buhlmann2006] for an overview), which, in the context of rating, can be applied to derive premiums that reflect the experience of a particular policyholder, by estimating premiums as a weighted average between the premium produced using the collective experience (i.e.
+of all policyholders) and the premium produced using the experience of the particular policyholder.
+The weight used in this average is called a credibility factor and is calculated with reference to te variability of the policyholder experience relative to the variability of the group experience.
+In this context, the implicit categorical variable is the policyholder under consideration.
 
-Generalized Linear Mixed Models (GLMMs) are an extension of GLMs that are designed for modelling categorical data using 
-a principle very similar to that of credibility theory [@Klinker2010]. Instead of calibrating indicator variables for 
-each level of the category, GLMMs estimate effects for each of these levels as a combination of the overall group mean 
-and the experience in each level of the category.
+Generalized Linear Mixed Models (GLMMs) are an extension of GLMs that are designed for modelling categorical data using a principle very similar to that of credibility theory [@Klinker2010].
+Instead of calibrating indicator variables for each level of the category, GLMMs estimate effects for each of these levels as a combination of the overall group mean and the experience in each level of the category.
 
-Embedding layers represent a different approach to the problem of modelling categorical data that was recently 
-introduced in an actuarial context. Note that in the next section, we reflect on similarities between the conventional 
-approaches discussed above and embedding layers. [@Richman2018] reviewed the concept of embedding layers and connected 
-the sharing of information across categories to the familiar concept of credibility theory. In that work, two 
-applications of embedding layers were demonstrated. The first of these was in a Property and Casualty (P&C) pricing 
-context, it was shown that the out-of-sample accuracy of a neural network trained to predict claims frequencies on motor 
-third party liability was enhanced by modelling the categorical variables within this dataset using embedding layers. 
-Second, a neural network with embedding layers was used to model all of the mortality rates in the Human Mortality 
-Database, where the differences in population mortality across countries and the differences in mortality at different 
-ages were modelled with embedding layers, again producing more accurate out of sample performance than the other models 
-tested.
+Embedding layers represent a different approach to the problem of modelling categorical data that was recently introduced in an actuarial context.
+Note that in the next section, we reflect on similarities between the conventional approaches discussed above and embedding layers.
+[@Richman2018] reviewed the concept of embedding layers and connected the sharing of information across categories to the familiar concept of credibility theory.
+In that work, two applications of embedding layers were demonstrated.
+The first of these was in a Property and Casualty (P&C) pricing context, it was shown that the out-of-sample accuracy of a neural network trained to predict claims frequencies on motor third party liability was enhanced by modelling the categorical variables within this dataset using embedding layers.
+Second, a neural network with embedding layers was used to model all of the mortality rates in the Human Mortality Database, where the differences in population mortality across countries and the differences in mortality at different ages were modelled with embedding layers, again producing more accurate out of sample performance than the other models tested.
 
-Contemporaneous with that work is the DeepTriangle model of [@Kuo2019], which applied recurrent neural networks to the 
-problem of Incurred but not Reported (IBNR) loss reserving, to model jointly the paid and incurred losses in the 
-Schedule P dataset. Embedding layers were used to capture the effect of differences in reserving delays and loss ratios 
-for each company in the Schedule P dataset. Evaluating the results of the DeepTriangle method showed that the out of 
-sample performance of the model (tested against the lower triangles in the Schedule P dataset) exceeded that of 
-traditional IBNR reserving techniques.
+Contemporaneous with that work is the DeepTriangle model of [@Kuo2019], which applied recurrent neural networks to the problem of Incurred but not Reported (IBNR) loss reserving, to model jointly the paid and incurred losses in the Schedule P dataset.
+Embedding layers were used to capture the effect of differences in reserving delays and loss ratios for each company in the Schedule P dataset.
+Evaluating the results of the DeepTriangle method showed that the out of sample performance of the model (tested against the lower triangles in the Schedule P dataset) exceeded that of traditional IBNR reserving techniques.
 
-Many other applications of embeddings have subsequently appeared in the actuarial literature. Within mortality 
-forecasting, [@Richman2019d] and [@Richman2020] both apply embeddings layers to model and forecast mortality rates on a 
-large scale. [@wuthrich2019yes] discussed how embeddings can be calibrated using GLM techniques and then incorporated 
-into a combined actuarial neural network, with subsequent contributions in P&C pricing by [@schelldorfer2019nesting] and 
-in IBNR reserving by [@Gabrielli2019c] and [@Gabrielli2019]. Other applications in IBNR reserving are in [@Kuo2020] and 
-[@Delong2020a] who use embedding layers to model individual claims development.
+Many other applications of embeddings have subsequently appeared in the actuarial literature.
+Within mortality forecasting, [@Richman2019d] and [@Richman2020] both apply embeddings layers to model and forecast mortality rates on a large scale.
+[@wuthrich2019yes] discussed how embeddings can be calibrated using GLM techniques and then incorporated into a combined actuarial neural network, with subsequent contributions in P&C pricing by [@schelldorfer2019nesting] and in IBNR reserving by [@Gabrielli2019c] and [@Gabrielli2019].
+Other applications in IBNR reserving are in [@Kuo2020] and [@Delong2020a] who use embedding layers to model individual claims development.
 
@@
 
-In this study, we are concerned with regression modelling, which is the task of predicting an unknown outcome $y$ on the 
-basis of information about that outcome contained in predictor variables, or features, stored in a matrix $X$. For 
-simplicity, we only consider the case of univariate outcomes, i.e., $y \in \mathbb{R}^1$. The outcomes and the rows of 
-the predictor variable matrix are indexed by $i \in \{1 \dots I\}$, where $i$ represents a particular observation of 
-$(y_i, \mathbf{x}_i)$, where bold indicates that we are now dealing with a vector. The columns of the predictor 
-variables are indexed by $j \in \{1 \dots J\}$, where $j$ represents a particular predictor variable, of which $J$ have 
-been observed, thus, we use the notation $X_j$ to represent the $j$th predictor variable and $X \in \mathbb{R}^J$. 
-Formally, we look to build regression models that map from the predictor variables $\mathbf{x}_i$ to the outcome $y$ 
-using a function $f$ of the form:
+In this study, we are concerned with regression modelling, which is the task of predicting an unknown outcome $y$ on the basis of information about that outcome contained in predictor variables, or features, stored in a matrix $X$.
+For simplicity, we only consider the case of univariate outcomes, i.e., $y \in \mathbb{R}^1$.
+The outcomes and the rows of the predictor variable matrix are indexed by $i \in \{1 \dots I\}$, where $i$ represents a particular observation of $(y_i, \mathbf{x}_i)$, where bold indicates that we are now dealing with a vector.
+The columns of the predictor variables are indexed by $j \in \{1 \dots J\}$, where $j$ represents a particular predictor variable, of which $J$ have been observed, thus, we use the notation $X_j$ to represent the $j$th predictor variable and $X \in \mathbb{R}^J$.
+Formally, we look to build regression models that map from the predictor variables $\mathbf{x}_i$ to the outcome $y$ using a function $f$ of the form:
 
@@
 
-The predictor variables that we consider here are comprised of two types: continuous variables, taking on numerical 
-values and represented by the matrix $X_{num}$ with $J^{num}$ columns, and categorical variables, which take on 
-discrete values indicating one of several possible categories, represented by the matrix $X_{cat}$ with $J^{cat}$ 
-columns, such that $J^{num} + J^{cat} = J$.
+The predictor variables that we consider here are comprised of two types: continuous variables, taking on numerical values and represented by the matrix $X_{num}$ with $J^{num}$ columns, and categorical variables, which take on discrete values indicating one of several possible categories, represented by the matrix $X_{cat}$ with $J^{cat}$ columns, such that $J^{num} + J^{cat} = J$.
 
@@
 
-A categorical variable $X_j, j \in J_{cat}$ takes as its value only one of a finite number of labels. Let the set of 
-labels be $\mathcal{P}^j = \{p^j_1, p^j_2,\dots, p^j_{n_{\mathcal{P}^j}} \}$, where $n_\mathcal{P}^j = |\mathcal{P}^j|$ 
-is the cardinality or number of levels, in $\mathcal{P}^j$. One-hot encoding maps each value $x_{i,j}$ of $X_j$ to 
-$n_\mathcal{P}^j$ indicator variables, which take a value of $1$ if the label of $x_{i,j}$ corresponds to the level of 
-the indicator variable, and $0$ otherwise. An example of one-hot encoding is shown in Table \ref{onehot}.
+A categorical variable $X_j, j \in J_{cat}$ takes as its value only one of a finite number of labels.
+Let the set of labels be $\mathcal{P}^j = \{p^j_1, p^j_2,\dots, p^j_{n_{\mathcal{P}^j}} \}$, where $n_\mathcal{P}^j = |\mathcal{P}^j|$ is the cardinality or number of levels, in $\mathcal{P}^j$.
+One-hot encoding maps each value $x_{i,j}$ of $X_j$ to $n_\mathcal{P}^j$ indicator variables, which take a value of $1$ if the label of $x_{i,j}$ corresponds to the level of the indicator variable, and $0$ otherwise.
+An example of one-hot encoding is shown in Table \ref{onehot}.
 
@@
 
-One-hot encoding is often used in the machine learning community while the statistical community often favors dummy 
-coding, which, instead of assigning $n_p^j$ indicator variables, assigns one of the levels of the categories as a 
-baseline, and maps all of the other $n_p^j -1$ variables to indicator variables. An example of dummy encoding is shown 
-in Table \ref{dummy}.
+One-hot encoding is often used in the machine learning community while the statistical community often favors dummy coding, which, instead of assigning $n_p^j$ indicator variables, assigns one of the levels of the categories as a baseline, and maps all of the other $n_p^j -1$ variables to indicator variables.
+An example of dummy encoding is shown in Table \ref{dummy}.
 
@@
 
-After encoding the categorical data in this manner, most regression models such as GLMs will then fit coefficients for 
-each level of the category in the table (if a tree based model is used, such as decision tree, then splits in the tree 
-may occur depending on the presence, or not, of the categorical variable for the data). If one-hot encoding has been 
-used, $n_\mathcal{P}^j$ coefficients will be fit, compared to $n_\mathcal{P}^j - 1$ coefficients in the case of dummy 
-coding.
+After encoding the categorical data in this manner, most regression models such as GLMs will then fit coefficients for each level of the category in the table (if a tree based model is used, such as decision tree, then splits in the tree may occur depending on the presence, or not, of the categorical variable for the data).
+If one-hot encoding has been used, $n_\mathcal{P}^j$ coefficients will be fit, compared to $n_\mathcal{P}^j - 1$ coefficients in the case of dummy coding.
 
-These coefficients represent the effect that each level of the categorical variable will have on the outcome. In the 
-case that there are no other variables available in the dataset, then the coefficients will reflect the average value of 
-the outcomes for that level of the categorical variable. For example, suppose that the categorical variable is a 
-policyholder identifier, and the outcomes are the value of claims in different years, then the coefficients will reflect 
-the average annual claims for each policyholder based on the experience. In other words, both of these encoding schemes 
-give full credibility to the data available for each category, thus, even if a relatively small amount of data is 
-available for a specific policyholder, the coefficient that is calibrated will only reflect that data. On the other 
-hand, a foundational technique within actuarial work is the application of credibility methods, which are used for 
-experience rating and other applications. These techniques provide an estimate that reflects not only the experience of 
-the individual policyholder but also that of the collective, based on an estimate of how credible the data for each 
-individual is. While we have described the application of credibility in a simple univariate context, it is also 
-possible to apply credibility considerations within GLMs. using models known as Generalized Linear Mixed Models or 
-GLMMs, and we refer to [@Klinker2010] for more details.
+These coefficients represent the effect that each level of the categorical variable will have on the outcome.
+In the case that there are no other variables available in the dataset, then the coefficients will reflect the average value of the outcomes for that level of the categorical variable.
+For example, suppose that the categorical variable is a policyholder identifier, and the outcomes are the value of claims in different years, then the coefficients will reflect the average annual claims for each policyholder based on the experience.
+In other words, both of these encoding schemes give full credibility to the data available for each category, thus, even if a relatively small amount of data is available for a specific policyholder, the coefficient that is calibrated will only reflect that data.
+On the other hand, a foundational technique within actuarial work is the application of credibility methods, which are used for experience rating and other applications.
+These techniques provide an estimate that reflects not only the experience of the individual policyholder but also that of the collective, based on an estimate of how credible the data for each individual is.
+While we have described the application of credibility in a simple univariate context, it is also possible to apply credibility considerations within GLMs.
+using models known as Generalized Linear Mixed Models or GLMMs, and we refer to [@Klinker2010] for more details.
 
-Having described traditional approaches for modeling categorical data, we now turn to neural networks, and discuss 
-embedding layers for categorical data modeling, which we define in more detail in the section on neural networks.
+Having described traditional approaches for modeling categorical data, we now turn to neural networks, and discuss embedding layers for categorical data modeling, which we define in more detail in the section on neural networks.
 
@@
 
-Neural networks are flexible machine learning models that have recently been applied to a number of problems with 
-Property and Casualty (P&C) insurance. Here, we provide a brief overview of these models, and refer the reader to 
-[@Richman2018] for a more detailed overview. Neural networks are characterized by multiple layers of non-linear 
-regression functions that are used to learn a new representation of the data input to the network that is then used to 
-make predictions. Here we focus on the most common type of neural networks, which are fully connected networks (FCNs), 
-which provide as the output of each set of non-linear functions to the subsequent layer of functions. Formally, a 
-$K$-layer neural network is:
+Neural networks are flexible machine learning models that have recently been applied to a number of problems with Property and Casualty (P&C) insurance.
+Here, we provide a brief overview of these models, and refer the reader to [@Richman2018] for a more detailed overview.
+Neural networks are characterized by multiple layers of non-linear regression functions that are used to learn a new representation of the data input to the network that is then used to make predictions.
+Here we focus on the most common type of neural networks, which are fully connected networks (FCNs), which provide as the output of each set of non-linear functions to the subsequent layer of functions.
+Formally, a $K$-layer neural network is:
 
+```{=tex}
 \begin{equation} 
@@
 \end{equation}
-
-where the regression parameters (weights) for each layer $$k \in [1;K]$$ are represented by the matrices $a_k$ and the 
-intercept terms are represented by $b_k$. Whereas the calculation inside each of the layers is nothing more than linear 
-regression, $\sigma$ represents the non-linear part of each layer. Choices for $\sigma$ are often the tanh function or 
-the rectified linear unit (ReLu) $max(0,x)$. The parameters of the network are estimated ('trained') as follows. First a 
-loss function $L(.,.)$ is specified for the network that measures the difference between the observed data $y$ and the 
-predictions of the network $\hat{y}$, for example, the Mean Squared Error ($(y - \hat{y})^2$). Then, the parameters of 
-the network are changed such that the loss decreases (formally, this is done using the technique of backpropagation).
+```
+where the regression parameters (weights) for each layer $$k \in [1;K]$$ are represented by the matrices $a_k$ and the intercept terms are represented by $b_k$.
+Whereas the calculation inside each of the layers is nothing more than linear regression, $\sigma$ represents the non-linear part of each layer.
+Choices for $\sigma$ are often the tanh function or the rectified linear unit (ReLu) $max(0,x)$.
+The parameters of the network are estimated ('trained') as follows.
+First a loss function $L(.,.)$ is specified for the network that measures the difference between the observed data $y$ and the predictions of the network $\hat{y}$, for example, the Mean Squared Error ($(y - \hat{y})^2$).
+Then, the parameters of the network are changed such that the loss decreases (formally, this is done using the technique of backpropagation).
 Finally, training is stopped once the predictive performance of the network on unseen data is suitably good.
 
-If $K$ is set equal to $1$, then Equation \ref{NN} reduced to nothing more than a GLM. A neural network with $K=2$ is 
-called a shallow neural network and for $K \geq 2$, the network is called a deep neural network. The matrix $X$ of data 
-input to the network can be composed of both continuous variables as well as categorical variables, which can be 
-pre-processed using one-hot or dummy encoding. As mentioned above, a different option is to use encodings, which we 
-discuss in more detail next.
+If $K$ is set equal to $1$, then Equation \ref{NN} reduced to nothing more than a GLM.
+A neural network with $K=2$ is called a shallow neural network and for $K \geq 2$, the network is called a deep neural network.
+The matrix $X$ of data input to the network can be composed of both continuous variables as well as categorical variables, which can be pre-processed using one-hot or dummy encoding.
+As mentioned above, a different option is to use encodings, which we discuss in more detail next.
 
@@
 
-Common issues with the traditional encoding schemes for categorical data occur when the number of levels for each 
-variable is very large. Often, in these cases, models do not converge quickly, and the very large matrices that result 
-from applying these schemes often cause computational difficulties. Besides for these practical issues, a deeper issue 
-is that one-hot or dummy encoded data assumes that each category is entirely independent of the rest of the categories, 
-in other words, there are no similarities between categories that could enable more robust estimation of models. In 
-technical terms, this is because the columns of the matrices created by one-hot encoding are all orthogonal to each 
-other. (These arguments appear in a similar form in [@Guo2016].) Solutions to these problems are provided by embedding 
-layers.
+Common issues with the traditional encoding schemes for categorical data occur when the number of levels for each variable is very large.
+Often, in these cases, models do not converge quickly, and the very large matrices that result from applying these schemes often cause computational difficulties.
+Besides for these practical issues, a deeper issue is that one-hot or dummy encoded data assumes that each category is entirely independent of the rest of the categories, in other words, there are no similarities between categories that could enable more robust estimation of models.
+In technical terms, this is because the columns of the matrices created by one-hot encoding are all orthogonal to each other.
+(These arguments appear in a similar form in [@Guo2016].) Solutions to these problems are provided by embedding layers.
 
-An embedding layer is a neural network component which maps each level of the categorical data to a low dimensional 
-vector of parameters that is learned together with the rest of the GLM or neural network that is used for the modeling 
-problem. Formally, an embedding is
+An embedding layer is a neural network component which maps each level of the categorical data to a low dimensional vector of parameters that is learned together with the rest of the GLM or neural network that is used for the modeling problem.
+Formally, an embedding is
 
@@
 
-where $q_\mathcal{P^j}$ is the dimension of the embedding for the $j$th categorical variable and $z_\mathcal{P^j}(.)$ is 
-a function that maps from the particular element of the labels $p$ to the embedding space. Equation \ref{eq:embedding} 
-states that an embedding maps a level of a categrical variable to a numerical vector. This function is left implicit, 
-meaning to say, we allow the embeddings to be derived during the process of fitting the model and do not attempt to 
-specify exactly how the embeddings can be derived from the input data. In Table \ref{embed} we show an example of two 
-dimensional embeddings for the state variables, where these have been generated randomly.
+where $q_\mathcal{P^j}$ is the dimension of the embedding for the $j$th categorical variable and $z_\mathcal{P^j}(.)$ is a function that maps from the particular element of the labels $p$ to the embedding space.
+Equation \ref{eq:embedding} states that an embedding maps a level of a categrical variable to a numerical vector.
+This function is left implicit, meaning to say, we allow the embeddings to be derived during the process of fitting the model and do not attempt to specify exactly how the embeddings can be derived from the input data.
+In Table \ref{embed} we show an example of two dimensional embeddings for the state variables, where these have been generated randomly.
 
@@
 
-When applying embeddings in a data modeling context using neural networks, the values of the embeddings will be 
-calibrated during the same fitting process that calibrates the parameters of the neural network.
+When applying embeddings in a data modeling context using neural networks, the values of the embeddings will be calibrated during the same fitting process that calibrates the parameters of the neural network.
+The following equation shows how the first layer of a neural network incorporating embeddings might be written:
+
+```{=tex}
+\begin{equation}
+  z^1 = \sigma(a_1.X'+ b_1), 
+\end{equation}
+```
+where we represent the output of embedding layers concatenated together with any numerical inputs as $X'$.
 
 ### Attention {#attention}
+
 Attention mechanisms have been widely applied within the deep learning literature to give more flexibility to RNNs [@Bahdanau2015a] and subsequently as a replacement for FCNs in the so-called Transformer architecture, which is now widely used in natural language processing [@Vaswani2017a], and, more recently, has been applied to computer vision and tabular modelling tasks.
 Attention mechanisms allow deep neural nets to choose covariates entering the model in a flexible manner; these types of applications are demonstrated in, for example, [@Vaswani2017a].
-In this section we provide an introduction to attention mechanisms and then discuss applications of attention to modeling tabular data .
+In this section we provide an introduction to attention mechanisms and then discuss applications of attention to modeling tabular data.
 
@@
 \mathbb{R}^{(1 \times q) \times (q \times d)} \to \mathbb{R}^{1 \times d}, ~~
-  (\bold{q}, K) ~\mapsto ~ \mathbf{a} = \langle \mathbf{q}, K^T \mathbb{R}angle.
+(\bold{q}, K) ~\mapsto ~ \mathbf{a} = \langle \mathbf{q}, K^T \mathbb\rangle.
 \label{eq:attention_scores}
@@
 \mathbb{R}^{(1 \times d) \times (d \times q)} \to \mathbb{R}^{1 \times q}, ~~
-  (\mathbf{a^*}, V) ~\mapsto ~ \mathbf{v} = \langle \mathbf{a^*}, V \mathbb{R}angle.
+(\mathbf{a^*}, V) ~\mapsto ~ \mathbf{v} = \langle \mathbf{a^*}, V \mathbb\rangle.
 \label{eq:attention_output}
@@
 ```
-
 # Predictive Modeling with Embeddings
 
-In this section, we walk through a simple predictive modeling exercise in order to illustrate the application of 
-embeddings. First, we pose a supervised regression problem, based on flood insurance claims severity. We then describe, 
-fit, and evaluate GLMs and neural networks utilizing embeddings for this problem. Finally, we discuss visualization 
-techniques for model interpretation. As we proceed, we also incorporate practical technical guidance on modeling
-procedure.
+In this section, we walk through a simple predictive modeling exercise in order to illustrate the application of embeddings.
+First, we pose a supervised regression problem, based on flood insurance claims severity.
+We then describe, fit, and evaluate GLMs and neural networks utilizing embeddings for this problem.
+Finally, we discuss visualization techniques for model interpretation.
+As we proceed, we also incorporate practical technical guidance on modeling procedure.
 
@@
 
-The working example for our experiments is as follows: Given a set of claim characteristics, we predict the losses paid 
-on the property coverage of the policy. The data we use comes from the National Flood Insurance Program (NFIP) and is 
-made available by the OpenFEMA initiative 
-of the Federal Emergency Management Agency (FEMA)[^9]. Two datasets are made available by OpenFEMA: A policies dataset 
-with exposure information, and a claims dataset with claims transactions, including paid amounts. Because there is no 
-way to associate records of the two datasets, we are limited to fitting severity models on the claims dataset. While the 
-complete dataset contains over two million transactions, for the purposes of our experiments we limit ourselves to data 
-from 2000 to August 2019, which amounts to approximately 1.4 million claims. The dataset can be downloaded from 
-Cellar[^10] The dataset includes a rich variety of variables, from occupancy type to coarse coordinates. For our models, 
-we work with a few selected variables that represent continuous and discrete variables of low and high cardinalities, 
-which we list in Table \@ref(tab:variables)
+The working example for our experiments is as follows: Given a set of claim characteristics, we predict the losses paid on the property coverage of the policy.
+The data we use comes from the National Flood Insurance Program (NFIP) and is made available by the OpenFEMA initiative of the Federal Emergency Management Agency (FEMA)[^1].
+Two datasets are made available by OpenFEMA: A policies dataset with exposure information, and a claims dataset with claims transactions, including paid amounts.
+Because there is no way to associate records of the two datasets, we are limited to fitting severity models on the claims dataset.
+While the complete dataset contains over two million transactions, for the purposes of our experiments we limit ourselves to data from 2000 to August 2019, which amounts to approximately 1.4 million claims.
+The dataset can be downloaded from Cellar[^2] The dataset includes a rich variety of variables, from occupancy type to coarse coordinates.
+For our models, we work with a few selected variables that represent continuous and discrete variables of low and high cardinalities, which we list in Table \@ref(tab:variables)
 
-[^9]: https://www.fema.gov/about/reports-and-data/openfema
-[^10]: https://cellar.kasa.ai
+[^1]: <https://www.fema.gov/about/reports-and-data/openfema>
+
+[^2]: <https://cellar.kasa.ai>
 
@@
 
-These model architectures are relatively uncomplicated by today's standards, and are so chosen to better highlight the
-embedding components. Later, in Section X (TODO), we will investigate more involved architectures utilizing embeddings
-that represent the state of the art for modeling tabular data.
+These model architectures are relatively uncomplicated by today's standards, and are so chosen to better highlight the embedding components.
+Later, in Section X (TODO), we will investigate more involved architectures utilizing embeddings that represent the state of the art for modeling tabular data.
 
@@
 
-While this paper focuses on embeddings in neural networks, we begin with a GLM to provide a common frame of 
-reference since most actuaries are familiar with the technique. 
-Although GLMs are commonplace and well-studied in the actuarial literature, there are still plenty of decisions to 
-be made in the modeling process; see, for example, @Goldburd for an in-depth discussion. For our purpose of 
-establishing a baseline, we proceed with what we perceive as reasonable decisions around feature engineering and model structure, outlined below:
+While this paper focuses on embeddings in neural networks, we begin with a GLM to provide a common frame of reference since most actuaries are familiar with the technique.
+Although GLMs are commonplace and well-studied in the actuarial literature, there are still plenty of decisions to be made in the modeling process; see, for example, @Goldburd for an in-depth discussion.
+For our purpose of establishing a baseline, we proceed with what we perceive as reasonable decisions around feature engineering and model structure, outlined below:
 
 -   Target variable: Amount paid on building claim
+
 -   Predictors:
+
     -   $\log$ `building_insurance_coverage`
@@
     -   `primary_residence`
+
 -   Link function: $\log$
+
 -   Distribution: gamma
 
-We take the log of the continuous predictor `building_insurance_coverage`, which allows the scale of the predictor to 
-match that of the target variable. Because the `flood_zone` variable in the original data contains 60 levels, we take 
-the prefix of the zone code, which corresponds to the level of risk as determined by FEMA [^8]. For example, `"A01"`, 
-`"A02"`, and so on are recoded as simply `"A"`.
+We take the log of the continuous predictor `building_insurance_coverage`, which allows the scale of the predictor to match that of the target variable.
+Because the `flood_zone` variable in the original data contains 60 levels, we take the prefix of the zone code, which corresponds to the level of risk as determined by FEMA [^3].
+For example, `"A01"`, `"A02"`, and so on are recoded as simply `"A"`.
 
-[^8]: https://www.floodsmart.gov/flood-map-zone/find-yours
+[^3]: <https://www.floodsmart.gov/flood-map-zone/find-yours>
 
-A log link together with the gamma distribution is a standard choice for severity modeling, which provides a 
-multiplicative structure where the response is positive.
+A log link together with the gamma distribution is a standard choice for severity modeling, which provides a multiplicative structure where the response is positive.
 
@@
 
-For Model 2, we build a feedforward neural network. The categorical inputs go through one-dimensional embedding
-layers where they are each mapped to a scalar. The embeddings are then concatenated with the numeric predictors, which
-have been normalized in data pre-processing, before being sent to a hidden linear layer of 16 units. A ReLU (TODO: reference an equation in prev. section) activation
-is then applied to the outputs before they are sent to a final output layer resulting in a scalar. To constrain
-predictions to be positive, we apply softplus activation, which is defined to be
+For Model 2, we build a feedforward neural network.
+The categorical inputs go through one-dimensional embedding layers where they are each mapped to a scalar.
+The embeddings are then concatenated with the numeric predictors, which have been normalized in data pre-processing, before being sent to a hidden linear layer of 16 units.
+A ReLU (TODO: reference an equation in prev.
+section) activation is then applied to the outputs before they are sent to a final output layer resulting in a scalar.
+To constrain predictions to be positive, we apply softplus activation, which is defined to be
 
@@
 
-With a single hidden layer, this architecture is the simplest nontrivial neural network; without the hidden layer and
-corresponding ReLU activation, we would actually recover a GLM structure where the link function is the output activation. 
-The choice of one for the embedding dimension is also due to simplicity: it is easily interpretable as the representation
-of each factor level as a point on the real number line, also, the trained embeddings are easily incorporated into a GLM
-which we will see in Model 3. In practice, the embedding dimension is a hyperparameter one can tune, for example via
-cross validation, and can vary for each variable. However, we also note that the choice of one for the 
-embedding output dimension is not an unreasonable one, especially when the cardinalities of the categorical variables
-are not unusually large.
+With a single hidden layer, this architecture is the simplest nontrivial neural network; without the hidden layer and corresponding ReLU activation, we would actually recover a GLM structure where the link function is the output activation.
+The choice of one for the embedding dimension is also due to simplicity: it is easily interpretable as the representation of each factor level as a point on the real number line, also, the trained embeddings are easily incorporated into a GLM which we will see in Model 3.
+In practice, the embedding dimension is a hyperparameter one can tune, for example via cross validation, and can vary for each variable.
+However, we also note that the choice of one for the embedding output dimension is not an unreasonable one, especially when the cardinalities of the categorical variables are not unusually large.
 
@@
 
-For Model 3, we return to the GLM, but now we replace the categorical variables with the trained embeddings from Model
-2. In other words, our model now contains only continuous variables, and each categorical factor is represented as a
-scalar value and obtains its own coefficient. (TODO: insert formal eqn for mean)
+For Model 3, we return to the GLM, but now we replace the categorical variables with the trained embeddings from Model 2.
+In other words, our model now contains only continuous variables, and each categorical factor is represented as a scalar value and obtains its own coefficient.
+(TODO: insert formal eqn for mean)
 
@@
 
-To evaluate these baseline models and other models in this paper, we perform 10-fold 
-cross validation and compare the 
-root mean square error (RMSE) on the predicted and actual paid amounts.
-(somehwere we should say we're not doing a kaggle competition here and the performance metrics are really meant
-to show that the models aren't complete shit)
-(maybe a couple boxplots showing metrics for baseline models)
+To evaluate these baseline models and other models in this paper, we perform 10-fold cross validation and compare the root mean square error (RMSE) on the predicted and actual paid amounts.
+(somehwere we should say we're not doing a kaggle competition here and the performance metrics are really meant to show that the models aren't complete shit) (maybe a couple boxplots showing metrics for baseline models)
 
@@
 
-Investigate approaches for using embedding layers for numeric variables, or numeric variables that were captured as 
-categorical variables (Can the modelling of numerical variables benefit from the application of embedding layers?) How 
-should this best be done? CatBoost - cut into 256 groups smoothness Map numeric to a dense layer and use that as 
-embedding - basis expansion Add a distribution to the embeddings Can insights from credibility theory lead to enhanced embeddings?
+Investigate approaches for using embedding layers for numeric variables, or numeric variables that were captured as categorical variables (Can the modelling of numerical variables benefit from the application of embedding layers?) How should this best be done?
+CatBoost - cut into 256 groups smoothness Map numeric to a dense layer and use that as embedding - basis expansion Add a distribution to the embeddings Can insights from credibility theory lead to enhanced embeddings?
 Take credibility mixture over embeddings Cluster embeddings PCA of embeddings
@@
 
-Description of tabnet, talk about how it's related to embeddings, show some plots 
-like \@ref(fig:masks) etc.
+Description of tabnet, talk about how it's related to embeddings, show some plots like \@ref(fig:masks) etc.
 

### 2021-03-10 manuscript/manuscript.Rmd
add ron's embeddings additions

--- 2021-03-10 manuscript/manuscript.Rmd
@@
     base_format: rticles::arxiv_article
-extra_dependencies: ["amsmath", "bm"]
-
+header-includes: |
+    \usepackage{amsmath}
+    \usepackage{mathtools}
+    \usepackage{bm}
+    \DeclarePairedDelimiter\ceil{\lceil}{\rceil}
 ---
@@
 
-When applying embeddings in a data modeling context using neural networks, the values of the embeddings will be 
-calibrated during the same fitting process that calibrates the parameters of the neural network.
+When applying embeddings in a data modeling context using neural networks, the values of the embeddings will be calibrated during the same fitting process that calibrates the parameters of the neural network.
+The following equation shows how the first layer of a neural network incorporating embeddings might be written:
+
+```{=latex}
+\begin{equation}
+  z^1 = \sigma(a_1.X'+ b_1), 
+\end{equation}
+```
+where we represent the output of embedding layers concatenated together with any numerical inputs as $X'$.
 
 ### Attention {#attention}
+
 Attention mechanisms have been widely applied within the deep learning literature to give more flexibility to RNNs [@Bahdanau2015a] and subsequently as a replacement for FCNs in the so-called Transformer architecture, which is now widely used in natural language processing [@Vaswani2017a], and, more recently, has been applied to computer vision and tabular modelling tasks.
 Attention mechanisms allow deep neural nets to choose covariates entering the model in a flexible manner; these types of applications are demonstrated in, for example, [@Vaswani2017a].
-In this section we provide an introduction to attention mechanisms and then discuss applications of attention to modeling tabular data .
+In this section we provide an introduction to attention mechanisms and then discuss applications of attention to modeling tabular data.
 
@@
 
-  ```{=tex}
+```{=latex}
 \begin{equation}
@@
 
-  ```{=tex}
+```{=latex}
 \begin{equation}
 \mathbb{R}^{(1 \times q) \times (q \times d)} \to \mathbb{R}^{1 \times d}, ~~
-  (\bold{q}, K) ~\mapsto ~ \mathbf{a} = \langle \mathbf{q}, K^T \mathbb{R}angle.
+(\bold{q}, K) ~\mapsto ~ \mathbf{a} = \langle \mathbf{q}, K^T \mathbb\rangle.
 \label{eq:attention_scores}
@@
 
-```{=tex}
+```{=latex}
 \begin{equation}
@@
 
-  ```{=tex}
+```{=latex}
 \begin{equation}
 \mathbb{R}^{(1 \times d) \times (d \times q)} \to \mathbb{R}^{1 \times q}, ~~
-  (\mathbf{a^*}, V) ~\mapsto ~ \mathbf{v} = \langle \mathbf{a^*}, V \mathbb{R}angle.
+(\mathbf{a^*}, V) ~\mapsto ~ \mathbf{v} = \langle \mathbf{a^*}, V \mathbb\rangle.
 \label{eq:attention_output}

### 2021-03-10 manuscript/manuscript.Rmd
lint

@@
 
-states= fread("../manuscript/states.csv")
+states <- fread("../manuscript/states.csv")
 set.seed(42)
-sample_dat = sample_n(states,5) %>% arrange(state)
+sample_dat <- sample_n(states, 5) %>% arrange(state)
 
-rec = recipe(~state, data = sample_dat)
+rec <- recipe(~state, data = sample_dat)
 
-dummies <- rec %>% step_dummy(state, one_hot =T)
+dummies <- rec %>% step_dummy(state, one_hot = TRUE)
 dummies <- prep(dummies, training = sample_dat)
 
-dummy_data <- bake(dummies, new_data =sample_dat)
+dummy_data <- bake(dummies, new_data = sample_dat)
 
@@
 
-states= fread("../manuscript/states.csv")
+states <- fread("../manuscript/states.csv")
 set.seed(42)
 
-sample_dat = sample_n(states,5) %>% arrange(state)
+sample_dat <- sample_n(states, 5) %>% arrange(state)
 
-rec = recipe(~state, data = sample_dat)
+rec <- recipe(~state, data = sample_dat)
 
-dummies <- rec %>% step_dummy(state, one_hot =F)
+dummies <- rec %>% step_dummy(state, one_hot = FALSE)
 dummies <- prep(dummies, training = sample_dat)
 
-dummy_data <- bake(dummies, new_data =sample_dat)
+dummy_data <- bake(dummies, new_data = sample_dat)
 
@@
   knitr::kable(label = "dummy", caption = "Example dummy encoding of the state variable")
-
 ```
@@
 ```
+
 where $\mathbf{q} \in \mathbb{R}^q$ is a query vector, $K \in \mathbb{R}^{q \times d}$ is a matrix of key vectors, $V \in \mathbb{R}^{q \times d}$ is a matrix of value vectors and $\mathbf{v} \in \mathbb{R}^q$, the output of the attention mechanism, is a new vector of values.

### 2021-03-10 R/cv-model-torch.R
cuda

@@ -99,7 +99,7 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
         step_log(total_building_insurance_coverage) %>%
         prep(strings_as_factors = FALSE)
 
-    key <- key_with_embeddings(model$embedder$embeddings, rec_nn$steps[[4]]$key)
+    key <- key_with_embeddings(model$embedder$embeddings, rec_nn$steps[[3]]$key)
     model_glm2 <- glm(form,
         family = Gamma(link = log), data = map_cats_to_embeddings(juice(rec_glm2), key),
         control = list(maxit = 100)
@@ -129,7 +129,7 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 }
 
 cv_results <- cvfolds$splits %>%
-    lapply(function(x) model_analyze_assess(x, 0.01, 1, 1100))
+    lapply(function(x) model_analyze_assess(x, 0.01, 1, 2000))
 
 cv_results %>%
     map(function(x) {

### 2021-03-10 R/model-utils.R

@@ -70,6 +70,8 @@ simple_net <- nn_module(
             sum()
         self$fc <- nn_linear(sum_embedding_dim + num_numerical, units)
         self$output <- nn_linear(units, 1)
+        device <- if (cuda_is_available()) torch_device("cuda:0") else "cpu"
+        self$to(device = device)
     },
     forward = function(xcat, xnum) {
         embedded <- self$embedder(xcat)
@@ -130,14 +132,15 @@ train_loop_alternate <- function(model, train_dl, valid_dl, epochs, optimizer) {
 }
 
 train_loop <- function(model, train_dl, valid_dl, epochs, optimizer) {
+    device <- if (cuda_is_available()) torch_device("cuda:0") else "cpu"
     for (epoch in seq_len(epochs)) {
         model$train()
         train_losses <- c()
 
         for (b in enumerate(train_dl)) {
             optimizer$zero_grad()
-            output <- model(b$x[[1]], b$x[[2]])
-            loss <- nnf_mse_loss(output, b$y)
+            output <- model(b$x[[1]]$to(device = device), b$x[[2]]$to(device = device))
+            loss <- nnf_mse_loss(output, b$y$to(device = device))
             loss$backward()
             optimizer$step()
             train_losses <- c(train_losses, loss$item())
@@ -147,8 +150,8 @@ train_loop <- function(model, train_dl, valid_dl, epochs, optimizer) {
         valid_losses <- c()
 
         for (b in enumerate(valid_dl)) {
-            output <- model(b$x[[1]], b$x[[2]])
-            loss <- nnf_mse_loss(output, b$y)
+            output <- model(b$x[[1]]$to(device = device), b$x[[2]]$to(device = device))
+            loss <- nnf_mse_loss(output, b$y$to(device = device))
             valid_losses <- c(valid_losses, loss$item())
         }
 
@@ -160,9 +163,13 @@ train_loop <- function(model, train_dl, valid_dl, epochs, optimizer) {
 }
 
 get_preds <- function(model, dl) {
+    device <- if (cuda_is_available()) torch_device("cuda:0") else "cpu"
     preds <- numeric(0)
     for (b in enumerate(dl)) {
-        preds <- c(preds, model(b$x[[1]], b$x[[2]]) %>% as.array())
+        preds <- c(
+            preds,
+            model(b$x[[1]]$to(device = device), b$x[[2]]$to(device = device))$to(device = "cpu") %>% as.array()
+        )
     }
     preds
 }
[…]

### 2021-03-11 manuscript/manuscript.Rmd
embedding tables

@@
 
-When applying embeddings in a data modeling context using neural networks, the values of the embeddings will be calibrated during the same fitting process that calibrates the parameters of the neural network.
-The following equation shows how the first layer of a neural network incorporating embeddings might be written:
+When applying embeddings in a data modeling context using neural networks, the values of the embeddings will be 
+calibrated during the same fitting process that calibrates the parameters of the neural network. The following equation 
+shows how the first layer of a neural network incorporating embeddings might be written:
 
@@
 
-Attention mechanisms have been widely applied within the deep learning literature to give more flexibility to RNNs [@Bahdanau2015a] and subsequently as a replacement for FCNs in the so-called Transformer architecture, which is now widely used in natural language processing [@Vaswani2017a], and, more recently, has been applied to computer vision and tabular modelling tasks.
-Attention mechanisms allow deep neural nets to choose covariates entering the model in a flexible manner; these types of applications are demonstrated in, for example, [@Vaswani2017a].
-In this section we provide an introduction to attention mechanisms and then discuss applications of attention to modeling tabular data.
+Attention mechanisms have been widely applied within the deep learning literature to give more flexibility to 
+RNNs [@Bahdanau2015a] and subsequently as a replacement for FCNs in the so-called Transformer architecture, which is 
+now widely used in natural language processing [@Vaswani2017a], and, more recently, has been applied to computer vision 
+and tabular modelling tasks. Attention mechanisms allow deep neural nets to choose covariates entering the model in a 
+flexible manner; these types of applications are demonstrated in, for example, [@Vaswani2017a]. In this section we 
+provide an introduction to attention mechanisms and then discuss applications of attention to modeling tabular data.
 
@@
 
-where $\mathbf{q} \in \mathbb{R}^q$ is a query vector, $K \in \mathbb{R}^{q \times d}$ is a matrix of key vectors, $V \in \mathbb{R}^{q \times d}$ is a matrix of value vectors and $\mathbf{v} \in \mathbb{R}^q$, the output of the attention mechanism, is a new vector of values.
-Several different options for the mapping \eqref{eq:attention} exist in the literature; here we first describe the self-attention mechanism used in [@Vaswani2017a].
-In more detail, consider that $V$ is a matrix of covariates relating to a regression problem, which can be composed of embeddings of the same dimension for several categorical variables.
-We wish to apply the attention mechanism to $V$ to estimate the most important of these embeddings for the regression problem.
-To do this, we formulate the query vector $\mathbf{q}$ which contains information about the regression problem at hand; this is usually done by passing $L$ through a FCN.
-Similarly, the matrix $K$ contains the relevance of each row of $L$ for the regression problem and is also usually derived by passing each row of $L$ through another FCN.
-Finally, the matrix $V$ can be set equal to $L$ or alternatively, can be derived as a transformation of $L$ using a third FCN.
-The first step of the attention mechanism is to derive a vector $\mathbf{a}$ of attention scores:
+where $\mathbf{q} \in \mathbb{R}^q$ is a query vector, $K \in \mathbb{R}^{q \times d}$ is a matrix of key vectors,
+$V \in \mathbb{R}^{q \times d}$ is a matrix of value vectors and $\mathbf{v} \in \mathbb{R}^q$, the output of the 
+attention mechanism, is a new vector of values. Several different options for the mapping \eqref{eq:attention} exist in 
+the literature; here we first describe the self-attention mechanism used in [@Vaswani2017a]. In more detail, consider 
+that $V$ is a matrix of covariates relating to a regression problem, which can be composed of embeddings of the same 
+dimension for several categorical variables. We wish to apply the attention mechanism to $V$ to estimate the most 
+important of these embeddings for the regression problem. To do this, we formulate the query vector $\mathbf{q}$ which 
+contains information about the regression problem at hand; this is usually done by passing $L$ through a FCN. 
+Similarly, the matrix $K$ contains the relevance of each row of $L$ for the regression problem and is also usually 
+derived by passing each row of $L$ through another FCN. Finally, the matrix $V$ can be set equal to $L$ or 
+alternatively, can be derived as a transformation of $L$ using a third FCN. The first step of the attention mechanism 
+is to derive a vector $\mathbf{a}$ of attention scores:
 
@@
 
-## Problem Description and Data
+## Problem Description and Experiment Setup
 
@@
 
+(talk about experiment setup -- we take a subset of data that's shared for all models, then for the CV performance
+evaluation only we use all data in CV splits?)
+
 ## Models
@@
 the prefix of the zone code, which corresponds to the level of risk as determined by FEMA [^8]. For example, `"A01"`, 
-`"A02"`, and so on are recoded as simply `"A"`.
+`"A02"`, and so on are recoded as simply `"A"`. A log link together with the gamma distribution is a standard choice 
+for severity modeling, which provides a multiplicative structure where the response is positive.
 
@@
 
-A log link together with the gamma distribution is a standard choice for severity modeling, which provides a 
-multiplicative structure where the response is positive.
+In Table \@ref(tab:relativities), we exhibit an exerpt of the relativities, or exponentiated fitted coefficients, 
+of a couple categorical variables. Recall that the choice of the log link gives a multiplicative structure, so the
+interpretation of 1.37 for `occupancy_type = "Non-residential building"` is that, all else equal, the expected 
+loss for
+a policy for a non-residential building is 1.37 times that of a policy for a single family home, which is the base,
+or reference, level for the factor.
+
+Table: (\#tab:relativities) Excerpt of relativities for Model 1.
+
+|variable       |label                                       | relativity|
+|:--------------|:-------------------------------------------|----------:|
+|occupancy_type |Single family residence                     |       1.00|
+|occupancy_type |Non-residential building                    |       1.37|
+|occupancy_type |2 to 4 unit residential buidling            |       1.15|
+|occupancy_type |Residential building with more than 4 units |       1.64|
+|flood_zone     |B                                           |       1.00|
+|flood_zone     |A                                           |       0.84|
+|flood_zone     |C                                           |       0.60|
+|flood_zone     |X                                           |       0.70|
+|flood_zone     |V                                           |       0.78|
+|flood_zone     |D                                           |       0.89|
 
@@
 
-For Model 2, we build a feedforward neural network. The categorical inputs go through one-dimensional embedding
+For Model 2, we build a feedforward neural network, whose architecture is shown in Figure \@ref(fig:nn-1). 
+The categorical inputs go through one-dimensional embedding
 layers where they are each mapped to a scalar. The embeddings are then concatenated with the numeric predictors, which
-have been normalized in data pre-processing, before being sent to a hidden linear layer of 16 units. A ReLU (TODO: reference an equation in prev. section) activation
+have been normalized in data pre-processing, before being sent to a hidden linear layer of 64 units. A ReLU (TODO: reference an equation in prev. section) activation
 is then applied to the outputs before they are sent to a final output layer resulting in a scalar. To constrain
@@
 
-Figure \@ref(fig:nn-1) exhibits the architecture of our simple neural network.
-
 ```{r nn-1, echo = FALSE, fig.cap = "Architecture of Models 2 and 4.", out.width = "90%", fig.align = "center"}
@@
 With a single hidden layer, this architecture is the simplest nontrivial neural network; without the hidden layer and
-corresponding ReLU activation, we would actually recover a GLM structure where the link function is the output activation. 
-The choice of one for the embedding dimension is also due to simplicity: it is easily interpretable as the representation
+corresponding ReLU activation, we would actually recover a GLM structure where the link function is the output 
+activation. 
+The choice of one for the embedding dimension is also due to simplicity: it is easily interpretable as the 
+representation
 of each factor level as a point on the real number line, also, the trained embeddings are easily incorporated into a GLM
@@
 are not unusually large.
+
+In Tables \@ref(tab:embeddings-occupancy-type) and \@ref(tab:embeddings-flood-zone), we show the learned embeddings
+for the `occupancy_type` and an excerpt of them for `flood_zone`. While it may be tempting to compare these values
+to those in Table \@ref(tab:relativities), they represent fundamentally different concepts. It is helpful to think
+of the embedding values for each variable as a continuous represention of the variable itself, rather than a 
+"coefficient" associated with the variable. Note that it is not straightforward to inspect the embeddings from a
+table and infer relationships to the response variable, even in a shallow network such as ours, due to nonlinearities
+within the model. Also note that we now have a way to incorporate the full granularity of the `flood_zone` variable,
+which is why more levels are shown in Table \@ref(tab:embeddings-flood-zone) as compared to Table 
+\@ref(tab:relativities). In Section TODO, we will discuss techniques to visualize these embeddings.
+
+Table: (\#tab:embeddings-occupancy-type) Learned embeddings for `occupancy_type`.
+
+|level                                       | embedding|
+|:-------------------------------------------|---------:|
+|2 to 4 unit residential buidling            |      6.69|
+|Non-residential building                    |      7.16|
+|Residential building with more than 4 units |      6.33|
+|Single family residence                     |      5.43|
+
+Table: (\#tab:embeddings-flood-zone) Excerpt of learned embeddings for `flood_zone`.
+
+|level | embedding|level | embedding|level | embedding|level | embedding|level | embedding|
+|:-----|---------:|:-----|---------:|:-----|---------:|:-----|---------:|:-----|---------:|
+|A     |      0.38|A09   |     -1.71|A18   |     -1.40|A99   |     -2.68|V     |     -0.41|
+|A00   |     -0.35|A0B   |      3.85|A19   |     -1.70|AE    |     -4.46|V02   |      0.65|
+|A01   |     -6.76|A10   |     -4.03|A20   |     -4.05|AH    |     -2.35|V03   |     -0.29|
+|A02   |     -4.28|A11   |     -5.32|A21   |     -2.08|AHB   |     -1.71|V04   |     -1.15|
+|A03   |     -5.93|A12   |     -3.23|A22   |     -2.11|AO    |     -6.07|V05   |     -0.50|
+|A04   |     -7.82|A13   |      2.03|A23   |     -1.40|AOB   |     -4.56|V06   |     -1.92|
+|A05   |     -3.42|A14   |     -5.72|A24   |      2.23|AR    |     -0.48|V07   |     -2.91|
+|A06   |     -4.97|A15   |     -3.67|A25   |      0.28|B     |     -5.36|V08   |     -2.24|
+|A07   |     -3.09|A16   |     -3.02|A27   |     -2.56|C     |     -4.47|V09   |     -0.75|
+|A08   |     -4.69|A17   |     -0.37|A30   |      1.13|D     |     -0.76|V10   |     -2.05|
 

### 2021-03-11 R/embedding-extract.R
embedding code

@@ -1,14 +1,15 @@
-model
-level_integer_mappings <- rec$steps[[3]]$key %>%
+model <- cv_results[[1]]$model_nn
+level_integer_mappings <- cv_results[[1]]$rec_nn$steps[[3]]$key %>%
     lapply(function(x) mutate(x, integer = as.integer(integer + 1L)))
 
 embeddings <- model$embedder$embeddings %>%
-    (function(x) lapply(1:length(cat_cols), function(i) x[[i]])) %>%
-    setNames(cat_cols) %>%
+    (function(x) lapply(1:length(categorical_cols), function(i) x[[i]])) %>%
+    setNames(categorical_cols) %>%
     purrr::imap(function(m, v) {
         outputs <- level_integer_mappings[[v]]$integer %>%
-            torch_tensor() %>%
+            torch_tensor(device = "cuda") %>%
             m() %>%
+            (function(x) x$to(device = "cpu")) %>% 
             as.array()
         mapping_tbl <- level_integer_mappings[[v]] 
         cbind(
@@ -17,7 +18,21 @@ embeddings <- model$embedder$embeddings %>%
         )
     })
 
-embeddings$flood_zone %>%
+
+emb_flood_zone <- embeddings$flood_zone %>%
+    rename(embedding = e1)
+list(emb_flood_zone[1:10, ], emb_flood_zone[11:20, ],
+     emb_flood_zone[21:30, ], emb_flood_zone[31:40, ],
+     emb_flood_zone[41:50, ]) %>%
+    Reduce(cbind, .) %>%
+    knitr::kable(digits = 2)
+
+emb_occupancy_type <- embeddings$occupancy_type %>%
+    rename(embedding = e1) %>% 
+    filter(!level == "new")
+knitr::kable(emb_occupancy_type, digits = 2)
+
+embeddings$condominium_indicator %>%
   ggplot() +
   geom_vline(xintercept = 0, linetype = "dashed") +
   geom_text(aes(-0.5, e1, label = round(e1, 2))) +
@@ -38,3 +53,30 @@ embeddings$state %>%
     ggplot() +
     geom_point(aes(e1, e2)) +
     geom_text(aes(e1, e2, label = level))
+
+embeddings$flood_zone %>% dim()
+
+lbls <- embeddings$flood_zone$level
+wts <- embeddings$flood_zone %>%
[…]

### 2021-03-11 R/model-inspect.R
glm table

@@ -1,0 +1,26 @@
+
+
+a <- broom::tidy(cv_results[[1]]$model_glm, exponentiate = TRUE)
+View(a)
+  # perform initial tidying of model
+library(broom.helpers)
+a <- cv_results[[1]]$model_glm %>% 
+  tidy_and_attach(exponentiate = TRUE) %>%
+  # add reference row
+  tidy_add_reference_rows() %>%
+  # add term labels
+  tidy_add_term_labels() %>%
+  # remove intercept
+  tidy_remove_intercept
+View(a)
+b <- a %>%
+    arrange(var_type) %>%
+    filter(variable %in% c("occupancy_type", "flood_zone")) %>%
+    select(variable, label, estimate) %>%
+    mutate(estimate = ifelse(is.na(estimate), 1, estimate)) %>%
+    rename(relativity = estimate)
+View(b)
+b %>% knitr::kable(digits = 2)
+
+model <- cv_results[[1]]$model_nn
+rec <- cv_results[[1]]$rec_nn

### 2021-03-11 R/cv-model-torch.R
code edits

@@ -48,7 +48,7 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
     valid_dl <- valid_ds %>% dataloader(batch_size = batch_size, shuffle = TRUE)
     test_dl <- test_ds %>% dataloader(batch_size = batch_size, shuffle = FALSE)
 
-    model <- simple_net(env$cardinalities, length(numeric_cols), units = 16, fn_embedding_dim = function(x) 1)
+    model <- simple_net(env$cardinalities, length(numeric_cols), units = 64, fn_embedding_dim = function(x) 1)
 
     optimizer <- optim_adam(model$parameters, lr = learning_rate, weight_decay = 0)
     # optimizer <- optim_rmsprop(model$parameters, lr = 0.1)
@@ -60,7 +60,7 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
     preds_nn <- get_preds(model, test_dl)
 
     model2 <- simple_net(env$cardinalities, length(numeric_cols),
-        units = 16,
+        units = 64,
         fn_embedding_dim = function(x) ceiling(x / 2)
     )
 
@@ -129,7 +129,7 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 }
 
 cv_results <- cvfolds$splits %>%
-    lapply(function(x) model_analyze_assess(x, 0.01, 1, 2000))
+    lapply(function(x) model_analyze_assess(x, 0.1, 1, 1024))
 
 cv_results %>%
     map(function(x) {

### 2021-03-11 R/model-utils.R
ship data on gpu might not be good idea

@@ -1,22 +1,23 @@
 flood_dataset <- dataset(
     "flood",
     initialize = function(df, categorical_cols, numeric_cols, response_col = NULL, env = NULL) {
+        device <- if (cuda_is_available()) torch_device("cuda:0") else "cpu"
         self$is_train <- if (!is.null(response_col)) TRUE else FALSE
         self$xcat <- df[categorical_cols] %>%
             as.matrix() %>%
             `+`(1L) %>%
-            torch_tensor()
+            torch_tensor(device = device)
         if (!is.null(env)) {
             assign("cardinalities", sapply(df[categorical_cols], function(x) max(x) + 2), envir = env)
         }
         self$xnum <- df[numeric_cols] %>%
             as.matrix() %>%
-            torch_tensor()
+            torch_tensor(device = device)
 
         if (self$is_train) {
             self$y <- df[[response_col]] %>%
                 as.matrix() %>%
-                torch_tensor()
+                torch_tensor(device = device)
         }
 
         self

### 2021-03-11 manuscript/manuscript.Rmd
models

@@
     \usepackage{bm}
+    \usepackage{bbm}
     \DeclarePairedDelimiter\ceil{\lceil}{\rceil}
@@
 
-# Definitions {#defns}
+# Theoretical Overview {#defns}
 
@@
 `"A02"`, and so on are recoded as simply `"A"`. A log link together with the gamma distribution is a standard choice 
-for severity modeling, which provides a multiplicative structure where the response is positive.
+for severity modeling, which provides a multiplicative structure where the response is positive. Following the notation
+in \@ref(catdata), the number of parameters in the GLM is
+
+\begin{equation}
+1 + |J^{\text{num}}| + \left(\sum_{j \in J^{\text{cat}}} n_{\mathcal{P}}^j\right) - |J^{\text{cat}}|:
+(\#eq:glm1)
+\end{equation}
+
+one for the intercept, one for each numeric variable, and the numbers of levels minus one (due to dummy coding) for 
+each categorical variable.
 
@@
 
-```{r nn-1, echo = FALSE, fig.cap = "Architecture of Models 2 and 4.", out.width = "90%", fig.align = "center"}
+```{r nn-1, echo = FALSE, fig.cap = "Architecture of Models 2 and 4.", out.width = "80%", fig.align = "center"}
 knitr::include_graphics("images/nn.png")
@@
 2. In other words, our model now contains only continuous variables, and each categorical factor is represented as a
-scalar value and obtains its own coefficient. (TODO: insert formal eqn for mean)
+scalar value and obtains its own coefficient. In contrast with the number of parameters computed in Equation
+\@ref(eq:glm1), we have fewer parameters for this model:
+
+\begin{equation}
+1 + |J^{\text{num}}| + |J^{\text{cat}}|.
+(\#eq:glm2)
+\end{equation}
+
+Hence, the model can be written as
+
+\begin{equation}
+\mu_i = \beta_0 + \sum_{j \in J^{\text{num}}}\beta_j x_{i,j} + \sum_{j \in J^{\text{cat}}} \beta_j z_{i,j},
+\end{equation}
+
+where $z_{i,j}$ represents the embedding value for $i$th instance of the categorical column $X_j$.
+
+Although in this particular example we incorporate one-dimensional embeddings, one can easily include multidimensional
+embeddings, which would increase the model's flexibility. The modeler would need to balance the additional lift with
+some loss of interpretability, since with one-dimensional embeddings, our GLM structure dictates that there is a 
+monotonic relationship between the predicted response and the input embedding, which could be desirable in certain
+use cases (and undesirable in others.)
+
+Since we only have a few parameters in this model, we exhibit the full list of fitted coefficients in Table 
+\@ref(tab:glm2).
+
+Table: (\#tab:glm2) Coefficients of Model 3.
+
+|term                                     | estimate|
+|:----------------------------------------|--------:|
+|(Intercept)                              |    2.389|
+|total_building_insurance_coverage        |    0.568|
+|basement_enclosure_crawlspace_type       |    0.136|
+|number_of_floors_in_the_insured_building |   -0.024|
+|occupancy_type                           |    0.067|
+|flood_zone                               |    0.035|
+|primary_residence                        |   -0.001|
+|community_rating_system_discount         |    0.504|
 
@@
 Model 4 is architecturally identical to Model 2, with the only difference being the number of embedding dimensions:
-instead of mapping factor levels to real numbers, we map them to a point in Euclidean space, where the dimension of the space is the ceiling
+instead of mapping factor levels to real numbers, we map them to points in Euclidean space, where the dimension of the 
+space is the ceiling
 of the factor's cardinality divided by two. Formally, in the notation of Section \ref{catdata},
-$q_{\mathcal{P}^j}=\ceil{n^j_{\mathcal{P}}/2}$ for variable $X_j$.
+$q_{\mathcal{P}^j}=\ceil{n^j_{\mathcal{P}}/2}$ for variable $X_j$. Following the practice from the previous three
+models, we list the fitted embeddings for a couple variables in Tables \@ref(tab:nn2-occupancy-type) and 
+\@ref(tab:nn2-flood-zone). Note that, for `flood_zone`, we are
+only displaying the embedding for *one* level.
+
+Table: (\#tab:nn2-occupancy-type) Learned embeddings for `occupancy_type` in Model 4.
+
+|level                                       |    e1|    e2|   e3|
+|:-------------------------------------------|-----:|-----:|----:|
+|2 to 4 unit residential buidling            | -1.44| -1.97| 2.35|
+|Non-residential building                    | -6.83| -8.11| 5.34|
+|Residential building with more than 4 units | -7.63| -6.58| 5.09|
+|Single family residence                     | -1.61| -2.54| 3.01|
+
+Table: (\#tab:nn2-flood-zone) Learned embeddings for level `"A00"` of variable `flood_zone` in Model 4.
+
+|dimension |value  |dimension |value  |dimension |value  |dimension |value  |
+|:---------|:------|:---------|:------|:---------|:------|:---------|:------|
+|e1        |0.020  |e11       |2.146  |e21       |-1.933 |e31       |-0.941 |
+|e2        |-0.885 |e12       |1.723  |e22       |1.150  |e32       |-1.279 |
+|e3        |-0.126 |e13       |0.378  |e23       |0.863  |e33       |-0.360 |
+|e4        |1.491  |e14       |-0.310 |e24       |-0.471 |e34       |-1.173 |
+|e5        |0.980  |e15       |2.482  |e25       |0.929  |          |       |
+|e6        |0.952  |e16       |1.823  |e26       |-1.139 |          |       |
+|e7        |-0.217 |e17       |-2.715 |e27       |0.113  |          |       |
+|e8        |-0.611 |e18       |1.144  |e28       |1.155  |          |       |
+|e9        |0.919  |e19       |-0.045 |e29       |0.707  |          |       |
+|e10       |-1.196 |e20       |0.467  |e30       |1.358  |          |       |
 

### 2021-03-12 R/model-torch.R
remove old code

@@ -1,56 +1,0 @@
-library(tidyverse)
-library(recipes)
-library(rsample)
-library(torch)
-
-source("R/model-utils.R")
-source("R/data-loading.R")
-
-categorical_cols <- c(
-    "state", "primary_residence", "basement_enclosure_crawlspace_type",
-    "condominium_indicator", "number_of_floors_in_the_insured_building",
-    "occupancy_type", "flood_zone"
-)
-
-numeric_cols <- c("total_building_insurance_coverage", "community_rating_system_discount")
-response_col <- "amount_paid_on_building_claim"
-
-env <- new.env()
-
-rec <- recipe(amount_paid_on_building_claim ~ .,
-   data = small_data %>%
-      select(-loss_proportion, -reported_zip_code)
-) %>%
-   step_normalize(all_numeric(), -all_outcomes()) %>%
-   step_unknown(all_nominal()) %>%
-   step_integer(all_nominal(), strict = TRUE, zero_based = TRUE) %>%
-   prep()
-
-glimpse(small_data)
-
-training_data <- juice(rec)
-
-ds <- flood_dataset(training_data, categorical_cols, numeric_cols, response_col, env)
-
-model <- net(env$cardinalities, length(numeric_cols), function(x) 2)
-
-train_dl <- ds %>% dataloader(batch_size = 1024, shuffle = TRUE)
-
-o1 <- model(ds[1:10]$x[[1]], ds[1:10]$x[[2]])
-o1
-y1 <- ds[1:10]$y
-y1
-optimizer <- optim_adam(model$parameters, lr = 0.1)
-
-train_loop(model, train_dl, train_dl, epochs = 2, optimizer = optimizer)
-
-ds
-test_ds <- flood_dataset(training_data, categorical_cols, numeric_cols) 
-test_dl <- test_ds %>% dataloader(batch_size = 1024, shuffle = FALSE)
-foo <- enumerate(test_dl)
-preds <- numeric(0)
-for (b in enumerate(test_dl))  {
-    preds <- c(preds, model(b$x[[1]], b$x[[2]]) %>% as.array())
-}
-preds
-length(preds)

### 2021-03-16 manuscript/manuscript.Rmd
start adding viz

@@
 
+## Visualization Techniques for Interpretation {#interpretation}
+
+With AI and ML coming into the mainstream across industries and use cases, the topic of model explainability
+has received increasing attention. In insurance pricing, @kuo2020explainability propose a framework for
+model interpretability in the context of regulation and actuarial standards of practice, while @henckaerts2020boosting
+investigate algorithm-specific techniques to inspect tree-based models. @kuo2020explainability and references
+therein also discuss
+commonly utilized model-agnostic explanation techniques, such as permutation variable importance and partial
+dependence plots, that can be applied to the neural networks we consider in this paper.
+
+In this section, we focus on ways to visualize the learned embeddings. In the authors' experiences, oftentimes
+the formats of the visualizations --- basic line and scatter plots --- even more so than the content of the data, is 
+helpful in explaining the concept to stakeholders.
+
+For Model 2, the neural network with one-dimensional embeddings, the task is simple: we can simply plot the levels
+on a line, as in Figure \@ref(fig:num-floors). In the case of `flood_zone`, since we happen to have the luxury of knowing a
+priori the meaning of the prefixes, we can plot them separately to see how the model mapped them. (TODO insert chart).
+(insert any observations).
+
+```{r num-floors, echo=FALSE, fig.cap="Number of floors", out.width = "90%", fig.align="center"}
+knitr::include_graphics("images/num_floors.png")
+```
+
+For Model 4, the neural network with multi-dimensional embeddings, we would need to treat the learned values before
+we can plot them. Specifically, we need to reduce the dimension of the data to 2D for embeddings with more than
+two dimensions. The standard approachs for this are principal component analysis (PCA) and t-distributed stochastic
+neighbor embedding (t-SNE), both of which we illustrate below.
+
+### PCA
+
+### t-SNE
+
 ## Model Training and Results
@@
 (maybe a couple boxplots showing metrics for baseline models)
-
-## Interpretations {#interpretation}
-
-- model explainability is important in insurance
-- the more we can learn about how we arrive at our models the better
-- cite some existing work on explainable models in actuarial literature to show people care
-- refer back to some definitions from previous sections
-- show some embedding weights from our models - 1d line plot
-- (need a multidimensional embedding for this) do some pca/tsne
-- stress that relationship of embedding weights to response variable may be nonlinear depending on architecture
 

### 2021-03-16 R/embedding-extract.R

@@ -9,9 +9,9 @@ embeddings <- model$embedder$embeddings %>%
         outputs <- level_integer_mappings[[v]]$integer %>%
             torch_tensor(device = "cuda") %>%
             m() %>%
-            (function(x) x$to(device = "cpu")) %>% 
+            (function(x) x$to(device = "cpu")) %>%
             as.array()
-        mapping_tbl <- level_integer_mappings[[v]] 
+        mapping_tbl <- level_integer_mappings[[v]]
         cbind(
             level = mapping_tbl$value,
             as.data.frame(outputs) %>% setNames(paste0("e", 1:ncol(outputs)))
@@ -21,33 +21,87 @@ embeddings <- model$embedder$embeddings %>%
 
 emb_flood_zone <- embeddings$flood_zone %>%
     rename(embedding = e1)
-list(emb_flood_zone[1:10, ], emb_flood_zone[11:20, ],
-     emb_flood_zone[21:30, ], emb_flood_zone[31:40, ],
-     emb_flood_zone[41:50, ]) %>%
+list(
+    emb_flood_zone[1:10, ], emb_flood_zone[11:20, ],
+    emb_flood_zone[21:30, ], emb_flood_zone[31:40, ],
+    emb_flood_zone[41:50, ]
+) %>%
     Reduce(cbind, .) %>%
     knitr::kable(digits = 2)
 
 emb_occupancy_type <- embeddings$occupancy_type %>%
-    rename(embedding = e1) %>% 
+    rename(embedding = e1) %>%
     filter(!level == "new")
 knitr::kable(emb_occupancy_type, digits = 2)
 
-embeddings$condominium_indicator %>%
-  ggplot() +
-  geom_vline(xintercept = 0, linetype = "dashed") +
-  geom_text(aes(-0.5, e1, label = round(e1, 2))) +
-  geom_text(aes(1, e1, label = level), hjust = 0) +
-  geom_point(aes(0, e1)) +
-  geom_segment(aes(x = 0.8, xend = 0.1, y = e1, yend = e1),
-               arrow = arrow(type = "closed", length = unit(0.075, "inches")),
-               alpha = 0.5) +
-  coord_cartesian(xlim = c(-3, 5)) +
-  theme_void()
+# for multidimensional
 
+emb_flood_zone <- embeddings$flood_zone %>%
+    filter(level == "A00") %>%
[…]

### 2021-03-16 R/embedding-extract.R
a little more progress

@@ -98,6 +98,19 @@ p2 <- embeddings$number_of_floors_in_the_insured_building %>%
     #     theme_void()
 p2
 ggsave("manuscript/images/num_floors.png", plot = p2, width = 8, height = 5)
+
+library(ggrepel)
+p3 <- embeddings$flood_zone %>%
+    filter(level != "new") %>%
+    mutate(prefix = substr(level, 1, 1)) %>%
+    ggplot(aes(e1, prefix, color = prefix, label = level)) +
+    geom_point() +
+    geom_label_repel() +
+    theme_bw()
+
+ggsave("manuscript/images/flood_zone.png", plot = p3, width = 8, height = 8)
+
+
 embeddings$flood_zone %>%
     mutate(prefix = substr(level, 1, 1)) %>%
     ggplot() +

### 2021-03-16 manuscript/manuscript.Rmd

@@
 on a line, as in Figure \@ref(fig:num-floors). In the case of `flood_zone`, since we happen to have the luxury of knowing a
-priori the meaning of the prefixes, we can plot them separately to see how the model mapped them. (TODO insert chart).
-(insert any observations).
+priori the meaning of the prefixes, we can plot them separately, as in Figure \@ref(fig:flood-zone) to see how the model 
+mapped them.
 
@@
 knitr::include_graphics("images/num_floors.png")
+```
+
+```{r flood-zone, echo = FALSE, fig.cap="Flood zone embeddings", out.width = "80%", fig.align = "center"}
+knitr::include_graphics("images/flood_zone.png")
 ```
@@
 
-To evaluate these baseline models and other models in this paper, we perform 10-fold 
-cross validation and compare the 
-root mean square error (RMSE) on the predicted and actual paid amounts.
-(somehwere we should say we're not doing a kaggle competition here and the performance metrics are really meant
-to show that the models aren't complete shit)
-(maybe a couple boxplots showing metrics for baseline models)
+(TODO)
 

### 2021-03-17 manuscript/manuscript.Rmd
more pics and fix refs

@@
     \usepackage{bbm}
+    \usepackage{float}
     \DeclarePairedDelimiter\ceil{\lceil}{\rceil}
 ---
+
+```{r setup, include = FALSE}
+knitr::opts_chunk$set(fig.pos = "!h", out.extra = "")
+```
 
@@
 and considers avenues for future research.
-
-(TODO: link to github repo)
 
@@
 These model architectures are relatively uncomplicated by today's standards, and are so chosen to better highlight the
-embedding components. Later, in Section X (TODO), we will investigate more involved architectures utilizing embeddings
+embedding components. Later, in Section \ref{attn}, we will investigate more involved architectures utilizing embeddings
 that represent the state of the art for modeling tabular data.
@@
 layers where they are each mapped to a scalar. The embeddings are then concatenated with the numeric predictors, which
-have been normalized in data pre-processing, before being sent to a hidden linear layer of 64 units. A ReLU (TODO: reference an equation in prev. section) activation
+have been normalized in data pre-processing, before being sent to a hidden linear layer of 64 units. A ReLU activation,
+
+\begin{equation}
+x \mapsto \max(0, x),
+\end{equation}
+
 is then applied to the outputs before they are sent to a final output layer resulting in a scalar. To constrain
@@
 
-$$
+\begin{equation}
 x \mapsto \log(1 + e^x). 
-$$
+\end{equation}
 
@@
 which is why more levels are shown in Table \@ref(tab:embeddings-flood-zone) as compared to Table 
-\@ref(tab:relativities). In Section TODO, we will discuss techniques to visualize these embeddings.
+\@ref(tab:relativities). In Section \ref{interpretation}, we will discuss techniques to visualize these embeddings.
 
@@
 
-```{r num-floors, echo=FALSE, fig.cap="Number of floors", out.width = "90%", fig.align="center"}
+```{r num-floors, echo=FALSE, fig.cap="Number of floors", out.width = "80%", fig.align="center"}
 knitr::include_graphics("images/num_floors.png")
@@
 
-```{r flood-zone, echo = FALSE, fig.cap="Flood zone embeddings", out.width = "80%", fig.align = "center"}
+```{r flood-zone, echo = FALSE, fig.cap="Flood zone embeddings", out.width = "60%", fig.align = "center"}
 knitr::include_graphics("images/flood_zone.png")
@@
 
+(TODO: insert brief theoretical stuff). See Figure \@ref(fig:flood-zone-pca).
+
+```{r flood-zone-pca, echo = FALSE, fig.cap="Flood zone PCA", out.width = "60%", fig.align = "center"}
+knitr::include_graphics("images/flood_zone_pca.png")
+```
+
 ### t-SNE
 
-## Model Training and Results
+(TODO: insert brief theoretical stuff). See Figure \@ref(fig:flood-zone-tsne).
+
+```{r flood-zone-tsne, echo = FALSE, fig.cap="Flood zone t-SNE", out.width = "60%", fig.align = "center"}
+knitr::include_graphics("images/flood_zone_tsne.png")
+```
+
+## Training and Inference
 
@@
 
-# Attention based modelling
+# Attention based modelling {#attn}
 
@@
 Conclusions
+
+\newpage
+
+# References {.unnumbered}

### 2021-03-17 R/embedding-extract.R

@@ -1,4 +1,4 @@
-model <- cv_results[[1]]$model_nn
+model <- cv_results[[1]]$model_nn2
 level_integer_mappings <- cv_results[[1]]$rec_nn$steps[[3]]$key %>%
     lapply(function(x) mutate(x, integer = as.integer(integer + 1L)))
 
@@ -123,27 +123,48 @@ embeddings$state %>%
 
 embeddings$flood_zone %>% dim()
 
+
+####### PCA stuff
+
+
+embeddings$flood_zone %>% str()
+
 lbls <- embeddings$flood_zone$level
 wts <- embeddings$flood_zone %>%
     select(starts_with("e")) %>%
     as.matrix()
-pca <- prcomp(wts, center = TRUE, scale. = TRUE, rank = 3)$x[, c("PC1", "PC2", "PC3")] %>%
+
+pca <- prcomp(wts, center = TRUE, scale. = TRUE, rank = 2)$x[, c("PC1", "PC2")] %>%
     as.data.frame()
 
-library(ggrepel)
 
 ggplot(data = pca, aes(x = PC1, y = PC2)) +
     geom_point()
-
-rayshader::plot_gg(ggp)
-
-pca %>%
+library(ggrepel)
+p4 <- pca %>%
     as.data.frame() %>%
     mutate(class = lbls) %>%
     mutate(prefix = substr(lbls, 1, 1)) %>%
+    filter(class != "new") %>% 
     ggplot(aes(x = PC1, y = PC2, color = prefix)) +
     geom_point() +
     geom_label_repel(aes(label = class)) +
-    coord_cartesian(xlim = c(-2, 2), ylim = c(-2, 2)) +
-    theme(aspect.ratio = 1) +
+    # coord_cartesian(xlim = c(-2, 2), ylim = c(-2, 2)) +
+    # theme(aspect.ratio = 1) +
     theme_classic()
+
+ggsave("manuscript/images/flood_zone_pca.png", plot = p4)
+
+library(Rtsne)
+tsne_out <- Rtsne::Rtsne(wts, perplexity = 5)
+p5 <- tsne_out$Y %>%
+    as.data.frame() %>%
+    mutate(class = lbls) %>%
+    mutate(prefix = substr(lbls, 1, 1)) %>%
+    filter(class != "new") %>%
+    ggplot(aes(x = V1, y = V2, color = prefix)) +
+    geom_point() +
+    geom_label_repel(aes(label = class)) +
[…]

### 2021-03-18 manuscript/manuscript.Rmd

@@
 In this section, we walk through a simple predictive modeling exercise in order to illustrate the application of 
-embeddings. First, we pose a supervised regression problem, based on flood insurance claims severity. We then describe, 
-fit, and evaluate GLMs and neural networks utilizing embeddings for this problem. Finally, we discuss visualization 
-techniques for model interpretation. As we proceed, we also incorporate practical technical guidance on modeling
-procedure.
+embeddings. First, we pose a supervised regression problem, based on flood insurance claims severity. We then develop 
+GLMs and neural networks utilizing embeddings for this problem, and inspect the trained parameters. Finally, we
+provide details of model optimization, inference, and performance.
 
@@
 with exposure information, and a claims dataset with claims transactions, including paid amounts. Because there is no 
-way to associate records of the two datasets, we are limited to fitting severity models on the claims dataset. While the 
+way to associate records of the two datasets, we are limited to fitting severity models on the claims dataset. While 
+the 
 complete dataset contains over two million transactions, for the purposes of our experiments we limit ourselves to data 
 from 2000 to August 2019, which amounts to approximately 1.4 million claims. The dataset can be downloaded from 
-Cellar[^10] The dataset includes a rich variety of variables, from occupancy type to coarse coordinates. For our models, 
+Cellar[^10] The dataset includes a rich variety of variables, from occupancy type to coarse coordinates. For our 
+models, 
 we work with a few selected variables that represent continuous and discrete variables of low and high cardinalities, 
@@
   variables,
-  caption = "Predicator variables.",
+  caption = "Predictor variables.",
   booktabs = TRUE,
@@
 
-(talk about experiment setup -- we take a subset of data that's shared for all models, then for the CV performance
-evaluation only we use all data in CV splits?)
+For our experiments, we set up a 10-fold cross validation scheme that is applied to each of the models
+we introduce. In Sections \ref{models} and \ref{interpretations}, the tables and figures are based on a single fold of 
+the cross validation split. In Section \ref{training-inference}, we provide the cross-validated performance
+metrics of each of the models.
 
-## Models
+We note that the focus of our contribution is on applications of categorical embeddings in predictive modeling, 
+rather than
+on fine-tuning models in order to beat or establish a benchmark. To this end, we do not perform systematic
+hyperparameter tuning in our experiments, and the performance metrics are provided to show that reasonable
+models utilizing categorical embeddings. However, as we describe the modeling procedure and results, we provide
+commentary on recommended practices in practical applications, especially with respect to the neural network models.
+
+## Models {#models}
 
@@
 
-## Training and Inference
+## Training and Inference {#training-inference}
 
-(TODO)
+For the GLMs, Models 1 and 3, we follow the standard optimization procedure using iteratively reweighted least 
+squares (IWLS) without regularization. For the neural networks, Models 2 and 4, we utilize the \texttt{Adam}
+optimizer [@Kingma2014] with a learning rate of TODO, and train the each network for TODO epochs with a batch
+size of TODO.
+
+During inference, or scoring, care must be taken to accommodate the categorical levels that are unseen
+during training. While we allow for an extra key in the embedding dictionary (TODO: mention this earlier), the initial
+weights are not updated during training, which could lead to nonsensical predictions in the validation or test sets. To
+circumvent this issue, before applying the trained model but after the final optimization epoch, we update the weights
+for the unseen levels manually. In practice, a common approach is to take an average value 
+of some sort of the weights of theother levels. In our case, we take the median (if there are multiple, the lower of
+the two), but a mean, mean weighted by frequency of observations, or trimmed mean could be used.
+
+In Table TODO, we exhibit the cross-validated performance metrics of each of the models.
 

### 2021-03-19 manuscript/manuscript.Rmd

@@
     \DeclarePairedDelimiter\ceil{\lceil}{\rceil}
+    \newcommand{\norm}[1]{\| #1 \|}
 ---
@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(fig.pos = "!h", out.extra = "")
+knitr::opts_chunk$set(out.extra = "")
 ```
@@
 
+\newpage
+
 \begin{equation}
-\mu_i = \beta_0 + \sum_{j \in J^{\text{num}}}\beta_j x_{i,j} + \sum_{j \in J^{\text{cat}}} \beta_j z_{i,j},
+\mu_i = \beta_0 + \sum_{j \in J^{\text{num}}}\beta_{j} x_{i,j} + \sum_{j \in J^{\text{cat}}} \beta_{j} z_{i,j},
 \end{equation}
@@
 we can plot them. Specifically, we need to reduce the dimension of the data to 2D for embeddings with more than
-two dimensions. The standard approachs for this are principal component analysis (PCA) and t-distributed stochastic
-neighbor embedding (t-SNE), both of which we illustrate below.
+two dimensions. The standard approachs for this are principal component analysis (PCA; @shlens2014tutorial) 
+and t-distributed stochastic
+neighbor embedding (t-SNE; @Maaten2008a), both of which we illustrate.
 
-### PCA
+### Principal Component Analysis
 
-(TODO: insert brief theoretical stuff). See Figure \@ref(fig:flood-zone-pca).
+In both approaches, the overarching theme is as follows: We have a collection of points in higher dimensional space,
+$\mathcal{X} = \{x_1, x_2, \dots, x_n\}$ that we wish to map to some lower dimensional space, typically $\mathbb{R}^2$,
+obtaining $\mathcal{Y} = \{y_1, y_2, \dots, y_n\}$. PCA performs a linear change of coordinates on 
+the input data so that the variance of the data is maximized along each orthogonal coordinate, also known as
+*principal component*, successively. Formally, if we denote $\mathbf{X}$ and $\mathbf{Y}$ to be the matrices whose 
+columns are elements of 
+$\mathcal{X}$ and $\mathcal{Y}$, respectively, this can be represented as looking for an orthonormal matrix $\mathbf{P}$
+in $\mathbf{Y} = \mathbf{PX}$ such that the covariance matrix of $\mathbf{Y}$, $\frac{1}{n}\mathbf{YY^T}$, is diagonal.
+Here, the rows of $\mathbf{P}$ are the principal components that define the resulting coordinate system. It turns out
+that that these principal components are the eigenvectors of the covariance matrix of $\mathbf{X}$, i.e., 
+$\mathbf{C_X} \equiv \frac{1}{n}\mathbf{XX^T}$. In practice, numerical procedures, including R's \texttt{prcomp()}
+which we use, utilize singular value decomposition (SVD) to compute the eigenvectors.
+
+In Figure \@ref(fig:flood-zone-pca), we plot the learned embeddings for `flood_zone` in Model 3 on the coordinate
+system defined by the first two principle components. (TODO: add commentary after update pic)
 
@@
 
-### t-SNE
+### t-Distributed Stochastic Neighbor Embedding
 
-(TODO: insert brief theoretical stuff). See Figure \@ref(fig:flood-zone-tsne).
+In contrast with PCA, t-SNE is a nonlinear technique. At a high level, it computes a similarity metric, in the form of
+conditional probabilities based on pairwise distances, among points in $\mathcal{X}$, then look for points $\mathcal{Y}$
+in the lower dimensional space which have similarity metric values (for a differently defined metric) that are "close" to those of corresponding pairs of 
+points in the original data.
+
+Let $p_{j|i}$ denote the probability that point $x_i$ picks point $x_j$ as its *neighbor*, if it picks neighbors in
+proportion to their density under an $n$-dimension Gaussian centered at $x_i$. Formally, we can write $p_{j|i}$ as
+
+\begin{equation}
+p_{j|i} = \frac{\exp(\norm{x_i - x_j}^2 / 2\sigma_i^2)}{\sum_{k\neq i} \exp(-\norm{x_i - x_k}^2 / 2\sigma_i^2)}. (\#eq:pji)
+\end{equation}
+
+The similarity metric for the originals space symmetrizes this conditional probability and is defined as
+
+\begin{equation}
+p_{ij} = \frac{p_{j|i} + p_{i|j}}{2n}.
+\end{equation}
+
+On the other hand, in the target space, t-SNE assumes the neighbor selection is driven by a Student 
+t-distribution with one
+degree of freedom, i.e., a Cauchy distribution. The similarity metric for a pair of points in $\mathcal{Y}$ is 
+then defined as the joint probability
+
+\begin{equation}
+q_{ij} = \frac{(1 + \norm{y_i - y_j}^2)^{-1}}{\sum_{k \neq l} (1 + \norm{y_k - y_l}^2)^{-1}}.
+\end{equation}
+
+With the similarity metrics defined for each space, we can then state the objective for "closeness" for the sets of
+points, which is the Kullback–Leibler divergence from Q to P:
+
+\begin{equation}
+D_{KL}(P || Q) = \sum_{i \neq j} p_{ij} \log \frac{p_{ij}}{q_{ij}}. (\#eq:tsne-obj)
+\end{equation}
+
+We now circle back to Equation \@ref(eq:pji) and discuss $\sigma_i$. The variance of the Gaussian is allowed to vary
+depending on where the point is in the space; specifically, it should reflect the density or sparsness of surrounding 
+points. To train this parameter, t-SNE introduces a hyperparameter, *perplexity*, which is a scalar value set by the
+user, and is defined as
+
+\begin{equation}
+Perp(P_i) = 2^{H(P_i)},
+\end{equation}
+
+where $H(P_i)$ denotes the entropy of $P_i$,
+
+\begin{equation}
+H(P_i) = -\sum_j p_{j|i}\log_2 p_{j|i},
+\end{equation}
+
+and $P_i$ is the Gaussian parameterized by $x_i$ and $\sigma_i$. During training, t-SNE looks for $P_i$ that have
+perpelxity corresponding to the user input. Finally, the objective as stated in Equation \@ref(eq:tsne-obj) is differentiable, and is trained via gradient descent.
+
+While t-SNE is a powerful visualization technique, there are a few points the modeler should be mindful of in practice.
+First, the resulting plot can be very sensitive to the perplexity hyperparameter. 
+In Figures \@ref(fig:flood-zone-tsne), we display the t-SNE of the learned embeddings for `flood_zone` in
+Model 3 with various perplexity settings. (TODO: add more commentary).
 

### 2021-03-22 manuscript/manuscript.Rmd
update pdf

--- 2021-03-17 manuscript/manuscript.Rmd
@@
     \usepackage{bm}
-    \usepackage{bbm}
-    \usepackage{float}
     \DeclarePairedDelimiter\ceil{\lceil}{\rceil}
@@
 
-```{r setup, include = FALSE}
-knitr::opts_chunk$set(fig.pos = "!h", out.extra = "")
-```
-
 # Introduction
 
-Categorical data are modelled by actuaries in many different contexts, from pricing of insurance products to reserving 
-for the liabilities generated by these products. Sometimes, these data are modelled in an explicit manner, for example, 
-when building models that apply across multiple categories, a form of dummy coding is usually used. For example, when 
-building models to price the frequency of motor insurance claims, claim experience relating to different types of motor
-vehicle will often be modelled by including a (single) factor within models that modifies the relative frequency 
-predicted for each type of vehicle. In other cases, modelling is performed for each category separately, thus the 
-categorical data is used within the modelling in an implicit manner, for example, common practice is to estimate 
-reserves for different lines of business separately, meaning to say, with no parameters being shared across each of the
-reserving models.
+Categorical data are modelled by actuaries in many different contexts, from pricing of insurance products to reserving for the liabilities generated by these products.
+Sometimes, these data are modelled in an explicit manner, for example, when building models that apply across multiple categories, a form of dummy coding is usually used.
+For example, when building models to price the frequency of motor insurance claims, claim experience relating to different types of motor vehicle will often be modelled by including a (single) factor within models that modifies the relative frequency predicted for each type of vehicle.
+In other cases, modelling is performed for each category separately, thus the categorical data is used within the modelling in an implicit manner, for example, common practice is to estimate reserves for different lines of business separately, meaning to say, with no parameters being shared across each of the reserving models.
 
-Recently, several studies of insurance problems have applied an alternative approach, originally from the natural 
-known as **categorical embeddings**. Instead of trying to capture the differences between categories using a single 
-factor, the categorical embedding approach rather maps each category to a low-dimensional numeric vector, which is then
-used within the model as a new predictor variable.
+Recently, several studies of insurance problems have applied an alternative approach, originally from the natural langauge processing literature known as **categorical embeddings**.
+Instead of trying to capture the differences between categories using a single factor, the categorical embedding approach rather maps each category to a low-dimensional numeric vector, which is then used within the model as a new predictor variable.
 
 This approach to modelling categorical data has several advantages over more traditional treatments of categorical data.
-Using categorical embeddings instead of traditional techniques has been shown to increase predictive accuracy of 
-models, for example, see [@Richman2018] in the context of pricing. Models incorporating categorical embeddings can be
-pre-calibrated to traditional actuarial models, increasing the speed with which these models can be calibrated and 
-leading to models with better explainability [@wuthrich2019yes]. Finally, the similarity between the vectors learned 
-for different categories can be inspected, sometimes leading to insights into the workings of models, see, for example,
-[@Kuo2019].
+Using categorical embeddings instead of traditional techniques has been shown to increase predictive accuracy of models, for example, see [@Richman2018] in the context of pricing.
+Models incorporating categorical embeddings can be pre-calibrated to traditional actuarial models, increasing the speed with which these models can be calibrated and leading to models with better explainability [@wuthrich2019yes].
+Finally, the similarity between the vectors learned for different categories can be inspected, sometimes leading to insights into the workings of models, see, for example, [@Kuo2019].
 
-On the other hand, several open questions about the use of embeddings within actuarial work remain, which we aim to 
-address in this study. First, hyperparameter settings for embeddings, such as the dimensions of the embedding layer and
-the use of regularization techniques such as dropout or normalization, that achieve optimal predictive performance has
-not yet been studied in detail in the actuarial literature. In this work, we aim to study how embeddings using 
-different settings perform in the context of a large-scale predictive modelling problem, and give guidance on the 
-process that can be followed to determine this in other problems. Although neural network have been shown to achieve
-excellent predictive accuracy on actuarial tasks, many actuaries still prefer to use GLM models for pricing tasks, 
-thus, the issue of whether transferring embeddings to GLM models can achieve better performance is considered in this
-paper. Traditional actuarial techniques such as credibility theory have been used to work with some types of 
-categorical data, but no study has been performed whether this can be applied within embeddings; here, we investigate
-whether performance is enhanced by applying credibility theory on embeddings relating to categorical variables with
-many labels. Whereas embedding layers are usually considered in the context of categorical data,the option exists to
-quantize numerical data and model it using embeddings, however, the results of doing so have not been investigated.
-Finally, in the past several years, a new type of neural network architecture based on attention [@Vaswani2017] has
-been successfully used on embeddings in the field of natural language processing and we incorporate attention 
-based models into our predictive modelling example.
+On the other hand, several open questions about the use of embeddings within actuarial work remain, which we aim to address in this study.
+First, hyperparameter settings for embeddings, such as the dimensions of the embedding layer and the use of regularization techniques such as dropout or normalization, that achieve optimal predictive performance has not yet been studied in detail in the actuarial literature.
+In this work, we aim to study how embeddings using different settings perform in the context of a large-scale predictive modelling problem, and give guidance on the process that can be followed to determine this in other problems.
+Although neural network have been shown to achieve excellent predictive accuracy on actuarial tasks, many actuaries still prefer to use GLM models for pricing tasks, thus, the issue of whether transferring embeddings to GLM models can achieve better performance is considered in this paper.
+Traditional actuarial techniques such as credibility theory have been used to work with some types of categorical data, but no study has been performed whether this can be applied within embeddings; here, we investigate whether performance is enhanced by applying credibility theory on embeddings relating to categorical variables with many labels.
+Whereas embedding layers are usually considered in the context of categorical data,the option exists to quantize numerical data and model it using embeddings, however, the results of doing so have not been investigated.
+Finally, in the past several years, a new type of neural network architecture based on attention [@Vaswani2017] has been successfully used on embeddings in the field of natural language processing and we incorporate attention based models into our predictive modelling example.
 
-In this work, we utilize the recently released National Flood Insurance Program (NFIP) dataset 
-[@FederalEmergencyManagementAgency2019] which provides exposure information for policies written under the NFIP since 
-XXXXDateXXXX, as well as the claims data relating to these exposures. We refer the reader to Appendix \ref{NFIP_eda} for
-an exploratory analysis of this dataset.
+In this work, we utilize the recently released National Flood Insurance Program (NFIP) dataset [@FederalEmergencyManagementAgency2019] which provides exposure information for policies written under the NFIP since XXXXDateXXXX, as well as the claims data relating to these exposures.
+We refer the reader to Appendix \ref{NFIP_eda} for an exploratory analysis of this dataset.
 
-The rest of this manuscript is organized as follows. Section \ref{lit_review} reviews recent applications of embeddings
-in the actuarial literature. Section \ref{defns} provides the notation used in the paper and defines GLMs, neural 
-networks and related modelling concepts, including embeddings and attention. In Section \ref{modelling}, we provide 
-initial models for the NFIP dataset and consider the influence of hyperparameter choices on the results of the neural 
-network model. Section \ref{tl} considers how successfully the embeddings used in the neural network model can be 
-transferred to a GLM model of the same data. Extensions to the modelling approach are considered in Section \ref{extend} 
-and we focus on attention based models in Section \ref{attention}. The interpretability of embedding layers is addressed
-in Section \ref{interpretation}. Finally, Section \ref{Conclusions} provides a discussion of the results of this paper
-and considers avenues for future research.
+The rest of this manuscript is organized as follows.
+Section \ref{lit_review} reviews recent applications of embeddings in the actuarial literature.
+Section \ref{defns} provides the notation used in the paper and defines GLMs, neural networks and related modelling concepts, including embeddings and attention.
+In Section \ref{modelling}, we provide initial models for the NFIP dataset and consider the influence of hyperparameter choices on the results of the neural network model.
+Section \ref{tl} considers how successfully the embeddings used in the neural network model can be transferred to a GLM model of the same data.
+Extensions to the modelling approach are considered in Section \ref{extend} and we focus on attention based models in Section \ref{attention}.
+The interpretability of embedding layers is addressed in Section \ref{interpretation}.
+Finally, Section \ref{Conclusions} provides a discussion of the results of this paper and considers avenues for future research.
+
+(TODO: link to github repo)
 
@@
 
-When applying embeddings in a data modeling context using neural networks, the values of the embeddings will be 
-calibrated during the same fitting process that calibrates the parameters of the neural network. The following equation 
-shows how the first layer of a neural network incorporating embeddings might be written:
+When applying embeddings in a data modeling context using neural networks, the values of the embeddings will be calibrated during the same fitting process that calibrates the parameters of the neural network.
+The following equation shows how the first layer of a neural network incorporating embeddings might be written:
 
@@
   z^1 = \sigma(a_1.X'+ b_1), 
+\label{eq:embed_to_nn}
 \end{equation}
@@
 
-Attention mechanisms have been widely applied within the deep learning literature to give more flexibility to 
-RNNs [@Bahdanau2015a] and subsequently as a replacement for FCNs in the so-called Transformer architecture, which is 
-now widely used in natural language processing [@Vaswani2017a], and, more recently, has been applied to computer vision 
-and tabular modelling tasks. Attention mechanisms allow deep neural nets to choose covariates entering the model in a 
-flexible manner; these types of applications are demonstrated in, for example, [@Vaswani2017a]. In this section we 
-provide an introduction to attention mechanisms and then discuss applications of attention to modeling tabular data.
+Attention mechanisms have been widely applied within the deep learning literature to give more flexibility to RNNs [@Bahdanau2015a] and subsequently as a replacement for FCNs in the so-called Transformer architecture, which is now widely used in natural language processing [@Vaswani2017a], and, more recently, has been applied to computer vision and tabular modelling tasks.
+Attention mechanisms allow deep neural nets to weight the covariates entering the model in a flexible manner; these types of applications are demonstrated in, for example, [@Vaswani2017a].
+In this section we provide an introduction to attention mechanisms and then discuss applications of attention to modeling tabular data.
 
@@
 \begin{equation}
-A: \mathbb{R}^{q \times (q \times d) \times (q \times d)} \to \mathbb{R}^q, ~~
-(\mathbf{q}, K, V) ~\mapsto ~ \mathbf{v} = A(\mathbf{q}, K, V),
+A: \mathbb{R}^{(q \times d) \times (q \times d) \times (q \times d)} \to \mathbb{R}^(q \times d), ~~
+(Q, K, V) ~\mapsto ~ V^* = A(Q, K, V),
 \label{eq:attention}
@@
 ```
-
-where $\mathbf{q} \in \mathbb{R}^q$ is a query vector, $K \in \mathbb{R}^{q \times d}$ is a matrix of key vectors,
-$V \in \mathbb{R}^{q \times d}$ is a matrix of value vectors and $\mathbf{v} \in \mathbb{R}^q$, the output of the 
-attention mechanism, is a new vector of values. Several different options for the mapping \eqref{eq:attention} exist in 
-the literature; here we first describe the self-attention mechanism used in [@Vaswani2017a]. In more detail, consider 
-that $V$ is a matrix of covariates relating to a regression problem, which can be composed of embeddings of the same 
-dimension for several categorical variables. We wish to apply the attention mechanism to $V$ to estimate the most 
-important of these embeddings for the regression problem. To do this, we formulate the query vector $\mathbf{q}$ which 
-contains information about the regression problem at hand; this is usually done by passing $L$ through a FCN. 
-Similarly, the matrix $K$ contains the relevance of each row of $L$ for the regression problem and is also usually 
-derived by passing each row of $L$ through another FCN. Finally, the matrix $V$ can be set equal to $L$ or 
-alternatively, can be derived as a transformation of $L$ using a third FCN. The first step of the attention mechanism 
-is to derive a vector $\mathbf{a}$ of attention scores:
+where $Q \in \mathbb{R}^{q \times d}$ is a matrix of query vectors, $K \in \mathbb{R}^{q \times d}$ is a matrix of key vectors, $V \in \mathbb{R}^{q \times d}$ is a matrix of value vectors and $V^* \in \mathbb{R}^{q \times d}$, the output of the attention mechanism, is a new matrix of values.
+Several different options for the mapping \eqref{eq:attention} exist in the literature; here we describe the self-attention mechanism used in [@Vaswani2017a].
+In more detail, consider that $V$ is a matrix of covariates relating to a regression problem, which, in the case of tabular data, will usually be composed of embeddings of the same dimension for several different categorical or numerical variables; in the case discussed here we have $q$ covariates in the form of embeddings of dimension $d$.
+We wish to apply the attention mechanism to $V$ to assign weights to the most important embeddings for the regression problem; this is done from the \`\`perspective" of each covariate in $V$.
+To do this, we formulate the query matrix $Q$ which contains information about the regression problem at hand; this is usually done by passing $V$ through a FCN trained to derive queries from the covariates.
+Similarly, the matrix $K$ contains the relevance of each row of $V$ for the regression problem and is also usually derived by passing each row of $V$ through another FCN.
+Finally, the matrix $V$ can be processed with a third FCN or left as is.
+The first step of the attention mechanism is to derive a matrix $A \in \mathbb{R}^{q \times q}$ of attention scores:
 
@@
 \begin{equation}
-\mathbb{R}^{(1 \times q) \times (q \times d)} \to \mathbb{R}^{1 \times d}, ~~
-(\bold{q}, K) ~\mapsto ~ \mathbf{a} = \langle \mathbf{q}, K^T \mathbb\rangle.
+\mathbb{R}^{(q \times d) \times (q \times d)} \to \mathbb{R}^{q \times q}, ~~
+(Q, K) ~\mapsto ~ A = Q~K^T.
 \label{eq:attention_scores}
@@
 ```
-The attention scores are then normalized using a soft max function i.e.
+The attention scores $A$ are then normalized, or made to sum to unity, across the columns of $A$ using a soft max function i.e.
 
@@
 \begin{equation}
-a^*_i = \frac{e^{(a_i)}}{\sum_{n=1}^{d} e^{(a_n)}}.
+A^*_{i,j} = \frac{e^{(A_{i,j})}}{\sum_{n=1}^{q} e^{(A_{i,n})}}.
 \end{equation}
 ```
-Finally, a linear combination of $V$ is formed:
+Finally, a linear combination of $V$ is formed to give the new matrix of covariates $V^*$:
 
@@
 \begin{equation}
-\mathbb{R}^{(1 \times d) \times (d \times q)} \to \mathbb{R}^{1 \times q}, ~~
-(\mathbf{a^*}, V) ~\mapsto ~ \mathbf{v} = \langle \mathbf{a^*}, V \mathbb\rangle.
+\mathbb{R}^{(q \times q) \times (q \times d)} \to \mathbb{R}^{q \times d}, ~~
+(A^*, V) ~\mapsto ~ V^* = A^*~V.
 \label{eq:attention_output}
@@
 ```
+In most applications of attention, Equation \ref{eq:attention_scores} is modified by dividing the attention scores by $d^{\frac{1}{2}}$.
+
+An intuitive explanation of the attention formula is as follows: we start by considering the importance of all of the covariates that we have for our modelling problem in the context of each individual covariate.
+This is done by assigning a score between zero and one to each covariate in the modelling problem, and we repeat this process for each of the covariates.
+Then, we replace each of the original covariates with a new covariate that has been formed by taking a weighted average of the covariates and the scores.
+
+### Transformer models
+
+Self-attention is the main building block of the current state of the art model for natural language processing, which is the Transformer model [@Vaswani2017].
+The basic Transformer model applies self-attention to the covariate matrix, $X'$ which is fed into the model, to produce a new matrix of covariates, $X^*$.
+The two matrices are added (in an element-wise manner) together and then normalized.
+This matrix is then further processed through a neural network and subsequently, these processed covariates are used in the machine learning task.
+The Transformer model is much more accurate on NLP tasks comapred to using the raw covariates before processing with a Transformer, to the extent that this model now underlies most NLP applications that use deep learning.
+
+### Attention Modelling for Tabular Data
+
+Several different approaches to applying attention within the modelling of tabular data have been proposed in the literature.
+Perhaps the simplest way of doing this is to insert an attention layer between the embeddings and the rest of the neural network.
+Mathematically, we can modify Equation \ref{eq:embed_to_nn} as follows:
+
+```{=latex}
+\begin{eqnarray}
+  X^* = Attn(X') \\
+  z^1 = \sigma(a_1.X^* + b_1),
+\label{eq:embed_to_attn_to_nn}
+\end{eqnarray}
+```
+where $X' \in \mathbb{R}^{q \times d}$ is the matrix of embeddings after concatenating $q$ embeddings of dimension $d$ together and $X^*$ represents the matrix of embeddings $X'$ after processing with attention.
+Below, we demonstrate the effect of adding this simple application of attention to a tabular model.
+
+[@Huang2020] refines this approach in a model they call the TabTransformer.
 
@@
 
-In this section, we walk through a simple predictive modeling exercise in order to illustrate the application of 
-embeddings. First, we pose a supervised regression problem, based on flood insurance claims severity. We then describe, 
-fit, and evaluate GLMs and neural networks utilizing embeddings for this problem. Finally, we discuss visualization 
-techniques for model interpretation. As we proceed, we also incorporate practical technical guidance on modeling
-procedure.
+In this section, we walk through a simple predictive modeling exercise in order to illustrate the application of embeddings.
+First, we pose a supervised regression problem, based on flood insurance claims severity.
+We then describe, fit, and evaluate GLMs and neural networks utilizing embeddings for this problem.
+Finally, we discuss visualization techniques for model interpretation.
+As we proceed, we also incorporate practical technical guidance on modeling procedure.
 
@@
 
-(talk about experiment setup -- we take a subset of data that's shared for all models, then for the CV performance
-evaluation only we use all data in CV splits?)
+(talk about experiment setup -- we take a subset of data that's shared for all models, then for the CV performance evaluation only we use all data in CV splits?)
 
@@
 
-These model architectures are relatively uncomplicated by today's standards, and are so chosen to better highlight the
-embedding components. Later, in Section \ref{attn}, we will investigate more involved architectures utilizing embeddings
-that represent the state of the art for modeling tabular data.
+These model architectures are relatively uncomplicated by today's standards, and are so chosen to better highlight the embedding components.
+Later, in Section X (TODO), we will investigate more involved architectures utilizing embeddings that represent the state of the art for modeling tabular data.
 
@@
     -   `primary_residence`
+
 -   Link function: $\log$
+
 -   Distribution: gamma
 
-We take the log of the continuous predictor `building_insurance_coverage`, which allows the scale of the predictor to 
-match that of the target variable. Because the `flood_zone` variable in the original data contains 60 levels, we take 
-the prefix of the zone code, which corresponds to the level of risk as determined by FEMA [^8]. For example, `"A01"`, 
-`"A02"`, and so on are recoded as simply `"A"`. A log link together with the gamma distribution is a standard choice 
-for severity modeling, which provides a multiplicative structure where the response is positive. Following the notation
-in \@ref(catdata), the number of parameters in the GLM is
+We take the log of the continuous predictor `building_insurance_coverage`, which allows the scale of the predictor to match that of the target variable.
+Because the `flood_zone` variable in the original data contains 60 levels, we take the prefix of the zone code, which corresponds to the level of risk as determined by FEMA [^3].
+For example, `"A01"`, `"A02"`, and so on are recoded as simply `"A"`.
+A log link together with the gamma distribution is a standard choice for severity modeling, which provides a multiplicative structure where the response is positive.
 
-\begin{equation}
-1 + |J^{\text{num}}| + \left(\sum_{j \in J^{\text{cat}}} n_{\mathcal{P}}^j\right) - |J^{\text{cat}}|:
-(\#eq:glm1)
-\end{equation}
+[^3]: <https://www.floodsmart.gov/flood-map-zone/find-yours>
 
-one for the intercept, one for each numeric variable, and the numbers of levels minus one (due to dummy coding) for 
-each categorical variable.
+In Table \@ref(tab:relativities), we exhibit an exerpt of the relativities, or exponentiated fitted coefficients, of a couple categorical variables.
+Recall that the choice of the log link gives a multiplicative structure, so the interpretation of 1.37 for `occupancy_type = "Non-residential building"` is that, all else equal, the expected loss for a policy for a non-residential building is 1.37 times that of a policy for a single family home, which is the base, or reference, level for the factor.
 
-[^8]: https://www.floodsmart.gov/flood-map-zone/find-yours
+| variable       | label                                       | relativity |
+|:---------------|:--------------------------------------------|-----------:|
+| occupancy_type | Single family residence                     |       1.00 |
+| occupancy_type | Non-residential building                    |       1.37 |
+| occupancy_type | 2 to 4 unit residential buidling            |       1.15 |
+| occupancy_type | Residential building with more than 4 units |       1.64 |
+| flood_zone     | B                                           |       1.00 |
+| flood_zone     | A                                           |       0.84 |
+| flood_zone     | C                                           |       0.60 |
+| flood_zone     | X                                           |       0.70 |
+| flood_zone     | V                                           |       0.78 |
+| flood_zone     | D                                           |       0.89 |
 
-In Table \@ref(tab:relativities), we exhibit an exerpt of the relativities, or exponentiated fitted coefficients, 
-of a couple categorical variables. Recall that the choice of the log link gives a multiplicative structure, so the
-interpretation of 1.37 for `occupancy_type = "Non-residential building"` is that, all else equal, the expected 
-loss for
-a policy for a non-residential building is 1.37 times that of a policy for a single family home, which is the base,
-or reference, level for the factor.
-
-Table: (\#tab:relativities) Excerpt of relativities for Model 1.
-
-|variable       |label                                       | relativity|
-|:--------------|:-------------------------------------------|----------:|
-|occupancy_type |Single family residence                     |       1.00|
-|occupancy_type |Non-residential building                    |       1.37|
-|occupancy_type |2 to 4 unit residential buidling            |       1.15|
-|occupancy_type |Residential building with more than 4 units |       1.64|
-|flood_zone     |B                                           |       1.00|
-|flood_zone     |A                                           |       0.84|
-|flood_zone     |C                                           |       0.60|
-|flood_zone     |X                                           |       0.70|
-|flood_zone     |V                                           |       0.78|
-|flood_zone     |D                                           |       0.89|
+: (\#tab:relativities) Excerpt of relativities for Model 1.
 
@@
 For Model 2, we build a feedforward neural network, whose architecture is shown in Figure \@ref(fig:nn-1).
-The categorical inputs go through one-dimensional embedding
-layers where they are each mapped to a scalar. The embeddings are then concatenated with the numeric predictors, which
-have been normalized in data pre-processing, before being sent to a hidden linear layer of 64 units. A ReLU activation,
+The categorical inputs go through one-dimensional embedding layers where they are each mapped to a scalar.
+The embeddings are then concatenated with the numeric predictors, which have been normalized in data pre-processing, before being sent to a hidden linear layer of 64 units.
+A ReLU (TODO: reference an equation in prev.
+section) activation is then applied to the outputs before they are sent to a final output layer resulting in a scalar.
+To constrain predictions to be positive, we apply softplus activation, which is defined to be
 
-\begin{equation}
-x \mapsto \max(0, x),
-\end{equation}
+$$
+x \mapsto \log(1 + e^x). 
+$$
 
-is then applied to the outputs before they are sent to a final output layer resulting in a scalar. To constrain
-predictions to be positive, we apply softplus activation, which is defined to be
-
-\begin{equation}
-x \mapsto \log(1 + e^x). 
-\end{equation}
-
-```{r nn-1, echo = FALSE, fig.cap = "Architecture of Models 2 and 4.", out.width = "80%", fig.align = "center"}
+```{r nn-1, echo = FALSE, fig.cap = "Architecture of Models 2 and 4.", out.width = "90%", fig.align = "center"}
 knitr::include_graphics("images/nn.png")
@@
 
-With a single hidden layer, this architecture is the simplest nontrivial neural network; without the hidden layer and
-corresponding ReLU activation, we would actually recover a GLM structure where the link function is the output 
-activation. 
-The choice of one for the embedding dimension is also due to simplicity: it is easily interpretable as the 
-representation
-of each factor level as a point on the real number line, also, the trained embeddings are easily incorporated into a GLM
-which we will see in Model 3. In practice, the embedding dimension is a hyperparameter one can tune, for example via
-cross validation, and can vary for each variable. However, we also note that the choice of one for the 
-embedding output dimension is not an unreasonable one, especially when the cardinalities of the categorical variables
-are not unusually large.
+With a single hidden layer, this architecture is the simplest nontrivial neural network; without the hidden layer and corresponding ReLU activation, we would actually recover a GLM structure where the link function is the output activation.
+The choice of one for the embedding dimension is also due to simplicity: it is easily interpretable as the representation of each factor level as a point on the real number line, also, the trained embeddings are easily incorporated into a GLM which we will see in Model 3.
+In practice, the embedding dimension is a hyperparameter one can tune, for example via cross validation, and can vary for each variable.
+However, we also note that the choice of one for the embedding output dimension is not an unreasonable one, especially when the cardinalities of the categorical variables are not unusually large.
 
-In Tables \@ref(tab:embeddings-occupancy-type) and \@ref(tab:embeddings-flood-zone), we show the learned embeddings
-for the `occupancy_type` and an excerpt of them for `flood_zone`. While it may be tempting to compare these values
-to those in Table \@ref(tab:relativities), they represent fundamentally different concepts. It is helpful to think
-of the embedding values for each variable as a continuous represention of the variable itself, rather than a 
-"coefficient" associated with the variable. Note that it is not straightforward to inspect the embeddings from a
-table and infer relationships to the response variable, even in a shallow network such as ours, due to nonlinearities
-within the model. Also note that we now have a way to incorporate the full granularity of the `flood_zone` variable,
-which is why more levels are shown in Table \@ref(tab:embeddings-flood-zone) as compared to Table 
-\@ref(tab:relativities). In Section \ref{interpretation}, we will discuss techniques to visualize these embeddings.
+In Tables \@ref(tab:embeddings-occupancy-type) and \@ref(tab:embeddings-flood-zone), we show the learned embeddings for the `occupancy_type` and an excerpt of them for `flood_zone`.
+While it may be tempting to compare these values to those in Table \@ref(tab:relativities), they represent fundamentally different concepts.
+It is helpful to think of the embedding values for each variable as a continuous represention of the variable itself, rather than a "coefficient" associated with the variable.
+Note that it is not straightforward to inspect the embeddings from a table and infer relationships to the response variable, even in a shallow network such as ours, due to nonlinearities within the model.
+Also note that we now have a way to incorporate the full granularity of the `flood_zone` variable, which is why more levels are shown in Table \@ref(tab:embeddings-flood-zone) as compared to Table \@ref(tab:relativities).
+In Section TODO, we will discuss techniques to visualize these embeddings.
 
-Table: (\#tab:embeddings-occupancy-type) Learned embeddings for `occupancy_type`.
+| level                                       | embedding |
+|:--------------------------------------------|----------:|
+| 2 to 4 unit residential buidling            |      6.69 |
+| Non-residential building                    |      7.16 |
+| Residential building with more than 4 units |      6.33 |
+| Single family residence                     |      5.43 |
 
-|level                                       | embedding|
-|:-------------------------------------------|---------:|
-|2 to 4 unit residential buidling            |      6.69|
-|Non-residential building                    |      7.16|
-|Residential building with more than 4 units |      6.33|
-|Single family residence                     |      5.43|
+: (\#tab:embeddings-occupancy-type) Learned embeddings for `occupancy_type`.
 
-Table: (\#tab:embeddings-flood-zone) Excerpt of learned embeddings for `flood_zone`.
+| level | embedding | level | embedding | level | embedding | level | embedding | level | embedding |
+|:------|----------:|:------|----------:|:------|----------:|:------|----------:|:------|----------:|
+| A     |      0.38 | A09   |     -1.71 | A18   |     -1.40 | A99   |     -2.68 | V     |     -0.41 |
+| A00   |     -0.35 | A0B   |      3.85 | A19   |     -1.70 | AE    |     -4.46 | V02   |      0.65 |
+| A01   |     -6.76 | A10   |     -4.03 | A20   |     -4.05 | AH    |     -2.35 | V03   |     -0.29 |
+| A02   |     -4.28 | A11   |     -5.32 | A21   |     -2.08 | AHB   |     -1.71 | V04   |     -1.15 |
+| A03   |     -5.93 | A12   |     -3.23 | A22   |     -2.11 | AO    |     -6.07 | V05   |     -0.50 |
+| A04   |     -7.82 | A13   |      2.03 | A23   |     -1.40 | AOB   |     -4.56 | V06   |     -1.92 |
+| A05   |     -3.42 | A14   |     -5.72 | A24   |      2.23 | AR    |     -0.48 | V07   |     -2.91 |
+| A06   |     -4.97 | A15   |     -3.67 | A25   |      0.28 | B     |     -5.36 | V08   |     -2.24 |
+| A07   |     -3.09 | A16   |     -3.02 | A27   |     -2.56 | C     |     -4.47 | V09   |     -0.75 |
+| A08   |     -4.69 | A17   |     -0.37 | A30   |      1.13 | D     |     -0.76 | V10   |     -2.05 |
 
-|level | embedding|level | embedding|level | embedding|level | embedding|level | embedding|
-|:-----|---------:|:-----|---------:|:-----|---------:|:-----|---------:|:-----|---------:|
-|A     |      0.38|A09   |     -1.71|A18   |     -1.40|A99   |     -2.68|V     |     -0.41|
-|A00   |     -0.35|A0B   |      3.85|A19   |     -1.70|AE    |     -4.46|V02   |      0.65|
-|A01   |     -6.76|A10   |     -4.03|A20   |     -4.05|AH    |     -2.35|V03   |     -0.29|
-|A02   |     -4.28|A11   |     -5.32|A21   |     -2.08|AHB   |     -1.71|V04   |     -1.15|
-|A03   |     -5.93|A12   |     -3.23|A22   |     -2.11|AO    |     -6.07|V05   |     -0.50|
-|A04   |     -7.82|A13   |      2.03|A23   |     -1.40|AOB   |     -4.56|V06   |     -1.92|
-|A05   |     -3.42|A14   |     -5.72|A24   |      2.23|AR    |     -0.48|V07   |     -2.91|
-|A06   |     -4.97|A15   |     -3.67|A25   |      0.28|B     |     -5.36|V08   |     -2.24|
-|A07   |     -3.09|A16   |     -3.02|A27   |     -2.56|C     |     -4.47|V09   |     -0.75|
-|A08   |     -4.69|A17   |     -0.37|A30   |      1.13|D     |     -0.76|V10   |     -2.05|
+: (\#tab:embeddings-flood-zone) Excerpt of learned embeddings for `flood_zone`.
 
@@
 
-For Model 3, we return to the GLM, but now we replace the categorical variables with the trained embeddings from Model
-2. In other words, our model now contains only continuous variables, and each categorical factor is represented as a
-scalar value and obtains its own coefficient. In contrast with the number of parameters computed in Equation
-\@ref(eq:glm1), we have fewer parameters for this model:
-
-\begin{equation}
-1 + |J^{\text{num}}| + |J^{\text{cat}}|.
-(\#eq:glm2)
-\end{equation}
-
-Hence, the model can be written as
-
-\begin{equation}
-\mu_i = \beta_0 + \sum_{j \in J^{\text{num}}}\beta_j x_{i,j} + \sum_{j \in J^{\text{cat}}} \beta_j z_{i,j},
-\end{equation}
-
-where $z_{i,j}$ represents the embedding value for $i$th instance of the categorical column $X_j$.
-
-Although in this particular example we incorporate one-dimensional embeddings, one can easily include multidimensional
-embeddings, which would increase the model's flexibility. The modeler would need to balance the additional lift with
-some loss of interpretability, since with one-dimensional embeddings, our GLM structure dictates that there is a 
-monotonic relationship between the predicted response and the input embedding, which could be desirable in certain
-use cases (and undesirable in others.)
-
-Since we only have a few parameters in this model, we exhibit the full list of fitted coefficients in Table 
-\@ref(tab:glm2).
-
-Table: (\#tab:glm2) Coefficients of Model 3.
-
-|term                                     | estimate|
-|:----------------------------------------|--------:|
-|(Intercept)                              |    2.389|
-|total_building_insurance_coverage        |    0.568|
-|basement_enclosure_crawlspace_type       |    0.136|
-|number_of_floors_in_the_insured_building |   -0.024|
-|occupancy_type                           |    0.067|
-|flood_zone                               |    0.035|
-|primary_residence                        |   -0.001|
-|community_rating_system_discount         |    0.504|
+For Model 3, we return to the GLM, but now we replace the categorical variables with the trained embeddings from Model 2.
+In other words, our model now contains only continuous variables, and each categorical factor is represented as a scalar value and obtains its own coefficient.
+(TODO: insert formal eqn for mean)
 
@@
 
-Model 4 is architecturally identical to Model 2, with the only difference being the number of embedding dimensions:
-instead of mapping factor levels to real numbers, we map them to points in Euclidean space, where the dimension of the 
-space is the ceiling
-of the factor's cardinality divided by two. Formally, in the notation of Section \ref{catdata},
-$q_{\mathcal{P}^j}=\ceil{n^j_{\mathcal{P}}/2}$ for variable $X_j$. Following the practice from the previous three
-models, we list the fitted embeddings for a couple variables in Tables \@ref(tab:nn2-occupancy-type) and 
-\@ref(tab:nn2-flood-zone). Note that, for `flood_zone`, we are
-only displaying the embedding for *one* level.
+Model 4 is architecturally identical to Model 2, with the only difference being the number of embedding dimensions: instead of mapping factor levels to real numbers, we map them to a point in Euclidean space, where the dimension of the space is the ceiling of the factor's cardinality divided by two.
+Formally, in the notation of Section \ref{catdata}, $q_{\mathcal{P}^j}=\ceil{n^j_{\mathcal{P}}/2}$ for variable $X_j$.
 
-Table: (\#tab:nn2-occupancy-type) Learned embeddings for `occupancy_type` in Model 4.
+## Model Training and Results
 
-|level                                       |    e1|    e2|   e3|
-|:-------------------------------------------|-----:|-----:|----:|
-|2 to 4 unit residential buidling            | -1.44| -1.97| 2.35|
-|Non-residential building                    | -6.83| -8.11| 5.34|
-|Residential building with more than 4 units | -7.63| -6.58| 5.09|
-|Single family residence                     | -1.61| -2.54| 3.01|
+To evaluate these baseline models and other models in this paper, we perform 10-fold cross validation and compare the root mean square error (RMSE) on the predicted and actual paid amounts.
+(somehwere we should say we're not doing a kaggle competition here and the performance metrics are really meant to show that the models aren't complete shit) (maybe a couple boxplots showing metrics for baseline models)
 
-Table: (\#tab:nn2-flood-zone) Learned embeddings for level `"A00"` of variable `flood_zone` in Model 4.
+## Interpretations {#interpretation}
 
-|dimension |value  |dimension |value  |dimension |value  |dimension |value  |
-|:---------|:------|:---------|:------|:---------|:------|:---------|:------|
-|e1        |0.020  |e11       |2.146  |e21       |-1.933 |e31       |-0.941 |
-|e2        |-0.885 |e12       |1.723  |e22       |1.150  |e32       |-1.279 |
-|e3        |-0.126 |e13       |0.378  |e23       |0.863  |e33       |-0.360 |
-|e4        |1.491  |e14       |-0.310 |e24       |-0.471 |e34       |-1.173 |
-|e5        |0.980  |e15       |2.482  |e25       |0.929  |          |       |
-|e6        |0.952  |e16       |1.823  |e26       |-1.139 |          |       |
-|e7        |-0.217 |e17       |-2.715 |e27       |0.113  |          |       |
-|e8        |-0.611 |e18       |1.144  |e28       |1.155  |          |       |
-|e9        |0.919  |e19       |-0.045 |e29       |0.707  |          |       |
-|e10       |-1.196 |e20       |0.467  |e30       |1.358  |          |       |
-
-## Visualization Techniques for Interpretation {#interpretation}
-
-With AI and ML coming into the mainstream across industries and use cases, the topic of model explainability
-has received increasing attention. In insurance pricing, @kuo2020explainability propose a framework for
-model interpretability in the context of regulation and actuarial standards of practice, while @henckaerts2020boosting
-investigate algorithm-specific techniques to inspect tree-based models. @kuo2020explainability and references
-therein also discuss
-commonly utilized model-agnostic explanation techniques, such as permutation variable importance and partial
-dependence plots, that can be applied to the neural networks we consider in this paper.
-
-In this section, we focus on ways to visualize the learned embeddings. In the authors' experiences, oftentimes
-the formats of the visualizations --- basic line and scatter plots --- even more so than the content of the data, is 
-helpful in explaining the concept to stakeholders.
-
-For Model 2, the neural network with one-dimensional embeddings, the task is simple: we can simply plot the levels
-on a line, as in Figure \@ref(fig:num-floors). In the case of `flood_zone`, since we happen to have the luxury of knowing a
-priori the meaning of the prefixes, we can plot them separately, as in Figure \@ref(fig:flood-zone) to see how the model 
-mapped them.
-
-```{r num-floors, echo=FALSE, fig.cap="Number of floors", out.width = "80%", fig.align="center"}
-knitr::include_graphics("images/num_floors.png")
-```
-
-```{r flood-zone, echo = FALSE, fig.cap="Flood zone embeddings", out.width = "60%", fig.align = "center"}
-knitr::include_graphics("images/flood_zone.png")
-```
-
-For Model 4, the neural network with multi-dimensional embeddings, we would need to treat the learned values before
-we can plot them. Specifically, we need to reduce the dimension of the data to 2D for embeddings with more than
-two dimensions. The standard approachs for this are principal component analysis (PCA) and t-distributed stochastic
-neighbor embedding (t-SNE), both of which we illustrate below.
-
-### PCA
-
-(TODO: insert brief theoretical stuff). See Figure \@ref(fig:flood-zone-pca).
-
-```{r flood-zone-pca, echo = FALSE, fig.cap="Flood zone PCA", out.width = "60%", fig.align = "center"}
-knitr::include_graphics("images/flood_zone_pca.png")
-```
-
-### t-SNE
-
-(TODO: insert brief theoretical stuff). See Figure \@ref(fig:flood-zone-tsne).
-
-```{r flood-zone-tsne, echo = FALSE, fig.cap="Flood zone t-SNE", out.width = "60%", fig.align = "center"}
-knitr::include_graphics("images/flood_zone_tsne.png")
-```
-
-## Training and Inference
-
-(TODO)
+-   model explainability is important in insurance
+-   the more we can learn about how we arrive at our models the better
+-   cite some existing work on explainable models in actuarial literature to show people care
+-   refer back to some definitions from previous sections
+-   show some embedding weights from our models - 1d line plot
+-   (need a multidimensional embedding for this) do some pca/tsne
+-   stress that relationship of embedding weights to response variable may be nonlinear depending on architecture
 
@@
 
-Investigate approaches for using embedding layers for numeric variables, or numeric variables that were captured as 
-categorical variables (Can the modelling of numerical variables benefit from the application of embedding layers?) How 
-should this best be done? CatBoost - cut into 256 groups smoothness Map numeric to a dense layer and use that as 
-embedding - basis expansion Add a distribution to the embeddings Can insights from credibility theory lead to enhanced embeddings?
+Investigate approaches for using embedding layers for numeric variables, or numeric variables that were captured as categorical variables (Can the modelling of numerical variables benefit from the application of embedding layers?) How should this best be done?
+CatBoost - cut into 256 groups smoothness Map numeric to a dense layer and use that as embedding - basis expansion Add a distribution to the embeddings Can insights from credibility theory lead to enhanced embeddings?
 Take credibility mixture over embeddings Cluster embeddings PCA of embeddings
 
-# Attention based modelling {#attn}
+# Attention based modelling
 
@@
 Conclusions
-
-\newpage
-
-# References {.unnumbered}

### 2021-03-25 manuscript/manuscript.Rmd
Update attn model

@@
 Attention mechanisms allow deep neural nets to weight the covariates entering the model in a flexible manner; these types of applications are demonstrated in, for example, [@Vaswani2017a].
-In this section we provide an introduction to attention mechanisms and then discuss applications of attention to modeling tabular data.
+In this section we provide a theoretical introduction to attention mechanisms and then discuss applications of attention to modeling tabular data.
+In the following sections of this paper, we then consider whether adding attention to an model that uses embeddings can provide better predictive accuracy.
 
@@
 ```
-where $Q \in \mathbb{R}^{q \times d}$ is a matrix of query vectors, $K \in \mathbb{R}^{q \times d}$ is a matrix of key vectors, $V \in \mathbb{R}^{q \times d}$ is a matrix of value vectors and $V^* \in \mathbb{R}^{q \times d}$, the output of the attention mechanism, is a new matrix of values.
+where $Q \in \mathbb{R}^{q \times d}$ is a matrix of query vectors, $K \in \mathbb{R}^{q \times d}$ is a matrix of key vectors, $X' \in \mathbb{R}^{q \times d}$ is a matrix of value vectors and $X^* \in \mathbb{R}^{q \times d}$, the output of the attention mechanism, is a new matrix of values.
 Several different options for the mapping \eqref{eq:attention} exist in the literature; here we describe the self-attention mechanism used in [@Vaswani2017a].
-In more detail, consider that $V$ is a matrix of covariates relating to a regression problem, which, in the case of tabular data, will usually be composed of embeddings of the same dimension for several different categorical or numerical variables; in the case discussed here we have $q$ covariates in the form of embeddings of dimension $d$.
-We wish to apply the attention mechanism to $V$ to assign weights to the most important embeddings for the regression problem; this is done from the \`\`perspective" of each covariate in $V$.
-To do this, we formulate the query matrix $Q$ which contains information about the regression problem at hand; this is usually done by passing $V$ through a FCN trained to derive queries from the covariates.
-Similarly, the matrix $K$ contains the relevance of each row of $V$ for the regression problem and is also usually derived by passing each row of $V$ through another FCN.
-Finally, the matrix $V$ can be processed with a third FCN or left as is.
+In more detail, consider that $X'$ is a matrix of covariates relating to a regression problem, which, in the case of tabular data, will usually be composed of embeddings of the same dimension for several different categorical or numerical variables; in the case discussed here we have $q$ covariates in the form of embeddings of dimension $d$.
+For clarity, note that in Equation \ref{eq:embed_to_nn} we have used the symbol $X'$ to denote the vector of embeddings and numerical inputs which is passed into the neural network.
+In what follows, we now use the symbol $X'$ to refer to the matrix of embeddings of dimension $q \times d$.
+
+We wish to apply the attention mechanism to $X'$ to assign weights to the most important embeddings for the regression problem; this is done from the \`\`perspective" of each covariate in $x'$.
+To do this, we formulate the query matrix $Q$ which contains information about the regression problem at hand; this is usually done by passing $X'$ through a FCN trained to derive queries from the covariates.
+Similarly, the matrix $K$ contains the relevance of each row of $V$ for the regression problem and is also usually derived by passing each row of $X'$ through another FCN.
+Finally, the matrix $X'$can be processed with a third FCN or left as is.
 The first step of the attention mechanism is to derive a matrix $A \in \mathbb{R}^{q \times q}$ of attention scores:
@@
 ```
-Finally, a linear combination of $V$ is formed to give the new matrix of covariates $V^*$:
+Finally, a linear combination of $X'$ is formed to give the new matrix of covariates $X^*$:
 
@@
 \mathbb{R}^{(q \times q) \times (q \times d)} \to \mathbb{R}^{q \times d}, ~~
-(A^*, V) ~\mapsto ~ V^* = A^*~V.
+(A^*, x') ~\mapsto ~ X^* = A^*~X'.
 \label{eq:attention_output}
@@
 Self-attention is the main building block of the current state of the art model for natural language processing, which is the Transformer model [@Vaswani2017].
-The basic Transformer model applies self-attention to the covariate matrix, $X'$ which is fed into the model, to produce a new matrix of covariates, $X^*$.
-The two matrices are added (in an element-wise manner) together and then normalized.
+The basic Transformer model applies a self-attention to the covariate matrix, $X'$ which is fed into the model, to produce a new matrix of covariates, $X^*$.
+These two matrices, the input matrix $X'$ and the output matrix $X^*$ are added (in an element-wise manner) together and then normalized.
 This matrix is then further processed through a neural network and subsequently, these processed covariates are used in the machine learning task.
+
 The Transformer model is much more accurate on NLP tasks comapred to using the raw covariates before processing with a Transformer, to the extent that this model now underlies most NLP applications that use deep learning.
@@
 
-[@Huang2020] refines this approach in a model they call the TabTransformer.
+[@Huang2020] refines this approach in a model they call the TabTransformer, which implements two main changes to the approach shown in Equations \ref{eq:embed_to_attn_to_nn}.
+The first of these is that, instead of using the matrix of embeddings after processing with self-attention ($X'$) directly in the model, the output of a Transformer model is used instead.
+The second of these refinements is that for each of the $q$ covariates with an embedding in the matrix $X'$, we include a new row embedding which denotes which covariate each embedding relates to.
+Thus, in the TabTransformer model, we augment the embedding matrix with extra columns, so that the dimension of this matrix is $q \times (d + d_col)$, where $d_col$ is the dimension of the row embedding.
+[@Huang2020] find that including this identifier improves the performance of the model.
+We compare the results of the TabTransformer model to the other models tested below.
+
+Finally, a different way of incorporating attention into the modeling of tabular data has been proposed by [@Ark2019], who refer to their model as TabNet.
 

### 2021-03-25 manuscript/manuscript.Rmd
Add TabNet description

@@
 In the following sections of this paper, we then consider whether adding attention to an model that uses embeddings can provide better predictive accuracy.
+The following is intended as a high level review of some of the relevant theory behind attention based approaches; for more technical details the sources quoted in this section can be consulted.
 
@@
 ```
-The attention scores $A$ are then normalized, or made to sum to unity, across the columns of $A$ using a soft max function i.e.
+The attention scores $A$ are then normalized, or made to sum to unity, across the columns of $A$ using a so-called softmax function i.e.
 
@@
 A^*_{i,j} = \frac{e^{(A_{i,j})}}{\sum_{n=1}^{q} e^{(A_{i,n})}}.
+\label{eq:softmax}
 \end{equation}
@@
 Finally, a different way of incorporating attention into the modeling of tabular data has been proposed by [@Ark2019], who refer to their model as TabNet.
+In summary, the main idea of the TabNet model is to try emulate the excellent performance of decision trees on tabular data modelling using deep neural networks.
+This is done by structuring the neural networks to emulate a key aspect of decision tree modelling, which is the efficient selection of relevant covariates for the model task.
+Within TabNet, an attention based model is used to select features by estimating attention scores for each covariate within $X$.
+The covariates are multiplied by the attention scores to downweight less relevant features for the prediction problem.
 

### 2021-03-25 R/model-utils.R
Added simple attn NN

@@ -85,6 +85,40 @@ simple_net <- nn_module(
     }
 )
 
+
+simple_net_attn <- nn_module(
+    "simple_net_attn",
+    initialize = function(cardinalities,
+                          num_numerical,
+                          units = 16,
+                          embed_dim = 5,
+                          fn_embedding_dim = function(x) embed_dim) {
+        self$embedder <- embedding_module_attn(cardinalities, fn_embedding_dim)
+        sum_embedding_dim <- sapply(cardinalities, fn_embedding_dim) %>%
+            sum()
+        self$embed_dim = fn_embedding_dim()
+        self$attn <- nn_multihead_attention(embed_dim = 5, num_heads = 1)
+        self$fc <- nn_linear(sum_embedding_dim + num_numerical, units)
+        self$output <- nn_linear(units, 1)
+        device <- if (cuda_is_available()) torch_device("cuda:0") else "cpu"
+        self$to(device = device)
+    },
+    forward = function(xcat, xnum) {
+        embedded <- self$embedder(xcat)
+        shapes = embedded$shape
+        embedded_reshape = embedded$view(list(embedded$shape[1],self$embed_dim,self$embed_dim))
+        embedded_attended <- self$attn(embedded_reshape, embedded_reshape, embedded_reshape)
+        embedded_attended <- embedded_attended[[1]]
+        embedded_attended = embedded_attended$view(list(embedded$shape[1],self$embed_dim * self$embed_dim))
+        all <- torch_cat(list(embedded_attended, xnum$to(dtype = torch_float())), dim = 2)
+        all %>%
+            self$fc() %>%
+            nnf_relu() %>%
+            self$output() %>%
+            nnf_softplus()
+    }
+)
+
 train_loop_alternate <- function(model, train_dl, valid_dl, epochs, optimizer) {
     for (epoch in seq_len(epochs)) {
         model$train()
@@ -211,7 +245,7 @@ key_with_embeddings <- function(embeddings, key) {
                 `+`(1L) %>%
                 torch_tensor(dtype = torch_int(), device = device) %>%
                 embedder() %>%
-                (function(x) x$to(device = "cpu")) %>% 
+                (function(x) x$to(device = "cpu")) %>%
                 as.numeric()
             key[["embedding"]] <- embedding
             key

### 2021-03-25 manuscript/manuscript.Rmd
Update Transformer details in manuscript

@@
 Self-attention is the main building block of the current state of the art model for natural language processing, which is the Transformer model [@Vaswani2017].
-The basic Transformer model applies a self-attention to the covariate matrix, $X'$ which is fed into the model, to produce a new matrix of covariates, $X^*$.
+A basic Transformer model applies self-attention to the covariate matrix, $X'$ which is fed into the model, to produce a new matrix of covariates, $X^*$.
 These two matrices, the input matrix $X'$ and the output matrix $X^*$ are added (in an element-wise manner) together and then normalized.
 This matrix is then further processed through a neural network and subsequently, these processed covariates are used in the machine learning task.
+Multiple Tranformer network "blocks" can be added to a network to create a deep Transformer network.
 
-The Transformer model is much more accurate on NLP tasks comapred to using the raw covariates before processing with a Transformer, to the extent that this model now underlies most NLP applications that use deep learning.
+The Transformer model is much more accurate on NLP tasks compared to using the raw covariates before processing with a Transformer, to the extent that this model now underlies most NLP applications that use deep learning.
 

### 2021-03-26 R/cv-model-torch.R
Added transformer net

@@ -77,13 +77,26 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
     model_attn <- simple_net_attn(env$cardinalities, length(numeric_cols), units = 64, embed_dim = 5)
 
     optimizer <- optim_adam(model_attn$parameters, lr = learning_rate, weight_decay = 0)
-    # optimizer <- optim_rmsprop(model$parameters, lr = 0.1)
 
     train_loop(model_attn, train_dl, valid_dl, epochs, optimizer)
 
-    replace_unseen_level_weights_(model$embedder$embeddings)
+    replace_unseen_level_weights_(model_attn$embedder$embeddings)
 
     preds_nn_attn <- get_preds(model_attn, test_dl)
+
+    ### add simple transformer based model
+
+    model_transformer <- simple_net_tabtrans(env$cardinalities, length(numeric_cols), units = 64, embed_dim = 5)
+
+    optimizer <- optim_adam(model_transformer$parameters, lr = learning_rate, weight_decay = 0)
+
+    train_loop(model_transformer, train_dl, valid_dl, epochs, optimizer)
+
+    replace_unseen_level_weights_(model_transformer$embedder$embeddings)
+
+    preds_nn_transformer  <- get_preds(model_transformer, test_dl)
+
+    ### use GLMs
 
     form <- amount_paid_on_building_claim ~ total_building_insurance_coverage +
         basement_enclosure_crawlspace_type + number_of_floors_in_the_insured_building +
@@ -129,6 +142,7 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
         model_nn = model,
         model_nn2 = model2,
         model_attn = model_attn,
+        model_transformer = model_transformer,
         rec_nn = rec_nn,
         model_glm = model_glm,
         rec_glm = rec_glm,
@@ -138,6 +152,7 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
         preds_nn = preds_nn,
         preds_nn2 = preds_nn2,
         preds_nn_attn = preds_nn_attn,
+        preds_nn_transformer = preds_nn_transformer,
         preds_glm = preds_glm,
         preds_glm2 = preds_glm2
     )
@@ -152,6 +167,7 @@ cv_results %>%
[…]

### 2021-03-26 R/model-utils.R

@@ -93,11 +93,11 @@ simple_net_attn <- nn_module(
                           units = 16,
                           embed_dim = 5,
                           fn_embedding_dim = function(x) embed_dim) {
-        self$embedder <- embedding_module_attn(cardinalities, fn_embedding_dim)
+        self$embedder <- embedding_module(cardinalities, fn_embedding_dim)
         sum_embedding_dim <- sapply(cardinalities, fn_embedding_dim) %>%
             sum()
         self$embed_dim = fn_embedding_dim()
-        self$attn <- nn_multihead_attention(embed_dim = 5, num_heads = 1)
+        self$attn <- nn_multihead_attention(embed_dim = embed_dim, num_heads = 1)
         self$fc <- nn_linear(sum_embedding_dim + num_numerical, units)
         self$output <- nn_linear(units, 1)
         device <- if (cuda_is_available()) torch_device("cuda:0") else "cpu"
@@ -118,6 +118,61 @@ simple_net_attn <- nn_module(
             nnf_softplus()
     }
 )
+
+
+simple_net_tabtrans <- nn_module(
+    "simple_net_tabtrans",
+    initialize = function(cardinalities,
+                          num_numerical,
+                          units = 16,
+                          embed_dim = 5,
+                          fn_embedding_dim = function(x) embed_dim) {
+        self$embedder <- embedding_module(cardinalities, fn_embedding_dim)
+        sum_embedding_dim <- sapply(cardinalities, fn_embedding_dim) %>%
+            sum()
+        self$embed_dim = fn_embedding_dim()
+
+        self$attn <- nn_multihead_attention(embed_dim = embed_dim, num_heads = 1)
+
+        self$linear1 = nn_linear(embed_dim, units*4)
+        self$dropout = nn_dropout(0.05)
+        self$linear2 = nn_linear(units*4, embed_dim)
+        self$norm1 = nn_layer_norm(embed_dim)
+        self$norm2 = nn_layer_norm(embed_dim)
+        self$dropout1 = nn_dropout(0.05)
+        self$dropout2 = nn_dropout(0.05)
+        self$activation = nn_relu()
+
+
+        self$fc <- nn_linear(sum_embedding_dim + num_numerical, units)
+        self$output <- nn_linear(units, 1)
+        device <- if (cuda_is_available()) torch_device("cuda:0") else "cpu"
+        self$to(device = device)
+    },
+    forward = function(xcat, xnum) {
[…]

### 2021-03-26 manuscript/manuscript.Rmd
Update manuscript.Rmd

@@
 Attention mechanisms have been widely applied within the deep learning literature to give more flexibility to RNNs [@Bahdanau2015a] and subsequently as a replacement for FCNs in the so-called Transformer architecture, which is now widely used in natural language processing [@Vaswani2017a], and, more recently, has been applied to computer vision and tabular modelling tasks.
-Attention mechanisms allow deep neural nets to weight the covariates entering the model in a flexible manner; these types of applications are demonstrated in, for example, [@Vaswani2017a].
+Attention mechanisms allow deep neural nets to weight the covariates entering the model in a flexible manner; these types of applications in natural langauge processing are demonstrated in, for example, [@Vaswani2017a].
+In an actuarial context, attention mechanisms can be understood as giving greater weight to covariates that are important for the modelling task.
 In this section we provide a theoretical introduction to attention mechanisms and then discuss applications of attention to modeling tabular data.

### 2021-03-27 R/cv-model-torch.R
tabtransformer

@@ -17,7 +17,7 @@ response_col <- "amount_paid_on_building_claim"
 
 
 cvfolds <- small_data %>%
-    rsample::vfold_cv(v = 5)
+    rsample::vfold_cv(v = 2)
 # cvfolds
 
 model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_size = 5000, ...) {
@@ -72,18 +72,31 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 
     preds_nn2 <- get_preds(model2, test_dl)
 
+
+    model_tabt <- tabtransformer(env$cardinalities, length(numeric_cols),
+        embedding_dim = 2, num_heads = 3, fc_units = 32
+    )
+    model_tabt <- model_tabt$to(device = "cuda")
+
+    optimizer <- optim_adam(model_tabt$parameters, lr = learning_rate)
+
+    train_loop(model_tabt, train_dl, valid_dl, epochs, optimizer)
+
+    replace_unseen_level_weights_(model_tabt$col_embedder$embeddings)
+
+    preds_tabt <- get_preds(model_tabt, test_dl)
     ### add simple attn model
 
-    model_attn <- simple_net_attn(env$cardinalities, length(numeric_cols), units = 64, embed_dim = 5)
+    # model_attn <- simple_net_attn(env$cardinalities, length(numeric_cols), units = 64, embed_dim = 5)
 
-    optimizer <- optim_adam(model_attn$parameters, lr = learning_rate, weight_decay = 0)
+    # optimizer <- optim_adam(model_attn$parameters, lr = learning_rate, weight_decay = 0)
     # optimizer <- optim_rmsprop(model$parameters, lr = 0.1)
 
-    train_loop(model_attn, train_dl, valid_dl, epochs, optimizer)
+    # train_loop(model_attn, train_dl, valid_dl, epochs, optimizer)
 
-    replace_unseen_level_weights_(model$embedder$embeddings)
+    # replace_unseen_level_weights_(model$embedder$embeddings)
 
-    preds_nn_attn <- get_preds(model_attn, test_dl)
+    # preds_nn_attn <- get_preds(model_attn, test_dl)
 
     form <- amount_paid_on_building_claim ~ total_building_insurance_coverage +
         basement_enclosure_crawlspace_type + number_of_floors_in_the_insured_building +
[…]

### 2021-03-29 R/cv-model-torch.R
remove base attention model

@@ -17,8 +17,7 @@ response_col <- "amount_paid_on_building_claim"
 
 
 cvfolds <- small_data %>%
-    rsample::vfold_cv(v = 2)
-# cvfolds
+    rsample::vfold_cv(v = 10)
 
 model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_size = 5000, ...) {
     env <- new.env()
@@ -29,10 +28,8 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
         data = analysis_data %>%
             select(-loss_proportion, -reported_zip_code)
     ) %>%
-        # step_log(total_building_insurance_coverage) %>%
         step_normalize(all_numeric(), -all_outcomes()) %>%
         step_novel(all_nominal()) %>%
-        # step_unknown(all_nominal(), new_level = "missing") %>%
         step_integer(all_nominal(), strict = TRUE, zero_based = TRUE) %>%
         prep(strings_as_factors = TRUE)
 
@@ -51,7 +48,6 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
     model <- simple_net(env$cardinalities, length(numeric_cols), units = 64, fn_embedding_dim = function(x) 1)
 
     optimizer <- optim_adam(model$parameters, lr = learning_rate, weight_decay = 0)
-    # optimizer <- optim_rmsprop(model$parameters, lr = 0.1)
 
     train_loop(model, train_dl, valid_dl, epochs, optimizer)
 
@@ -85,18 +81,6 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
     replace_unseen_level_weights_(model_tabt$col_embedder$embeddings)
 
     preds_tabt <- get_preds(model_tabt, test_dl)
-    ### add simple attn model
-
-    # model_attn <- simple_net_attn(env$cardinalities, length(numeric_cols), units = 64, embed_dim = 5)
-
-    # optimizer <- optim_adam(model_attn$parameters, lr = learning_rate, weight_decay = 0)
-    # optimizer <- optim_rmsprop(model$parameters, lr = 0.1)
-
-    # train_loop(model_attn, train_dl, valid_dl, epochs, optimizer)
-
-    # replace_unseen_level_weights_(model$embedder$embeddings)
-
-    # preds_nn_attn <- get_preds(model_attn, test_dl)
 
[…]

### 2021-03-29 R/data-loading.R
data loading seed

@@ -1,6 +1,7 @@
 claims <- cellar::cellar_pull("nfip_claims") %>%
     filter(year_of_loss > 2000)
 
+set.seed(42069)
 small_data <- claims %>%
     filter(
         amount_paid_on_building_claim > 0,
@@ -10,7 +11,6 @@ small_data <- claims %>%
     select(
         amount_paid_on_building_claim, total_building_insurance_coverage,
         reported_zip_code, primary_residence, basement_enclosure_crawlspace_type,
-        # condominium_indicator, 
         number_of_floors_in_the_insured_building, occupancy_type,
         community_rating_system_discount, flood_zone
     ) %>%

### 2021-03-29 R/model-utils.R
remove alternating training loop

@@ -119,53 +119,6 @@ simple_net_attn <- nn_module(
     }
 )
 
-train_loop_alternate <- function(model, train_dl, valid_dl, epochs, optimizer) {
-    for (epoch in seq_len(epochs)) {
-        model$train()
-        train_losses <- c()
-
-        odd_epoch <- epoch %% 2 == 1
-
-        for (p in model$embedder$parameters) {
-            p$requires_grad_(odd_epoch)
-        }
-
-        for (p in model$output$parameters) {
-            p$requires_grad_(!odd_epoch)
-        }
-
-        for (b in enumerate(train_dl)) {
-            optimizer$zero_grad()
-            output <- model(b$x[[1]], b$x[[2]])
-            loss <- nnf_mse_loss(output, b$y)
-            loss$backward()
-
-            # if (odd_epoch) {
-            #     nn_utils_clip_grad_value_(model$embedder$parameters, 1)
-            # } else {
-            #     nn_utils_clip_grad_value_(model$output$parameters, 1)
-            # }
-
-            optimizer$step()
-            train_losses <- c(train_losses, loss$item())
-        }
-
-        model$eval()
-        valid_losses <- c()
-
-        for (b in enumerate(valid_dl)) {
-            output <- model(b$x[[1]], b$x[[2]])
-            loss <- nnf_mse_loss(output, b$y)
-            valid_losses <- c(valid_losses, loss$item())
-        }
-
-        cat(sprintf(
-            "Loss at epoch %d: training: %3f, validation: %3f\n", epoch,
-            mean(train_losses), mean(valid_losses)
-        ))
-    }
-}
-
 train_loop <- function(model, train_dl, valid_dl, epochs, optimizer) {
     device <- if (cuda_is_available()) torch_device("cuda:0") else "cpu"
     for (epoch in seq_len(epochs)) {

### 2021-03-29 R/scratch.R
remove scratch code

@@ -1,142 +1,0 @@
-library(tidyverse)
-library(recipes)
-library(rsample)
-library(torch)
-
-source("R/model-utils.R")
-source("R/data-loading.R")
-
-categorical_cols <- c(
-    "primary_residence", "basement_enclosure_crawlspace_type",
-    "number_of_floors_in_the_insured_building",
-    "occupancy_type", "flood_zone"
-)
-
-numeric_cols <- c("total_building_insurance_coverage", "community_rating_system_discount")
-response_col <- "amount_paid_on_building_claim"
-
-
-cvfolds <- small_data %>%
-    rsample::vfold_cv(v = 2)
-# cvfolds
-
-model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_size = 5000, ...) {
-    env <- new.env()
-    analysis_data <- analysis(splits)
-    assessment_data <- assessment(splits)
-
-    rec_nn <- recipe(amount_paid_on_building_claim ~ .,
-        data = analysis_data %>%
-            select(-loss_proportion, -reported_zip_code)
-    ) %>%
-        # step_log(total_building_insurance_coverage) %>%
-        step_normalize(all_numeric(), -all_outcomes()) %>%
-        step_novel(all_nominal()) %>%
-        # step_unknown(all_nominal(), new_level = "missing") %>%
-        step_integer(all_nominal(), strict = TRUE, zero_based = TRUE) %>%
-        prep(strings_as_factors = TRUE)
-
-    ds <- flood_dataset(juice(rec_nn), categorical_cols, numeric_cols, response_col, env)
-    baked_test_data <- bake(rec_nn, assessment_data)
-    test_ds <- flood_dataset(baked_test_data, categorical_cols, numeric_cols)
-    train_indx <- sample(length(ds), 0.8 * length(ds))
-    valid_indx <- seq_len(length(ds)) %>% setdiff(train_indx)
-    train_ds <- dataset_subset(ds, train_indx)
-    valid_ds <- dataset_subset(ds, valid_indx)
-
-    train_dl <- train_ds %>% dataloader(batch_size = batch_size, shuffle = TRUE)
-    valid_dl <- valid_ds %>% dataloader(batch_size = batch_size, shuffle = TRUE)
-    test_dl <- test_ds %>% dataloader(batch_size = batch_size, shuffle = FALSE)
-
[…]

### 2021-03-29 R/cv-model-torch.R
model saving

@@ -15,9 +15,8 @@ categorical_cols <- c(
 numeric_cols <- c("total_building_insurance_coverage", "community_rating_system_discount")
 response_col <- "amount_paid_on_building_claim"
 
-
 cvfolds <- small_data %>%
-    rsample::vfold_cv(v = 10)
+    rsample::vfold_cv(v = 2)
 
 model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_size = 5000, ...) {
     env <- new.env()
@@ -152,3 +151,10 @@ cv_results %>%
             rmse_glm2 = rmse(x$actuals, x$preds_glm2)
         )
     })
+
+dir.create("model_files")
+saveRDS(cv_results[[1]]$model_glm, "model_files/glm1.rds")
+saveRDS(cv_results[[1]]$model_glm2, "model_files/glm2.rds")
+saveRDS(cv_results[[1]]$rec_nn$steps[[3]]$key, "model_files/rec_nn_key.rds")
+torch_save(cv_results[[1]]$model_nn, "model_files/nn1.pt")
+torch_save(cv_results[[1]]$model_nn2, "model_files/nn2.pt")

### 2021-03-30 manuscript/manuscript.Rmd
Clean copy in first sections

@@
 Using categorical embeddings instead of traditional techniques has been shown to increase predictive accuracy of 
-models, for example, see [@Richman2018] in the context of pricing. Models incorporating categorical embeddings can be
+models, for example, see @Richman2018 in the context of pricing. Models incorporating categorical embeddings can be
 pre-calibrated to traditional actuarial models, increasing the speed with which these models can be calibrated and 
@@
 for different categories can be inspected, sometimes leading to insights into the workings of models, see, for example,
-[@Kuo2019].
+@Kuo2019.
 
@@
 initial models for the NFIP dataset and consider the influence of hyperparameter choices on the results of the neural 
-network model. Section \ref{tl} considers how successfully the embeddings used in the neural network model can be 
-transferred to a GLM model of the same data. Extensions to the modelling approach are considered in Section \ref{extend} 
-and we focus on attention based models in Section \ref{attention}. The interpretability of embedding layers is addressed
-in Section \ref{interpretation}. Finally, Section \ref{Conclusions} provides a discussion of the results of this paper
+network model. That section also considers how successfully the embeddings used in the neural network model can be 
+transferred to a GLM model of the same data and how learned embeddings can be interpreted. We focus on attention based models 
+in Section \ref{attention_models}. Finally, Section \ref{Conclusions} provides a discussion of the results of this paper
 and considers avenues for future research.
@@
 Categorical data are usually modelled within GLMs and other predictive models using indicator variables which capture 
-the effect of each level of the category, see, for example, Section 2 in [@Goldburd], using one of two main encoding 
+the effect of each level of the category, see, for example, Section 2 in @Goldburd, using one of two main encoding 
 schemes: dummy-coding and one-hot encoding. Dummy-coding, used in the popular \texttt{R} statistical software, assigns 
@@
 
-A different approach to modelling categorical data is credibility theory (see [@Buhlmann2006] for an overview), which, 
+A different approach to modelling categorical data is credibility theory (see @Buhlmann2006 for an overview), which, 
 in the context of rating, can be applied to derive premiums that reflect the experience of a particular policyholder, by 
@@
 introduced in an actuarial context. Note that in the next section, we reflect on similarities between the conventional 
-approaches discussed above and embedding layers. [@Richman2018] reviewed the concept of embedding layers and connected 
+approaches discussed above and embedding layers. @Richman2018 reviewed the concept of embedding layers and connected 
 the sharing of information across categories to the familiar concept of credibility theory. In that work, two 
@@
 
-Contemporaneous with that work is the DeepTriangle model of [@Kuo2019], which applied recurrent neural networks to the 
+Contemporaneous with that work is the DeepTriangle model of @Kuo2019, which applied recurrent neural networks to the 
 problem of Incurred but not Reported (IBNR) loss reserving, to model jointly the paid and incurred losses in the 
@@
 Many other applications of embeddings have subsequently appeared in the actuarial literature. Within mortality 
-forecasting, [@Richman2019d] and [@Richman2020] both apply embeddings layers to model and forecast mortality rates on a 
-large scale. [@wuthrich2019yes] discussed how embeddings can be calibrated using GLM techniques and then incorporated 
-into a combined actuarial neural network, with subsequent contributions in P&C pricing by [@schelldorfer2019nesting] and 
-in IBNR reserving by [@Gabrielli2019c] and [@Gabrielli2019]. Other applications in IBNR reserving are in [@Kuo2020] and 
-[@Delong2020a] who use embedding layers to model individual claims development.
+forecasting, @Richman2019d and @Richman2020 both apply embeddings layers to model and forecast mortality rates on a 
+large scale. @wuthrich2019yes discussed how embeddings can be calibrated using GLM techniques and then incorporated 
+into a combined actuarial neural network, with subsequent contributions in P&C pricing by @schelldorfer2019nesting and 
+in IBNR reserving by @Gabrielli2019c and @Gabrielli2019. Other applications in IBNR reserving are in @Kuo2020 and 
+@Delong2020a who use embedding layers to model individual claims development.
 
@@
 $n_\mathcal{P}^j$ indicator variables, which take a value of $1$ if the label of $x_{i,j}$ corresponds to the level of 
-the indicator variable, and $0$ otherwise. An example of one-hot encoding is shown in Table \ref{onehot}.
+the indicator variable, and $0$ otherwise. An example of one-hot encoding is shown in Table \@ref(tab:onehot).
 
@@
 baseline, and maps all of the other $n_p^j -1$ variables to indicator variables. An example of dummy encoding is shown 
-in Table \ref{dummy}.
+in Table \@ref(tab:dummy).
 
@@
 possible to apply credibility considerations within GLMs. using models known as Generalized Linear Mixed Models or 
-GLMMs, and we refer to [@Klinker2010] for more details.
+GLMMs, and we refer to @Klinker2010 for more details.
 
@@
 Property and Casualty (P&C) insurance. Here, we provide a brief overview of these models, and refer the reader to 
-[@Richman2018] for a more detailed overview. Neural networks are characterized by multiple layers of non-linear 
+@Richman2018 for a more detailed overview. Neural networks are characterized by multiple layers of non-linear 
 regression functions that are used to learn a new representation of the data input to the network that is then used to 
@@
 
-where the regression parameters (weights) for each layer $$k \in [1;K]$$ are represented by the matrices $a_k$ and the 
+where the regression parameters (weights) for each layer $k \in [1;K+1]$ are represented by the matrices $a_k$ and the 
 intercept terms are represented by $b_k$. Whereas the calculation inside each of the layers is nothing more than linear 
-regression, $\sigma$ represents the non-linear part of each layer. Choices for $\sigma$ are often the tanh function or 
-the rectified linear unit (ReLu) $max(0,x)$. The parameters of the network are estimated ('trained') as follows. First a 
-loss function $L(.,.)$ is specified for the network that measures the difference between the observed data $y$ and the 
-predictions of the network $\hat{y}$, for example, the Mean Squared Error ($(y - \hat{y})^2$). Then, the parameters of 
+regression, $\sigma$ represents the non-linear part of each layer. Choices for $\sigma$ are often the hyperbolic tangent 
+(tanh) function or the rectified linear unit (ReLu) $max(0,x)$. The parameters of the network are estimated ('trained') 
+as follows. First a loss function $L(.,.)$ is specified for the network that measures the difference between the observed data $y$ 
+and the predictions of the network $\hat{y}$, for example, the Mean Squared Error ($(y - \hat{y})^2$). Then, the parameters of 
 the network are changed such that the loss decreases (formally, this is done using the technique of backpropagation).
@@
 
-If $K$ is set equal to $1$, then Equation \ref{NN} reduced to nothing more than a GLM. A neural network with $K=2$ is 
+If $K$ is set equal to $1$, then Equation \ref{NN} reduces to nothing more than a GLM. A neural network with $K=2$ is 
 called a shallow neural network and for $K \geq 2$, the network is called a deep neural network. The matrix $X$ of data 
@@
 technical terms, this is because the columns of the matrices created by one-hot encoding are all orthogonal to each 
-other. (These arguments appear in a similar form in [@Guo2016].) Solutions to these problems are provided by embedding 
+other. (These arguments appear in a similar form in @Guo2016.) Solutions to these problems are provided by embedding 
 layers.
@@
 
-$$
-z_\mathcal{P^j} : \mathcal{P^j} \to \mathbb{R}^{q_\mathcal{P^j} }, \quad \quad p^j \mapsto  z_\mathcal{P^j}(p),
-$$
+\begin{equation} 
+\label{embed_map}
+  z_\mathcal{P}^j : \mathcal{P}^j \to \mathbb{R}^{q_\mathcal{P}^j }, \quad \quad p^j \mapsto  z_\mathcal{P}^j(p),
+\end{equation}
 
-where $q_\mathcal{P^j}$ is the dimension of the embedding for the $j$th categorical variable and $z_\mathcal{P^j}(.)$ is 
-a function that maps from the particular element of the labels $p$ to the embedding space. Equation \ref{eq:embedding} 
-states that an embedding maps a level of a categrical variable to a numerical vector. This function is left implicit, 
+where $q_\mathcal{P}^j$ is the dimension of the embedding for the $j$th categorical variable and $z_\mathcal{P}^j(.)$ is 
+an implicit function that maps from the particular element of the labels $p$ to the embedding space. Equation \ref{embed_map} 
+states that an embedding maps a level of a categorical variable to a numerical vector. This function is left implicit, 
 meaning to say, we allow the embeddings to be derived during the process of fitting the model and do not attempt to 
-specify exactly how the embeddings can be derived from the input data. In Table \ref{embed} we show an example of two 
+specify exactly how the embeddings can be derived from the input data. In Table \@ref(tab:embed) we show an example of two 
 dimensional embeddings for the state variables, where these have been generated randomly.
@@
 data.frame(sample_dat, dimension1 = rnorm(5), dimension2 = rnorm(5)) %>%
-  knitr::kable(label = "", caption = "Example (random) embeddings of the state variable")
+  knitr::kable(label = "embed", caption = "Example (random) embeddings of the state variable")
 ```
@@
 
-Attention mechanisms have been widely applied within the deep learning literature to give more flexibility to RNNs [@Bahdanau2015a] and subsequently as a replacement for FCNs in the so-called Transformer architecture, which is now widely used in natural language processing [@Vaswani2017a], and, more recently, has been applied to computer vision and tabular modelling tasks.
-Attention mechanisms allow deep neural nets to weight the covariates entering the model in a flexible manner; these types of applications in natural langauge processing are demonstrated in, for example, [@Vaswani2017a].
-In an actuarial context, attention mechanisms can be understood as giving greater weight to covariates that are important for the modelling task.
+Attention mechanisms have been widely applied within the deep learning literature to give more flexibility to RNNs [@Bahdanau2015a] 
+and subsequently as a replacement for FCNs in the so-called Transformer architecture, which is now widely used in natural language processing [@Vaswani2017a], 
+and, more recently, has been applied to computer vision and tabular modelling tasks. 
+Attention mechanisms allow deep neural nets to weight the covariates entering the model in a flexible manner; these types of applications in natural language 
+processing are demonstrated in,
+for example, @Vaswani2017a. In an actuarial context, attention mechanisms can be understood as giving greater weight to covariates that are important for the modelling task. 
 In this section we provide a theoretical introduction to attention mechanisms and then discuss applications of attention to modeling tabular data. 
@@
 The following is intended as a high level review of some of the relevant theory behind attention based approaches; for more technical details the sources quoted in this section can be consulted.
+
+At a high level, attention mechanisms reweight the covariates $X$ within a predictive model to give greater weight to covariates that are more
+predictive for a particular problem. The attention weights can be derived in several different manners. Earlier works, such as @Bahdanau2015a
+used so-called "additive" attention scores derived as the output of a neural network taking the covariates as inputs. Currently, the most popular
+form of attention is the "scaled dot-product" attention of @Vaswani2017a which we describe in what follows. We also mention that usually, so-called
+"self-attention" is applied, meaning to say that the importance scores for the covariates are derived using the covariates themselves (i.e. in what follows,
+the attention scores are derived in Equation \ref{eq:attention_scores} using the transformed covariates). Other options, such as using a different source of
+data to derive the attention scores, are also possible.
 
@@
 \begin{equation}
-A: \mathbb{R}^{(q \times d) \times (q \times d) \times (q \times d)} \to \mathbb{R}^(q \times d), ~~
-(Q, K, V) ~\mapsto ~ V^* = A(Q, K, V),
+X^*: \mathbb{R}^{(q \times d) \times (q \times d) \times (q \times d)} \to \mathbb{R}^{(q \times d)}, ~~
+(Q, K, X') ~\mapsto ~ X^* = A(Q, K, X'),
 \label{eq:attention}
@@
 ```
-where $Q \in \mathbb{R}^{q \times d}$ is a matrix of query vectors, $K \in \mathbb{R}^{q \times d}$ is a matrix of key vectors, $X' \in \mathbb{R}^{q \times d}$ is a matrix of value vectors and $X^* \in \mathbb{R}^{q \times d}$, the output of the attention mechanism, is a new matrix of values.
-Several different options for the mapping \eqref{eq:attention} exist in the literature; here we describe the self-attention mechanism used in [@Vaswani2017a].
-In more detail, consider that $X'$ is a matrix of covariates relating to a regression problem, which, in the case of tabular data, will usually be composed of embeddings of the same dimension for several different categorical or numerical variables; in the case discussed here we have $q$ covariates in the form of embeddings of dimension $d$.
-For clarity, note that in Equation \ref{eq:embed_to_nn} we have used the symbol $X'$ to denote the vector of embeddings and numerical inputs which is passed into the neural network.
-In what follows, we now use the symbol $X'$ to refer to the matrix of embeddings of dimension $q \times d$.
+where $Q \in \mathbb{R}^{q \times d}$ is a matrix of query vectors, $K \in \mathbb{R}^{q \times d}$ is a matrix of key vectors,
+ $X' \in \mathbb{R}^{q \times d}$ is a matrix of value vectors and $X^* \in \mathbb{R}^{q \times d}$, 
+ the output of the attention mechanism, is a new matrix of values that have been reweighted according to their importance for the modelling problem. 
+ As noted above, several different options for the mapping in Equation \ref{eq:attention} exist in the literature; here we describe the scaled dot-product self-attention mechanism 
+ used in @Vaswani2017a. In more detail, consider that $X'$ is a matrix of covariates relating to a regression problem, which, 
+ in the case of tabular data, will usually be composed of embeddings of the same dimension for several different categorical or numerical variables.
+ In the case discussed here we have $q$ covariates mapped to embeddings of dimension $d$. For clarity, note that in Equation \ref{eq:embed_to_nn} 
+ we have used the symbol $X'$ to denote the vector of embeddings and numerical inputs which is passed into the neural network. 
+ We slightly overload this notation and, in what follows, we now use the symbol $X'$ to refer to the matrix of embeddings of dimension $q \times d$.
 
-We wish to apply the attention mechanism to $X'$ to assign weights to the most important embeddings for the regression problem; this is done from the \`\`perspective" of each covariate in $x'$.
-To do this, we formulate the query matrix $Q$ which contains information about the regression problem at hand; this is usually done by passing $X'$ through a FCN trained to derive queries from the covariates.
-Similarly, the matrix $K$ contains the relevance of each row of $V$ for the regression problem and is also usually derived by passing each row of $X'$ through another FCN.
-Finally, the matrix $X'$can be processed with a third FCN or left as is.
+We wish to apply the attention mechanism to $X'$ to assign weights to the most important embeddings for the regression problem; 
+this is done from the "perspective" of each covariate represented by the $q$ rows of $X'$. To do this, we formulate a so-called query matrix $Q$ 
+which contains information about the regression problem at hand; this is usually done by passing $X'$ through a neural network trained to derive 
+queries from the covariates. Similarly, the matrix $K$ contains the relevance of each row of $X'$ for the regression problem and 
+is also usually derived by passing each row of $X'$ through another neural network. Finally, the matrix $X'$ can be left as is, or processed through another neural network. 
 The first step of the attention mechanism is to derive a matrix $A \in \mathbb{R}^{q \times q}$ of attention scores:
@@
 \begin{equation}
-\mathbb{R}^{(q \times d) \times (q \times d)} \to \mathbb{R}^{q \times q}, ~~
-(Q, K) ~\mapsto ~ A = Q~K^T.
+A: \mathbb{R}^{(q \times d) \times (q \times d)} \to \mathbb{R}^{q \times q}, ~~
+(Q, K) ~\mapsto ~ A = \frac{Q~K^T}{\sqrt{d}},
 \label{eq:attention_scores}
@@
 ```
-The attention scores $A$ are then normalized, or made to sum to unity, across the columns of $A$ using a so-called softmax function i.e.
+
+and where the division by $\sqrt{d}$ is done element-wise. The attention scores $A$ are then normalized, or made to sum to unity, 
+across the columns of $A$ using a so-called softmax function i.e.
 
@@
 \begin{equation}
-\mathbb{R}^{(q \times q) \times (q \times d)} \to \mathbb{R}^{q \times d}, ~~
-(A^*, x') ~\mapsto ~ X^* = A^*~X'.
+X^*: \mathbb{R}^{(q \times q) \times (q \times d)} \to \mathbb{R}^{q \times d}, ~~
+(A^*, X') ~\mapsto ~ X^* = A^*~X'.
 \label{eq:attention_output}
@@
 ```
-In most applications of attention, Equation \ref{eq:attention_scores} is modified by dividing the attention scores by $d^{\frac{1}{2}}$.
+<!-- In most applications of attention, Equation \ref{eq:attention_scores} is modified by dividing the attention scores by $d^{\frac{1}{2}}$. -->
 
-An intuitive explanation of the attention formula is as follows: we start by considering the importance of all of the covariates that we have for our modelling problem in the context of each individual covariate.
-This is done by assigning a score between zero and one to each covariate in the modelling problem, and we repeat this process for each of the covariates.
-Then, we replace each of the original covariates with a new covariate that has been formed by taking a weighted average of the covariates and the scores.
+An intuitive explanation of the attention formula is as follows: we start by considering the importance of all of the covariates 
+that we have for our modelling problem in the context of each individual covariate. This is done by assigning a score between zero
+and one to each covariate in the modelling problem, and we repeat this process for each of the covariates. Then, we replace each 
+of the original covariates with a new covariate that has been formed by taking a weighted average of the covariates and the scores.
 
@@
 
-Self-attention is the main building block of the current state of the art model for natural language processing, which is the Transformer model [@Vaswani2017].
+Self-attention is the main building block of the current state of the art model for natural language processing, which is the Transformer model [@Vaswani2017a]. 
 A basic Transformer model applies self-attention to the covariate matrix, $X'$ which is fed into the model, to produce a new matrix of covariates, $X^*$. 
 These two matrices, the input matrix $X'$ and the output matrix $X^*$ are added (in an element-wise manner) together and then normalized. 
-This matrix is then further processed through a neural network and subsequently, these processed covariates are used in the machine learning task.
-Multiple Tranformer network "blocks" can be added to a network to create a deep Transformer network.
+This matrix is then further processed through a neural network and subsequently, these processed covariates are used in the machine learning task. These stages of the 
+Transformer model help to make the optimization of the network easier than applying scaled self-attention directly to the matrix of covariates $X'$.
 
-The Transformer model is much more accurate on NLP tasks compared to using the raw covariates before processing with a Transformer, to the extent that this model now underlies most NLP applications that use deep learning.
+Multiple Transformer network "blocks" can be added to a network to create a deep Transformer network.
+
+The Transformer model is much more accurate on NLP tasks compared to using the raw covariates before processing with a Transformer, to the extent that 
+this model now underlies most NLP applications that use deep learning.
 
@@
 
-Several different approaches to applying attention within the modelling of tabular data have been proposed in the literature.
-Perhaps the simplest way of doing this is to insert an attention layer between the embeddings and the rest of the neural network.
-Mathematically, we can modify Equation \ref{eq:embed_to_nn} as follows:
+Several different approaches to applying attention within the modelling of tabular data have been proposed in the literature. Perhaps the simplest way of doing 
+this is to insert an attention layer between the embeddings and the rest of the neural network. Mathematically, we can modify Equation \ref{eq:embed_to_nn} as follows:
 
 ```{=latex}
-\begin{eqnarray}
-  X^* = Attn(X') \\
-  z^1 = \sigma(a_1.X^* + b_1),
+\begin{equation}
+\begin{split}
+  X^* &= A(X') \\
+  z^1 &= \sigma(a_1.X^* + b_1),
+\end{split}
 \label{eq:embed_to_attn_to_nn}
-\end{eqnarray}
+\end{equation}
 ```
-where $X' \in \mathbb{R}^{q \times d}$ is the matrix of embeddings after concatenating $q$ embeddings of dimension $d$ together and $X^*$ represents the matrix of embeddings $X'$ after processing with attention.
+where $X' \in \mathbb{R}^{q \times d}$ is the matrix of embeddings after concatenating $q$ embeddings of dimension $d$ together, $X^*$ 
+represents the matrix of embeddings $X'$ after processing with attention and $A$ is the attention function defined in Equations \ref{eq:attention} - \ref{eq:attention_output}. 
 Below, we demonstrate the effect of adding this simple application of attention to a tabular model.
 
-[@Huang2020] refines this approach in a model they call the TabTransformer, which implements two main changes to the approach shown in Equations \ref{eq:embed_to_attn_to_nn}.
-The first of these is that, instead of using the matrix of embeddings after processing with self-attention ($X'$) directly in the model, the output of a Transformer model is used instead.
-The second of these refinements is that for each of the $q$ covariates with an embedding in the matrix $X'$, we include a new row embedding which denotes which covariate each embedding relates to.
-Thus, in the TabTransformer model, we augment the embedding matrix with extra columns, so that the dimension of this matrix is $q \times (d + d_col)$, where $d_col$ is the dimension of the row embedding.
-[@Huang2020] find that including this identifier improves the performance of the model.
-We compare the results of the TabTransformer model to the other models tested below.
+@Huang2020 refines this approach in a model they call the TabTransformer, which implements two main changes to the approach shown in Equations \ref{eq:embed_to_attn_to_nn}. 
+The first of these is that, instead of using the matrix of embeddings after processing with self-attention ($X'$) directly in the model, 
+the output of a Transformer model is used instead. The second of these refinements is that for each of the $q$ covariates with an embedding in the matrix $X'$, 
+we include a new row embedding which denotes which covariate each embedding relates to. Thus, in the TabTransformer model, we augment 
+the embedding matrix with extra columns, so that the dimension of this matrix is $q \times (d + d_{col})$, where $d_{col}$ is the dimension of the row embedding.
+@Huang2020 find that including this identifier improves the performance of the model. We compare the results of the TabTransformer model to the other models tested below.
 
-Finally, a different way of incorporating attention into the modeling of tabular data has been proposed by [@Ark2019], who refer to their model as TabNet.
+Finally, a different way of incorporating attention into the modeling of tabular data has been proposed by @Ark2019, who refer to their model as TabNet. 
 In summary, the main idea of the TabNet model is to try emulate the excellent performance of decision trees on tabular data modelling using deep neural networks. 
-This is done by structuring the neural networks to emulate a key aspect of decision tree modelling, which is the efficient selection of relevant covariates for the model task.
-Within TabNet, an attention based model is used to select features by estimating attention scores for each covariate within $X$.
-The covariates are multiplied by the attention scores to downweight less relevant features for the prediction problem.
+This is done by structuring the neural networks to emulate a key aspect of decision tree modelling, which is the efficient selection of relevant covariates
+for the model task. Within TabNet, an attention based model is used to select features by estimating attention scores for each covariate within $X$. 
+The covariates are multiplied by the attention scores to down-weight less relevant features for the prediction problem. Other less important details of the Tabnwet
+model are given in @Ark2019.
 
-# Predictive Modeling with Embeddings
+# Predictive Modeling with Embeddings {#modelling}
 
@@
 
-# Extending the model {#extend}
+<!-- # Extending the model {#extend}
 
@@
 Take credibility mixture over embeddings Cluster embeddings PCA of embeddings
-
-# Attention based modelling {#attn}
+-->
+# Attention based modelling {#attention_models}
 

### 2021-03-30 manuscript/manuscript.Rmd
Clean up intro

@@
 thus, the issue of whether transferring embeddings to GLM models can achieve better performance is considered in this
-paper. Traditional actuarial techniques such as credibility theory have been used to work with some types of 
-categorical data, but no study has been performed whether this can be applied within embeddings; here, we investigate
-whether performance is enhanced by applying credibility theory on embeddings relating to categorical variables with
-many labels. Whereas embedding layers are usually considered in the context of categorical data,the option exists to
-quantize numerical data and model it using embeddings, however, the results of doing so have not been investigated.
+paper. <!-- Traditional actuarial techniques such as credibility theory have been used to work with some types of categorical data, but no study has been -->
+<!-- performed whether this can be applied within embeddings; here, we investigate whether performance is enhanced by applying credibility theory on embeddings 
+relating to categorical variables with many labels. Whereas embedding layers are usually considered in the context of categorical data,the 
+option exists to quantize numerical data and model it using embeddings, however, the results of doing so have not been investigated. -->
 Finally, in the past several years, a new type of neural network architecture based on attention [@Vaswani2017] has

### 2021-03-30 R/cv-model-torch.R
Add simple_attn
Removed extraneous  embedding_module_attn

@@ -80,6 +80,17 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 
     preds_nn2 <- get_preds(model2, test_dl)
 
+    model_simple_attn <- simple_net_attn(env$cardinalities, length(numeric_cols),
+                         units = 8)
+
+    optimizer <- optim_adam(model_simple_attn$parameters, lr = learning_rate, weight_decay = 0)
+
+    train_loop(model_simple_attn, train_dl, valid_dl, epochs, optimizer)
+
+    replace_unseen_level_weights_(model_simple_attn$embedder$embeddings)
+
+    preds_simple_attn <- get_preds(model_simple_attn, test_dl)
+
     form <- amount_paid_on_building_claim ~ total_building_insurance_coverage +
         basement_enclosure_crawlspace_type + number_of_floors_in_the_insured_building +
         occupancy_type + flood_zone + primary_residence + community_rating_system_discount
@@ -126,6 +137,7 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
     list(
         model_nn = model,
         model_nn2 = model2,
+        model_simple_attn = model_simple_attn,
         model_tabt = model_tabt,
         rec_nn = rec_nn,
         model_glm = model_glm,
@@ -136,6 +148,7 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
         actuals = actuals,
         preds_nn = preds_nn,
         preds_nn2 = preds_nn2,
+        preds_simple_attn = preds_simple_attn,
         preds_tabt = preds_tabt,
         preds_glm = preds_glm,
         preds_glm_gaussian = preds_glm_gaussian,
@@ -151,12 +164,14 @@ cv_results %>%
         list(
             rmse_nn = rmse(x$actuals, x$preds_nn),
             rmse_nn2 = rmse(x$actuals, x$preds_nn2),
+            rmse_simple_attn = rmse(x$actuals, x$preds_simple_attn),
             rmse_tabt = rmse(x$actuals, x$preds_tabt),
             rmse_glm = rmse(x$actuals, x$preds_glm),
             rmse_glm2 = rmse(x$actuals, x$preds_glm2),
[…]

### 2021-03-30 R/model-utils.R

@@ -99,7 +99,7 @@ simple_net_attn <- nn_module(
                           units = 16,
                           embed_dim = 5,
                           fn_embedding_dim = function(x) embed_dim) {
-        self$embedder <- embedding_module_attn(cardinalities, fn_embedding_dim)
+        self$embedder <- embedding_module(cardinalities, fn_embedding_dim)
         sum_embedding_dim <- sapply(cardinalities, fn_embedding_dim) %>%
             sum()
         self$embed_dim <- fn_embedding_dim()

### 2021-03-31 R/cv-model-torch.R
Quick and dirty keras version

@@ -2,9 +2,16 @@ library(tidyverse)
 library(recipes)
 library(rsample)
 library(torch)
+library(data.table)
+library(keras)
+require(tensorflow)
+tf$compat$v1 = T
 
 source("R/model-utils.R")
 source("R/data-loading.R")
+source("R/keras_working_file.R")
+source("R/keras_working_file_attn.R")
+source("R/keras_working_file_tabtrans.R")
 
 categorical_cols <- c(
     "primary_residence", "basement_enclosure_crawlspace_type",
@@ -18,6 +25,14 @@ response_col <- "amount_paid_on_building_claim"
 set.seed(420)
 cvfolds <- small_data %>%
     rsample::vfold_cv(v = 5)
+
+### t remove later
+
+splits = cvfolds$splits[[1]]
+
+learning_rate = 0.001
+epochs = 10
+batch_size = 5000
 
 model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_size = 5000, ...) {
     env <- new.env()
@@ -33,63 +48,101 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
         step_integer(all_nominal(), strict = TRUE, zero_based = TRUE) %>%
         prep(strings_as_factors = TRUE)
 
-    ds <- flood_dataset(juice(rec_nn), categorical_cols, numeric_cols, response_col, env)
+    #ds <- flood_dataset(juice(rec_nn), categorical_cols, numeric_cols, response_col, env)
+    juiced_train_data <- juice(rec_nn)
     baked_test_data <- bake(rec_nn, assessment_data)
-    test_ds <- flood_dataset(baked_test_data, categorical_cols, numeric_cols)
+    for_card = juiced_train_data %>% data.table()
+    for_card_test = baked_test_data %>% data.table()
+    #test_ds <- flood_dataset(baked_test_data, categorical_cols, numeric_cols)
 
-    train_dl <- ds %>% dataloader(batch_size = batch_size, shuffle = TRUE)
-    # valid_dl <- valid_ds %>% dataloader(batch_size = batch_size, shuffle = TRUE)
-    test_dl <- test_ds %>% dataloader(batch_size = batch_size, shuffle = FALSE)
+    get_keras_data = function(dat){
+        dat = dat %>% data.table
+        dat_list = list()
+        for (column in categorical_cols) dat_list[[column]] = as.matrix(dat[, get(column)])
[…]

### 2021-03-31 R/keras_working_file.R

@@ -1,0 +1,70 @@
+get_keras_model = function(hidden_layer_units = 64, embed = 1) {
+
+k_clear_session()
+
+input_list = list()
+embedding_list = list()
+cardinalities = list()
+count = 0
+
+get_embed_dim = function(cards, embed){
+  if (embed == 1) {1}
+  else{
+  (trunc(cards/2)+1)
+  }
+}
+
+for (column in categorical_cols){
+  count = count + 1
+  cardinalities[[column]] = for_card[, max(get(column))]
+  input_list[[count]] = layer_input(shape = 1, dtype = "int32", name = column)
+  embed_dim = get_embed_dim(cardinalities[[column]], embed)
+  embedding_list[[count]] = input_list[[count]] %>%
+    layer_embedding(input_dim = cardinalities[[column]]*2+1, output_dim =embed_dim)  %>%
+    layer_flatten(name = paste0(column, "_embed"))
+}
+
+input_list[[count+1]] = layer_input(shape = numeric_cols %>% length, dtype = "float32", name = "num_input")
+
+embeddings = embedding_list %>% layer_concatenate()
+main = list(embeddings, input_list[[count+1]]) %>% layer_concatenate() %>%
+  layer_dense(units = hidden_layer_units, activation = "relu")
+
+output = main %>%
+  layer_dense(units = 1, activation = "sigmoid", name = "output")
+
+model <- keras_model(
+  inputs = input_list,
+  outputs = c(output))
+
+adam = optimizer_adam(lr=0.001)
+
+model %>% compile(
+  loss = 'mean_squared_error',
+  optimizer = adam
+)
+
+lr_call = callback_reduce_lr_on_plateau(monitor = "val_loss", patience = 50, verbose = 1, cooldown = 5,
+                                        factor = 0.9, min_lr = 0.0001)
+mod_save = callback_model_checkpoint(filepath = paste0("c:/r/keras_mod.h5"), verbose = T, save_best_only = T)
+
+fit <- model %>% fit(x = train_dl,
+                     y= list(output = as.matrix(output_list$y_train)),
+                     epochs=1000,
+                     batch_size=4096,
+                     verbose=2,
+                     validation_split = 0.05,
+                     shuffle=T,
+                     callbacks = list(lr_call, mod_save))
+
+model = load_model_hdf5("c:/r/keras_mod.h5")
+
+preds_nn_train = model %>% predict(train_dl)
[…]

### 2021-03-31 R/keras_working_file_attn.R

@@ -1,0 +1,77 @@
+get_keras_model_attn = function(hidden_layer_units = 64, embed = 1) {
+
+  k_clear_session()
+
+  input_list = list()
+  embedding_list = list()
+  cardinalities = list()
+  count = 0
+
+  get_embed_dim = function(cards, embed){
+    if (embed == 1) {1}
+    else{
+      if(embed ==0) {8}
+      else {(trunc(cards/2)+1)}
+    }
+  }
+
+  for (column in categorical_cols){
+    count = count + 1
+    cardinalities[[column]] = for_card[, max(get(column))]
+    input_list[[count]] = layer_input(shape = 1, dtype = "int32", name = column)
+    embed_dim = get_embed_dim(cardinalities[[column]], embed)
+    embedding_list[[count]] = input_list[[count]] %>%
+      layer_embedding(input_dim = cardinalities[[column]]*2+1, output_dim =embed_dim,name = paste0(column, "_embed"))
+  }
+
+  input_list[[count+1]] = layer_input(shape = numeric_cols %>% length, dtype = "float32", name = "num_input")
+
+  embeddings = embedding_list %>% layer_concatenate(axis = 1)
+  key = embeddings %>% (layer = layer_dense(units = 8))
+  query = embeddings %>% (layer = layer_dense(units = 8))
+  value = embeddings %>% (layer = layer_dense(units = 8))
+
+  attn = layer_attention(list(key, query, value), use_scale = T)
+  attn_flat = attn %>% layer_flatten() %>% layer_dropout(rate = 0.05)
+
+  main = list(attn_flat, input_list[[count+1]]) %>% layer_concatenate() %>%
+    layer_dense(units = hidden_layer_units, activation = "relu")
+
+  output = main %>%
+    layer_dense(units = 1, activation = "sigmoid", name = "output")
+
+  model <- keras_model(
+    inputs = input_list,
+    outputs = c(output))
+
+  adam = optimizer_adam(lr=0.001)
+
+  model %>% compile(
+    loss = 'mean_squared_error',
+    optimizer = adam
+  )
+
+  lr_call = callback_reduce_lr_on_plateau(monitor = "val_loss", patience = 50, verbose = 1, cooldown = 5,
+                                          factor = 0.9, min_lr = 0.0001)
+  mod_save = callback_model_checkpoint(filepath = paste0("c:/r/keras_mod.h5"), verbose = T, save_best_only = T)
+
+  fit <- model %>% fit(x = train_dl,
[…]

### 2021-03-31 R/keras_working_file_tabtrans.R

@@ -1,0 +1,96 @@
+get_keras_model_tabtrans = function(hidden_layer_units = 64, embed = 0) {
+
+  k_clear_session()
+
+  input_list = list()
+  embedding_list = list()
+  cardinalities = list()
+  count = 0
+
+  get_embed_dim = function(cards, embed){
+    if (embed == 1) {1}
+    else{
+      if(embed ==0) {32}
+      else {(trunc(cards/2)+1)}
+    }
+  }
+
+  for (column in categorical_cols){
+    count = count + 1
+    cardinalities[[column]] = for_card[, max(get(column))]
+    input_list[[count]] = layer_input(shape = 1, dtype = "int32", name = column)
+    embed_dim = get_embed_dim(cardinalities[[column]], embed)
+    embedding_list[[count]] = input_list[[count]] %>%
+      layer_embedding(input_dim = cardinalities[[column]]*2+1, output_dim =embed_dim,name = paste0(column, "_embed"))
+  }
+
+  input_list[[count+1]] = layer_input(shape = numeric_cols %>% length, dtype = "float32", name = "num_input")
+  input_list[[count+2]] = layer_input(shape = 5, dtype = "int32", name = "col_idx")
+
+  col_idx_int = input_list[[count+2]] %>%
+    layer_reshape(c(5,1), name = "col_idx_int")
+
+  embeddings = embedding_list %>% layer_concatenate(axis = 1)
+  col_embed = layer_embedding(input_dim = 6, output_dim = 8)
+  col_embeds = col_idx_int %>% time_distributed(col_embed) %>% layer_reshape(c(5,8), name = "col_embeds")
+  all_embeds = list(embeddings, col_embeds) %>% layer_concatenate(axis = 2)
+
+  attn_heads = list()
+
+  for (i in 1:4){
+    key = all_embeds %>% (layer = layer_dense(units = 10))
+    query = all_embeds %>% (layer = layer_dense(units = 10))
+    value = all_embeds %>% (layer = layer_dense(units = 10))
+    attn = layer_attention(list(key, query, value), use_scale = T)
+    attn_heads[[i]] = attn
+  }
+
+  multi_head_attn = attn_heads %>% layer_concatenate(axis=2) %>% layer_dense(units = 40)
+  stage1 = list(all_embeds, multi_head_attn) %>% layer_add() %>% layer_layer_normalization()
+
[…]

### 2021-03-31 R/cv-model-torch.R
Update cv-model-torch.R

@@ -23,16 +23,16 @@ numeric_cols <- c("total_building_insurance_coverage", "community_rating_system_
 response_col <- "amount_paid_on_building_claim"
 
 set.seed(420)
-cvfolds <- small_data %>%
+cvfolds <- small_data %>% #sample_frac(0.01) %>%
     rsample::vfold_cv(v = 5)
 
 ### t remove later
-
-splits = cvfolds$splits[[1]]
-
-learning_rate = 0.001
-epochs = 10
-batch_size = 5000
+#
+# splits = cvfolds$splits[[1]]
+#
+# learning_rate = 0.001
+# epochs = 10
+# batch_size = 5000
 
 model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_size = 5000, ...) {
     env <- new.env()

### 2021-04-01 R/model-utils.R
train/validation split

@@ -147,24 +147,24 @@ train_loop <- function(model, train_dl, valid_dl = NULL, epochs, optimizer) {
             train_losses <- c(train_losses, loss$item())
         })
 
-        # model$eval()
-        # valid_losses <- c()
+        model$eval()
+        valid_losses <- c()
 
-        # for (b in enumerate(valid_dl)) {
-        #     output <- model(b$x[[1]]$to(device = device), b$x[[2]]$to(device = device))
-        #     loss <- nnf_mse_loss(output, b$y$to(device = device))
-        #     valid_losses <- c(valid_losses, loss$item())
-        # }
-
-        # cat(sprintf(
-        #     "Loss at epoch %d: training: %3f, validation: %3f\n", epoch,
-        #     mean(train_losses), mean(valid_losses)
-        # ))
+        for (b in enumerate(valid_dl)) {
+            output <- model(b$x[[1]]$to(device = device), b$x[[2]]$to(device = device), b$x[[3]])
+            loss <- nnf_mse_loss(output, b$y$to(device = device))
+            valid_losses <- c(valid_losses, loss$item())
+        }
 
         cat(sprintf(
-            "Loss at epoch %d: training: %3f\n", epoch,
-            mean(train_losses)
+            "Loss at epoch %d: training: %3f, validation: %3f\n", epoch,
+            mean(train_losses), mean(valid_losses)
         ))
+
+        # cat(sprintf(
+        #     "Loss at epoch %d: training: %3f\n", epoch,
+        #     mean(train_losses)
+        # ))
     }
 }
 

### 2021-04-01 R/model-utils.R
add early stopping

@@ -130,10 +130,12 @@ simple_net_attn <- nn_module(
     }
 )
 
-train_loop <- function(model, train_dl, valid_dl = NULL, epochs, optimizer) {
+train_loop <- function(model, train_dl, valid_dl = NULL, epochs, optimizer, patience = 2) {
     # print(valid_dl)
     # device <- if (cuda_is_available()) torch_device("cuda:0") else "cpu"
     device <- "cpu"
+    best_loss <- NULL
+    counter <- 0
     for (epoch in seq_len(epochs)) {
         model$train()
         train_losses <- c()
@@ -150,21 +152,31 @@ train_loop <- function(model, train_dl, valid_dl = NULL, epochs, optimizer) {
         model$eval()
         valid_losses <- c()
 
-        for (b in enumerate(valid_dl)) {
+        coro::loop(for (b in valid_dl) {
             output <- model(b$x[[1]]$to(device = device), b$x[[2]]$to(device = device), b$x[[3]])
             loss <- nnf_mse_loss(output, b$y$to(device = device))
             valid_losses <- c(valid_losses, loss$item())
-        }
+        })
 
         cat(sprintf(
             "Loss at epoch %d: training: %3f, validation: %3f\n", epoch,
             mean(train_losses), mean(valid_losses)
         ))
 
-        # cat(sprintf(
-        #     "Loss at epoch %d: training: %3f\n", epoch,
-        #     mean(train_losses)
-        # ))
+        if (is.null(best_loss)) {
+            best_loss <- mean(valid_losses)
+        } else {
+            if (mean(valid_losses) < best_loss) {
+                best_loss <- mean(valid_losses)
+                counter <- 0
+            } else {
+                counter <- counter + 1
+            }
+        }
+        if (counter >= patience) {
+            cat("**Early stopping!\n")
+            break
+        }
     }
 }
 

### 2021-04-02 R/cv-model-torch.R
added save function and simple attn

@@ -2,9 +2,12 @@ library(tidyverse)
 library(recipes)
 library(rsample)
 library(torch)
+library(tabnet)
 
 source("R/model-utils.R")
 source("R/data-loading.R")
+
+dir.create("model_files")
 
 categorical_cols <- c(
     "primary_residence", "basement_enclosure_crawlspace_type",
@@ -18,7 +21,7 @@ coverage_col <- "coverage"
 
 set.seed(420)
 cvfolds <- small_data %>%
-    rsample::vfold_cv(v = 2)
+    rsample::vfold_cv(v = 5)
 
 model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_size = 5000, ...) {
     env <- new.env()
@@ -61,12 +64,14 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 
     optimizer <- optim_adam(model_tabt$parameters, lr = learning_rate)
 
-    train_loop(model_tabt, train_dl, valid_dl, epochs, optimizer)
+    train_loop(model_tabt, train_dl, valid_dl, epochs, optimizer, "tabt", patience = 5)
+
+    torch_load("model_files/tabt.pt")
 
     replace_unseen_level_weights_(model_tabt$col_embedder$embeddings)
 
     preds_tabt <- get_preds(model_tabt, test_dl)
-    
+
     # Model02
     model <- simple_net(
         env$cardinalities, length(numeric_cols),
@@ -75,7 +80,9 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 
     optimizer <- optim_adam(model$parameters, lr = learning_rate, amsgrad = TRUE)
 
-    train_loop(model, train_dl, valid_dl, epochs, optimizer)
+    train_loop(model, train_dl, valid_dl, epochs, optimizer, "Model02", patience = 5)
+
+    torch_load("model_files/Model02.pt")
 
     replace_unseen_level_weights_(model$embedder$embeddings)
 
@@ -89,7 +96,9 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 
     optimizer <- optim_adam(model2$parameters, lr = learning_rate, amsgrad = TRUE)
 
-    train_loop(model2, train_dl, valid_dl, epochs, optimizer)
+    train_loop(model2, train_dl, valid_dl, epochs, optimizer, "Model04", patience = 5)
+
+    torch_load("model_files/Model04.pt")
 
[…]

### 2021-04-02 R/model-utils.R

@@ -14,7 +14,7 @@ flood_dataset <- dataset(
         self$xnum <- df[numeric_cols] %>%
             as.matrix() %>%
             torch_tensor(device = device)
-        
+
         self$xcoverage <- df[coverage_col] %>%
             as.matrix() %>%
             torch_tensor(device = device)
@@ -130,7 +130,7 @@ simple_net_attn <- nn_module(
     }
 )
 
-train_loop <- function(model, train_dl, valid_dl = NULL, epochs, optimizer, patience = 2) {
+train_loop <- function(model, train_dl, valid_dl = NULL, epochs, optimizer, patience = 2, model_name) {
     # print(valid_dl)
     # device <- if (cuda_is_available()) torch_device("cuda:0") else "cpu"
     device <- "cpu"
@@ -165,9 +165,13 @@ train_loop <- function(model, train_dl, valid_dl = NULL, epochs, optimizer, pati
 
         if (is.null(best_loss)) {
             best_loss <- mean(valid_losses)
+            torch_save(model, paste0("model_files/", model_name, ".pt"))
+            cat("**Saved model\n")
         } else {
             if (mean(valid_losses) < best_loss) {
                 best_loss <- mean(valid_losses)
+                torch_save(model, paste0("model_files/", model_name, ".pt"))
+                cat("**Saved model\n")
                 counter <- 0
             } else {
                 counter <- counter + 1

### 2021-04-02 R/cv-model-torch.R
Assign models and swap order of func call

@@ -64,9 +64,9 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 
     optimizer <- optim_adam(model_tabt$parameters, lr = learning_rate)
 
-    train_loop(model_tabt, train_dl, valid_dl, epochs, optimizer, "tabt", patience = 5)
+    train_loop(model_tabt, train_dl, valid_dl, epochs, optimizer, patience = 5, "tabt")
 
-    torch_load("model_files/tabt.pt")
+    model_tabt = torch_load("model_files/tabt.pt")
 
     replace_unseen_level_weights_(model_tabt$col_embedder$embeddings)
 
@@ -80,9 +80,9 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 
     optimizer <- optim_adam(model$parameters, lr = learning_rate, amsgrad = TRUE)
 
-    train_loop(model, train_dl, valid_dl, epochs, optimizer, "Model02", patience = 5)
+    train_loop(model, train_dl, valid_dl, epochs, optimizer, patience = 5, "Model02")
 
-    torch_load("model_files/Model02.pt")
+    model = torch_load("model_files/Model02.pt")
 
     replace_unseen_level_weights_(model$embedder$embeddings)
 
@@ -96,9 +96,9 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 
     optimizer <- optim_adam(model2$parameters, lr = learning_rate, amsgrad = TRUE)
 
-    train_loop(model2, train_dl, valid_dl, epochs, optimizer, "Model04", patience = 5)
+    train_loop(model2, train_dl, valid_dl, epochs, optimizer, patience = 5, "Model04")
 
-    torch_load("model_files/Model04.pt")
+    model2 = torch_load("model_files/Model04.pt")
 
     replace_unseen_level_weights_(model2$embedder$embeddings)
 
@@ -133,16 +133,13 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 
      optimizer <- optim_adam(model_simple_attn$parameters, lr = learning_rate, amsgrad = TRUE)
 
-     train_loop(model_simple_attn, train_dl, valid_dl, epochs, optimizer, "simple_attn", patience = 5)
+     train_loop(model_simple_attn, train_dl, valid_dl, epochs, optimizer, patience = 5, "simple_attn")
 
[…]

### 2021-04-02 manuscript/manuscript.Rmd
add cv results table

@@
 
-For our experiments, we set up a 10-fold cross validation scheme that is applied to each of the models
+For our experiments, we set up a 5-fold cross validation scheme that is applied to each of the models
 we introduce. In Sections \ref{models} and \ref{interpretations}, the tables and figures are based on a single fold of 
@@
 squares (IWLS) without regularization. For the neural networks, Models 2 and 4, we utilize the \texttt{Adam}
-optimizer [@Kingma2014] with a learning rate of TODO, and train the each network for TODO epochs with a batch
-size of TODO.
+optimizer [@Kingma2014] with a learning rate of 0.01 and a minibatch size of 1000. We split the training set into
+analysis and assessment sets, containing 80% and 20% of the rows, respectively. We train on the analysis set for a
+maximum of 15 epochs, and stop early if the loss on the assessment set does not improve for 5 epochs.
 
 During inference, or scoring, care must be taken to accommodate the categorical levels that are unseen
-during training. While we allow for an extra key in the embedding dictionary (TODO: mention this earlier), the initial
+during training. While we allow for an extra key in the embedding dictionary, the initial
 weights are not updated during training, which could lead to nonsensical predictions in the validation or test sets. To
@@
 
-In Table TODO, we exhibit the cross-validated performance metrics of each of the models.
+In Table \@ref(tab:cv-results), we exhibit the cross-validated performance metrics of each of the models. We report
+both the root mean squared error (RMSE) and the mean absolute error (MAE); we note that these are just a couple of many potential metrics to use, and are so chosen for their interpretability and prevalence in the literature for comparing
+different types of models. Recall that, between the two metrics, RMSE penalizes large mispredictions than MAE. Also,
+in the optimization process, GLM with a gamma distribution optimizes the deviance, rather than MSE directly.
+
+We see that the neural networks generally outperform the GLMs; however, what is more interesting is that using learned 
+embeddings in place of categorical levels improves the GLM, at least from the RMSE perspective.
+
+While linear regression (i.e., the specific case of GLM with a gaussian distribution and identity link function) is not
+commonly used for severity modeling, we throw it into the mix as a benchmark, a practice we recommend in order to
+check reasonablness of other models' results. Since it is possible for a linear
+regression to output negative values, we cap the predictions below by 0.01 during scoring. Somewhat surprisingly, in 
+the problem we
+are considering, it performs similary to the more complex neural network models in the RMSE metric (which it optimizes
+for, as the unit deviance of the normal distribution corresponds with MSE.) Of course, this is not to discredit neural
+networks or GLMs, as the experiments are performed without extensive hyperparameter tuning or feature engineering.
+
+Table: (\#tab:cv-results) Cross validation results.
+
+|Model                                                                         |   RMSE|    MAE|
+|:-----------------------------------------------------------------------------|------:|------:|
+|Model 1: GLM (gamma/log link)                                                 | 65,138| 38,367|
+|Model 2: MLP with 1-dimensional embeddings                                    | 60,979| 37,605|
+|Model 3: GLM (gamma/log link), categorical variables replaced with embeddings | 63,170| 38,360|
+|Model 4: MLP with multidimensional embeddings                                 | 60,973| 37,574|
+|Linear regression, predictions capped below at 0.01                           | 60,879| 38,431|
 

### 2021-04-02 R/table-charts-utils.R

@@ -6,7 +6,7 @@ extract_embeddings <- function(model, key) {
         setNames(categorical_cols) %>%
         purrr::imap(function(m, v) {
             outputs <- level_integer_mappings[[v]]$integer %>%
-                torch_tensor(device = "cuda") %>%
+                torch_tensor(device = "cpu") %>%
                 m() %>%
                 (function(x) x$to(device = "cpu")) %>%
                 as.array()

### 2021-04-02 manuscript/manuscript.Rmd
update tables

@@
 |occupancy_type |Single family residence                     |       1.00|
-|occupancy_type |Non-residential building                    |       1.37|
-|occupancy_type |2 to 4 unit residential buidling            |       1.15|
-|occupancy_type |Residential building with more than 4 units |       1.64|
-|flood_zone     |B                                           |       1.00|
-|flood_zone     |A                                           |       0.84|
-|flood_zone     |C                                           |       0.60|
-|flood_zone     |X                                           |       0.70|
-|flood_zone     |V                                           |       0.78|
-|flood_zone     |D                                           |       0.89|
+|occupancy_type |2 to 4 unit residential buidling            |       1.10|
+|occupancy_type |Non-residential building                    |       1.34|
+|occupancy_type |Residential building with more than 4 units |       1.59|
+|flood_zone     |C                                           |       1.00|
+|flood_zone     |A                                           |       1.42|
+|flood_zone     |X                                           |       1.18|
+|flood_zone     |B                                           |       1.65|
+|flood_zone     |V                                           |       1.38|
+|flood_zone     |D                                           |       1.45|
 
@@
 |:-------------------------------------------|---------:|
-|2 to 4 unit residential buidling            |      6.69|
-|Non-residential building                    |      7.16|
-|Residential building with more than 4 units |      6.33|
-|Single family residence                     |      5.43|
+|2 to 4 unit residential buidling            |      1.46|
+|Non-residential building                    |     -1.04|
+|Residential building with more than 4 units |      0.12|
+|Single family residence                     |      0.36|
 
@@
 |:-----|---------:|:-----|---------:|:-----|---------:|:-----|---------:|:-----|---------:|
-|A     |      0.38|A09   |     -1.71|A18   |     -1.40|A99   |     -2.68|V     |     -0.41|
-|A00   |     -0.35|A0B   |      3.85|A19   |     -1.70|AE    |     -4.46|V02   |      0.65|
-|A01   |     -6.76|A10   |     -4.03|A20   |     -4.05|AH    |     -2.35|V03   |     -0.29|
-|A02   |     -4.28|A11   |     -5.32|A21   |     -2.08|AHB   |     -1.71|V04   |     -1.15|
-|A03   |     -5.93|A12   |     -3.23|A22   |     -2.11|AO    |     -6.07|V05   |     -0.50|
-|A04   |     -7.82|A13   |      2.03|A23   |     -1.40|AOB   |     -4.56|V06   |     -1.92|
-|A05   |     -3.42|A14   |     -5.72|A24   |      2.23|AR    |     -0.48|V07   |     -2.91|
-|A06   |     -4.97|A15   |     -3.67|A25   |      0.28|B     |     -5.36|V08   |     -2.24|
-|A07   |     -3.09|A16   |     -3.02|A27   |     -2.56|C     |     -4.47|V09   |     -0.75|
-|A08   |     -4.69|A17   |     -0.37|A30   |      1.13|D     |     -0.76|V10   |     -2.05|
+|A     |      1.48|A09   |     -0.48|A18   |      0.39|A28   |      1.19|C     |      1.73|
+|A00   |     -1.05|A0B   |      1.47|A19   |     -1.06|A30   |     -0.01|D     |     -1.15|
+|A01   |     -0.18|A10   |     -0.25|A20   |     -1.01|A99   |     -0.44|V     |     -1.85|
+|A02   |     -0.06|A11   |      0.35|A21   |      2.08|AE    |      1.12|V01   |      0.02|
+|A03   |     -0.01|A12   |     -0.38|A22   |     -0.15|AH    |      2.19|V02   |     -1.55|
+|A04   |      0.05|A13   |      2.81|A23   |     -0.76|AHB   |     -0.68|V03   |     -0.98|
+|A05   |      1.30|A14   |      0.58|A24   |     -0.87|AO    |      0.55|V04   |      1.73|
+|A06   |     -0.76|A15   |     -0.91|A25   |      0.02|AOB   |      0.08|V05   |     -1.97|
+|A07   |     -0.62|A16   |      0.79|A26   |      0.00|AR    |      2.93|V06   |      0.43|
+|A08   |     -0.53|A17   |      1.35|A27   |      0.80|B     |      0.33|V07   |      1.91||
 
@@
 |:----------------------------------------|--------:|
-|(Intercept)                              |    2.389|
-|total_building_insurance_coverage        |    0.568|
-|basement_enclosure_crawlspace_type       |    0.136|
-|number_of_floors_in_the_insured_building |   -0.024|
-|occupancy_type                           |    0.067|
-|flood_zone                               |    0.035|
-|primary_residence                        |   -0.001|
-|community_rating_system_discount         |    0.504|
+|(Intercept)                              |    3.371|
+|total_building_insurance_coverage        |    0.586|
+|basement_enclosure_crawlspace_type       |    0.597|
+|number_of_floors_in_the_insured_building |   -0.278|
+|occupancy_type                           |   -0.075|
+|flood_zone                               |   -0.007|
+|primary_residence                        |   -0.062|
+|community_rating_system_discount         |    0.706|
 
@@
 |level                                       |    e1|    e2|    e3|
-|:-------------------------------------------|-----:|-----:|----:|
-|2 to 4 unit residential buidling            | -1.44| -1.97| 2.35|
-|Non-residential building                    | -6.83| -8.11| 5.34|
-|Residential building with more than 4 units | -7.63| -6.58| 5.09|
-|Single family residence                     | -1.61| -2.54| 3.01|
+|:-------------------------------------------|-----:|-----:|-----:|
+|2 to 4 unit residential buidling            |  0.37| -1.76|  1.36|
+|Non-residential building                    |  0.13|  1.47|  1.77|
+|Residential building with more than 4 units | -1.12| -0.15| -1.43|
+|Single family residence                     |  0.85|  0.16| -0.99|
 
@@
 |:---------|:------|:---------|:------|:---------|:------|:---------|:------|
-|e1        |0.020  |e11       |2.146  |e21       |-1.933 |e31       |-0.941 |
-|e2        |-0.885 |e12       |1.723  |e22       |1.150  |e32       |-1.279 |
-|e3        |-0.126 |e13       |0.378  |e23       |0.863  |e33       |-0.360 |
-|e4        |1.491  |e14       |-0.310 |e24       |-0.471 |e34       |-1.173 |
-|e5        |0.980  |e15       |2.482  |e25       |0.929  |          |       |
-|e6        |0.952  |e16       |1.823  |e26       |-1.139 |          |       |
-|e7        |-0.217 |e17       |-2.715 |e27       |0.113  |          |       |
-|e8        |-0.611 |e18       |1.144  |e28       |1.155  |          |       |
-|e9        |0.919  |e19       |-0.045 |e29       |0.707  |          |       |
-|e10       |-1.196 |e20       |0.467  |e30       |1.358  |          |       |
+|e1        |-0.167 |e11       |-0.810 |e21       |-0.300 |e31       |-0.421 |
+|e2        |-0.363 |e12       |1.380  |e22       |-0.194 |e32       |0.594  |
+|e3        |-0.893 |e13       |-0.180 |e23       |-0.320 |e33       |1.681  |
+|e4        |0.130  |e14       |-1.612 |e24       |-0.035 |e34       |1.668  |
+|e5        |-1.588 |e15       |-1.327 |e25       |-1.128 |          |       |
+|e6        |-0.123 |e16       |-0.965 |e26       |0.168  |          |       |
+|e7        |-0.259 |e17       |-1.356 |e27       |-1.022 |          |       |
+|e8        |0.324  |e18       |-0.061 |e28       |1.011  |          |       |
+|e9        |-1.430 |e19       |-0.120 |e29       |-0.843 |          |       |
+|e10       |-1.598 |e20       |-0.488 |e30       |-0.743 |          |       ||
 

### 2021-04-02 manuscript/manuscript.Rmd
occupancy type pic

@@
 For Model 2, the neural network with one-dimensional embeddings, the task is simple: we can simply plot the levels
-on a line, as in Figure \@ref(fig:num-floors). In the case of `flood_zone`, since we happen to have the luxury of knowing a
+on a line, as in Figure \@ref(fig:occ-type). In the case of `flood_zone`, since we happen to have the luxury of knowing a
 priori the meaning of the prefixes, we can plot them separately, as in Figure \@ref(fig:flood-zone) to see how the model 
@@
 
-```{r num-floors, echo=FALSE, fig.cap="Number of floors", out.width = "80%", fig.align="center"}
-knitr::include_graphics("images/num_floors.png")
+```{r occ-type, echo=FALSE, fig.cap="Occupancy type", out.width = "80%", fig.align="center"}
+knitr::include_graphics("images/occupancy_type.png")
 ```

### 2021-04-03 R/table-charts-utils.R
tsne and pca

@@ -17,3 +17,16 @@ extract_embeddings <- function(model, key) {
             )
         })
 }
+
+make_tsne_plot <- function(wts, lbls, perplexity) {
+    tsne_out <- Rtsne::Rtsne(wts, pca = FALSE, perplexity = perplexity, eta = 100, theta = 0, max_iter = 10000)
+    p <- tsne_out$Y %>%
+        as.data.frame() %>%
+        mutate(class = lbls) %>%
+        mutate(prefix = substr(lbls, 1, 1)) %>%
+        filter(class != "new") %>%
+        ggplot(aes(x = V1, y = V2, color = prefix)) +
+        geom_point() +
+        theme_classic()
+    p
+}

### 2021-04-03 manuscript/manuscript.Rmd

@@
 In Figure \@ref(fig:flood-zone-pca), we plot the learned embeddings for `flood_zone` in Model 3 on the coordinate
-system defined by the first two principle components. (TODO: add commentary after update pic)
+system defined by the first two principle components. In our case, however, we are not able to identify discernable
+clusters in the plot. From inspecting the matrix decomposition results, we see that the cumulative proportion of
+variance for the first two principal components are just 0.18, which may suggest that perhaps PCA is not the most
+appropriate dimensionality reduction technique in this case.
 
-```{r flood-zone-pca, echo = FALSE, fig.cap="Flood zone PCA", out.width = "60%", fig.align = "center"}
+```{r flood-zone-pca, echo = FALSE, fig.cap="Flood zone PCA", out.width = "50%", fig.align = "center"}
 knitr::include_graphics("images/flood_zone_pca.png")
@@
 While t-SNE is a powerful visualization technique, there are a few points the modeler should be mindful of in practice.
-First, the resulting plot can be very sensitive to the perplexity hyperparameter. 
+We refer the reader to @wattenberg2016how for a more thorough discussion, but stress here that the resulting plot can
+be very sensitive to the perplexity hyperparameter. In addition, for our use case, which is to explore the
+learned embeddings, we have fewer data points than most other applications in the literature. Accordingly, our
+reaosnable range of hyperparameter values need to be adjusted down.
 In Figures \@ref(fig:flood-zone-tsne), we display the t-SNE of the learned embeddings for `flood_zone` in
-Model 3 with various perplexity settings. (TODO: add more commentary).
+Model 3 with various perplexity settings: 0.1, 0.5, 1.0, and 10; the learning rate and the number of steps are fixed at
+100 and 10,000, respectively, for all plots. In the first three plots, we can see the semblance of clusters forming. In
+particular, flood zone D appears in its own cluster, which implies it is far away from other levels in the embedding
+space. When the perplexity is set to 10 (and beyond), however, we lose the geometric properties.
 

### 2021-04-03 R/model-utils.R
fix model utils

@@ -28,9 +28,9 @@ flood_dataset <- dataset(
         self
     },
     .getitem = function(i) {
-        xcat <- self$xcat[i, ]
-        xnum <- self$xnum[i, ]
-        xcoverage <- self$xcoverage[i, ]
+        xcat <- self$xcat[i, , drop = TRUE]
+        xnum <- self$xnum[i, , drop = TRUE]
+        xcoverage <- self$xcoverage[i]
 
         if (self$is_train) {
             y <- self$y[i]
@@ -142,7 +142,7 @@ train_loop <- function(model, train_dl, valid_dl = NULL, epochs, optimizer, pati
 
         coro::loop(for (b in train_dl) {
             optimizer$zero_grad()
-            output <- model(b$x[[1]]$to(device = device), b$x[[2]]$to(device = device), b$x[[3]])
+            output <- model(b$x[[1]]$to(device = device), b$x[[2]]$to(device = device), b$x[[3]]$to(device = device))
             loss <- nnf_mse_loss(output, b$y$to(device = device))
             loss$backward()
             optimizer$step()
@@ -153,7 +153,7 @@ train_loop <- function(model, train_dl, valid_dl = NULL, epochs, optimizer, pati
         valid_losses <- c()
 
         coro::loop(for (b in valid_dl) {
-            output <- model(b$x[[1]]$to(device = device), b$x[[2]]$to(device = device), b$x[[3]])
+            output <- model(b$x[[1]]$to(device = device), b$x[[2]]$to(device = device), b$x[[3]]$to(device = device))
             loss <- nnf_mse_loss(output, b$y$to(device = device))
             valid_losses <- c(valid_losses, loss$item())
         })
@@ -192,7 +192,11 @@ get_preds <- function(model, dl) {
     for (b in enumerate(dl)) {
         preds <- c(
             preds,
-            model(b$x[[1]]$to(device = device), b$x[[2]]$to(device = device), b$x[[3]])$to(device = "cpu") %>% as.array()
+            model(
+                b$x[[1]]$to(device = device),
+                b$x[[2]]$to(device = device),
+                b$x[[3]]$to(device = device)
+            )$to(device = "cpu") %>% as.array()
         )
     }
     preds
@@ -327,6 +331,10 @@ tabtransformer <- nn_module(
 
 rmse <- function(actuals, preds) {
     sqrt(sum((actuals - preds)^2) / length(actuals))
+}
+
[…]

### 2021-04-03 R/modeling-section-models.R
cv results table code

@@ -59,7 +59,7 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
         env$cardinalities, length(numeric_cols),
         units = 16, fn_embedding_dim = function(x) 1
     )
-    
+
     # model <- model$to(device = "cuda")
 
     optimizer <- optim_adam(model$parameters, lr = learning_rate, amsgrad = TRUE)
@@ -160,13 +160,27 @@ cv_results %>%
             rmse_glm2 = rmse(x$actuals, x$preds_glm2),
             rmse_glm_gaussian = rmse(x$actuals, pmax(x$preds_glm_gaussian, 0.01)),
             rmse_zeros = rmse(x$actuals, 0),
-            mae_nn   = mae(x$actuals, x$preds_nn),
-            mae_nn2  = mae(x$actuals, x$preds_nn2),
-            mae_glm  = mae(x$actuals, x$preds_glm),
+            mae_nn = mae(x$actuals, x$preds_nn),
+            mae_nn2 = mae(x$actuals, x$preds_nn2),
+            mae_glm = mae(x$actuals, x$preds_glm),
             mae_glm2 = mae(x$actuals, x$preds_glm2),
             mae_glm_gaussian = mae(x$actuals, pmax(x$preds_glm_gaussian, 0.01))
         )
-    })
+    }) %>%
+    transpose() %>%
+    as_tibble() %>%
+    pivot_longer(everything()) %>%
+    separate(name, into = c("metric", "mod"), sep = "_", extra = "merge") %>%
+    pivot_wider(names_from = "metric") %>%
+    left_join(model_names_mapping, by = "mod") %>%
+    select(-mod) %>%
+    arrange(id) %>%
+    select(Model, rmse, mae) %>%
+    rename(RMSE = rmse, MAE = mae) %>%
+    knitr::kable(digits = 0, format.args = list(
+        big.mark = ",",
+        scientific = FALSE
+    ), format = "pipe")
 
 dir.create("model_files")
 saveRDS(cv_results[[1]]$model_glm, "model_files/glm1.rds")

### 2021-04-03 manuscript/manuscript.Rmd
fix basic nn description

@@
 layers where they are each mapped to a scalar. The embeddings are then concatenated with the numeric predictors, which
-have been normalized in data pre-processing, before being sent to a hidden linear layer of 64 units. A ReLU activation,
-
-\begin{equation}
-x \mapsto \max(0, x),
-\end{equation}
-
-is then applied to the outputs before they are sent to a final output layer resulting in a scalar. To constrain
-predictions to be positive, we apply softplus activation, which is defined to be
-
-\begin{equation}
-x \mapsto \log(1 + e^x). 
-\end{equation}
+have been normalized in data pre-processing, before being passed through a feedforward layer (with ReLU activation)
+ to obtain a scalar
+value between 0 and 1, as constrained by a sigmoid output activation. This scalar output represents the proportion of
+coverage amount that is paid out, so we multiply it by the unnormalized dollar amount of the coverage amount to obtain
+our prediction of the claims paid.
 

### 2021-04-03 manuscript/manuscript.Rmd
more fix

@@
 
-With a single hidden layer, this architecture is the simplest nontrivial neural network; without the hidden layer and
-corresponding ReLU activation, we would actually recover a GLM structure where the link function is the output 
-activation. 
+With a single hidden layer, this architecture is relatively simple; without the hidden layer and
+corresponding ReLU activation, we would actually recover a logistic regression structure. 
 The choice of one for the embedding dimension is also due to simplicity: it is easily interpretable as the 

### 2021-04-03 manuscript/manuscript.Rmd

@@
 the 
-complete dataset contains over two million transactions, for the purposes of our experiments we limit ourselves to data 
-from 2000 to August 2019, which amounts to approximately 1.4 million claims. The dataset can be downloaded from 
+complete dataset contains over two million transactions, for the purposes of our experiments, we limit ourselves to 
+data from 2000 to August 2019 and further subsample 100K data points to make experiments feasiable on a CPU.
+ The dataset can be downloaded from 
 Cellar[^10] The dataset includes a rich variety of variables, from occupancy type to coarse coordinates. For our 
@@
 layers where they are each mapped to a scalar. The embeddings are then concatenated with the numeric predictors, which
-have been normalized in data pre-processing, before being passed through a feedforward layer (with ReLU activation)
+have been normalized in data pre-processing, before being passed through a feedforward layer (with 8 hidden units 
+and ReLU activation)
  to obtain a scalar
@@
 coverage amount that is paid out, so we multiply it by the unnormalized dollar amount of the coverage amount to obtain
-our prediction of the claims paid.
+our prediction of the claims paid, which we evaluate using the mean squared error (MSE) loss function.
 

### 2021-04-04 manuscript/manuscript.Rmd
some typos

@@
 complete dataset contains over two million transactions, for the purposes of our experiments, we limit ourselves to 
-data from 2000 to August 2019 and further subsample 100K data points to make experiments feasiable on a CPU.
- The dataset can be downloaded from 
-Cellar[^10] The dataset includes a rich variety of variables, from occupancy type to coarse coordinates. For our 
+data from 2000 to August 2019 and further subsample 100K data points to make experiments feasible on a CPU.
+The dataset includes a rich variety of variables, from occupancy type to flood zone. For our 
 models, 
@@
 [^9]: https://www.fema.gov/about/reports-and-data/openfema
-[^10]: https://cellar.kasa.ai
 
@@
 For our experiments, we set up a 5-fold cross validation scheme that is applied to each of the models
-we introduce. In Sections \ref{models} and \ref{interpretations}, the tables and figures are based on a single fold of 
+we introduce. In Sections \ref{models} and \ref{interpretation}, the tables and figures are based on a single fold of 
 the cross validation split. In Section \ref{training-inference}, we provide the cross-validated performance
@@
 1. A GLM with gamma distribution and log link function,
-2. A neural network with unidimensional categorical embeddings,
-3. A GLM with the categorical predictors replaced by the trained embeddings from Model 2,
+2. A neural network with one-dimensional categorical embeddings,
+3. A GLM with the categorical predictors replaced by the learned embeddings from Model 2,
 4. A neural network with multidimensional categorical embeddings.
@@
 While this paper focuses on embeddings in neural networks, we begin with a GLM to provide a common frame of 
-reference since most actuaries are familiar with the technique. 
+reference, since most actuaries are familiar with the technique. 
 Although GLMs are commonplace and well-studied in the actuarial literature, there are still plenty of decisions to 
@@
 of a couple categorical variables. Recall that the choice of the log link gives a multiplicative structure, so the
-interpretation of 1.37 for `occupancy_type = "Non-residential building"` is that, all else equal, the expected 
+interpretation of 1.34 for `occupancy_type = "Non-residential building"` is that, all else equal, the expected 
 loss for
-a policy for a non-residential building is 1.37 times that of a policy for a single family home, which is the base,
+a policy for a non-residential building is 1.34 times that of a policy for a single family home, which is the base,
 or reference, level for the factor.
@@
 value between 0 and 1, as constrained by a sigmoid output activation. This scalar output represents the proportion of
-coverage amount that is paid out, so we multiply it by the unnormalized dollar amount of the coverage amount to obtain
-our prediction of the claims paid, which we evaluate using the mean squared error (MSE) loss function.
+coverage amount that is paid out, which we then multiply by the dollar amount of the coverage amount to obtain
+our prediction of the claims paid. For optimization, we use the mean squared error (MSE) loss function.
 
@@
 representation
-of each factor level as a point on the real number line, also, the trained embeddings are easily incorporated into a GLM
+of each factor level as a point on the real number line; also, the trained embeddings are easily incorporated into a GLM
 which we will see in Model 3. In practice, the embedding dimension is a hyperparameter one can tune, for example via
@@
 embedding output dimension is not an unreasonable one, especially when the cardinalities of the categorical variables
-are not unusually large.
+are not large (i.e., when they are in the 10s).
 
 In Tables \@ref(tab:embeddings-occupancy-type) and \@ref(tab:embeddings-flood-zone), we show the learned embeddings
-for the `occupancy_type` and an excerpt of them for `flood_zone`. While it may be tempting to compare these values
+for `occupancy_type` and an excerpt of them for `flood_zone`. While it may be tempting to compare these values
 to those in Table \@ref(tab:relativities), they represent fundamentally different concepts. It is helpful to think

### 2021-04-04 manuscript/manuscript.Rmd
more fixes

@@
 
-Table: (\#tab:embeddings-occupancy-type) Learned embeddings for `occupancy_type`.
+Table: (\#tab:embeddings-occupancy-type) Learned embeddings for `occupancy_type` in Model 2.
 
@@
 
-Table: (\#tab:embeddings-flood-zone) Excerpt of learned embeddings for `flood_zone`.
+Table: (\#tab:embeddings-flood-zone) Excerpt of learned embeddings for `flood_zone` in Model 2.
 
@@
 
-Although in this particular example we incorporate one-dimensional embeddings, one can easily include multidimensional
-embeddings, which would increase the model's flexibility. The modeler would need to balance the additional lift with
-some loss of interpretability, since with one-dimensional embeddings, our GLM structure dictates that there is a 
+Although, in this particular example, we incorporate one-dimensional embeddings, one can easily include multidimensional
+embeddings, which would increase the model's flexibility. The modeler would need to balance the potential 
+additional lift with overfitting and
+some loss of interpretability, since, with one-dimensional embeddings, our GLM structure dictates that there is a 
 monotonic relationship between the predicted response and the input embedding, which could be desirable in certain
@@
 
-Table: (\#tab:glm2) Coefficients of Model 3.
+Table: (\#tab:glm2) Fitted coefficients of Model 3.
 
@@
 of the factor's cardinality divided by two. Formally, in the notation of Section \ref{catdata},
-$q_{\mathcal{P}^j}=\ceil{n^j_{\mathcal{P}}/2}$ for variable $X_j$. Following the practice from the previous three
-models, we list the fitted embeddings for a couple variables in Tables \@ref(tab:nn2-occupancy-type) and 
+$q_{\mathcal{P}^j}=\ceil{n^j_{\mathcal{P}}/2}$ for variable $X_j$. Following the discussion thus far, we list the
+ learned embeddings for a couple variables in Tables \@ref(tab:nn2-occupancy-type) and 
 \@ref(tab:nn2-flood-zone). Note that, for `flood_zone`, we are

### 2021-04-04 manuscript/manuscript.Rmd
fix caption

@@
 |e9        |-1.430 |e19       |-0.120 |e29       |-0.843 |          |       |
-|e10       |-1.598 |e20       |-0.488 |e30       |-0.743 |          |       ||
+|e10       |-1.598 |e20       |-0.488 |e30       |-0.743 |          |       |
 
@@
 In this section, we focus on ways to visualize the learned embeddings. In the authors' experiences, oftentimes
-the formats of the visualizations --- basic line and scatter plots --- even more so than the content of the data, is 
+the formats of the visualizations---basic line and scatter plots---even more so than the content of the data, are 
 helpful in explaining the concept to stakeholders.
@@
 For Model 2, the neural network with one-dimensional embeddings, the task is simple: we can simply plot the levels
-on a line, as in Figure \@ref(fig:occ-type). In the case of `flood_zone`, since we happen to have the luxury of knowing a
-priori the meaning of the prefixes, we can plot them separately, as in Figure \@ref(fig:flood-zone) to see how the model 
+on a line, as in Figure \@ref(fig:occ-type). In the case of `flood_zone`, where we happen to have the luxury of knowing
+ a
+priori the meaning of the prefixes, we can plot them separately, as in Figure \@ref(fig:flood-zone) to see how the
+ model 
 mapped them.
 
-```{r occ-type, echo=FALSE, fig.cap="Occupancy type", out.width = "80%", fig.align="center"}
+```{r occ-type, echo=FALSE, fig.cap="Learned embeddings of occupancy type visualized on a number line.", out.width = "80%", fig.align="center"}
 knitr::include_graphics("images/occupancy_type.png")
@@
 
-```{r flood-zone, echo = FALSE, fig.cap="Flood zone embeddings", out.width = "60%", fig.align = "center"}
+```{r flood-zone, echo = FALSE, fig.cap="Learned embeddings of flood zone by prefix.", out.width = "60%", fig.align = "center"}
 knitr::include_graphics("images/flood_zone.png")

### 2021-04-04 manuscript/manuscript.Rmd

@@
 These model architectures are relatively uncomplicated by today's standards, and are so chosen to better highlight the
-embedding components. Later, in Section \ref{attn}, we will investigate more involved architectures utilizing embeddings
+embedding components. Later, in Section \ref{attention_models}, we will investigate more involved architectures utilizing embeddings
 that represent the state of the art for modeling tabular data.
@@
 
-In both approaches, the overarching theme is as follows: We have a collection of points in higher dimensional space,
+In both approaches, the overarching theme is as follows: we have a collection of points in higher dimensional space,
 $\mathcal{X} = \{x_1, x_2, \dots, x_n\}$ that we wish to map to some lower dimensional space, typically $\mathbb{R}^2$,
@@
 
-```{r flood-zone-pca, echo = FALSE, fig.cap="Flood zone PCA", out.width = "50%", fig.align = "center"}
+```{r flood-zone-pca, echo = FALSE, fig.cap="First two principal components of learned embeddings of flood zone in Model 4.", out.width = "50%", fig.align = "center"}
 knitr::include_graphics("images/flood_zone_pca.png")
@@
 Let $p_{j|i}$ denote the probability that point $x_i$ picks point $x_j$ as its *neighbor*, if it picks neighbors in
-proportion to their density under an $n$-dimension Gaussian centered at $x_i$. Formally, we can write $p_{j|i}$ as
+proportion to its density under an $n$-dimension Gaussian centered at $x_i$. Formally, we can write $p_{j|i}$ as
 
 \begin{equation}
-p_{j|i} = \frac{\exp(\norm{x_i - x_j}^2 / 2\sigma_i^2)}{\sum_{k\neq i} \exp(-\norm{x_i - x_k}^2 / 2\sigma_i^2)}. (\#eq:pji)
+p_{j|i} = \frac{\exp(\norm{x_i - x_j}^2 / 2\sigma_i^2)}{\sum_{k\neq i} \exp(-\norm{x_i - x_k}^2 / 2\sigma_i^2)}, (\#eq:pji)
 \end{equation}
-
-The similarity metric for the originals space symmetrizes this conditional probability and is defined as
+where $\sigma_i^2$ denotes the variance of the Gaussian associated with $x_i$. The similarity metric for the original
+ space symmetrizes this conditional probability and is defined as
 
@@
 In Figures \@ref(fig:flood-zone-tsne), we display the t-SNE of the learned embeddings for `flood_zone` in
-Model 3 with various perplexity settings: 0.1, 0.5, 1.0, and 10; the learning rate and the number of steps are fixed at
+Model 3 with various perplexity settings: 2, 3, 5, and 10; the learning rate and the number of steps are fixed at
 100 and 10,000, respectively, for all plots. In the first three plots, we can see the semblance of clusters forming. In
 particular, flood zone D appears in its own cluster, which implies it is far away from other levels in the embedding
-space. When the perplexity is set to 10 (and beyond), however, we lose the geometric properties.
+space. When the perplexity is set to 10 (and beyond), however, we start to lose the geometric properties.
 
-```{r flood-zone-tsne, echo = FALSE, fig.cap="Flood zone t-SNE", out.width = "60%", fig.align = "center"}
+```{r flood-zone-tsne, echo = FALSE, fig.cap="t-SNE plots of learned embeddings of flood zone in Model 4, with various perplexity values.
+From left to right then top to bottom: 2, 3, 5, and 10.", out.width = "60%", fig.align = "center"}
 knitr::include_graphics("images/flood_zone_tsne.png")
@@
 are considering, it performs similary to the more complex neural network models in the RMSE metric (which it optimizes
-for, as the unit deviance of the normal distribution corresponds with MSE.) Of course, this is not to discredit neural
+for, as the unit deviance of the normal distribution correspond to MSE.) Of course, this is not to discredit neural
 networks or GLMs, as the experiments are performed without extensive hyperparameter tuning or feature engineering.

### 2021-04-05 R/attn-section-models.R
Align attention hyperparameters to Section 4

@@ -1,0 +1,171 @@
+library(tidyverse)
+library(recipes)
+library(rsample)
+library(torch)
+library(tabnet)
+
+source("R/model-utils.R")
+source("R/data-loading.R")
+
+categorical_cols <- c(
+  "primary_residence", "basement_enclosure_crawlspace_type",
+  "number_of_floors_in_the_insured_building",
+  "occupancy_type", "flood_zone"
+)
+
+numeric_cols <- c("total_building_insurance_coverage", "community_rating_system_discount")
+response_col <- "amount_paid_on_building_claim"
+coverage_col <- "coverage"
+
+set.seed(420)
+cvfolds <- small_data %>%
+  rsample::vfold_cv(v = 5)
+
+model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_size = 5000, ...) {
+  env <- new.env()
+  analysis_data <- analysis(splits)
+  assessment_data <- assessment(splits)
+
+  rec_nn <- recipe(amount_paid_on_building_claim ~ .,
+                   data = analysis_data %>%
+                     select(-loss_proportion, -reported_zip_code)
+  ) %>%
+    step_normalize(all_numeric(), -all_outcomes()) %>%
+    step_novel(all_nominal()) %>%
+    step_integer(all_nominal(), strict = TRUE, zero_based = TRUE) %>%
+    prep(strings_as_factors = TRUE)
+
+  ds <- flood_dataset(
+    juice(rec_nn) %>% mutate(coverage = analysis_data$total_building_insurance_coverage),
+    categorical_cols, numeric_cols, coverage_col, response_col, env
+  )
+  baked_test_data <- bake(rec_nn, assessment_data)
+
+  test_ds <- flood_dataset(
+    baked_test_data %>% mutate(coverage = assessment_data$total_building_insurance_coverage),
+    categorical_cols, numeric_cols, coverage_col
+  )
+
+  train_indx <- sample(length(ds), 0.8 * length(ds))
+  valid_indx <- seq_len(length(ds)) %>% setdiff(train_indx)
+  train_ds <- dataset_subset(ds, train_indx)
+  valid_ds <- dataset_subset(ds, valid_indx)
+
+  train_dl <- train_ds %>% dataloader(batch_size = batch_size, shuffle = TRUE)
+  valid_dl <- valid_ds %>% dataloader(batch_size = batch_size, shuffle = TRUE)
[…]

### 2021-04-05 R/attn-section-models.R
Update attn-section-models.R

@@ -103,9 +103,7 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 
   model_tabnet <- tabnet_fit(form,
                              data = juice(rec_tabnet), epochs = epochs,
-                             num_independent = 1, num_shared = 1, num_steps = 3,
-                             decision_width = 1, attention_width = 1,
-                             learn_rate = learning_rate, verbose = TRUE, batch_size = batch_size,
+                             verbose = TRUE,
                              valid_split = 0.2
   )
 
@@ -129,38 +127,38 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 }
 
 cv_results <- cvfolds$splits %>%
-  lapply(function(x) model_analyze_assess(x, 0.01, 15, 1000))
+  lapply(function(x) model_analyze_assess(x, 0.001, 30, 1000))
 
-cv_results %>%
+model_names_mapping = data.frame(mod = c("tabnet", "tabt", "simpleattn"), Model = c("TabNet", "TabTransformer", "Simple Attention"))
+
+require(data.table)
+res = cv_results %>%
   map(function(x) {
     list(
-      rmse_nn = rmse(x$actuals, pmax(x$preds_nn, 0.01)),
-      rmse_nn2 = rmse(x$actuals, pmax(x$preds_nn2, 0.01)),
-      rmse_glm = rmse(x$actuals, x$preds_glm),
-      rmse_glm2 = rmse(x$actuals, x$preds_glm2),
-      rmse_glm_gaussian = rmse(x$actuals, pmax(x$preds_glm_gaussian, 0.01)),
-      rmse_zeros = rmse(x$actuals, 0),
-      mae_nn = mae(x$actuals, x$preds_nn),
-      mae_nn2 = mae(x$actuals, x$preds_nn2),
-      mae_glm = mae(x$actuals, x$preds_glm),
-      mae_glm2 = mae(x$actuals, x$preds_glm2),
-      mae_glm_gaussian = mae(x$actuals, pmax(x$preds_glm_gaussian, 0.01))
+      rmse_tabnet = rmse(x$actuals, pmax(x$preds_tabnet, 0.01)),
+      rmse_tabt = rmse(x$actuals, pmax(x$preds_tabt, 0.01)),
+      rmse_simpleattn = rmse(x$actuals, x$preds_simple_attn),
[…]

### 2021-04-05 manuscript/manuscript.Rmd
Several changes
- fix draw.io diagrams
- add attention section

@@
 ```{r nn-1, echo = FALSE, fig.cap = "Architecture of Models 2 and 4.", out.width = "80%", fig.align = "center"}
-knitr::include_graphics("images/nn.png")
+knitr::include_graphics("images/nn.pdf")
 ```
@@
 commonly used for severity modeling, we throw it into the mix as a benchmark, a practice we recommend in order to
-check reasonablness of other models' results. Since it is possible for a linear
+check reasonableness of other models' results. Since it is possible for a linear
 regression to output negative values, we cap the predictions below by 0.01 during scoring. Somewhat surprisingly, in 
 the problem we
-are considering, it performs similary to the more complex neural network models in the RMSE metric (which it optimizes
+are considering, it performs similar to the more complex neural network models in the RMSE metric (which it optimizes
 for, as the unit deviance of the normal distribution correspond to MSE.) Of course, this is not to discredit neural
@@
 # Attention based modelling {#attention_models}
+In this section we investigate whether the predictive performance of the models applied to the NFIP dataset can be improved
+by applying the attention based models defined in Section \ref{attention}. We discuss the implementation of each of the 
+Simple Attention, TabTransformer and TabNet models in the following sub-section, then discuss how the modifications made
+to the embeddings through the application of attention can be visualized in the following sub-section. We conclude the 
+section with a discussion of the model results.
+
+## Models
+
+In this subsection, we develop the following models:
+
+5. A neural network based on the design of Model 4, with an attention component
+6. Similar to Model 5, a neural network implementing the TabTransformer architecture
+7. A neural network implementing the TabNet architecture
+
+Compared to the models presented in the previous section, the models presented here are closer to state of the art models that
+might be used for tabular data modelling problems. To the best of our knowledge, this is the first analysis of these architectures
+within the actuarial literature.
+
+### Model 5: Simple Attention Network
+Model 5 is conceptually similar to Model 4, except for the following two aspects. First, we standardize the dimension of the embedding 
+layers to 8 dimensions for each categorical covariate. This is done to allow for the application of the attention component, which 
+requires the embeddings for each covariate to have the same dimension. Second, we apply a self-attention mechanism within the network, 
+as shown in Equation \ref{eq:embed_to_attn_to_nn}. We illustrate this architecture in Figure \@ref(fig:nn-2).
+
+```{r nn-2, echo = FALSE, fig.cap = "Architecture of Model 5.", out.width = "80%", fig.align = "center"}
+knitr::include_graphics("images/sna2.pdf")
+```
+
+### Model 6: Neural Network with Unidimensional Embeddings
+
+### Model 7: Neural Network with Unidimensional Embeddings
 

### 2021-04-05 R/attn-section-models.R

@@ -57,7 +57,7 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 
   # tabtransformer
   model_tabt <- tabtransformer(env$cardinalities, length(numeric_cols),
-                               embedding_dim = 8, num_heads = 3, fc_units = 8
+                               embedding_dim = 8, num_heads = 3, fc_units = 16
   )
 
   optimizer <- optim_adam(model_tabt$parameters, lr = learning_rate)
@@ -74,7 +74,7 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
   # simple attention
 
   model_simple_attn <- simple_net_attn(env$cardinalities, length(numeric_cols),
-                                       units = 8)
+                                       units = 16)
 
   optimizer <- optim_adam(model_simple_attn$parameters, lr = learning_rate, amsgrad = TRUE)
 
@@ -102,7 +102,7 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
     prep(strings_as_factors = TRUE)
 
   model_tabnet <- tabnet_fit(form,
-                             data = juice(rec_tabnet), epochs = epochs,
+                             data = juice(rec_tabnet), epochs = 15,
                              verbose = TRUE,
                              valid_split = 0.2
   )

### 2021-04-05 manuscript/manuscript.Rmd
Add to manuscript

@@
 for the model task. Within TabNet, an attention based model is used to select features by estimating attention scores for each covariate within $X$. 
-The covariates are multiplied by the attention scores to down-weight less relevant features for the prediction problem. Other less important details of the Tabnwet
+The covariates are multiplied by the attention scores to down-weight less relevant features for the prediction problem. Other less important details of the TabNet
 model are given in @Ark2019.
@@
 
-### Model 6: Neural Network with Unidimensional Embeddings
+### Model 6: TabTransformer
+Whereas Model 5 makes a simple modification to the structure of Model 4, the TabTransformer model is slightly more complex. With respect to
+similarities between Model 5 and 6, both use embeddings with a standard 8 dimensions for each categorical covariate. In terms of differences,
+Model 6 uses a Transformer layer in place of self-attention and a positional encoding of a single dimension, i.e. $d_col = 1$. The TabTransformer
+architecture is shown in Figure Figure \@ref(fig:nn-3).
 
-### Model 7: Neural Network with Unidimensional Embeddings
+```{r nn-3, echo = FALSE, fig.cap = "Architecture of Model 6.", out.width = "80%", fig.align = "center"}
+knitr::include_graphics("images/tabt.pdf")
+```
 
-Can we get some lift by adding attention layers? TabNet model Transformer model
+### Model 7: TabNet
+The final model we consider in this subsection is the TabNet architecture. The structure of the model is quite similar to Model 6, except 
+that a more specialized form of self-attention is used to select the most important covariates for the modelling problem.
 
-Description of tabnet, talk about how it's related to embeddings, show some plots 
-like \@ref(fig:masks) etc.
+## Explaining Attention Based models
 
-```{r masks, echo = FALSE, fig.cap = "blahblah", out.width = "100%", fig.align = "center"}
-knitr::include_graphics("images/masks.png")
-```
+## Results
 

### 2021-04-06 R/attn-section-models.R
Changed models to reflect axes

@@ -92,22 +92,22 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
     basement_enclosure_crawlspace_type + number_of_floors_in_the_insured_building +
     occupancy_type + flood_zone + primary_residence + community_rating_system_discount
 
-  # tabnet
-  rec_tabnet <- recipe(amount_paid_on_building_claim ~ .,
-                       data = analysis_data %>%
-                         select(-loss_proportion, -reported_zip_code)
-  ) %>%
-    step_normalize(all_numeric(), -all_outcomes()) %>%
-    step_novel(all_nominal()) %>%
-    prep(strings_as_factors = TRUE)
-
-  model_tabnet <- tabnet_fit(form,
-                             data = juice(rec_tabnet), epochs = 15,
-                             verbose = TRUE,
-                             valid_split = 0.2
-  )
-
-  preds_tabnet <- predict(model_tabnet, bake(rec_tabnet, assessment_data))$.pred
+  # # tabnet
+  # rec_tabnet <- recipe(amount_paid_on_building_claim ~ .,
+  #                      data = analysis_data %>%
+  #                        select(-loss_proportion, -reported_zip_code)
+  # ) %>%
+  #   step_normalize(all_numeric(), -all_outcomes()) %>%
+  #   step_novel(all_nominal()) %>%
+  #   prep(strings_as_factors = TRUE)
+  #
+  # model_tabnet <- tabnet_fit(form,
+  #                            data = juice(rec_tabnet), epochs = 15,
+  #                            verbose = TRUE,
+  #                            valid_split = 0.2
+  # )
+  #
+  # preds_tabnet <- predict(model_tabnet, bake(rec_tabnet, assessment_data))$.pred
 
 
 
@@ -115,12 +115,12 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
     pull(amount_paid_on_building_claim)
 
   list(
-    model_tabnet = model_tabt,
-    model_tabt = model_tabnet,
+    #model_tabnet = model_tabnet,
+    model_tabt = model_tabt,
     model_simple_attn = model_simple_attn,
     rec_nn = rec_nn,
     actuals = actuals,
-    preds_tabnet = preds_tabnet,
[…]

### 2021-04-06 R/get_attn.R

@@ -1,0 +1,264 @@
+library(tidyverse)
+library(recipes)
+library(rsample)
+library(torch)
+library(tabnet)
+
+source("R/model-utils.R")
+source("R/data-loading.R")
+
+categorical_cols <- c(
+  "primary_residence", "basement_enclosure_crawlspace_type",
+  "number_of_floors_in_the_insured_building",
+  "occupancy_type", "flood_zone"
+)
+
+numeric_cols <- c("total_building_insurance_coverage", "community_rating_system_discount")
+response_col <- "amount_paid_on_building_claim"
+coverage_col <- "coverage"
+
+set.seed(420)
+cvfolds <- small_data %>%
+  rsample::vfold_cv(v = 5)
+
+####### get data
+splits = cvfolds$splits[[1]]
+env <- new.env()
+analysis_data <- analysis(splits)
+assessment_data <- assessment(splits)
+
+batch_size = 1
+
+rec_nn <- recipe(amount_paid_on_building_claim ~ .,
+                 data = analysis_data %>%
+                   select(-loss_proportion, -reported_zip_code)
+) %>%
+  step_normalize(all_numeric(), -all_outcomes()) %>%
+  step_novel(all_nominal()) %>%
+  step_integer(all_nominal(), strict = TRUE, zero_based = TRUE) %>%
+  prep(strings_as_factors = TRUE)
+
+ds <- flood_dataset(
+  juice(rec_nn) %>% mutate(coverage = analysis_data$total_building_insurance_coverage),
+  categorical_cols, numeric_cols, coverage_col, response_col, env
+)
+baked_test_data <- bake(rec_nn, assessment_data)
+
+test_ds <- flood_dataset(
+  baked_test_data %>% mutate(coverage = assessment_data$total_building_insurance_coverage),
+  categorical_cols, numeric_cols, coverage_col
+)
+
+train_indx <- sample(length(ds), 0.8 * length(ds))
+valid_indx <- seq_len(length(ds)) %>% setdiff(train_indx)
+train_ds <- dataset_subset(ds, train_indx)
+valid_ds <- dataset_subset(ds, valid_indx)
+
+train_dl <- train_ds %>% dataloader(batch_size = batch_size, shuffle = TRUE)
[…]

### 2021-04-06 R/model-utils.R

@@ -107,7 +107,7 @@ simple_net_attn <- nn_module(
         sum_embedding_dim <- sapply(cardinalities, fn_embedding_dim) %>%
             sum()
         self$embed_dim <- fn_embedding_dim()
-        self$attn <- nn_multihead_attention(embed_dim = embed_dim, num_heads = 1)
+        self$attn <- nn_multihead_attention(embed_dim = embed_dim, num_heads = 1, dropout = 0.02)
         self$fc <- nn_linear(sum_embedding_dim + num_numerical, units)
         self$output <- nn_linear(units, 1)
         self
@@ -115,7 +115,7 @@ simple_net_attn <- nn_module(
     forward = function(xcat, xnum, xcoverage) {
         embedded <- self$embedder(xcat)
         shapes <- embedded$shape
-        embedded_reshape <- embedded$view(list(embedded$shape[1], self$embed_dim, self$embed_dim))
+        embedded_reshape <- embedded$view(list(self$embed_dim,embedded$shape[1],  self$embed_dim))
         embedded_attended <- self$attn(embedded_reshape, embedded_reshape, embedded_reshape)
         embedded_attended <- embedded_attended[[1]]
         embedded_attended <- embedded_attended$view(list(embedded$shape[1], self$embed_dim * self$embed_dim))
@@ -302,7 +302,7 @@ tabtransformer <- nn_module(
     "tabtransformer",
     initialize = function(cardinalities, num_numerical, embedding_dim = 2, num_heads = 3, fc_units = 32) {
         self$col_embedder <- embedding_with_position(cardinalities, embedding_dim)
-        self$attn <- nn_multihead_attention(embedding_dim + 1, num_heads)
+        self$attn <- nn_multihead_attention(embedding_dim + 1, num_heads, dropout = 0.02)
         self$lnorm1 <- nn_layer_norm(embedding_dim + 1)
         self$lnorm2 <- nn_layer_norm(embedding_dim + 1)
         self$linear1 <- nn_linear(embedding_dim + 1, 4 * (embedding_dim + 1))

### 2021-04-06 R/attn-section-models.R
fix attn

@@ -57,7 +57,7 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 
   # tabtransformer
   model_tabt <- tabtransformer(env$cardinalities, length(numeric_cols),
-                               embedding_dim = 8, num_heads = 3, fc_units = 16
+                               embedding_dim = 10, num_heads = 3, fc_units = 16
   )
 
   optimizer <- optim_adam(model_tabt$parameters, lr = learning_rate)
@@ -73,7 +73,7 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 
   # simple attention
 
-  model_simple_attn <- simple_net_attn(env$cardinalities, length(numeric_cols),
+  model_simple_attn <- simple_net_attn(env$cardinalities, length(numeric_cols),embed_dim = 10,
                                        units = 16)
 
   optimizer <- optim_adam(model_simple_attn$parameters, lr = learning_rate, amsgrad = TRUE)

### 2021-04-06 R/get_attn.R

@@ -59,7 +59,7 @@ valid_dl <- valid_ds %>% dataloader(batch_size = batch_size, shuffle = TRUE)
 test_dl <- test_ds %>% dataloader(batch_size = batch_size, shuffle = FALSE)
 ####################
 
-xcat = train_ds[1]$x[[1]]$to(device = "cpu")
+xcat = train_ds[20]$x[[1]]$to(device = "cpu")
 xcat = torch_reshape(xcat, c(1,5))
 
 #### simple attn
@@ -82,6 +82,7 @@ xcat_out <- model$col_embedder(xcat)
 shapes <- xcat_out$shape
 embedded_reshape <- xcat_out$view(list(shapes[2], shapes[1], shapes[3]))
 
+attn = model$attn(embedded_reshape, embedded_reshape, embedded_reshape)[[2]]
 embedded_reshape <- model$attn(embedded_reshape, embedded_reshape, embedded_reshape)[[1]] + embedded_reshape
 embedded_reshape <- model$lnorm1(embedded_reshape)
 xcat_out_a <- embedded_reshape %>%

### 2021-04-06 R/model-utils.R

@@ -101,7 +101,7 @@ simple_net_attn <- nn_module(
     initialize = function(cardinalities,
                           num_numerical,
                           units = 16,
-                          embed_dim = 5,
+                          embed_dim = 10,
                           fn_embedding_dim = function(x) embed_dim) {
         self$embedder <- embedding_module(cardinalities, fn_embedding_dim)
         sum_embedding_dim <- sapply(cardinalities, fn_embedding_dim) %>%
@@ -115,10 +115,10 @@ simple_net_attn <- nn_module(
     forward = function(xcat, xnum, xcoverage) {
         embedded <- self$embedder(xcat)
         shapes <- embedded$shape
-        embedded_reshape <- embedded$view(list(self$embed_dim,embedded$shape[1],  self$embed_dim))
-        embedded_attended <- self$attn(embedded_reshape, embedded_reshape, embedded_reshape)
-        embedded_attended <- embedded_attended[[1]]
-        embedded_attended <- embedded_attended$view(list(embedded$shape[1], self$embed_dim * self$embed_dim))
+        embedded_reshape <- embedded$view(list(model$embed_dim, embedded$shape[1], model$embed_dim))
+        embedded_attention <- model$attn(embedded_reshape, embedded_reshape, embedded_reshape)
+        embedded_attended <- embedded_attention[[1]]
+        embedded_attended <- embedded_attended$view(list(embedded$shape[1], model$embed_dim * model$embed_dim))
         all <- torch_cat(list(embedded_attended, xnum$to(dtype = torch_float())), dim = 2)
         ratio <- all %>%
             self$fc() %>%
@@ -300,7 +300,7 @@ mlp <- nn_module(
 
 tabtransformer <- nn_module(
     "tabtransformer",
-    initialize = function(cardinalities, num_numerical, embedding_dim = 2, num_heads = 3, fc_units = 32) {
+    initialize = function(cardinalities, num_numerical, embedding_dim = 10, num_heads = 3, fc_units = 32) {
         self$col_embedder <- embedding_with_position(cardinalities, embedding_dim)
         self$attn <- nn_multihead_attention(embedding_dim + 1, num_heads, dropout = 0.02)
         self$lnorm1 <- nn_layer_norm(embedding_dim + 1)
@@ -313,16 +313,21 @@ tabtransformer <- nn_module(
         self
     },
[…]

### 2021-04-06 R/attn-section-models.R
Update shapes

@@ -57,7 +57,7 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 
   # tabtransformer
   model_tabt <- tabtransformer(env$cardinalities, length(numeric_cols),
-                               embedding_dim = 10, num_heads = 3, fc_units = 16
+                               embedding_dim = 10, num_heads = 11, fc_units = 16
   )
 
   optimizer <- optim_adam(model_tabt$parameters, lr = learning_rate)

### 2021-04-06 R/model-utils.R

@@ -107,7 +107,7 @@ simple_net_attn <- nn_module(
         sum_embedding_dim <- sapply(cardinalities, fn_embedding_dim) %>%
             sum()
         self$embed_dim <- fn_embedding_dim()
-        self$attn <- nn_multihead_attention(embed_dim = embed_dim, num_heads = 1, dropout = 0.02)
+        self$attn <- nn_multihead_attention(embed_dim = 10, num_heads = 1, dropout = 0.02)
         self$fc <- nn_linear(sum_embedding_dim + num_numerical, units)
         self$output <- nn_linear(units, 1)
         self
@@ -115,10 +115,11 @@ simple_net_attn <- nn_module(
     forward = function(xcat, xnum, xcoverage) {
         embedded <- self$embedder(xcat)
         shapes <- embedded$shape
-        embedded_reshape <- embedded$view(list(model$embed_dim, embedded$shape[1], model$embed_dim))
-        embedded_attention <- model$attn(embedded_reshape, embedded_reshape, embedded_reshape)
+        print(shapes)
+        embedded_reshape <- embedded$view(list(5, shapes[1], 10))
+        embedded_attention <- self$attn(embedded_reshape, embedded_reshape, embedded_reshape)
         embedded_attended <- embedded_attention[[1]]
-        embedded_attended <- embedded_attended$view(list(embedded$shape[1], model$embed_dim * model$embed_dim))
+        embedded_attended <- embedded_attended$view(list(shapes[1], 50))
         all <- torch_cat(list(embedded_attended, xnum$to(dtype = torch_float())), dim = 2)
         ratio <- all %>%
             self$fc() %>%
@@ -300,9 +301,9 @@ mlp <- nn_module(
 
 tabtransformer <- nn_module(
     "tabtransformer",
-    initialize = function(cardinalities, num_numerical, embedding_dim = 10, num_heads = 3, fc_units = 32) {
+    initialize = function(cardinalities, num_numerical, embedding_dim = 5, num_heads = 3, fc_units = 32) {
         self$col_embedder <- embedding_with_position(cardinalities, embedding_dim)
-        self$attn <- nn_multihead_attention(embedding_dim + 1, num_heads, dropout = 0.02)
+        self$attn <- nn_multihead_attention(embedding_dim + 1, num_heads, dropout = 0.05)
         self$lnorm1 <- nn_layer_norm(embedding_dim + 1)
[…]

### 2021-04-06 R/attn-section-models.R
fix hyper-pars

@@ -57,7 +57,7 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 
   # tabtransformer
   model_tabt <- tabtransformer(env$cardinalities, length(numeric_cols),
-                               embedding_dim = 10, num_heads = 11, fc_units = 16
+                               embedding_dim = 5, num_heads = 3, fc_units = 16
   )
 
   optimizer <- optim_adam(model_tabt$parameters, lr = learning_rate)
@@ -73,7 +73,7 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 
   # simple attention
 
-  model_simple_attn <- simple_net_attn(env$cardinalities, length(numeric_cols),embed_dim = 10,
+  model_simple_attn <- simple_net_attn(env$cardinalities, length(numeric_cols),embed_dim = 5,
                                        units = 16)
 
   optimizer <- optim_adam(model_simple_attn$parameters, lr = learning_rate, amsgrad = TRUE)

### 2021-04-06 R/model-utils.R

@@ -101,13 +101,14 @@ simple_net_attn <- nn_module(
     initialize = function(cardinalities,
                           num_numerical,
                           units = 16,
-                          embed_dim = 10,
+                          embed_dim = 5,
                           fn_embedding_dim = function(x) embed_dim) {
         self$embedder <- embedding_module(cardinalities, fn_embedding_dim)
         sum_embedding_dim <- sapply(cardinalities, fn_embedding_dim) %>%
             sum()
         self$embed_dim <- fn_embedding_dim()
-        self$attn <- nn_multihead_attention(embed_dim = 10, num_heads = 1, dropout = 0.02)
+        self$drop = nn_dropout(p=0.01)
+        self$attn <- nn_multihead_attention(embed_dim = 5, num_heads = 1, dropout = 0.01)
         self$fc <- nn_linear(sum_embedding_dim + num_numerical, units)
         self$output <- nn_linear(units, 1)
         self
@@ -115,11 +116,11 @@ simple_net_attn <- nn_module(
     forward = function(xcat, xnum, xcoverage) {
         embedded <- self$embedder(xcat)
         shapes <- embedded$shape
-        print(shapes)
-        embedded_reshape <- embedded$view(list(5, shapes[1], 10))
+        embedded_reshape <- embedded$view(list(5, shapes[1], 5))
         embedded_attention <- self$attn(embedded_reshape, embedded_reshape, embedded_reshape)
         embedded_attended <- embedded_attention[[1]]
-        embedded_attended <- embedded_attended$view(list(shapes[1], 50))
+        embedded_attended <- embedded_attended$view(list(shapes[1], 25))
+        embedded_attended <- self$drop(embedded_attended)
         all <- torch_cat(list(embedded_attended, xnum$to(dtype = torch_float())), dim = 2)
         ratio <- all %>%
             self$fc() %>%
@@ -308,6 +309,7 @@ tabtransformer <- nn_module(
         self$lnorm2 <- nn_layer_norm(embedding_dim + 1)
         self$linear1 <- nn_linear(embedding_dim + 1, 4 * (embedding_dim + 1))
         self$linear2 <- nn_linear(4 * (embedding_dim + 1), (embedding_dim + 1))
+        self$drop = nn_dropout(p=0.01)
         self$mlp1 <- mlp(length(cardinalities) * (embedding_dim + 1) + num_numerical, fc_units)
[…]

### 2021-04-06 R/model-utils.R
Update model-utils.R

@@ -103,6 +103,7 @@ simple_net_attn <- nn_module(
                           units = 16,
                           embed_dim = 5,
                           fn_embedding_dim = function(x) embed_dim) {
+        self$no_embeds = length(cardinalities)
         self$embedder <- embedding_module(cardinalities, fn_embedding_dim)
         sum_embedding_dim <- sapply(cardinalities, fn_embedding_dim) %>%
             sum()
@@ -115,11 +116,20 @@ simple_net_attn <- nn_module(
     },
     forward = function(xcat, xnum, xcoverage) {
         embedded <- self$embedder(xcat)
-        shapes <- embedded$shape
-        embedded_reshape <- embedded$view(list(5, shapes[1], 5))
+        batch_size <- embedded$shape[1]
+        no_embeds = self$no_embeds
+        embed_dim = self$embed_dim
+
+        embedded_reshape <- torch_unsqueeze(embedded,3) # batch_size * (no_embeds * embed_dim) * 1
+        embedded_reshape <- torch_reshape(embedded_reshape,c(batch_size, no_embeds, embed_dim)) # batch_size * no_embeds * embed_dim
+        embedded_reshape <- torch_transpose(embedded_reshape,2,1) # no_embeds * batch_size * embed_dim
+
         embedded_attention <- self$attn(embedded_reshape, embedded_reshape, embedded_reshape)
         embedded_attended <- embedded_attention[[1]]
-        embedded_attended <- embedded_attended$view(list(shapes[1], 25))
+
+        embedded_attended <- torch_transpose(embedded_attended, 1, 2)
+        embedded_attended <- torch_reshape(embedded_attended, c(batch_size, no_embeds*embed_dim))
+
         embedded_attended <- self$drop(embedded_attended)
         all <- torch_cat(list(embedded_attended, xnum$to(dtype = torch_float())), dim = 2)
         ratio <- all %>%
@@ -303,6 +313,9 @@ mlp <- nn_module(
 tabtransformer <- nn_module(
     "tabtransformer",
     initialize = function(cardinalities, num_numerical, embedding_dim = 5, num_heads = 3, fc_units = 32) {
+        self$no_embeds = length(cardinalities)
+        self$embed_dim <- embedding_dim
+
         self$col_embedder <- embedding_with_position(cardinalities, embedding_dim)
[…]

### 2021-04-07 manuscript/manuscript.Rmd
Changed models to reflect axes
Update manuscript section 6

@@
 ---
-title: Categorical Predictor Embeddings in Actuarial Modeling
+title: Categorical Predictor Embeddings and Attention Based Neural Networks in Actuarial Modeling
 authors:
@@
 keywords:
-  - blah
-  - blee
-  - bloo
-  - these are optional and can be removed
+  - categorical data
+  - neural networks
+  - embeddings
+  - attention
+  - severity modelling
+  - National Flood Insurance Program 
 bibliography: references.bib
@@
 been successfully used on embeddings in the field of natural language processing and we incorporate attention 
-based models into our predictive modelling example.
+based models into our predictive modelling example to demonstrate the use of these models for actuarial purposes.
 
@@
 for the unseen levels manually. In practice, a common approach is to take an average value 
-of some sort of the weights of theother levels. In our case, we take the median (if there are multiple, the lower of
+of some sort of the weights of the other levels. In our case, we take the median (if there are multiple, the lower of
 the two), but a mean, mean weighted by frequency of observations, or trimmed mean could be used.
@@
 In Table \@ref(tab:cv-results), we exhibit the cross-validated performance metrics of each of the models. We report
-both the root mean squared error (RMSE) and the mean absolute error (MAE); we note that these are just a couple of many potential metrics to use, and are so chosen for their interpretability and prevalence in the literature for comparing
+both the root mean squared error (RMSE) and the mean absolute error (MAE); we note that these are just two of many 
+potential metrics to use, and are so chosen for their interpretability and prevalence in the literature for comparing
 different types of models. Recall that, between the two metrics, RMSE penalizes large mispredictions than MAE. Also,
@@
 While linear regression (i.e., the specific case of GLM with a gaussian distribution and identity link function) is not
-commonly used for severity modeling, we throw it into the mix as a benchmark, a practice we recommend in order to
+commonly used for severity modeling, we add it into the mix as a benchmark, a practice we recommend in order to
 check reasonableness of other models' results. Since it is possible for a linear
@@
 the problem we
-are considering, it performs similar to the more complex neural network models in the RMSE metric (which it optimizes
-for, as the unit deviance of the normal distribution correspond to MSE.) Of course, this is not to discredit neural
-networks or GLMs, as the experiments are performed without extensive hyperparameter tuning or feature engineering.
+are considering, it performs similarly to the more complex neural network models in the RMSE metric (which it optimizes
+for, as the unit deviance of the normal distribution correspond to MSE.) On the other hand, the performance of the linear model
+is quite significantly worse on the MAE metric. Of course, this is not to discredit neural networks or GLMs, as the experiments 
+are performed without extensive hyperparameter tuning or feature engineering.
 
@@
 ```
-
 ### Model 7: TabNet
@@
 
+## Training and Inference {#training-inference-attn}
+We follow a similar training setup for the three attention based models, to the neural networks discussed in the previous section. For Models 5 and 6, 
+we utilize the \texttt{Adam} optimizer as before, however, due to the increased complexity of the models in this section,
+we use learning rate of 0.001 (compared to 0.01 for the simpler models). Reflecting this reduced learning rate, 
+we train on the analysis set for a maximum of 150 epochs, and select the best model based on the lowest loss achieved on the assessment. Moreover, since these models are
+more complex than those tested in the previous section, we also add some minimal regularization using dropout [@srivastava2014dropout] to the attention layers 
+and the last layer of the network. Dropout functions by setting some components of the network randomly to zero during each epoch of training. This forces each
+component of the network to learn an independent representation of the data. In this section, we drop out components with a probability of 2.5\%. A final detail is that, 
+for both of these models, we use an embedding dimension of size 16 for each of the categorical covariates, since the attention mechanism requires that the embeddings 
+be of a common length. For the TabTransformer model, we use a row embedding of dimension 4.
+
+For Model 7, we use the suggested training setup that utilizes the \texttt{Adam} optimizer with a learning rate of 0.02, and train for 15 epochs (since longer training
+times did not lead to improved performance).
+
+In Table \@ref(tab:cv-results-attn), we show the cross-validated performance metrics of each of the models, 
+as well as the two best performing models from the previous section. As before, we report both the root mean squared error (RMSE) 
+and the mean absolute error (MAE). The results show that Model 5, which simply adds attention to Model 4, achieves slightly worse
+performance than Model 4 as measured by the RMSE, but using the MAE as a metric, outperforms Model 4. Thus, there is some room to argue that
+for tabular data modelling that uses embeddings, the use of attention within models should be considered. Disappointingly, the TabNet 
+architecture performs poorly, perhaps due to insufficient hyperparameter tuning, but indicating that ``out of the box", TabNet does not
+appear to work well for this modelling task. Finally, the TabTransformer model shows the best performance of all models considered in 
+this research, beating the others by a significant margin on both the RMSE and MAE metrics.
+
+Table: (\#tab:cv-results-attn) Cross validation results for Models 5-7.
+
+|Model                                                                          |   RMSE|    MAE|
+|:-----------------------------------------------------------------------------|------:|------:|
+|Model 4: MLP with multidimensional embeddings                                 | 60,973| 37,574|
+|Model 5: Simple Attention                                                     | 61,022| 37,025|
+|Model 6: TabNet                                                               | 62,938| 38,386|
+|Model 7: TabTransformer                                                       | 59,900| 36,343|
+|Linear regression, predictions capped below at 0.01                           | 60,879| 38,431|
+
+In what follows, we focus on understanding the TabTransformer model in more detail.
+
 ## Explaining Attention Based models
-
-## Results
 

### 2021-04-07 R/attn-section-models.R

@@ -76,7 +76,7 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
   model_simple_attn <- simple_net_attn(env$cardinalities, length(numeric_cols),embed_dim = 5,
                                        units = 16)
 
-  optimizer <- optim_adam(model_simple_attn$parameters, lr = learning_rate, amsgrad = TRUE)
+  optimizer <- optim_adam(model_simple_attn$parameters, lr = learning_rate)
 
   train_loop(model_simple_attn, train_dl, valid_dl, epochs, optimizer, patience = 5, "simple_attn")
 

### 2021-04-07 R/model-utils.R

@@ -317,7 +317,7 @@ tabtransformer <- nn_module(
         self$embed_dim <- embedding_dim
 
         self$col_embedder <- embedding_with_position(cardinalities, embedding_dim)
-        self$attn <- nn_multihead_attention(embedding_dim + 1, num_heads, dropout = 0.05)
+        self$attn <- nn_multihead_attention(embedding_dim + 1, num_heads, dropout = 0.01)
         self$lnorm1 <- nn_layer_norm(embedding_dim + 1)
         self$lnorm2 <- nn_layer_norm(embedding_dim + 1)
         self$linear1 <- nn_linear(embedding_dim + 1, 4 * (embedding_dim + 1))

### 2021-04-07 manuscript/manuscript.Rmd
Add Section 6 and 7

@@
 Model 6 uses a Transformer layer in place of self-attention and a positional encoding of a single dimension, i.e. $d_col = 1$. The TabTransformer
-architecture is shown in Figure Figure \@ref(fig:nn-3).
+architecture is shown in Figure \@ref(fig:nn-3).
 
@@
 we train on the analysis set for a maximum of 150 epochs, and select the best model based on the lowest loss achieved on the assessment. Moreover, since these models are
-more complex than those tested in the previous section, we also add some minimal regularization using dropout [@srivastava2014dropout] to the attention layers 
-and the last layer of the network. Dropout functions by setting some components of the network randomly to zero during each epoch of training. This forces each
-component of the network to learn an independent representation of the data. In this section, we drop out components with a probability of 2.5\%. A final detail is that, 
+significantly more complex than those tested in the previous section, we also add some minimal regularization using dropout [@srivastava2014dropout] to the attention layers 
+and the last layer of the network, to prevent overfitting. Dropout functions by setting some components of the network randomly to zero during each epoch of training. 
+This forces each component of the network to learn a somewhat independent representation of the data, thus helping to avoid overfitting by preventing components of the 
+network from becoming too specialized. In this section, we drop out components with a probability of 2.5\%. A final detail is that, 
 for both of these models, we use an embedding dimension of size 16 for each of the categorical covariates, since the attention mechanism requires that the embeddings 
@@
 as well as the two best performing models from the previous section. As before, we report both the root mean squared error (RMSE) 
-and the mean absolute error (MAE). The results show that Model 5, which simply adds attention to Model 4, achieves slightly worse
-performance than Model 4 as measured by the RMSE, but using the MAE as a metric, outperforms Model 4. Thus, there is some room to argue that
-for tabular data modelling that uses embeddings, the use of attention within models should be considered. Disappointingly, the TabNet 
-architecture performs poorly, perhaps due to insufficient hyperparameter tuning, but indicating that ``out of the box", TabNet does not
-appear to work well for this modelling task. Finally, the TabTransformer model shows the best performance of all models considered in 
-this research, beating the others by a significant margin on both the RMSE and MAE metrics.
+and the mean absolute error (MAE). The results show that Model 5, which simply adds attention to Model 4, outperforms Model 4 on both the RMSE and 
+MAE metrics. Thus, there is some room to argue that for tabular data modelling that uses embeddings for categorical data, 
+the use of attention within models should be considered. Disappointingly, the TabNet architecture performs poorly, perhaps due to insufficient hyperparameter tuning, 
+but indicating that ``out of the box", TabNet does not appear to work well for this modelling task. Finally, the TabTransformer model shows the best performance of all
+ models considered in this research, beating the other models by a significant margin on both the RMSE and MAE metrics.
 
@@
 |Model 4: MLP with multidimensional embeddings                                 | 60,973| 37,574|
-|Model 5: Simple Attention                                                     | 61,022| 37,025|
+|Model 5: Simple Attention                                                     | 60,601| 36,739|
 |Model 6: TabNet                                                               | 62,938| 38,386|
@@
 
-## Explaining Attention Based models
+## Exploring the TabTransformer model
+
+Here, we explore what the TabTransformer model has learned from the data via the attention process that forms the core of the model. We focus on the difference 
+between the flood embedding learned by the model, compared with the output of the Transformer layer that processes the embeddings before these enter the model. 
+@Huang2020 call the latter ``contextual embeddings", because the attention mechanism within the TabTransformer model augments the embeddings based on the 
+other covariates that appear for each observation $i$.
+
+To illustrate this, we selected a single TabTransformer fit on one fold of the training data, and selected at random 10 000 individual observations. For each
+observation, the embedding relating to the flood zone of the observation was extracted from the model, as well as the contextual embedding that was produced 
+for that observation by the TabTransformer model. We found that a PCA and t-SNE analysis of the embeddings produced very similar results to those shown in the previous section,
+so we do not show these plots here. To investigate the difference between the embeddings and contextual embeddings for the `flood_zone` variable, 
+we show the first component from a PCA analysis of each of these in Figure \@ref(fig:embd).
+
+```{r embd, echo = FALSE, fig.cap = "Embedding versus Contextual Embedding, Flood Zone, first PCA components", out.width = "80%", fig.align = "center"}
+knitr::include_graphics("images/emb_vs_cembd.pdf")
+```
+
+The figure shows that, whereas the first principal component of the embeddings occupy discrete points only (shown on the $x$-axis), 
+the first principal component of the **contextual** embeddings is continuous (shown on the $y$-axis), meaning that the model has modified the values
+of the embedding in a smooth manner. Since the inputs to the attention mechanism which is responsible for this are the embeddings for the other categorical
+variables for each observation, these other variables have influenced the final embedding used within the model for the `flood_zone` variable. By considering 
+each of the other categorical variables entering the model, it was found that the basement enclosure crawl space variable explains most of the variation
+observed within the flood zone embeddings, as shown in Figure \@ref(fig:embdexp). The attention mechanism produces the lowest values for those observations
+with an unfinished basement, whereas the model produces the highest values for buildings without a crawl space.
+
+```{r embdexp, echo = FALSE, fig.cap = "Embedding versus Contextual Embedding, Flood Zone, first PCA components, points coloured based on crawl space variable", out.width = "80%", fig.align = "center"}
+knitr::include_graphics("images/emb_vs_cembd_exp.pdf")
+```
+To investigate the predictive value added by the contextual embeddings, a simple Gamma GLM was fit to these 10 000 observations, with the goal of predicting the 
+claim amount based only on either the embeddings or the contextual embeddings. As shown in Table \@ref(tab:emd-vs-cembd), the performance of the latter model, 
+as indicated by the Aikaike Information Criterion (AIC) was significantly better than the latter model (37 129 compared with 37 463), 
+in other words, the contextual embeddings that incorporate information across all of the categorical variables are significantly better predictors 
+of claim severity compared with the embeddings.
+
+Table: (\#tab:emd-vs-cembd) AIC for GLMs predicting claim severity, embeddings compared with contextual embeddings.
+
+|Embedding Type       |      AIC|
+|:--------------------|--------:|
+|Embedding            | 37,464|
+|Contextual embedding | 37,129|
 
@@
 
-Conclusions
+This study has focused on how embeddings can be applied within the context of actuarial modelling, by illustrating a range of approaches: first, relatively simple
+neural networks with embeddings were defined, the embeddings from these models were reused within traditional GLM models and, finally, more advanced attention based models 
+were studied. These models were demonstrated within the context of a claims severity modelling problem based on data from the NFIP. Whereas we have only considered severity 
+in this study, it is likely that our findings will replicate for the modelling of claim frequency, which is usually an easier problem. Our key findings are that 
+processing categorical variables with multi-dimensional embeddings leads to enhanced performance within simple neural networks, and that, by including these within traditional
+GLM models, the predictive performance of these models can be enhanced, compared to the usual encoding scheme for categorical variables. Some of the attention based models 
+considered within this study performed well, in particular, the TabTransformer model of @Huang2020 appears quite promising for use in actuarial modelling. The study has also 
+illustrated how embeddings can be visualized using the PCA and t-SNE techniques. We found that, in the case of the NFIP data, it is possible to explain which variables modify 
+the embeddings based on the context of each observation.
+
+Several avenues for future research can be considered. One surprising finding of our work is that the TabNet model performed quite poorly, leading us to conclude that this 
+model appears to be less suitable for actuarial modelling. Understanding these findings in more detail would be a valuable contribution to the literature. Another helpful contribution
+would be to investigate the optimal hyperparameters for the TabTransformer model in the context of actuarial modelling. Finally, extneding our findings to a claims frequency example
+could be considered.
 

### 2021-04-07 manuscript/manuscript.Rmd
Update manuscript.Rmd

@@
   - attention
-  - severity modelling
+  - severity Modeling
   - National Flood Insurance Program 
@@
 vehicle will often be modelled by including a (single) factor within models that modifies the relative frequency 
-predicted for each type of vehicle. In other cases, modelling is performed for each category separately, thus the 
-categorical data is used within the modelling in an implicit manner, for example, common practice is to estimate 
+predicted for each type of vehicle. In other cases, Modeling is performed for each category separately, thus the 
+categorical data is used within the Modeling in an implicit manner, for example, common practice is to estimate 
 reserves for different lines of business separately, meaning to say, with no parameters being shared across each of the
@@
 
-This approach to modelling categorical data has several advantages over more traditional treatments of categorical data.
+This approach to Modeling categorical data has several advantages over more traditional treatments of categorical data.
 Using categorical embeddings instead of traditional techniques has been shown to increase predictive accuracy of 
@@
 not yet been studied in detail in the actuarial literature. In this work, we aim to study how embeddings using 
-different settings perform in the context of a large-scale predictive modelling problem, and give guidance on the 
+different settings perform in the context of a large-scale predictive Modeling problem, and give guidance on the 
 process that can be followed to determine this in other problems. Although neural network have been shown to achieve
@@
 been successfully used on embeddings in the field of natural language processing and we incorporate attention 
-based models into our predictive modelling example to demonstrate the use of these models for actuarial purposes.
+based models into our predictive Modeling example to demonstrate the use of these models for actuarial purposes.
 
@@
 in the actuarial literature. Section \ref{defns} provides the notation used in the paper and defines GLMs, neural 
-networks and related modelling concepts, including embeddings and attention. In Section \ref{modelling}, we provide 
+networks and related Modeling concepts, including embeddings and attention. In Section \ref{Modeling}, we provide 
 initial models for the NFIP dataset and consider the influence of hyperparameter choices on the results of the neural 
@@
 
-A different approach to modelling categorical data is credibility theory (see @Buhlmann2006 for an overview), which, 
+A different approach to Modeling categorical data is credibility theory (see @Buhlmann2006 for an overview), which, 
 in the context of rating, can be applied to derive premiums that reflect the experience of a particular policyholder, by 
@@
 
-Generalized Linear Mixed Models (GLMMs) are an extension of GLMs that are designed for modelling categorical data using 
+Generalized Linear Mixed Models (GLMMs) are an extension of GLMs that are designed for Modeling categorical data using 
 a principle very similar to that of credibility theory [@Klinker2010]. Instead of calibrating indicator variables for 
@@
 
-Embedding layers represent a different approach to the problem of modelling categorical data that was recently 
+Embedding layers represent a different approach to the problem of Modeling categorical data that was recently 
 introduced in an actuarial context. Note that in the next section, we reflect on similarities between the conventional 
@@
 context, it was shown that the out-of-sample accuracy of a neural network trained to predict claims frequencies on motor 
-third party liability was enhanced by modelling the categorical variables within this dataset using embedding layers. 
+third party liability was enhanced by Modeling the categorical variables within this dataset using embedding layers. 
 Second, a neural network with embedding layers was used to model all of the mortality rates in the Human Mortality 
@@
 
-In this study, we are concerned with regression modelling, which is the task of predicting an unknown outcome $y$ on the 
+In this study, we are concerned with regression Modeling, which is the task of predicting an unknown outcome $y$ on the 
 basis of information about that outcome contained in predictor variables, or features, stored in a matrix $X$. For 
@@
 and subsequently as a replacement for FCNs in the so-called Transformer architecture, which is now widely used in natural language processing [@Vaswani2017a], 
-and, more recently, has been applied to computer vision and tabular modelling tasks. 
+and, more recently, has been applied to computer vision and tabular Modeling tasks. 
 Attention mechanisms allow deep neural nets to weight the covariates entering the model in a flexible manner; these types of applications in natural language 
 processing are demonstrated in,
-for example, @Vaswani2017a. In an actuarial context, attention mechanisms can be understood as giving greater weight to covariates that are important for the modelling task. 
+for example, @Vaswani2017a. In an actuarial context, attention mechanisms can be understood as giving greater weight to covariates that are important for the Modeling task. 
 In this section we provide a theoretical introduction to attention mechanisms and then discuss applications of attention to modeling tabular data. 
@@
 X^*: \mathbb{R}^{(q \times d) \times (q \times d) \times (q \times d)} \to \mathbb{R}^{(q \times d)}, ~~
-(Q, K, X') ~\mapsto ~ X^* = A(Q, K, X'),
+(Q, K, X') ~\mapsto ~ X^* = Attn(Q, K, X'),
 \label{eq:attention}
@@
  $X' \in \mathbb{R}^{q \times d}$ is a matrix of value vectors and $X^* \in \mathbb{R}^{q \times d}$, 
- the output of the attention mechanism, is a new matrix of values that have been reweighted according to their importance for the modelling problem. 
+ the output of the attention mechanism, is a new matrix of values that have been reweighted according to their importance for the Modeling problem. 
  As noted above, several different options for the mapping in Equation \ref{eq:attention} exist in the literature; here we describe the scaled dot-product self-attention mechanism 
@@
 An intuitive explanation of the attention formula is as follows: we start by considering the importance of all of the covariates 
-that we have for our modelling problem in the context of each individual covariate. This is done by assigning a score between zero
-and one to each covariate in the modelling problem, and we repeat this process for each of the covariates. Then, we replace each 
+that we have for our Modeling problem in the context of each individual covariate. This is done by assigning a score between zero
+and one to each covariate in the Modeling problem, and we repeat this process for each of the covariates. Then, we replace each 
 of the original covariates with a new covariate that has been formed by taking a weighted average of the covariates and the scores.
@@
 
-### Attention Modelling for Tabular Data
-
-Several different approaches to applying attention within the modelling of tabular data have been proposed in the literature. Perhaps the simplest way of doing 
+### Attention Modeling for Tabular Data
+
+Several different approaches to applying attention within the Modeling of tabular data have been proposed in the literature. Perhaps the simplest way of doing 
 this is to insert an attention layer between the embeddings and the rest of the neural network. Mathematically, we can modify Equation \ref{eq:embed_to_nn} as follows:
@@
 Finally, a different way of incorporating attention into the modeling of tabular data has been proposed by @Ark2019, who refer to their model as TabNet. 
-In summary, the main idea of the TabNet model is to try emulate the excellent performance of decision trees on tabular data modelling using deep neural networks. 
-This is done by structuring the neural networks to emulate a key aspect of decision tree modelling, which is the efficient selection of relevant covariates
+In summary, the main idea of the TabNet model is to try emulate the excellent performance of decision trees on tabular data Modeling using deep neural networks. 
+This is done by structuring the neural networks to emulate a key aspect of decision tree Modeling, which is the efficient selection of relevant covariates
 for the model task. Within TabNet, an attention based model is used to select features by estimating attention scores for each covariate within $X$. 
@@
 
-# Predictive Modeling with Embeddings {#modelling}
+# Predictive Modeling with Embeddings {#Modeling}
 
@@
 Investigate approaches for using embedding layers for numeric variables, or numeric variables that were captured as 
-categorical variables (Can the modelling of numerical variables benefit from the application of embedding layers?) How 
+categorical variables (Can the Modeling of numerical variables benefit from the application of embedding layers?) How 
 should this best be done? CatBoost - cut into 256 groups smoothness Map numeric to a dense layer and use that as 
@@
 -->
-# Attention based modelling {#attention_models}
+# Attention based Modeling {#attention_models}
 In this section we investigate whether the predictive performance of the models applied to the NFIP dataset can be improved
@@
 Compared to the models presented in the previous section, the models presented here are closer to state of the art models that
-might be used for tabular data modelling problems. To the best of our knowledge, this is the first analysis of these architectures
+might be used for tabular data Modeling problems. To the best of our knowledge, this is the first analysis of these architectures
 within the actuarial literature.
@@
 The final model we consider in this subsection is the TabNet architecture. The structure of the model is quite similar to Model 6, except 
-that a more specialized form of self-attention is used to select the most important covariates for the modelling problem.
+that a more specialized form of self-attention is used to select the most important covariates for the Modeling problem.
 
@@
 and the mean absolute error (MAE). The results show that Model 5, which simply adds attention to Model 4, outperforms Model 4 on both the RMSE and 
-MAE metrics. Thus, there is some room to argue that for tabular data modelling that uses embeddings for categorical data, 
+MAE metrics. Thus, there is some room to argue that for tabular data Modeling that uses embeddings for categorical data, 
 the use of attention within models should be considered. Disappointingly, the TabNet architecture performs poorly, perhaps due to insufficient hyperparameter tuning, 
-but indicating that ``out of the box", TabNet does not appear to work well for this modelling task. Finally, the TabTransformer model shows the best performance of all
+but indicating that ``out of the box", TabNet does not appear to work well for this Modeling task. Finally, the TabTransformer model shows the best performance of all
  models considered in this research, beating the other models by a significant margin on both the RMSE and MAE metrics.
@@
 claim amount based only on either the embeddings or the contextual embeddings. As shown in Table \@ref(tab:emd-vs-cembd), the performance of the latter model, 
-as indicated by the Aikaike Information Criterion (AIC) was significantly better than the latter model (37 129 compared with 37 463), 
-in other words, the contextual embeddings that incorporate information across all of the categorical variables are significantly better predictors 
+as indicated by the RMSE and MAE metrics is significantly better, in other words, the contextual embeddings that incorporate information across all of the categorical variables are significantly better predictors
 of claim severity compared with the embeddings.
 
-Table: (\#tab:emd-vs-cembd) AIC for GLMs predicting claim severity, embeddings compared with contextual embeddings.
-
-|Embedding Type       |      AIC|
-|:--------------------|--------:|
-|Embedding            | 37,464|
-|Contextual embedding | 37,129|
+Table: (\#tab:emd-vs-cembd) RMSE and MAE for GLMs predicting claim severity, embeddings compared with contextual embeddings.
+
+|Embedding Type       |     RMSE|      MAE|
+|:--------------------|--------:|--------:|
+|Embedding            | 62596.84| 40323.82|
+|Contextual embedding | 62027.85| 39450.45|
 
@@
 
-This study has focused on how embeddings can be applied within the context of actuarial modelling, by illustrating a range of approaches: first, relatively simple
+This study has focused on how embeddings can be applied within the context of actuarial Modeling, by illustrating a range of approaches: first, relatively simple
 neural networks with embeddings were defined, the embeddings from these models were reused within traditional GLM models and, finally, more advanced attention based models 
-were studied. These models were demonstrated within the context of a claims severity modelling problem based on data from the NFIP. Whereas we have only considered severity 
-in this study, it is likely that our findings will replicate for the modelling of claim frequency, which is usually an easier problem. Our key findings are that 
+were studied. These models were demonstrated within the context of a claims severity Modeling problem based on data from the NFIP. Whereas we have only considered severity 
+in this study, it is likely that our findings will replicate for the Modeling of claim frequency, which is usually an easier problem. Our key findings are that 
 processing categorical variables with multi-dimensional embeddings leads to enhanced performance within simple neural networks, and that, by including these within traditional
 GLM models, the predictive performance of these models can be enhanced, compared to the usual encoding scheme for categorical variables. Some of the attention based models 
-considered within this study performed well, in particular, the TabTransformer model of @Huang2020 appears quite promising for use in actuarial modelling. The study has also 
+considered within this study performed well, in particular, the TabTransformer model of @Huang2020 appears quite promising for use in actuarial Modeling. The study has also 
 illustrated how embeddings can be visualized using the PCA and t-SNE techniques. We found that, in the case of the NFIP data, it is possible to explain which variables modify 
@@
 Several avenues for future research can be considered. One surprising finding of our work is that the TabNet model performed quite poorly, leading us to conclude that this 
-model appears to be less suitable for actuarial modelling. Understanding these findings in more detail would be a valuable contribution to the literature. Another helpful contribution
-would be to investigate the optimal hyperparameters for the TabTransformer model in the context of actuarial modelling. Finally, extneding our findings to a claims frequency example
+model appears to be less suitable for actuarial Modeling. Understanding these findings in more detail would be a valuable contribution to the literature. Another helpful contribution
+would be to investigate the optimal hyperparameters for the TabTransformer model in the context of actuarial Modeling. Finally, extending our findings to a claims frequency example
 could be considered.

### 2021-04-07 manuscript/manuscript.Rmd
work on manuscript

@@
 
-Categorical data are modelled by actuaries in many different contexts, from pricing of insurance products to reserving 
-for the liabilities generated by these products. Sometimes, these data are modelled in an explicit manner, for example, 
-when building models that apply across multiple categories, a form of dummy coding is usually used. For example, when 
-building models to price the frequency of motor insurance claims, claim experience relating to different types of motor
-vehicle will often be modelled by including a (single) factor within models that modifies the relative frequency 
-predicted for each type of vehicle. In other cases, Modeling is performed for each category separately, thus the 
-categorical data is used within the Modeling in an implicit manner, for example, common practice is to estimate 
-reserves for different lines of business separately, meaning to say, with no parameters being shared across each of the
-reserving models.
+Categorical data are modelled by actuaries in many different contexts, from pricing of insurance products to reserving for the liabilities generated by these products.
+Sometimes, these data are modelled in an explicit manner, for example, when building models that apply across multiple categories, a form of dummy coding is usually used.
+For example, when building models to price the frequency of motor insurance claims, claim experience relating to different types of motor vehicle will often be modelled by including a (single) factor within models that modifies the relative frequency predicted for each type of vehicle.
+In other cases, Modeling is performed for each category separately, thus the categorical data is used within the Modeling in an implicit manner, for example, common practice is to estimate reserves for different lines of business separately, meaning to say, with no parameters being shared across each of the reserving models.
 
-Recently, several studies of insurance problems have applied an alternative approach, originally from the natural 
-known as **categorical embeddings**. Instead of trying to capture the differences between categories using a single 
-factor, the categorical embedding approach rather maps each category to a low-dimensional numeric vector, which is then
-used within the model as a new predictor variable.
+Recently, several studies of insurance problems have applied an alternative approach, originally from the natural known as **categorical embeddings**.
+Instead of trying to capture the differences between categories using a single factor, the categorical embedding approach rather maps each category to a low-dimensional numeric vector, which is then used within the model as a new predictor variable.
 
 This approach to Modeling categorical data has several advantages over more traditional treatments of categorical data.
-Using categorical embeddings instead of traditional techniques has been shown to increase predictive accuracy of 
-models, for example, see @Richman2018 in the context of pricing. Models incorporating categorical embeddings can be
-pre-calibrated to traditional actuarial models, increasing the speed with which these models can be calibrated and 
-leading to models with better explainability [@wuthrich2019yes]. Finally, the similarity between the vectors learned 
-for different categories can be inspected, sometimes leading to insights into the workings of models, see, for example,
-@Kuo2019.
+Using categorical embeddings instead of traditional techniques has been shown to increase predictive accuracy of models, for example, see @Richman2018 in the context of pricing.
+Models incorporating categorical embeddings can be pre-calibrated to traditional actuarial models, increasing the speed with which these models can be calibrated and leading to models with better explainability [@wuthrich2019yes].
+Finally, the similarity between the vectors learned for different categories can be inspected, sometimes leading to insights into the workings of models, see, for example, @Kuo2019.
 
-On the other hand, several open questions about the use of embeddings within actuarial work remain, which we aim to 
-address in this study. First, hyperparameter settings for embeddings, such as the dimensions of the embedding layer and
-the use of regularization techniques such as dropout or normalization, that achieve optimal predictive performance has
-not yet been studied in detail in the actuarial literature. In this work, we aim to study how embeddings using 
-different settings perform in the context of a large-scale predictive Modeling problem, and give guidance on the 
-process that can be followed to determine this in other problems. Although neural network have been shown to achieve
-excellent predictive accuracy on actuarial tasks, many actuaries still prefer to use GLM models for pricing tasks, 
-thus, the issue of whether transferring embeddings to GLM models can achieve better performance is considered in this
-paper. <!-- Traditional actuarial techniques such as credibility theory have been used to work with some types of categorical data, but no study has been -->
-<!-- performed whether this can be applied within embeddings; here, we investigate whether performance is enhanced by applying credibility theory on embeddings 
+On the other hand, several open questions about the use of embeddings within actuarial work remain, which we aim to address in this study.
+First, hyperparameter settings for embeddings, such as the dimensions of the embedding layer and the use of regularization techniques such as dropout or normalization, that achieve optimal predictive performance has not yet been studied in detail in the actuarial literature.
+In this work, we aim to study how embeddings using different settings perform in the context of a large-scale predictive Modeling problem, and give guidance on the process that can be followed to determine this in other problems.
+Although neural network have been shown to achieve excellent predictive accuracy on actuarial tasks, many actuaries still prefer to use GLM models for pricing tasks, thus, the issue of whether transferring embeddings to GLM models can achieve better performance is considered in this paper.
+<!-- Traditional actuarial techniques such as credibility theory have been used to work with some types of categorical data, but no study has been --> <!-- performed whether this can be applied within embeddings; here, we investigate whether performance is enhanced by applying credibility theory on embeddings
 relating to categorical variables with many labels. Whereas embedding layers are usually considered in the context of categorical data,the 
-option exists to quantize numerical data and model it using embeddings, however, the results of doing so have not been investigated. -->
-Finally, in the past several years, a new type of neural network architecture based on attention [@Vaswani2017] has
-been successfully used on embeddings in the field of natural language processing and we incorporate attention 
-based models into our predictive Modeling example to demonstrate the use of these models for actuarial purposes.
+option exists to quantize numerical data and model it using embeddings, however, the results of doing so have not been investigated.
+--> Finally, in the past several years, a new type of neural network architecture based on attention [@Vaswani2017] has been successfully used on embeddings in the field of natural language processing and we incorporate attention based models into our predictive Modeling example to demonstrate the use of these models for actuarial purposes.
 
-In this work, we utilize the recently released National Flood Insurance Program (NFIP) dataset 
-[@FederalEmergencyManagementAgency2019] which provides exposure information for policies written under the NFIP since 
-XXXXDateXXXX, as well as the claims data relating to these exposures. We refer the reader to Appendix \ref{NFIP_eda} for
-an exploratory analysis of this dataset.
+In this work, we utilize the recently released National Flood Insurance Program (NFIP) dataset [@FederalEmergencyManagementAgency2019] which provides exposure information for policies written under the NFIP since XXXXDateXXXX, as well as the claims data relating to these exposures.
+We refer the reader to Appendix \ref{NFIP_eda} for an exploratory analysis of this dataset.
 
-The rest of this manuscript is organized as follows. Section \ref{lit_review} reviews recent applications of embeddings
-in the actuarial literature. Section \ref{defns} provides the notation used in the paper and defines GLMs, neural 
-networks and related Modeling concepts, including embeddings and attention. In Section \ref{Modeling}, we provide 
-initial models for the NFIP dataset and consider the influence of hyperparameter choices on the results of the neural 
-network model. That section also considers how successfully the embeddings used in the neural network model can be 
-transferred to a GLM model of the same data and how learned embeddings can be interpreted. We focus on attention based models 
-in Section \ref{attention_models}. Finally, Section \ref{Conclusions} provides a discussion of the results of this paper
-and considers avenues for future research.
+The rest of this manuscript is organized as follows.
+Section \ref{lit_review} reviews recent applications of embeddings in the actuarial literature.
+Section \ref{defns} provides the notation used in the paper and defines GLMs, neural networks and related Modeling concepts, including embeddings and attention.
+In Section \ref{Modeling}, we provide initial models for the NFIP dataset and consider the influence of hyperparameter choices on the results of the neural network model.
+That section also considers how successfully the embeddings used in the neural network model can be transferred to a GLM model of the same data and how learned embeddings can be interpreted.
+We focus on attention based models in Section \ref{attention_models}.
+Finally, Section \ref{Conclusions} provides a discussion of the results of this paper and considers avenues for future research.
 
@@
 
-Categorical data are usually modelled within GLMs and other predictive models using indicator variables which capture 
-the effect of each level of the category, see, for example, Section 2 in @Goldburd, using one of two main encoding 
-schemes: dummy-coding and one-hot encoding. Dummy-coding, used in the popular \texttt{R} statistical software, assigns 
-one level of the category as a baseline, for which an indicator variable is not calibrated, and the rest of the levels 
-are assigned indicator variables, thus, producing estimates within the model of how the effects of each level differ 
-from the baselines. One-hot encoding, often used in machine learning, is similar to dummy-coding, but assigns 
-indicator variables to each level, in other words, calibrates an extra indicator variable compared with dummy-coding.
+Categorical data are usually modelled within GLMs and other predictive models using indicator variables which capture the effect of each level of the category, see, for example, Section 2 in @Goldburd, using one of two main encoding schemes: dummy-coding and one-hot encoding.
+Dummy-coding, used in the popular \texttt{R} statistical software, assigns one level of the category as a baseline, for which an indicator variable is not calibrated, and the rest of the levels are assigned indicator variables, thus, producing estimates within the model of how the effects of each level differ from the baselines.
+One-hot encoding, often used in machine learning, is similar to dummy-coding, but assigns indicator variables to each level, in other words, calibrates an extra indicator variable compared with dummy-coding.
 
-A different approach to Modeling categorical data is credibility theory (see @Buhlmann2006 for an overview), which, 
-in the context of rating, can be applied to derive premiums that reflect the experience of a particular policyholder, by 
-estimating premiums as a weighted average between the premium produced using the collective experience (i.e. of all 
-policyholders) and the premium produced using the experience of the particular policyholder. The weight used in this 
-average is called a credibility factor and is calculated with reference to te variability of the policyholder experience 
-relative to the variability of the group experience. In this context, the implicit categorical variable is the 
-policyholder under consideration.
+A different approach to Modeling categorical data is credibility theory (see @Buhlmann2006 for an overview), which, in the context of rating, can be applied to derive premiums that reflect the experience of a particular policyholder, by estimating premiums as a weighted average between the premium produced using the collective experience (i.e.
+of all policyholders) and the premium produced using the experience of the particular policyholder.
+The weight used in this average is called a credibility factor and is calculated with reference to te variability of the policyholder experience relative to the variability of the group experience.
+In this context, the implicit categorical variable is the policyholder under consideration.
 
-Generalized Linear Mixed Models (GLMMs) are an extension of GLMs that are designed for Modeling categorical data using 
-a principle very similar to that of credibility theory [@Klinker2010]. Instead of calibrating indicator variables for 
-each level of the category, GLMMs estimate effects for each of these levels as a combination of the overall group mean 
-and the experience in each level of the category.
+Generalized Linear Mixed Models (GLMMs) are an extension of GLMs that are designed for Modeling categorical data using a principle very similar to that of credibility theory [@Klinker2010].
+Instead of calibrating indicator variables for each level of the category, GLMMs estimate effects for each of these levels as a combination of the overall group mean and the experience in each level of the category.
 
-Embedding layers represent a different approach to the problem of Modeling categorical data that was recently 
-introduced in an actuarial context. Note that in the next section, we reflect on similarities between the conventional 
-approaches discussed above and embedding layers. @Richman2018 reviewed the concept of embedding layers and connected 
-the sharing of information across categories to the familiar concept of credibility theory. In that work, two 
-applications of embedding layers were demonstrated. The first of these was in a Property and Casualty (P&C) pricing 
-context, it was shown that the out-of-sample accuracy of a neural network trained to predict claims frequencies on motor 
-third party liability was enhanced by Modeling the categorical variables within this dataset using embedding layers. 
-Second, a neural network with embedding layers was used to model all of the mortality rates in the Human Mortality 
-Database, where the differences in population mortality across countries and the differences in mortality at different 
-ages were modelled with embedding layers, again producing more accurate out of sample performance than the other models 
-tested.
+Embedding layers represent a different approach to the problem of Modeling categorical data that was recently introduced in an actuarial context.
+Note that in the next section, we reflect on similarities between the conventional approaches discussed above and embedding layers.
+@Richman2018 reviewed the concept of embedding layers and connected the sharing of information across categories to the familiar concept of credibility theory.
+In that work, two applications of embedding layers were demonstrated.
+The first of these was in a Property and Casualty (P&C) pricing context, it was shown that the out-of-sample accuracy of a neural network trained to predict claims frequencies on motor third party liability was enhanced by Modeling the categorical variables within this dataset using embedding layers.
+Second, a neural network with embedding layers was used to model all of the mortality rates in the Human Mortality Database, where the differences in population mortality across countries and the differences in mortality at different ages were modelled with embedding layers, again producing more accurate out of sample performance than the other models tested.
 
-Contemporaneous with that work is the DeepTriangle model of @Kuo2019, which applied recurrent neural networks to the 
-problem of Incurred but not Reported (IBNR) loss reserving, to model jointly the paid and incurred losses in the 
-Schedule P dataset. Embedding layers were used to capture the effect of differences in reserving delays and loss ratios 
-for each company in the Schedule P dataset. Evaluating the results of the DeepTriangle method showed that the out of 
-sample performance of the model (tested against the lower triangles in the Schedule P dataset) exceeded that of 
-traditional IBNR reserving techniques.
+Contemporaneous with that work is the DeepTriangle model of @Kuo2019, which applied recurrent neural networks to the problem of Incurred but not Reported (IBNR) loss reserving, to model jointly the paid and incurred losses in the Schedule P dataset.
+Embedding layers were used to capture the effect of differences in reserving delays and loss ratios for each company in the Schedule P dataset.
+Evaluating the results of the DeepTriangle method showed that the out of sample performance of the model (tested against the lower triangles in the Schedule P dataset) exceeded that of traditional IBNR reserving techniques.
 
-Many other applications of embeddings have subsequently appeared in the actuarial literature. Within mortality 
-forecasting, @Richman2019d and @Richman2020 both apply embeddings layers to model and forecast mortality rates on a 
-large scale. @wuthrich2019yes discussed how embeddings can be calibrated using GLM techniques and then incorporated 
-into a combined actuarial neural network, with subsequent contributions in P&C pricing by @schelldorfer2019nesting and 
-in IBNR reserving by @Gabrielli2019c and @Gabrielli2019. Other applications in IBNR reserving are in @Kuo2020 and 
-@Delong2020a who use embedding layers to model individual claims development.
+Many other applications of embeddings have subsequently appeared in the actuarial literature.
+Within mortality forecasting, @Richman2019d and @Richman2020 both apply embeddings layers to model and forecast mortality rates on a large scale.
+@wuthrich2019yes discussed how embeddings can be calibrated using GLM techniques and then incorporated into a combined actuarial neural network, with subsequent contributions in P&C pricing by @schelldorfer2019nesting and in IBNR reserving by @Gabrielli2019c and @Gabrielli2019.
+Other applications in IBNR reserving are in @Kuo2020 and @Delong2020a who use embedding layers to model individual claims development.
 
@@
 
-In this study, we are concerned with regression Modeling, which is the task of predicting an unknown outcome $y$ on the 
-basis of information about that outcome contained in predictor variables, or features, stored in a matrix $X$. For 
-simplicity, we only consider the case of univariate outcomes, i.e., $y \in \mathbb{R}^1$. The outcomes and the rows of 
-the predictor variable matrix are indexed by $i \in \{1 \dots I\}$, where $i$ represents a particular observation of 
-$(y_i, \mathbf{x}_i)$, where bold indicates that we are now dealing with a vector. The columns of the predictor 
-variables are indexed by $j \in \{1 \dots J\}$, where $j$ represents a particular predictor variable, of which $J$ have 
-been observed, thus, we use the notation $X_j$ to represent the $j$th predictor variable and $X \in \mathbb{R}^J$. 
-Formally, we look to build regression models that map from the predictor variables $\mathbf{x}_i$ to the outcome $y$ 
-using a function $f$ of the form:
+In this study, we are concerned with regression Modeling, which is the task of predicting an unknown outcome $y$ on the basis of information about that outcome contained in predictor variables, or features, stored in a matrix $X$.
+For simplicity, we only consider the case of univariate outcomes, i.e., $y \in \mathbb{R}^1$.
+The outcomes and the rows of the predictor variable matrix are indexed by $i \in \{1 \dots I\}$, where $i$ represents a particular observation of $(y_i, \mathbf{x}_i)$, where bold indicates that we are now dealing with a vector.
+The columns of the predictor variables are indexed by $j \in \{1 \dots J\}$, where $j$ represents a particular predictor variable, of which $J$ have been observed, thus, we use the notation $X_j$ to represent the $j$th predictor variable and $X \in \mathbb{R}^J$.
+Formally, we look to build regression models that map from the predictor variables $\mathbf{x}_i$ to the outcome $y$ using a function $f$ of the form:
 
@@
 
-A categorical variable $X_j, j \in J_{cat}$ takes as its value only one of a finite number of labels. Let the set of 
-labels be $\mathcal{P}^j = \{p^j_1, p^j_2,\dots, p^j_{n_{\mathcal{P}^j}} \}$, where $n_\mathcal{P}^j = |\mathcal{P}^j|$ 
-is the cardinality or number of levels, in $\mathcal{P}^j$. One-hot encoding maps each value $x_{i,j}$ of $X_j$ to 
-$n_\mathcal{P}^j$ indicator variables, which take a value of $1$ if the label of $x_{i,j}$ corresponds to the level of 
-the indicator variable, and $0$ otherwise. An example of one-hot encoding is shown in Table \@ref(tab:onehot).
+A categorical variable $X_j, j \in J_{cat}$ takes as its value only one of a finite number of labels.
+Let the set of labels be $\mathcal{P}^j = \{p^j_1, p^j_2,\dots, p^j_{n_{\mathcal{P}^j}} \}$, where $n_\mathcal{P}^j = |\mathcal{P}^j|$ is the cardinality or number of levels, in $\mathcal{P}^j$.
+One-hot encoding maps each value $x_{i,j}$ of $X_j$ to $n_\mathcal{P}^j$ indicator variables, which take a value of $1$ if the label of $x_{i,j}$ corresponds to the level of the indicator variable, and $0$ otherwise.
+An example of one-hot encoding is shown in Table \@ref(tab:onehot).
 
@@
 
-One-hot encoding is often used in the machine learning community while the statistical community often favors dummy 
-coding, which, instead of assigning $n_p^j$ indicator variables, assigns one of the levels of the categories as a 
-baseline, and maps all of the other $n_p^j -1$ variables to indicator variables. An example of dummy encoding is shown 
-in Table \@ref(tab:dummy).
+One-hot encoding is often used in the machine learning community while the statistical community often favors dummy coding, which, instead of assigning $n_p^j$ indicator variables, assigns one of the levels of the categories as a baseline, and maps all of the other $n_p^j -1$ variables to indicator variables.
+An example of dummy encoding is shown in Table \@ref(tab:dummy).
 
@@
 
-After encoding the categorical data in this manner, most regression models such as GLMs will then fit coefficients for 
-each level of the category in the table (if a tree based model is used, such as decision tree, then splits in the tree 
-may occur depending on the presence, or not, of the categorical variable for the data). If one-hot encoding has been 
-used, $n_\mathcal{P}^j$ coefficients will be fit, compared to $n_\mathcal{P}^j - 1$ coefficients in the case of dummy 
-coding.
+After encoding the categorical data in this manner, most regression models such as GLMs will then fit coefficients for each level of the category in the table (if a tree based model is used, such as decision tree, then splits in the tree may occur depending on the presence, or not, of the categorical variable for the data).
+If one-hot encoding has been used, $n_\mathcal{P}^j$ coefficients will be fit, compared to $n_\mathcal{P}^j - 1$ coefficients in the case of dummy coding.
 
-These coefficients represent the effect that each level of the categorical variable will have on the outcome. In the 
-case that there are no other variables available in the dataset, then the coefficients will reflect the average value of 
-the outcomes for that level of the categorical variable. For example, suppose that the categorical variable is a 
-policyholder identifier, and the outcomes are the value of claims in different years, then the coefficients will reflect 
-the average annual claims for each policyholder based on the experience. In other words, both of these encoding schemes 
-give full credibility to the data available for each category, thus, even if a relatively small amount of data is 
-available for a specific policyholder, the coefficient that is calibrated will only reflect that data. On the other 
-hand, a foundational technique within actuarial work is the application of credibility methods, which are used for 
-experience rating and other applications. These techniques provide an estimate that reflects not only the experience of 
-the individual policyholder but also that of the collective, based on an estimate of how credible the data for each 
-individual is. While we have described the application of credibility in a simple univariate context, it is also 
-possible to apply credibility considerations within GLMs. using models known as Generalized Linear Mixed Models or 
-GLMMs, and we refer to @Klinker2010 for more details.
+These coefficients represent the effect that each level of the categorical variable will have on the outcome.
+In the case that there are no other variables available in the dataset, then the coefficients will reflect the average value of the outcomes for that level of the categorical variable.
+For example, suppose that the categorical variable is a policyholder identifier, and the outcomes are the value of claims in different years, then the coefficients will reflect the average annual claims for each policyholder based on the experience.
+In other words, both of these encoding schemes give full credibility to the data available for each category, thus, even if a relatively small amount of data is available for a specific policyholder, the coefficient that is calibrated will only reflect that data.
+On the other hand, a foundational technique within actuarial work is the application of credibility methods, which are used for experience rating and other applications.
+These techniques provide an estimate that reflects not only the experience of the individual policyholder but also that of the collective, based on an estimate of how credible the data for each individual is.
+While we have described the application of credibility in a simple univariate context, it is also possible to apply credibility considerations within GLMs.
+using models known as Generalized Linear Mixed Models or GLMMs, and we refer to @Klinker2010 for more details.
 
-Having described traditional approaches for modeling categorical data, we now turn to neural networks, and discuss 
-embedding layers for categorical data modeling, which we define in more detail in the section on neural networks.
+Having described traditional approaches for modeling categorical data, we now turn to neural networks, and discuss embedding layers for categorical data modeling, which we define in more detail in the section on neural networks.
 
@@
 
-Neural networks are flexible machine learning models that have recently been applied to a number of problems with 
-Property and Casualty (P&C) insurance. Here, we provide a brief overview of these models, and refer the reader to 
-@Richman2018 for a more detailed overview. Neural networks are characterized by multiple layers of non-linear 
-regression functions that are used to learn a new representation of the data input to the network that is then used to 
-make predictions. Here we focus on the most common type of neural networks, which are fully connected networks (FCNs), 
-which provide as the output of each set of non-linear functions to the subsequent layer of functions. Formally, a 
-$K$-layer neural network is:
+Neural networks are flexible machine learning models that have recently been applied to a number of problems with Property and Casualty (P&C) insurance.
+Here, we provide a brief overview of these models, and refer the reader to @Richman2018 for a more detailed overview.
+Neural networks are characterized by multiple layers of non-linear regression functions that are used to learn a new representation of the data input to the network that is then used to make predictions.
+Here we focus on the most common type of neural networks, which are fully connected networks (FCNs), which provide as the output of each set of non-linear functions to the subsequent layer of functions.
+Formally, a $K$-layer neural network is:
 
+```{=tex}
 \begin{equation} 
@@
 \end{equation}
-
-where the regression parameters (weights) for each layer $k \in [1;K+1]$ are represented by the matrices $a_k$ and the 
-intercept terms are represented by $b_k$. Whereas the calculation inside each of the layers is nothing more than linear 
-regression, $\sigma$ represents the non-linear part of each layer. Choices for $\sigma$ are often the hyperbolic tangent 
-(tanh) function or the rectified linear unit (ReLu) $max(0,x)$. The parameters of the network are estimated ('trained') 
-as follows. First a loss function $L(.,.)$ is specified for the network that measures the difference between the observed data $y$ 
-and the predictions of the network $\hat{y}$, for example, the Mean Squared Error ($(y - \hat{y})^2$). Then, the parameters of 
-the network are changed such that the loss decreases (formally, this is done using the technique of backpropagation).
+```
+where the regression parameters (weights) for each layer $k \in [1;K+1]$ are represented by the matrices $a_k$ and the intercept terms are represented by $b_k$.
+Whereas the calculation inside each of the layers is nothing more than linear regression, $\sigma$ represents the non-linear part of each layer.
+Choices for $\sigma$ are often the hyperbolic tangent (tanh) function or the rectified linear unit (ReLu) $max(0,x)$.
+The parameters of the network are estimated ('trained') as follows.
+First a loss function $L(.,.)$ is specified for the network that measures the difference between the observed data $y$ and the predictions of the network $\hat{y}$, for example, the Mean Squared Error ($(y - \hat{y})^2$).
+Then, the parameters of the network are changed such that the loss decreases (formally, this is done using the technique of backpropagation).
 Finally, training is stopped once the predictive performance of the network on unseen data is suitably good.
 
-If $K$ is set equal to $1$, then Equation \ref{NN} reduces to nothing more than a GLM. A neural network with $K=2$ is 
-called a shallow neural network and for $K \geq 2$, the network is called a deep neural network. The matrix $X$ of data 
-input to the network can be composed of both continuous variables as well as categorical variables, which can be 
-pre-processed using one-hot or dummy encoding. As mentioned above, a different option is to use encodings, which we 
-discuss in more detail next.
+If $K$ is set equal to $1$, then Equation \ref{NN} reduces to nothing more than a GLM.
+A neural network with $K=2$ is called a shallow neural network and for $K \geq 2$, the network is called a deep neural network.
+The matrix $X$ of data input to the network can be composed of both continuous variables as well as categorical variables, which can be pre-processed using one-hot or dummy encoding.
+As mentioned above, a different option is to use encodings, which we discuss in more detail next.
 
@@
 
-Common issues with the traditional encoding schemes for categorical data occur when the number of levels for each 
-variable is very large. Often, in these cases, models do not converge quickly, and the very large matrices that result 
-from applying these schemes often cause computational difficulties. Besides for these practical issues, a deeper issue 
-is that one-hot or dummy encoded data assumes that each category is entirely independent of the rest of the categories, 
-in other words, there are no similarities between categories that could enable more robust estimation of models. In 
-technical terms, this is because the columns of the matrices created by one-hot encoding are all orthogonal to each 
-other. (These arguments appear in a similar form in @Guo2016.) Solutions to these problems are provided by embedding 
-layers.
+Common issues with the traditional encoding schemes for categorical data occur when the number of levels for each variable is very large.
+Often, in these cases, models do not converge quickly, and the very large matrices that result from applying these schemes often cause computational difficulties.
+Besides for these practical issues, a deeper issue is that one-hot or dummy encoded data assumes that each category is entirely independent of the rest of the categories, in other words, there are no similarities between categories that could enable more robust estimation of models.
+In technical terms, this is because the columns of the matrices created by one-hot encoding are all orthogonal to each other.
+(These arguments appear in a similar form in @Guo2016.) Solutions to these problems are provided by embedding layers.
 
-An embedding layer is a neural network component which maps each level of the categorical data to a low dimensional 
-vector of parameters that is learned together with the rest of the GLM or neural network that is used for the modeling 
-problem. Formally, an embedding is
+An embedding layer is a neural network component which maps each level of the categorical data to a low dimensional vector of parameters that is learned together with the rest of the GLM or neural network that is used for the modeling problem.
+Formally, an embedding is
 
+```{=tex}
 \begin{equation} 
@@
 \end{equation}
-
-where $q_\mathcal{P}^j$ is the dimension of the embedding for the $j$th categorical variable and $z_\mathcal{P}^j(.)$ is 
-an implicit function that maps from the particular element of the labels $p$ to the embedding space. Equation \ref{embed_map} 
-states that an embedding maps a level of a categorical variable to a numerical vector. This function is left implicit, 
-meaning to say, we allow the embeddings to be derived during the process of fitting the model and do not attempt to 
-specify exactly how the embeddings can be derived from the input data. In Table \@ref(tab:embed) we show an example of two 
-dimensional embeddings for the state variables, where these have been generated randomly.
+```
+where $q_\mathcal{P}^j$ is the dimension of the embedding for the $j$th categorical variable and $z_\mathcal{P}^j(.)$ is an implicit function that maps from the particular element of the labels $p$ to the embedding space.
+Equation \ref{embed_map} states that an embedding maps a level of a categorical variable to a numerical vector.
+This function is left implicit, meaning to say, we allow the embeddings to be derived during the process of fitting the model and do not attempt to specify exactly how the embeddings can be derived from the input data.
+In Table \@ref(tab:embed) we show an example of two dimensional embeddings for the state variables, where these have been generated randomly.
 
@@
 
-Attention mechanisms have been widely applied within the deep learning literature to give more flexibility to RNNs [@Bahdanau2015a] 
-and subsequently as a replacement for FCNs in the so-called Transformer architecture, which is now widely used in natural language processing [@Vaswani2017a], 
-and, more recently, has been applied to computer vision and tabular Modeling tasks. 
-Attention mechanisms allow deep neural nets to weight the covariates entering the model in a flexible manner; these types of applications in natural language 
-processing are demonstrated in,
-for example, @Vaswani2017a. In an actuarial context, attention mechanisms can be understood as giving greater weight to covariates that are important for the Modeling task. 
+Attention mechanisms have been widely applied within the deep learning literature to give more flexibility to RNNs [@Bahdanau2015a] and subsequently as a replacement for FCNs in the so-called Transformer architecture, which is now widely used in natural language processing [@Vaswani2017a], and, more recently, has been applied to computer vision and tabular Modeling tasks.
+Attention mechanisms allow deep neural nets to weight the covariates entering the model in a flexible manner; these types of applications in natural language processing are demonstrated in, for example, @Vaswani2017a.
+In an actuarial context, attention mechanisms can be understood as giving greater weight to covariates that are important for the Modeling task.
 In this section we provide a theoretical introduction to attention mechanisms and then discuss applications of attention to modeling tabular data.
@@
 
-At a high level, attention mechanisms reweight the covariates $X$ within a predictive model to give greater weight to covariates that are more
-predictive for a particular problem. The attention weights can be derived in several different manners. Earlier works, such as @Bahdanau2015a
-used so-called "additive" attention scores derived as the output of a neural network taking the covariates as inputs. Currently, the most popular
-form of attention is the "scaled dot-product" attention of @Vaswani2017a which we describe in what follows. We also mention that usually, so-called
-"self-attention" is applied, meaning to say that the importance scores for the covariates are derived using the covariates themselves (i.e. in what follows,
-the attention scores are derived in Equation \ref{eq:attention_scores} using the transformed covariates). Other options, such as using a different source of
-data to derive the attention scores, are also possible.
+At a high level, attention mechanisms reweight the covariates $X$ within a predictive model to give greater weight to covariates that are more predictive for a particular problem.
+The attention weights can be derived in several different manners.
+Earlier works, such as @Bahdanau2015a used so-called "additive" attention scores derived as the output of a neural network taking the covariates as inputs.
+Currently, the most popular form of attention is the "scaled dot-product" attention of @Vaswani2017a which we describe in what follows.
+We also mention that usually, so-called "self-attention" is applied, meaning to say that the importance scores for the covariates are derived using the covariates themselves (i.e.
+in what follows, the attention scores are derived in Equation \ref{eq:attention_scores} using the transformed covariates).
+Other options, such as using a different source of data to derive the attention scores, are also possible.
 
@@
 ```
-where $Q \in \mathbb{R}^{q \times d}$ is a matrix of query vectors, $K \in \mathbb{R}^{q \times d}$ is a matrix of key vectors,
- $X' \in \mathbb{R}^{q \times d}$ is a matrix of value vectors and $X^* \in \mathbb{R}^{q \times d}$, 
- the output of the attention mechanism, is a new matrix of values that have been reweighted according to their importance for the Modeling problem. 
- As noted above, several different options for the mapping in Equation \ref{eq:attention} exist in the literature; here we describe the scaled dot-product self-attention mechanism 
- used in @Vaswani2017a. In more detail, consider that $X'$ is a matrix of covariates relating to a regression problem, which, 
- in the case of tabular data, will usually be composed of embeddings of the same dimension for several different categorical or numerical variables.
- In the case discussed here we have $q$ covariates mapped to embeddings of dimension $d$. For clarity, note that in Equation \ref{eq:embed_to_nn} 
- we have used the symbol $X'$ to denote the vector of embeddings and numerical inputs which is passed into the neural network. 
+where $Q \in \mathbb{R}^{q \times d}$ is a matrix of query vectors, $K \in \mathbb{R}^{q \times d}$ is a matrix of key vectors, $X' \in \mathbb{R}^{q \times d}$ is a matrix of value vectors and $X^* \in \mathbb{R}^{q \times d}$, the output of the attention mechanism, is a new matrix of values that have been reweighted according to their importance for the Modeling problem.
+As noted above, several different options for the mapping in Equation \ref{eq:attention} exist in the literature; here we describe the scaled dot-product self-attention mechanism used in @Vaswani2017a.
+In more detail, consider that $X'$ is a matrix of covariates relating to a regression problem, which, in the case of tabular data, will usually be composed of embeddings of the same dimension for several different categorical or numerical variables.
+In the case discussed here we have $q$ covariates mapped to embeddings of dimension $d$.
+For clarity, note that in Equation \ref{eq:embed_to_nn} we have used the symbol $X'$ to denote the vector of embeddings and numerical inputs which is passed into the neural network.
 We slightly overload this notation and, in what follows, we now use the symbol $X'$ to refer to the matrix of embeddings of dimension $q \times d$.
 
-We wish to apply the attention mechanism to $X'$ to assign weights to the most important embeddings for the regression problem; 
-this is done from the "perspective" of each covariate represented by the $q$ rows of $X'$. To do this, we formulate a so-called query matrix $Q$ 
-which contains information about the regression problem at hand; this is usually done by passing $X'$ through a neural network trained to derive 
-queries from the covariates. Similarly, the matrix $K$ contains the relevance of each row of $X'$ for the regression problem and 
-is also usually derived by passing each row of $X'$ through another neural network. Finally, the matrix $X'$ can be left as is, or processed through another neural network. 
+We wish to apply the attention mechanism to $X'$ to assign weights to the most important embeddings for the regression problem; this is done from the "perspective" of each covariate represented by the $q$ rows of $X'$.
+To do this, we formulate a so-called query matrix $Q$ which contains information about the regression problem at hand; this is usually done by passing $X'$ through a neural network trained to derive queries from the covariates.
+Similarly, the matrix $K$ contains the relevance of each row of $X'$ for the regression problem and is also usually derived by passing each row of $X'$ through another neural network.
+Finally, the matrix $X'$ can be left as is, or processed through another neural network.
 The first step of the attention mechanism is to derive a matrix $A \in \mathbb{R}^{q \times q}$ of attention scores:
@@
 ```
-
-and where the division by $\sqrt{d}$ is done element-wise. The attention scores $A$ are then normalized, or made to sum to unity, 
-across the columns of $A$ using a so-called softmax function i.e.
+and where the division by $\sqrt{d}$ is done element-wise. The attention scores $A$ are then normalized, or made to sum to unity, across the columns of $A$ using a so-called softmax function i.e.
 
@@
 
-An intuitive explanation of the attention formula is as follows: we start by considering the importance of all of the covariates 
-that we have for our Modeling problem in the context of each individual covariate. This is done by assigning a score between zero
-and one to each covariate in the Modeling problem, and we repeat this process for each of the covariates. Then, we replace each 
-of the original covariates with a new covariate that has been formed by taking a weighted average of the covariates and the scores.
+An intuitive explanation of the attention formula is as follows: we start by considering the importance of all of the covariates that we have for our Modeling problem in the context of each individual covariate.
+This is done by assigning a score between zero and one to each covariate in the Modeling problem, and we repeat this process for each of the covariates.
+Then, we replace each of the original covariates with a new covariate that has been formed by taking a weighted average of the covariates and the scores.
 
@@
 These two matrices, the input matrix $X'$ and the output matrix $X^*$ are added (in an element-wise manner) together and then normalized.
-This matrix is then further processed through a neural network and subsequently, these processed covariates are used in the machine learning task. These stages of the 
-Transformer model help to make the optimization of the network easier than applying scaled self-attention directly to the matrix of covariates $X'$.
+This matrix is then further processed through a neural network and subsequently, these processed covariates are used in the machine learning task.
+These stages of the Transformer model help to make the optimization of the network easier than applying scaled self-attention directly to the matrix of covariates $X'$.
 
@@
 
-The Transformer model is much more accurate on NLP tasks compared to using the raw covariates before processing with a Transformer, to the extent that 
-this model now underlies most NLP applications that use deep learning.
+The Transformer model is much more accurate on NLP tasks compared to using the raw covariates before processing with a Transformer, to the extent that this model now underlies most NLP applications that use deep learning.
 
@@
 
-Several different approaches to applying attention within the Modeling of tabular data have been proposed in the literature. Perhaps the simplest way of doing 
-this is to insert an attention layer between the embeddings and the rest of the neural network. Mathematically, we can modify Equation \ref{eq:embed_to_nn} as follows:
+Several different approaches to applying attention within the Modeling of tabular data have been proposed in the literature.
+Perhaps the simplest way of doing this is to insert an attention layer between the embeddings and the rest of the neural network.
+Mathematically, we can modify Equation \ref{eq:embed_to_nn} as follows:
 
@@
 ```
-where $X' \in \mathbb{R}^{q \times d}$ is the matrix of embeddings after concatenating $q$ embeddings of dimension $d$ together, $X^*$ 
-represents the matrix of embeddings $X'$ after processing with attention and $A$ is the attention function defined in Equations \ref{eq:attention} - \ref{eq:attention_output}. 
+where $X' \in \mathbb{R}^{q \times d}$ is the matrix of embeddings after concatenating $q$ embeddings of dimension $d$ together, $X^*$ represents the matrix of embeddings $X'$ after processing with attention and $A$ is the attention function defined in Equations \ref{eq:attention} - \ref{eq:attention_output}.
 Below, we demonstrate the effect of adding this simple application of attention to a tabular model.
@@
 @Huang2020 refines this approach in a model they call the TabTransformer, which implements two main changes to the approach shown in Equations \ref{eq:embed_to_attn_to_nn}.
-The first of these is that, instead of using the matrix of embeddings after processing with self-attention ($X'$) directly in the model, 
-the output of a Transformer model is used instead. The second of these refinements is that for each of the $q$ covariates with an embedding in the matrix $X'$, 
-we include a new row embedding which denotes which covariate each embedding relates to. Thus, in the TabTransformer model, we augment 
-the embedding matrix with extra columns, so that the dimension of this matrix is $q \times (d + d_{col})$, where $d_{col}$ is the dimension of the row embedding.
-@Huang2020 find that including this identifier improves the performance of the model. We compare the results of the TabTransformer model to the other models tested below.
+The first of these is that, instead of using the matrix of embeddings after processing with self-attention ($X'$) directly in the model, the output of a Transformer model is used instead.
+The second of these refinements is that for each of the $q$ covariates with an embedding in the matrix $X'$, we include a new row embedding which denotes which covariate each embedding relates to.
+Thus, in the TabTransformer model, we augment the embedding matrix with extra columns, so that the dimension of this matrix is $q \times (d + d_{col})$, where $d_{col}$ is the dimension of the row embedding.
+@Huang2020 find that including this identifier improves the performance of the model.
+We compare the results of the TabTransformer model to the other models tested below.
 
@@
 In summary, the main idea of the TabNet model is to try emulate the excellent performance of decision trees on tabular data Modeling using deep neural networks.
-This is done by structuring the neural networks to emulate a key aspect of decision tree Modeling, which is the efficient selection of relevant covariates
-for the model task. Within TabNet, an attention based model is used to select features by estimating attention scores for each covariate within $X$. 
-The covariates are multiplied by the attention scores to down-weight less relevant features for the prediction problem. Other less important details of the TabNet
-model are given in @Ark2019.
+This is done by structuring the neural networks to emulate a key aspect of decision tree Modeling, which is the efficient selection of relevant covariates for the model task.
+Within TabNet, an attention based model is used to select features by estimating attention scores for each covariate within $X$.
+The covariates are multiplied by the attention scores to down-weight less relevant features for the prediction problem.
+Other less important details of the TabNet model are given in @Ark2019.
 
@@
 
-In this section, we walk through a simple predictive modeling exercise in order to illustrate the application of 
-embeddings. First, we pose a supervised regression problem, based on flood insurance claims severity. We then develop 
-GLMs and neural networks utilizing embeddings for this problem, and inspect the trained parameters. Finally, we
-provide details of model optimization, inference, and performance.
+In this section, we walk through a simple predictive modeling exercise in order to illustrate the application of embeddings.
+First, we pose a supervised regression problem, based on flood insurance claims severity.
+We then develop GLMs and neural networks utilizing embeddings for this problem, and inspect the trained parameters.
+Finally, we provide details of model optimization, inference, and performance.
 
@@
 
-The working example for our experiments is as follows: Given a set of claim characteristics, we predict the losses paid 
-on the property coverage of the policy. The data we use comes from the National Flood Insurance Program (NFIP) and is 
-made available by the OpenFEMA initiative 
-of the Federal Emergency Management Agency (FEMA)[^9]. Two datasets are made available by OpenFEMA: A policies dataset 
-with exposure information, and a claims dataset with claims transactions, including paid amounts. Because there is no 
-way to associate records of the two datasets, we are limited to fitting severity models on the claims dataset. While 
-the 
-complete dataset contains over two million transactions, for the purposes of our experiments, we limit ourselves to 
-data from 2000 to August 2019 and further subsample 100K data points to make experiments feasible on a CPU.
-The dataset includes a rich variety of variables, from occupancy type to flood zone. For our 
-models, 
-we work with a few selected variables that represent continuous and discrete variables of low and high cardinalities, 
-which we list in Table \@ref(tab:variables)
+The working example for our experiments is as follows: Given a set of claim characteristics, we predict the losses paid on the property coverage of the policy.
+The data we use comes from the National Flood Insurance Program (NFIP) and is made available by the OpenFEMA initiative of the Federal Emergency Management Agency (FEMA)[^1].
+Two datasets are made available by OpenFEMA: A policies dataset with exposure information, and a claims dataset with claims transactions, including paid amounts.
+Because there is no way to associate records of the two datasets, we are limited to fitting severity models on the claims dataset.
+While the complete dataset contains over two million transactions, for the purposes of our experiments, we limit ourselves to data from 2000 to August 2019 and further subsample 100K data points to make experiments feasible on a CPU.
+The dataset includes a rich variety of variables, from occupancy type to flood zone.
+For our models, we work with a few selected variables that represent continuous and discrete variables of low and high cardinalities, which we list in Table \@ref(tab:variables)
 
-[^9]: https://www.fema.gov/about/reports-and-data/openfema
+[^1]: <https://www.fema.gov/about/reports-and-data/openfema>
 
@@
 
-For our experiments, we set up a 5-fold cross validation scheme that is applied to each of the models
-we introduce. In Sections \ref{models} and \ref{interpretation}, the tables and figures are based on a single fold of 
-the cross validation split. In Section \ref{training-inference}, we provide the cross-validated performance
-metrics of each of the models.
+For our experiments, we set up a 5-fold cross validation scheme that is applied to each of the models we introduce.
+In Sections \ref{models} and \ref{interpretation}, the tables and figures are based on a single fold of the cross validation split.
+In Section \ref{training-inference}, we provide the cross-validated performance metrics of each of the models.
 
-We note that the focus of our contribution is on applications of categorical embeddings in predictive modeling, 
-rather than
-on fine-tuning models in order to beat or establish a benchmark. To this end, we do not perform systematic
-hyperparameter tuning in our experiments, and the performance metrics are provided to show that reasonable
-models utilizing categorical embeddings. However, as we describe the modeling procedure and results, we provide
-commentary on recommended practices in practical applications, especially with respect to the neural network models.
+We note that the focus of our contribution is on applications of categorical embeddings in predictive modeling, rather than on fine-tuning models in order to beat or establish a benchmark.
+To this end, we do not perform systematic hyperparameter tuning in our experiments, and the performance metrics are provided to show that reasonable models utilizing categorical embeddings.
+However, as we describe the modeling procedure and results, we provide commentary on recommended practices in practical applications, especially with respect to the neural network models.
 
@@
 
-These model architectures are relatively uncomplicated by today's standards, and are so chosen to better highlight the
-embedding components. Later, in Section \ref{attention_models}, we will investigate more involved architectures utilizing embeddings
-that represent the state of the art for modeling tabular data.
+These model architectures are relatively uncomplicated by today's standards, and are so chosen to better highlight the embedding components.
+Later, in Section \ref{attention_models}, we will investigate more involved architectures utilizing embeddings that represent the state of the art for modeling tabular data.
 
@@
 
-While this paper focuses on embeddings in neural networks, we begin with a GLM to provide a common frame of 
-reference, since most actuaries are familiar with the technique. 
-Although GLMs are commonplace and well-studied in the actuarial literature, there are still plenty of decisions to 
-be made in the modeling process; see, for example, @Goldburd for an in-depth discussion. For our purpose of 
-establishing a baseline, we proceed with what we perceive as reasonable decisions around feature engineering and model structure, outlined below:
+While this paper focuses on embeddings in neural networks, we begin with a GLM to provide a common frame of reference, since most actuaries are familiar with the technique.
+Although GLMs are commonplace and well-studied in the actuarial literature, there are still plenty of decisions to be made in the modeling process; see, for example, @Goldburd for an in-depth discussion.
+For our purpose of establishing a baseline, we proceed with what we perceive as reasonable decisions around feature engineering and model structure, outlined below:
 
 -   Target variable: Amount paid on building claim
+
 -   Predictors:
+
     -   $\log$ `building_insurance_coverage`
@@
     -   `primary_residence`
+
 -   Link function: $\log$
+
 -   Distribution: gamma
 
-We take the log of the continuous predictor `building_insurance_coverage`, which allows the scale of the predictor to 
-match that of the target variable. Because the `flood_zone` variable in the original data contains 60 levels, we take 
-the prefix of the zone code, which corresponds to the level of risk as determined by FEMA [^8]. For example, `"A01"`, 
-`"A02"`, and so on are recoded as simply `"A"`. A log link together with the gamma distribution is a standard choice 
-for severity modeling, which provides a multiplicative structure where the response is positive. Following the notation
-in \@ref(catdata), the number of parameters in the GLM is
+We take the log of the continuous predictor `building_insurance_coverage`, which allows the scale of the predictor to match that of the target variable.
+Because the `flood_zone` variable in the original data contains 60 levels, we take the prefix of the zone code, which corresponds to the level of risk as determined by FEMA [^2].
+For example, `"A01"`, `"A02"`, and so on are recoded as simply `"A"`.
+A log link together with the gamma distribution is a standard choice for severity modeling, which provides a multiplicative structure where the response is positive.
+Following the notation in \@ref(catdata), the number of parameters in the GLM is
 
+[^2]: <https://www.floodsmart.gov/flood-map-zone/find-yours>
+
+```{=tex}
 \begin{equation}
@@
 \end{equation}
+```
+one for the intercept, one for each numeric variable, and the numbers of levels minus one (due to dummy coding) for each categorical variable.
 
-one for the intercept, one for each numeric variable, and the numbers of levels minus one (due to dummy coding) for 
-each categorical variable.
+In Table \@ref(tab:relativities), we exhibit an exerpt of the relativities, or exponentiated fitted coefficients, of a couple categorical variables.
+Recall that the choice of the log link gives a multiplicative structure, so the interpretation of 1.34 for `occupancy_type = "Non-residential building"` is that, all else equal, the expected loss for a policy for a non-residential building is 1.34 times that of a policy for a single family home, which is the base, or reference, level for the factor.
 
-[^8]: https://www.floodsmart.gov/flood-map-zone/find-yours
+| variable       | label                                       | relativity |
+|:---------------|:--------------------------------------------|-----------:|
+| occupancy_type | Single family residence                     |       1.00 |
+| occupancy_type | 2 to 4 unit residential buidling            |       1.10 |
+| occupancy_type | Non-residential building                    |       1.34 |
+| occupancy_type | Residential building with more than 4 units |       1.59 |
+| flood_zone     | C                                           |       1.00 |
+| flood_zone     | A                                           |       1.42 |
+| flood_zone     | X                                           |       1.18 |
+| flood_zone     | B                                           |       1.65 |
+| flood_zone     | V                                           |       1.38 |
+| flood_zone     | D                                           |       1.45 |
 
-In Table \@ref(tab:relativities), we exhibit an exerpt of the relativities, or exponentiated fitted coefficients, 
-of a couple categorical variables. Recall that the choice of the log link gives a multiplicative structure, so the
-interpretation of 1.34 for `occupancy_type = "Non-residential building"` is that, all else equal, the expected 
-loss for
-a policy for a non-residential building is 1.34 times that of a policy for a single family home, which is the base,
-or reference, level for the factor.
-
-Table: (\#tab:relativities) Excerpt of relativities for Model 1.
-
-|variable       |label                                       | relativity|
-|:--------------|:-------------------------------------------|----------:|
-|occupancy_type |Single family residence                     |       1.00|
-|occupancy_type |2 to 4 unit residential buidling            |       1.10|
-|occupancy_type |Non-residential building                    |       1.34|
-|occupancy_type |Residential building with more than 4 units |       1.59|
-|flood_zone     |C                                           |       1.00|
-|flood_zone     |A                                           |       1.42|
-|flood_zone     |X                                           |       1.18|
-|flood_zone     |B                                           |       1.65|
-|flood_zone     |V                                           |       1.38|
-|flood_zone     |D                                           |       1.45|
+: (\#tab:relativities) Excerpt of relativities for Model 1.
 
@@
 For Model 2, we build a feedforward neural network, whose architecture is shown in Figure \@ref(fig:nn-1).
-The categorical inputs go through one-dimensional embedding
-layers where they are each mapped to a scalar. The embeddings are then concatenated with the numeric predictors, which
-have been normalized in data pre-processing, before being passed through a feedforward layer (with 8 hidden units 
-and ReLU activation)
- to obtain a scalar
-value between 0 and 1, as constrained by a sigmoid output activation. This scalar output represents the proportion of
-coverage amount that is paid out, which we then multiply by the dollar amount of the coverage amount to obtain
-our prediction of the claims paid. For optimization, we use the mean squared error (MSE) loss function.
+The categorical inputs go through one-dimensional embedding layers where they are each mapped to a scalar.
+The embeddings are then concatenated with the numeric predictors, which have been normalized in data pre-processing, before being passed through a feedforward layer (with 8 hidden units and ReLU activation) to obtain a scalar value between 0 and 1, as constrained by a sigmoid output activation.
+This scalar output represents the proportion of coverage amount that is paid out, which we then multiply by the dollar amount of the coverage amount to obtain our prediction of the claims paid.
+For optimization, we use the mean squared error (MSE) loss function.
 
@@
 
-With a single hidden layer, this architecture is relatively simple; without the hidden layer and
-corresponding ReLU activation, we would actually recover a logistic regression structure. 
-The choice of one for the embedding dimension is also due to simplicity: it is easily interpretable as the 
-representation
-of each factor level as a point on the real number line; also, the trained embeddings are easily incorporated into a GLM
-which we will see in Model 3. In practice, the embedding dimension is a hyperparameter one can tune, for example via
-cross validation, and can vary for each variable. However, we also note that the choice of one for the 
-embedding output dimension is not an unreasonable one, especially when the cardinalities of the categorical variables
-are not large (i.e., when they are in the 10s).
+With a single hidden layer, this architecture is relatively simple; without the hidden layer and corresponding ReLU activation, we would actually recover a logistic regression structure.
+The choice of one for the embedding dimension is also due to simplicity: it is easily interpretable as the representation of each factor level as a point on the real number line; also, the trained embeddings are easily incorporated into a GLM which we will see in Model 3.
+In practice, the embedding dimension is a hyperparameter one can tune, for example via cross validation, and can vary for each variable.
+However, we also note that the choice of one for the embedding output dimension is not an unreasonable one, especially when the cardinalities of the categorical variables are not large (i.e., when they are in the 10s).
 
-In Tables \@ref(tab:embeddings-occupancy-type) and \@ref(tab:embeddings-flood-zone), we show the learned embeddings
-for `occupancy_type` and an excerpt of them for `flood_zone`. While it may be tempting to compare these values
-to those in Table \@ref(tab:relativities), they represent fundamentally different concepts. It is helpful to think
-of the embedding values for each variable as a continuous represention of the variable itself, rather than a 
-"coefficient" associated with the variable. Note that it is not straightforward to inspect the embeddings from a
-table and infer relationships to the response variable, even in a shallow network such as ours, due to nonlinearities
-within the model. Also note that we now have a way to incorporate the full granularity of the `flood_zone` variable,
-which is why more levels are shown in Table \@ref(tab:embeddings-flood-zone) as compared to Table 
-\@ref(tab:relativities). In Section \ref{interpretation}, we will discuss techniques to visualize these embeddings.
+In Tables \@ref(tab:embeddings-occupancy-type) and \@ref(tab:embeddings-flood-zone), we show the learned embeddings for `occupancy_type` and an excerpt of them for `flood_zone`.
+While it may be tempting to compare these values to those in Table \@ref(tab:relativities), they represent fundamentally different concepts.
+It is helpful to think of the embedding values for each variable as a continuous represention of the variable itself, rather than a "coefficient" associated with the variable.
+Note that it is not straightforward to inspect the embeddings from a table and infer relationships to the response variable, even in a shallow network such as ours, due to nonlinearities within the model.
+Also note that we now have a way to incorporate the full granularity of the `flood_zone` variable, which is why more levels are shown in Table \@ref(tab:embeddings-flood-zone) as compared to Table \@ref(tab:relativities).
+In Section \ref{interpretation}, we will discuss techniques to visualize these embeddings.
 
-Table: (\#tab:embeddings-occupancy-type) Learned embeddings for `occupancy_type` in Model 2.
+| level                                       | embedding |
+|:--------------------------------------------|----------:|
+| 2 to 4 unit residential buidling            |      1.46 |
+| Non-residential building                    |     -1.04 |
+| Residential building with more than 4 units |      0.12 |
+| Single family residence                     |      0.36 |
 
-|level                                       | embedding|
-|:-------------------------------------------|---------:|
-|2 to 4 unit residential buidling            |      1.46|
-|Non-residential building                    |     -1.04|
-|Residential building with more than 4 units |      0.12|
-|Single family residence                     |      0.36|
+: (\#tab:embeddings-occupancy-type) Learned embeddings for `occupancy_type` in Model 2.
 
-Table: (\#tab:embeddings-flood-zone) Excerpt of learned embeddings for `flood_zone` in Model 2.
+| level | embedding | level | embedding | level | embedding | level | embedding | level | embedding |
+|:------|----------:|:------|----------:|:------|----------:|:------|----------:|:------|----------:|
+| A     |      1.48 | A09   |     -0.48 | A18   |      0.39 | A28   |      1.19 | C     |      1.73 |
+| A00   |     -1.05 | A0B   |      1.47 | A19   |     -1.06 | A30   |     -0.01 | D     |     -1.15 |
+| A01   |     -0.18 | A10   |     -0.25 | A20   |     -1.01 | A99   |     -0.44 | V     |     -1.85 |
+| A02   |     -0.06 | A11   |      0.35 | A21   |      2.08 | AE    |      1.12 | V01   |      0.02 |
+| A03   |     -0.01 | A12   |     -0.38 | A22   |     -0.15 | AH    |      2.19 | V02   |     -1.55 |
+| A04   |      0.05 | A13   |      2.81 | A23   |     -0.76 | AHB   |     -0.68 | V03   |     -0.98 |
+| A05   |      1.30 | A14   |      0.58 | A24   |     -0.87 | AO    |      0.55 | V04   |      1.73 |
+| A06   |     -0.76 | A15   |     -0.91 | A25   |      0.02 | AOB   |      0.08 | V05   |     -1.97 |
+| A07   |     -0.62 | A16   |      0.79 | A26   |      0.00 | AR    |      2.93 | V06   |      0.43 |
+| A08   |     -0.53 | A17   |      1.35 | A27   |      0.80 | B     |      0.33 | V07   |      1.91 |
 
-|level | embedding|level | embedding|level | embedding|level | embedding|level | embedding|
-|:-----|---------:|:-----|---------:|:-----|---------:|:-----|---------:|:-----|---------:|
-|A     |      1.48|A09   |     -0.48|A18   |      0.39|A28   |      1.19|C     |      1.73|
-|A00   |     -1.05|A0B   |      1.47|A19   |     -1.06|A30   |     -0.01|D     |     -1.15|
-|A01   |     -0.18|A10   |     -0.25|A20   |     -1.01|A99   |     -0.44|V     |     -1.85|
-|A02   |     -0.06|A11   |      0.35|A21   |      2.08|AE    |      1.12|V01   |      0.02|
-|A03   |     -0.01|A12   |     -0.38|A22   |     -0.15|AH    |      2.19|V02   |     -1.55|
-|A04   |      0.05|A13   |      2.81|A23   |     -0.76|AHB   |     -0.68|V03   |     -0.98|
-|A05   |      1.30|A14   |      0.58|A24   |     -0.87|AO    |      0.55|V04   |      1.73|
-|A06   |     -0.76|A15   |     -0.91|A25   |      0.02|AOB   |      0.08|V05   |     -1.97|
-|A07   |     -0.62|A16   |      0.79|A26   |      0.00|AR    |      2.93|V06   |      0.43|
-|A08   |     -0.53|A17   |      1.35|A27   |      0.80|B     |      0.33|V07   |      1.91||
+: (\#tab:embeddings-flood-zone) Excerpt of learned embeddings for `flood_zone` in Model 2.
 
@@
 
-For Model 3, we return to the GLM, but now we replace the categorical variables with the trained embeddings from Model
-2. In other words, our model now contains only continuous variables, and each categorical factor is represented as a
-scalar value and obtains its own coefficient. In contrast with the number of parameters computed in Equation
-\@ref(eq:glm1), we have fewer parameters for this model:
+For Model 3, we return to the GLM, but now we replace the categorical variables with the trained embeddings from Model 2.
+In other words, our model now contains only continuous variables, and each categorical factor is represented as a scalar value and obtains its own coefficient.
+In contrast with the number of parameters computed in Equation \@ref(eq:glm1), we have fewer parameters for this model:
 
+```{=tex}
 \begin{equation}
@@
 (\#eq:glm2)
-\end{equation}
-
+\end{equation}```
 Hence, the model can be written as
@@
 
+```{=tex}
 \begin{equation}
@@
 \end{equation}
-
+```
 where $z_{i,j}$ represents the embedding value for $i$th instance of the categorical column $X_j$.
 
-Although, in this particular example, we incorporate one-dimensional embeddings, one can easily include multidimensional
-embeddings, which would increase the model's flexibility. The modeler would need to balance the potential 
-additional lift with overfitting and
-some loss of interpretability, since, with one-dimensional embeddings, our GLM structure dictates that there is a 
-monotonic relationship between the predicted response and the input embedding, which could be desirable in certain
-use cases (and undesirable in others.)
+Although, in this particular example, we incorporate one-dimensional embeddings, one can easily include multidimensional embeddings, which would increase the model's flexibility.
+The modeler would need to balance the potential additional lift with overfitting and some loss of interpretability, since, with one-dimensional embeddings, our GLM structure dictates that there is a monotonic relationship between the predicted response and the input embedding, which could be desirable in certain use cases (and undesirable in others.)
 
-Since we only have a few parameters in this model, we exhibit the full list of fitted coefficients in Table 
-\@ref(tab:glm2).
+Since we only have a few parameters in this model, we exhibit the full list of fitted coefficients in Table \@ref(tab:glm2).
 
-Table: (\#tab:glm2) Fitted coefficients of Model 3.
+| term                                     | estimate |
+|:-----------------------------------------|---------:|
+| (Intercept)                              |    3.371 |
+| total_building_insurance_coverage        |    0.586 |
+| basement_enclosure_crawlspace_type       |    0.597 |
+| number_of_floors_in_the_insured_building |   -0.278 |
+| occupancy_type                           |   -0.075 |
+| flood_zone                               |   -0.007 |
+| primary_residence                        |   -0.062 |
+| community_rating_system_discount         |    0.706 |
 
-|term                                     | estimate|
-|:----------------------------------------|--------:|
-|(Intercept)                              |    3.371|
-|total_building_insurance_coverage        |    0.586|
-|basement_enclosure_crawlspace_type       |    0.597|
-|number_of_floors_in_the_insured_building |   -0.278|
-|occupancy_type                           |   -0.075|
-|flood_zone                               |   -0.007|
-|primary_residence                        |   -0.062|
-|community_rating_system_discount         |    0.706|
+: (\#tab:glm2) Fitted coefficients of Model 3.
 
@@
 
-Model 4 is architecturally identical to Model 2, with the only difference being the number of embedding dimensions:
-instead of mapping factor levels to real numbers, we map them to points in Euclidean space, where the dimension of the 
-space is the ceiling
-of the factor's cardinality divided by two. Formally, in the notation of Section \ref{catdata},
-$q_{\mathcal{P}^j}=\ceil{n^j_{\mathcal{P}}/2}$ for variable $X_j$. Following the discussion thus far, we list the
- learned embeddings for a couple variables in Tables \@ref(tab:nn2-occupancy-type) and 
-\@ref(tab:nn2-flood-zone). Note that, for `flood_zone`, we are
-only displaying the embedding for *one* level.
+Model 4 is architecturally identical to Model 2, with the only difference being the number of embedding dimensions: instead of mapping factor levels to real numbers, we map them to points in Euclidean space, where the dimension of the space is the ceiling of the factor's cardinality divided by two.
+Formally, in the notation of Section \ref{catdata}, $q_{\mathcal{P}^j}=\ceil{n^j_{\mathcal{P}}/2}$ for variable $X_j$.
+Following the discussion thus far, we list the learned embeddings for a couple variables in Tables \@ref(tab:nn2-occupancy-type) and \@ref(tab:nn2-flood-zone).
+Note that, for `flood_zone`, we are only displaying the embedding for *one* level.
 
-Table: (\#tab:nn2-occupancy-type) Learned embeddings for `occupancy_type` in Model 4.
+| level                                       |    e1 |    e2 |    e3 |
+|:--------------------------------------------|------:|------:|------:|
+| 2 to 4 unit residential buidling            |  0.37 | -1.76 |  1.36 |
+| Non-residential building                    |  0.13 |  1.47 |  1.77 |
+| Residential building with more than 4 units | -1.12 | -0.15 | -1.43 |
+| Single family residence                     |  0.85 |  0.16 | -0.99 |
 
-|level                                       |    e1|    e2|    e3|
-|:-------------------------------------------|-----:|-----:|-----:|
-|2 to 4 unit residential buidling            |  0.37| -1.76|  1.36|
-|Non-residential building                    |  0.13|  1.47|  1.77|
-|Residential building with more than 4 units | -1.12| -0.15| -1.43|
-|Single family residence                     |  0.85|  0.16| -0.99|
+: (\#tab:nn2-occupancy-type) Learned embeddings for `occupancy_type` in Model 4.
 
-Table: (\#tab:nn2-flood-zone) Learned embeddings for level `"A00"` of variable `flood_zone` in Model 4.
+| dimension | value  | dimension | value  | dimension | value  | dimension | value  |
+|:----------|:-------|:----------|:-------|:----------|:-------|:----------|:-------|
+| e1        | -0.167 | e11       | -0.810 | e21       | -0.300 | e31       | -0.421 |
+| e2        | -0.363 | e12       | 1.380  | e22       | -0.194 | e32       | 0.594  |
+| e3        | -0.893 | e13       | -0.180 | e23       | -0.320 | e33       | 1.681  |
+| e4        | 0.130  | e14       | -1.612 | e24       | -0.035 | e34       | 1.668  |
+| e5        | -1.588 | e15       | -1.327 | e25       | -1.128 |           |        |
+| e6        | -0.123 | e16       | -0.965 | e26       | 0.168  |           |        |
+| e7        | -0.259 | e17       | -1.356 | e27       | -1.022 |           |        |
+| e8        | 0.324  | e18       | -0.061 | e28       | 1.011  |           |        |
+| e9        | -1.430 | e19       | -0.120 | e29       | -0.843 |           |        |
+| e10       | -1.598 | e20       | -0.488 | e30       | -0.743 |           |        |
 
-|dimension |value  |dimension |value  |dimension |value  |dimension |value  |
-|:---------|:------|:---------|:------|:---------|:------|:---------|:------|
-|e1        |-0.167 |e11       |-0.810 |e21       |-0.300 |e31       |-0.421 |
-|e2        |-0.363 |e12       |1.380  |e22       |-0.194 |e32       |0.594  |
-|e3        |-0.893 |e13       |-0.180 |e23       |-0.320 |e33       |1.681  |
-|e4        |0.130  |e14       |-1.612 |e24       |-0.035 |e34       |1.668  |
-|e5        |-1.588 |e15       |-1.327 |e25       |-1.128 |          |       |
-|e6        |-0.123 |e16       |-0.965 |e26       |0.168  |          |       |
-|e7        |-0.259 |e17       |-1.356 |e27       |-1.022 |          |       |
-|e8        |0.324  |e18       |-0.061 |e28       |1.011  |          |       |
-|e9        |-1.430 |e19       |-0.120 |e29       |-0.843 |          |       |
-|e10       |-1.598 |e20       |-0.488 |e30       |-0.743 |          |       |
+: (\#tab:nn2-flood-zone) Learned embeddings for level `"A00"` of variable `flood_zone` in Model 4.
 
@@
 
-With AI and ML coming into the mainstream across industries and use cases, the topic of model explainability
-has received increasing attention. In insurance pricing, @kuo2020explainability propose a framework for
-model interpretability in the context of regulation and actuarial standards of practice, while @henckaerts2020boosting
-investigate algorithm-specific techniques to inspect tree-based models. @kuo2020explainability and references
-therein also discuss
-commonly utilized model-agnostic explanation techniques, such as permutation variable importance and partial
-dependence plots, that can be applied to the neural networks we consider in this paper.
+With AI and ML coming into the mainstream across industries and use cases, the topic of model explainability has received increasing attention.
+In insurance pricing, @kuo2020explainability propose a framework for model interpretability in the context of regulation and actuarial standards of practice, while @henckaerts2020boosting investigate algorithm-specific techniques to inspect tree-based models.
+@kuo2020explainability and references therein also discuss commonly utilized model-agnostic explanation techniques, such as permutation variable importance and partial dependence plots, that can be applied to the neural networks we consider in this paper.
 
-In this section, we focus on ways to visualize the learned embeddings. In the authors' experiences, oftentimes
-the formats of the visualizations---basic line and scatter plots---even more so than the content of the data, are 
-helpful in explaining the concept to stakeholders.
+In this section, we focus on ways to visualize the learned embeddings.
+In the authors' experiences, oftentimes the formats of the visualizations---basic line and scatter plots---even more so than the content of the data, are helpful in explaining the concept to stakeholders.
 
-For Model 2, the neural network with one-dimensional embeddings, the task is simple: we can simply plot the levels
-on a line, as in Figure \@ref(fig:occ-type). In the case of `flood_zone`, where we happen to have the luxury of knowing
- a
-priori the meaning of the prefixes, we can plot them separately, as in Figure \@ref(fig:flood-zone) to see how the
- model 
-mapped them.
+For Model 2, the neural network with one-dimensional embeddings, the task is simple: we can simply plot the levels on a line, as in Figure \@ref(fig:occ-type).
+In the case of `flood_zone`, where we happen to have the luxury of knowing a priori the meaning of the prefixes, we can plot them separately, as in Figure \@ref(fig:flood-zone) to see how the model mapped them.
 
@@
 
-For Model 4, the neural network with multi-dimensional embeddings, we would need to treat the learned values before
-we can plot them. Specifically, we need to reduce the dimension of the data to 2D for embeddings with more than
-two dimensions. The standard approachs for this are principal component analysis (PCA; @shlens2014tutorial) 
-and t-distributed stochastic
-neighbor embedding (t-SNE; @Maaten2008a), both of which we illustrate.
+For Model 4, the neural network with multi-dimensional embeddings, we would need to treat the learned values before we can plot them.
+Specifically, we need to reduce the dimension of the data to 2D for embeddings with more than two dimensions.
+The standard approachs for this are principal component analysis (PCA; @shlens2014tutorial) and t-distributed stochastic neighbor embedding (t-SNE; @Maaten2008a), both of which we illustrate.
 
@@
 
-In both approaches, the overarching theme is as follows: we have a collection of points in higher dimensional space,
-$\mathcal{X} = \{x_1, x_2, \dots, x_n\}$ that we wish to map to some lower dimensional space, typically $\mathbb{R}^2$,
-obtaining $\mathcal{Y} = \{y_1, y_2, \dots, y_n\}$. PCA performs a linear change of coordinates on 
-the input data so that the variance of the data is maximized along each orthogonal coordinate, also known as
-*principal component*, successively. Formally, if we denote $\mathbf{X}$ and $\mathbf{Y}$ to be the matrices whose 
-columns are elements of 
-$\mathcal{X}$ and $\mathcal{Y}$, respectively, this can be represented as looking for an orthonormal matrix $\mathbf{P}$
-in $\mathbf{Y} = \mathbf{PX}$ such that the covariance matrix of $\mathbf{Y}$, $\frac{1}{n}\mathbf{YY^T}$, is diagonal.
-Here, the rows of $\mathbf{P}$ are the principal components that define the resulting coordinate system. It turns out
-that that these principal components are the eigenvectors of the covariance matrix of $\mathbf{X}$, i.e., 
-$\mathbf{C_X} \equiv \frac{1}{n}\mathbf{XX^T}$. In practice, numerical procedures, including R's \texttt{prcomp()}
-which we use, utilize singular value decomposition (SVD) to compute the eigenvectors.
+In both approaches, the overarching theme is as follows: we have a collection of points in higher dimensional space, $\mathcal{X} = \{x_1, x_2, \dots, x_n\}$ that we wish to map to some lower dimensional space, typically $\mathbb{R}^2$, obtaining $\mathcal{Y} = \{y_1, y_2, \dots, y_n\}$.
+PCA performs a linear change of coordinates on the input data so that the variance of the data is maximized along each orthogonal coordinate, also known as *principal component*, successively.
+Formally, if we denote $\mathbf{X}$ and $\mathbf{Y}$ to be the matrices whose columns are elements of $\mathcal{X}$ and $\mathcal{Y}$, respectively, this can be represented as looking for an orthonormal matrix $\mathbf{P}$ in $\mathbf{Y} = \mathbf{PX}$ such that the covariance matrix of $\mathbf{Y}$, $\frac{1}{n}\mathbf{YY^T}$, is diagonal.
+Here, the rows of $\mathbf{P}$ are the principal components that define the resulting coordinate system.
+It turns out that that these principal components are the eigenvectors of the covariance matrix of $\mathbf{X}$, i.e., $\mathbf{C_X} \equiv \frac{1}{n}\mathbf{XX^T}$.
+In practice, numerical procedures, including R's \texttt{prcomp()} which we use, utilize singular value decomposition (SVD) to compute the eigenvectors.
 
-In Figure \@ref(fig:flood-zone-pca), we plot the learned embeddings for `flood_zone` in Model 3 on the coordinate
-system defined by the first two principle components. In our case, however, we are not able to identify discernable
-clusters in the plot. From inspecting the matrix decomposition results, we see that the cumulative proportion of
-variance for the first two principal components are just 0.18, which may suggest that perhaps PCA is not the most
-appropriate dimensionality reduction technique in this case.
+In Figure \@ref(fig:flood-zone-pca), we plot the learned embeddings for `flood_zone` in Model 3 on the coordinate system defined by the first two principle components.
+In our case, however, we are not able to identify discernable clusters in the plot.
+From inspecting the matrix decomposition results, we see that the cumulative proportion of variance for the first two principal components are just 0.18, which may suggest that perhaps PCA is not the most appropriate dimensionality reduction technique in this case.
 
@@
 
-In contrast with PCA, t-SNE is a nonlinear technique. At a high level, it computes a similarity metric, in the form of
-conditional probabilities based on pairwise distances, among points in $\mathcal{X}$, then look for points $\mathcal{Y}$
-in the lower dimensional space which have similarity metric values (for a differently defined metric) that are "close" to those of corresponding pairs of 
-points in the original data.
+In contrast with PCA, t-SNE is a nonlinear technique.
+At a high level, it computes a similarity metric, in the form of conditional probabilities based on pairwise distances, among points in $\mathcal{X}$, then look for points $\mathcal{Y}$ in the lower dimensional space which have similarity metric values (for a differently defined metric) that are "close" to those of corresponding pairs of points in the original data.
 
-Let $p_{j|i}$ denote the probability that point $x_i$ picks point $x_j$ as its *neighbor*, if it picks neighbors in
-proportion to its density under an $n$-dimension Gaussian centered at $x_i$. Formally, we can write $p_{j|i}$ as
+Let $p_{j|i}$ denote the probability that point $x_i$ picks point $x_j$ as its *neighbor*, if it picks neighbors in proportion to its density under an $n$-dimension Gaussian centered at $x_i$.
+Formally, we can write $p_{j|i}$ as
 
@@
 p_{j|i} = \frac{\exp(\norm{x_i - x_j}^2 / 2\sigma_i^2)}{\sum_{k\neq i} \exp(-\norm{x_i - x_k}^2 / 2\sigma_i^2)}, (\#eq:pji)
-\end{equation}
-where $\sigma_i^2$ denotes the variance of the Gaussian associated with $x_i$. The similarity metric for the original
- space symmetrizes this conditional probability and is defined as
+\end{equation} where $\sigma_i^2$ denotes the variance of the Gaussian associated with $x_i$. The similarity metric for the original space symmetrizes this conditional probability and is defined as
 
+```{=tex}
 \begin{equation}
@@
 \end{equation}
+```
+On the other hand, in the target space, t-SNE assumes the neighbor selection is driven by a Student t-distribution with one degree of freedom, i.e., a Cauchy distribution.
+The similarity metric for a pair of points in $\mathcal{Y}$ is then defined as the joint probability
 
-On the other hand, in the target space, t-SNE assumes the neighbor selection is driven by a Student 
-t-distribution with one
-degree of freedom, i.e., a Cauchy distribution. The similarity metric for a pair of points in $\mathcal{Y}$ is 
-then defined as the joint probability
-
+```{=tex}
 \begin{equation}
@@
 \end{equation}
+```
+With the similarity metrics defined for each space, we can then state the objective for "closeness" for the sets of points, which is the Kullback--Leibler divergence from Q to P:
 
-With the similarity metrics defined for each space, we can then state the objective for "closeness" for the sets of
-points, which is the Kullback–Leibler divergence from Q to P:
-
+```{=tex}
 \begin{equation}
@@
 \end{equation}
+```
+We now circle back to Equation \@ref(eq:pji) and discuss $\sigma_i$.
+The variance of the Gaussian is allowed to vary depending on where the point is in the space; specifically, it should reflect the density or sparsness of surrounding points.
+To train this parameter, t-SNE introduces a hyperparameter, *perplexity*, which is a scalar value set by the user, and is defined as
 
-We now circle back to Equation \@ref(eq:pji) and discuss $\sigma_i$. The variance of the Gaussian is allowed to vary
-depending on where the point is in the space; specifically, it should reflect the density or sparsness of surrounding 
-points. To train this parameter, t-SNE introduces a hyperparameter, *perplexity*, which is a scalar value set by the
-user, and is defined as
-
+```{=tex}
 \begin{equation}
 Perp(P_i) = 2^{H(P_i)},
-\end{equation}
-
+\end{equation}```
 where $H(P_i)$ denotes the entropy of $P_i$,
 
+```{=tex}
 \begin{equation}
@@
 \end{equation}
-
-and $P_i$ is the Gaussian parameterized by $x_i$ and $\sigma_i$. During training, t-SNE looks for $P_i$ that have
-perpelxity corresponding to the user input. Finally, the objective as stated in Equation \@ref(eq:tsne-obj) is differentiable, and is trained via gradient descent.
+```
+and $P_i$ is the Gaussian parameterized by $x_i$ and $\sigma_i$.
+During training, t-SNE looks for $P_i$ that have perpelxity corresponding to the user input.
+Finally, the objective as stated in Equation \@ref(eq:tsne-obj) is differentiable, and is trained via gradient descent.
 
 While t-SNE is a powerful visualization technique, there are a few points the modeler should be mindful of in practice.
-We refer the reader to @wattenberg2016how for a more thorough discussion, but stress here that the resulting plot can
-be very sensitive to the perplexity hyperparameter. In addition, for our use case, which is to explore the
-learned embeddings, we have fewer data points than most other applications in the literature. Accordingly, our
-reaosnable range of hyperparameter values need to be adjusted down.
-In Figures \@ref(fig:flood-zone-tsne), we display the t-SNE of the learned embeddings for `flood_zone` in
-Model 3 with various perplexity settings: 2, 3, 5, and 10; the learning rate and the number of steps are fixed at
-100 and 10,000, respectively, for all plots. In the first three plots, we can see the semblance of clusters forming. In
-particular, flood zone D appears in its own cluster, which implies it is far away from other levels in the embedding
-space. When the perplexity is set to 10 (and beyond), however, we start to lose the geometric properties.
+We refer the reader to @wattenberg2016how for a more thorough discussion, but stress here that the resulting plot can be very sensitive to the perplexity hyperparameter.
+In addition, for our use case, which is to explore the learned embeddings, we have fewer data points than most other applications in the literature.
+Accordingly, our reaosnable range of hyperparameter values need to be adjusted down.
+In Figures \@ref(fig:flood-zone-tsne), we display the t-SNE of the learned embeddings for `flood_zone` in Model 3 with various perplexity settings: 2, 3, 5, and 10; the learning rate and the number of steps are fixed at 100 and 10,000, respectively, for all plots.
+In the first three plots, we can see the semblance of clusters forming.
+In particular, flood zone D appears in its own cluster, which implies it is far away from other levels in the embedding space.
+When the perplexity is set to 10 (and beyond), however, we start to lose the geometric properties.
 
@@
 
-For the GLMs, Models 1 and 3, we follow the standard optimization procedure using iteratively reweighted least 
-squares (IWLS) without regularization. For the neural networks, Models 2 and 4, we utilize the \texttt{Adam}
-optimizer [@Kingma2014] with a learning rate of 0.01 and a minibatch size of 1000. We split the training set into
-analysis and assessment sets, containing 80% and 20% of the rows, respectively. We train on the analysis set for a
-maximum of 15 epochs, and stop early if the loss on the assessment set does not improve for 5 epochs.
+For the GLMs, Models 1 and 3, we follow the standard optimization procedure using iteratively reweighted least squares (IWLS) without regularization.
+For the neural networks, Models 2 and 4, we utilize the \texttt{Adam} optimizer [@Kingma2014] with a learning rate of 0.01 and a minibatch size of 1000.
+We split the training set into analysis and assessment sets, containing 80% and 20% of the rows, respectively.
+We train on the analysis set for a maximum of 15 epochs, and stop early if the loss on the assessment set does not improve for 5 epochs.
 
-During inference, or scoring, care must be taken to accommodate the categorical levels that are unseen
-during training. While we allow for an extra key in the embedding dictionary, the initial
-weights are not updated during training, which could lead to nonsensical predictions in the validation or test sets. To
-circumvent this issue, before applying the trained model but after the final optimization epoch, we update the weights
-for the unseen levels manually. In practice, a common approach is to take an average value 
-of some sort of the weights of the other levels. In our case, we take the median (if there are multiple, the lower of
-the two), but a mean, mean weighted by frequency of observations, or trimmed mean could be used.
+During inference, or scoring, care must be taken to accommodate the categorical levels that are unseen during training.
+While we allow for an extra key in the embedding dictionary, the initial weights are not updated during training, which could lead to nonsensical predictions in the validation or test sets.
+To circumvent this issue, before applying the trained model but after the final optimization epoch, we update the weights for the unseen levels manually.
+In practice, a common approach is to take an average value of some sort of the weights of the other levels.
+In our case, we take the median (if there are multiple, the lower of the two), but a mean, mean weighted by frequency of observations, or trimmed mean could be used.
 
-In Table \@ref(tab:cv-results), we exhibit the cross-validated performance metrics of each of the models. We report
-both the root mean squared error (RMSE) and the mean absolute error (MAE); we note that these are just two of many 
-potential metrics to use, and are so chosen for their interpretability and prevalence in the literature for comparing
-different types of models. Recall that, between the two metrics, RMSE penalizes large mispredictions than MAE. Also,
-in the optimization process, GLM with a gamma distribution optimizes the deviance, rather than MSE directly.
+In Table \@ref(tab:cv-results), we exhibit the cross-validated performance metrics of each of the models.
+We report both the root mean squared error (RMSE) and the mean absolute error (MAE); we note that these are just two of many potential metrics to use, and are so chosen for their interpretability and prevalence in the literature for comparing different types of models.
+Recall that, between the two metrics, RMSE penalizes large mispredictions than MAE.
+Also, in the optimization process, GLM with a gamma distribution optimizes the deviance, rather than MSE directly.
 
-We see that the neural networks generally outperform the GLMs; however, what is more interesting is that using learned 
-embeddings in place of categorical levels improves the GLM, at least from the RMSE perspective.
+We see that the neural networks generally outperform the GLMs; however, what is more interesting is that using learned embeddings in place of categorical levels improves the GLM, at least from the RMSE perspective.
 
-While linear regression (i.e., the specific case of GLM with a gaussian distribution and identity link function) is not
-commonly used for severity modeling, we add it into the mix as a benchmark, a practice we recommend in order to
-check reasonableness of other models' results. Since it is possible for a linear
-regression to output negative values, we cap the predictions below by 0.01 during scoring. Somewhat surprisingly, in 
-the problem we
-are considering, it performs similarly to the more complex neural network models in the RMSE metric (which it optimizes
-for, as the unit deviance of the normal distribution correspond to MSE.) On the other hand, the performance of the linear model
-is quite significantly worse on the MAE metric. Of course, this is not to discredit neural networks or GLMs, as the experiments 
-are performed without extensive hyperparameter tuning or feature engineering.
+While linear regression (i.e., the specific case of GLM with a gaussian distribution and identity link function) is not commonly used for severity modeling, we add it into the mix as a benchmark, a practice we recommend in order to check reasonableness of other models' results.
+Since it is possible for a linear regression to output negative values, we cap the predictions below by 0.01 during scoring.
+Somewhat surprisingly, in the problem we are considering, it performs similarly to the more complex neural network models in the RMSE metric (which it optimizes for, as the unit deviance of the normal distribution correspond to MSE.) On the other hand, the performance of the linear model is quite significantly worse on the MAE metric.
+Of course, this is not to discredit neural networks or GLMs, as the experiments are performed without extensive hyperparameter tuning or feature engineering.
 
-Table: (\#tab:cv-results) Cross validation results.
+| Model                                                                         |   RMSE |    MAE |
+|:------------------------------------------------------------------------------|-------:|-------:|
+| Model 1: GLM (gamma/log link)                                                 | 65,138 | 38,367 |
+| Model 2: MLP with 1-dimensional embeddings                                    | 60,979 | 37,605 |
+| Model 3: GLM (gamma/log link), categorical variables replaced with embeddings | 63,170 | 38,360 |
+| Model 4: MLP with multidimensional embeddings                                 | 60,973 | 37,574 |
+| Linear regression, predictions capped below at 0.01                           | 60,879 | 38,431 |
 
-|Model                                                                         |   RMSE|    MAE|
-|:-----------------------------------------------------------------------------|------:|------:|
-|Model 1: GLM (gamma/log link)                                                 | 65,138| 38,367|
-|Model 2: MLP with 1-dimensional embeddings                                    | 60,979| 37,605|
-|Model 3: GLM (gamma/log link), categorical variables replaced with embeddings | 63,170| 38,360|
-|Model 4: MLP with multidimensional embeddings                                 | 60,973| 37,574|
-|Linear regression, predictions capped below at 0.01                           | 60,879| 38,431|
+: (\#tab:cv-results) Cross validation results.
 
+```{=html}
 <!-- # Extending the model {#extend}
@@
 -->
+```
 # Attention based Modeling {#attention_models}
-In this section we investigate whether the predictive performance of the models applied to the NFIP dataset can be improved
-by applying the attention based models defined in Section \ref{attention}. We discuss the implementation of each of the 
-Simple Attention, TabTransformer and TabNet models in the following sub-section, then discuss how the modifications made
-to the embeddings through the application of attention can be visualized in the following sub-section. We conclude the 
-section with a discussion of the model results.
+
+In this section we investigate whether the predictive performance of the models applied to the NFIP dataset can be improved by applying the attention based models defined in Section \ref{attention}.
+We discuss the implementation of each of the Simple Attention, TabTransformer and TabNet models in the following sub-section, then discuss how the modifications made to the embeddings through the application of attention can be visualized in the following sub-section.
+We conclude the section with a discussion of the model results.
 
@@
 
-Compared to the models presented in the previous section, the models presented here are closer to state of the art models that
-might be used for tabular data Modeling problems. To the best of our knowledge, this is the first analysis of these architectures
-within the actuarial literature.
+Compared to the models presented in the previous section, the models presented here are closer to state of the art models that might be used for tabular data Modeling problems.
+To the best of our knowledge, this is the first analysis of these architectures within the actuarial literature.
 
 ### Model 5: Simple Attention Network
-Model 5 is conceptually similar to Model 4, except for the following two aspects. First, we standardize the dimension of the embedding 
-layers to 8 dimensions for each categorical covariate. This is done to allow for the application of the attention component, which 
-requires the embeddings for each covariate to have the same dimension. Second, we apply a self-attention mechanism within the network, 
-as shown in Equation \ref{eq:embed_to_attn_to_nn}. We illustrate this architecture in Figure \@ref(fig:nn-2).
+
+Model 5 is conceptually similar to Model 4, except for the following two aspects.
+First, we standardize the dimension of the embedding layers to 8 dimensions for each categorical covariate.
+This is done to allow for the application of the attention component, which requires the embeddings for each covariate to have the same dimension.
+Second, we apply a self-attention mechanism within the network, as shown in Equation \ref{eq:embed_to_attn_to_nn}.
+We illustrate this architecture in Figure \@ref(fig:nn-2).
 
@@
 ### Model 6: TabTransformer
-Whereas Model 5 makes a simple modification to the structure of Model 4, the TabTransformer model is slightly more complex. With respect to
-similarities between Model 5 and 6, both use embeddings with a standard 8 dimensions for each categorical covariate. In terms of differences,
-Model 6 uses a Transformer layer in place of self-attention and a positional encoding of a single dimension, i.e. $d_col = 1$. The TabTransformer
-architecture is shown in Figure \@ref(fig:nn-3).
+
+Whereas Model 5 makes a simple modification to the structure of Model 4, the TabTransformer model is slightly more complex.
+With respect to similarities between Model 5 and 6, both use embeddings with a standard 8 dimensions for each categorical covariate.
+In terms of differences, Model 6 uses a Transformer layer in place of self-attention and a positional encoding of a single dimension, i.e.
+$d_col = 1$.
+The TabTransformer architecture is shown in Figure \@ref(fig:nn-3).
 
@@
 ```
+
 ### Model 7: TabNet
-The final model we consider in this subsection is the TabNet architecture. The structure of the model is quite similar to Model 6, except 
-that a more specialized form of self-attention is used to select the most important covariates for the Modeling problem.
+
+The final model we consider in this subsection is the TabNet architecture.
+The structure of the model is quite similar to Model 6, except that a more specialized form of self-attention is used to select the most important covariates for the Modeling problem.
 
 ## Training and Inference {#training-inference-attn}
-We follow a similar training setup for the three attention based models, to the neural networks discussed in the previous section. For Models 5 and 6, 
-we utilize the \texttt{Adam} optimizer as before, however, due to the increased complexity of the models in this section,
-we use learning rate of 0.001 (compared to 0.01 for the simpler models). Reflecting this reduced learning rate, 
-we train on the analysis set for a maximum of 150 epochs, and select the best model based on the lowest loss achieved on the assessment. Moreover, since these models are
-significantly more complex than those tested in the previous section, we also add some minimal regularization using dropout [@srivastava2014dropout] to the attention layers 
-and the last layer of the network, to prevent overfitting. Dropout functions by setting some components of the network randomly to zero during each epoch of training. 
-This forces each component of the network to learn a somewhat independent representation of the data, thus helping to avoid overfitting by preventing components of the 
-network from becoming too specialized. In this section, we drop out components with a probability of 2.5\%. A final detail is that, 
-for both of these models, we use an embedding dimension of size 16 for each of the categorical covariates, since the attention mechanism requires that the embeddings 
-be of a common length. For the TabTransformer model, we use a row embedding of dimension 4.
 
-For Model 7, we use the suggested training setup that utilizes the \texttt{Adam} optimizer with a learning rate of 0.02, and train for 15 epochs (since longer training
-times did not lead to improved performance).
+We follow a similar training setup for the three attention based models, to the neural networks discussed in the previous section.
+For Models 5 and 6, we utilize the \texttt{Adam} optimizer as before, however, due to the increased complexity of the models in this section, we use learning rate of 0.001 (compared to 0.01 for the simpler models).
+Reflecting this reduced learning rate, we train on the analysis set for a maximum of 150 epochs, and select the best model based on the lowest loss achieved on the assessment.
+Moreover, since these models are significantly more complex than those tested in the previous section, we also add some minimal regularization using dropout [@srivastava2014dropout] to the attention layers and the last layer of the network, to prevent overfitting.
+Dropout functions by setting some components of the network randomly to zero during each epoch of training.
+This forces each component of the network to learn a somewhat independent representation of the data, thus helping to avoid overfitting by preventing components of the network from becoming too specialized.
+In this section, we drop out components with a probability of 2.5%.
+A final detail is that, for both of these models, we use an embedding dimension of size 16 for each of the categorical covariates, since the attention mechanism requires that the embeddings be of a common length.
+For the TabTransformer model, we use a row embedding of dimension 4.
 
-In Table \@ref(tab:cv-results-attn), we show the cross-validated performance metrics of each of the models, 
-as well as the two best performing models from the previous section. As before, we report both the root mean squared error (RMSE) 
-and the mean absolute error (MAE). The results show that Model 5, which simply adds attention to Model 4, outperforms Model 4 on both the RMSE and 
-MAE metrics. Thus, there is some room to argue that for tabular data Modeling that uses embeddings for categorical data, 
-the use of attention within models should be considered. Disappointingly, the TabNet architecture performs poorly, perhaps due to insufficient hyperparameter tuning, 
-but indicating that ``out of the box", TabNet does not appear to work well for this Modeling task. Finally, the TabTransformer model shows the best performance of all
- models considered in this research, beating the other models by a significant margin on both the RMSE and MAE metrics.
+For Model 7, we use the suggested training setup that utilizes the \texttt{Adam} optimizer with a learning rate of 0.02, and train for 15 epochs (since longer training times did not lead to improved performance).
 
-Table: (\#tab:cv-results-attn) Cross validation results for Models 5-7.
+In Table \@ref(tab:cv-results-attn), we show the cross-validated performance metrics of each of the models, as well as the two best performing models from the previous section.
+As before, we report both the root mean squared error (RMSE) and the mean absolute error (MAE).
+The results show that Model 5, which simply adds attention to Model 4, outperforms Model 4 on both the RMSE and MAE metrics.
+Thus, there is some room to argue that for tabular data Modeling that uses embeddings for categorical data, the use of attention within models should be considered.
+Disappointingly, the TabNet architecture performs poorly, perhaps due to insufficient hyperparameter tuning, but indicating that \`\`out of the box", TabNet does not appear to work well for this Modeling task.
+Finally, the TabTransformer model shows the best performance of all models considered in this research, beating the other models by a significant margin on both the RMSE and MAE metrics.
 
-|Model                                                                          |   RMSE|    MAE|
-|:-----------------------------------------------------------------------------|------:|------:|
-|Model 4: MLP with multidimensional embeddings                                 | 60,973| 37,574|
-|Model 5: Simple Attention                                                     | 60,601| 36,739|
-|Model 6: TabNet                                                               | 62,938| 38,386|
-|Model 7: TabTransformer                                                       | 59,900| 36,343|
-|Linear regression, predictions capped below at 0.01                           | 60,879| 38,431|
+| Model                                               |   RMSE |    MAE |
+|:----------------------------------------------------|-------:|-------:|
+| Model 4: MLP with multidimensional embeddings       | 60,973 | 37,574 |
+| Model 5: Simple Attention                           | 60,601 | 36,739 |
+| Model 6: TabNet                                     | 62,938 | 38,386 |
+| Model 7: TabTransformer                             | 59,900 | 36,343 |
+| Linear regression, predictions capped below at 0.01 | 60,879 | 38,431 |
+
+: (\#tab:cv-results-attn) Cross validation results for Models 5-7.
 
@@
 
-Here, we explore what the TabTransformer model has learned from the data via the attention process that forms the core of the model. We focus on the difference 
-between the flood embedding learned by the model, compared with the output of the Transformer layer that processes the embeddings before these enter the model. 
-@Huang2020 call the latter ``contextual embeddings", because the attention mechanism within the TabTransformer model augments the embeddings based on the 
-other covariates that appear for each observation $i$.
+Here, we explore what the TabTransformer model has learned from the data via the attention process that forms the core of the model.
+We focus on the difference between the flood embedding learned by the model, compared with the output of the Transformer layer that processes the embeddings before these enter the model.
+@Huang2020 call the latter \`\`contextual embeddings", because the attention mechanism within the TabTransformer model augments the embeddings based on the other covariates that appear for each observation $i$.
 
-To illustrate this, we selected a single TabTransformer fit on one fold of the training data, and selected at random 10 000 individual observations. For each
-observation, the embedding relating to the flood zone of the observation was extracted from the model, as well as the contextual embedding that was produced 
-for that observation by the TabTransformer model. We found that a PCA and t-SNE analysis of the embeddings produced very similar results to those shown in the previous section,
-so we do not show these plots here. To investigate the difference between the embeddings and contextual embeddings for the `flood_zone` variable, 
-we show the first component from a PCA analysis of each of these in Figure \@ref(fig:embd).
+To illustrate this, we selected a single TabTransformer fit on one fold of the training data, and selected at random 10 000 individual observations.
+For each observation, the embedding relating to the flood zone of the observation was extracted from the model, as well as the contextual embedding that was produced for that observation by the TabTransformer model.
+We found that a PCA and t-SNE analysis of the embeddings produced very similar results to those shown in the previous section, so we do not show these plots here.
+To investigate the difference between the embeddings and contextual embeddings for the `flood_zone` variable, we show the first component from a PCA analysis of each of these in Figure \@ref(fig:embd).
 
@@
 
-The figure shows that, whereas the first principal component of the embeddings occupy discrete points only (shown on the $x$-axis), 
-the first principal component of the **contextual** embeddings is continuous (shown on the $y$-axis), meaning that the model has modified the values
-of the embedding in a smooth manner. Since the inputs to the attention mechanism which is responsible for this are the embeddings for the other categorical
-variables for each observation, these other variables have influenced the final embedding used within the model for the `flood_zone` variable. By considering 
-each of the other categorical variables entering the model, it was found that the basement enclosure crawl space variable explains most of the variation
-observed within the flood zone embeddings, as shown in Figure \@ref(fig:embdexp). The attention mechanism produces the lowest values for those observations
-with an unfinished basement, whereas the model produces the highest values for buildings without a crawl space.
+The figure shows that, whereas the first principal component of the embeddings occupy discrete points only (shown on the $x$-axis), the first principal component of the **contextual** embeddings is continuous (shown on the $y$-axis), meaning that the model has modified the values of the embedding in a smooth manner.
+Since the inputs to the attention mechanism which is responsible for this are the embeddings for the other categorical variables for each observation, these other variables have influenced the final embedding used within the model for the `flood_zone` variable.
+By considering each of the other categorical variables entering the model, it was found that the basement enclosure crawl space variable explains most of the variation observed within the flood zone embeddings, as shown in Figure \@ref(fig:embdexp).
+The attention mechanism produces the lowest values for those observations with an unfinished basement, whereas the model produces the highest values for buildings without a crawl space.
 
@@
 ```
-To investigate the predictive value added by the contextual embeddings, a simple Gamma GLM was fit to these 10 000 observations, with the goal of predicting the 
-claim amount based only on either the embeddings or the contextual embeddings. As shown in Table \@ref(tab:emd-vs-cembd), the performance of the latter model, 
-as indicated by the RMSE and MAE metrics is significantly better, in other words, the contextual embeddings that incorporate information across all of the categorical variables are significantly better predictors
-of claim severity compared with the embeddings.
 
-Table: (\#tab:emd-vs-cembd) RMSE and MAE for GLMs predicting claim severity, embeddings compared with contextual embeddings.
+To investigate the predictive value added by the contextual embeddings, a simple Gamma GLM was fit to these 10 000 observations, with the goal of predicting the claim amount based only on either the embeddings or the contextual embeddings.
+As shown in Table \@ref(tab:emd-vs-cembd), the performance of the latter model, as indicated by the RMSE and MAE metrics is significantly better, in other words, the contextual embeddings that incorporate information across all of the categorical variables are significantly better predictors of claim severity compared with the embeddings.
 
-|Embedding Type       |     RMSE|      MAE|
-|:--------------------|--------:|--------:|
-|Embedding            | 62596.84| 40323.82|
-|Contextual embedding | 62027.85| 39450.45|
+| Embedding Type       |     RMSE |      MAE |
+|:---------------------|---------:|---------:|
+| Embedding            | 62596.84 | 40323.82 |
+| Contextual embedding | 62027.85 | 39450.45 |
+
+: (\#tab:emd-vs-cembd) RMSE and MAE for GLMs predicting claim severity, embeddings compared with contextual embeddings.
 
@@
 
-This study has focused on how embeddings can be applied within the context of actuarial Modeling, by illustrating a range of approaches: first, relatively simple
-neural networks with embeddings were defined, the embeddings from these models were reused within traditional GLM models and, finally, more advanced attention based models 
-were studied. These models were demonstrated within the context of a claims severity Modeling problem based on data from the NFIP. Whereas we have only considered severity 
-in this study, it is likely that our findings will replicate for the Modeling of claim frequency, which is usually an easier problem. Our key findings are that 
-processing categorical variables with multi-dimensional embeddings leads to enhanced performance within simple neural networks, and that, by including these within traditional
-GLM models, the predictive performance of these models can be enhanced, compared to the usual encoding scheme for categorical variables. Some of the attention based models 
-considered within this study performed well, in particular, the TabTransformer model of @Huang2020 appears quite promising for use in actuarial Modeling. The study has also 
-illustrated how embeddings can be visualized using the PCA and t-SNE techniques. We found that, in the case of the NFIP data, it is possible to explain which variables modify 
-the embeddings based on the context of each observation.
+This study has focused on how embeddings can be applied within the context of actuarial Modeling, by illustrating a range of approaches: first, relatively simple neural networks with embeddings were defined, the embeddings from these models were reused within traditional GLM models and, finally, more advanced attention based models were studied.
+These models were demonstrated within the context of a claims severity Modeling problem based on data from the NFIP.
+Whereas we have only considered severity in this study, it is likely that our findings will replicate for the Modeling of claim frequency, which is usually an easier problem.
+Our key findings are that processing categorical variables with multi-dimensional embeddings leads to enhanced performance within simple neural networks, and that, by including these within traditional GLM models, the predictive performance of these models can be enhanced, compared to the usual encoding scheme for categorical variables.
+Some of the attention based models considered within this study performed well, in particular, the TabTransformer model of @Huang2020 appears quite promising for use in actuarial Modeling.
+The study has also illustrated how embeddings can be visualized using the PCA and t-SNE techniques.
+We found that, in the case of the NFIP data, it is possible to explain which variables modify the embeddings based on the context of each observation.
 
-Several avenues for future research can be considered. One surprising finding of our work is that the TabNet model performed quite poorly, leading us to conclude that this 
-model appears to be less suitable for actuarial Modeling. Understanding these findings in more detail would be a valuable contribution to the literature. Another helpful contribution
-would be to investigate the optimal hyperparameters for the TabTransformer model in the context of actuarial Modeling. Finally, extending our findings to a claims frequency example
-could be considered.
+Several avenues for future research can be considered.
+One surprising finding of our work is that the TabNet model performed quite poorly, leading us to conclude that this model appears to be less suitable for actuarial Modeling.
+Understanding these findings in more detail would be a valuable contribution to the literature.
+Another helpful contribution would be to investigate the optimal hyperparameters for the TabTransformer model in the context of actuarial Modeling.
+Finally, extending our findings to a claims frequency example could be considered.
 
-\newpage
+\appendix
 
-# References {.unnumbered}
+# Appendix {.unnumbered}
+
+# Exploratory Data Analysis
+
+In this appendix we present an exploratory data analysis of the NFIP claims dataset.
+
+Figure \@ref(fig:sev) shows the distribution of the claim size that we model in this study. It can be seen that claim size varies over several orders of magnitude.
+
+```{r sev, echo = FALSE, fig.cap = "Histogram of the Log Claim Amount", out.width = "80%", fig.align = "center"}
+knitr::include_graphics("images/claim_size.pdf")
+```
+
+Figure \@ref(fig:loglog) shows the claim size seemingly follows a relatively heavy-tailed distribution.
+
+```{r loglog, echo = FALSE, fig.cap = "Log-log plot of Claim amount", out.width = "80%", fig.align = "center"}
+knitr::include_graphics("images/loglog.pdf")
+```
+
+Figures \@ref(fig:catprimres) - \@ref(fig:catflood) illustrate the distribution of the categorical covariates within the dataset.
+
+```{r catprimres, echo = FALSE, fig.cap = "Distribution of observations across the Primary Residence covariate", out.width = "80%", fig.align = "center"}
+knitr::include_graphics("images/primary_residence.pdf")
+```
+
+```{r catocc, echo = FALSE, fig.cap = "Distribution of observations across the Occupancy type covariate", out.width = "80%", fig.align = "center"}
+knitr::include_graphics("images/occupancy_type.pdf")
+```
+
+```{r catbasement, echo = FALSE, fig.cap = "Distribution of observations across the Basement Enclosure and Crawlspace covariate", out.width = "80%", fig.align = "center"}
+knitr::include_graphics("images/basement_enclosure_crawlspace_type.pdf")
+```
+
+```{r catfloors, echo = FALSE, fig.cap = "Distribution of observations across the Number of Floors covariate", out.width = "80%", fig.align = "center"}
+knitr::include_graphics("images/number_of_floors_in_the_insured_building.pdf")
+```
+
+```{r catflood, echo = FALSE, fig.cap = "Distribution of observations across the Flood Zone covariate", out.width = "80%", fig.align = "center"}
+knitr::include_graphics("images/flood_zone.pdf")
+```
+
+Similarly, Figures \@ref(fig:numcov) - \@ref(fig:numdisc) illustrate the distribution of the continuous covariates within the dataset.
+
+```{r numcov, echo = FALSE, fig.cap = "Histogram of the Building Coverage covariate", out.width = "80%", fig.align = "center"}
+knitr::include_graphics("images/total_building_insurance_coverage.pdf")
+```
+
+```{r numdisc, echo = FALSE, fig.cap = "Distribution of the Comunity Rating System Discount covariate", out.width = "80%", fig.align = "center"}
+knitr::include_graphics("images/community_rating_system_discount.pdf")
+```
+
+# References {.unnumbered

### 2021-04-07 manuscript/manuscript.Rmd
Appendix fixed

@@
 
-In this work, we utilize the recently released National Flood Insurance Program (NFIP) dataset [@FederalEmergencyManagementAgency2019] which provides exposure information for policies written under the NFIP since XXXXDateXXXX, as well as the claims data relating to these exposures.
-We refer the reader to Appendix \ref{NFIP_eda} for an exploratory analysis of this dataset.
+In this work, we utilize the recently released National Flood Insurance Program (NFIP) dataset [@FederalEmergencyManagementAgency2019] which provides exposure information for policies written under the NFIP, as well as the claims data relating to these exposures.
+We refer the reader to Appendix \ref{EDA} for an exploratory analysis of this dataset.
 
@@
 
+\newpage
+
 # Conclusions {#Conclusions}
@@
 
+\clearpage
+
 \appendix
@@
 
-# Exploratory Data Analysis
+# Exploratory Data Analysis {#EDA}
 
@@
 
-```{r sev, echo = FALSE, fig.cap = "Histogram of the Log Claim Amount", out.width = "80%", fig.align = "center"}
+```{r sev, echo = FALSE, fig.cap = "Histogram of the Log Claim Amount", out.width = "60%", fig.align = "center"}
 knitr::include_graphics("images/claim_size.pdf")
@@
 
-```{r loglog, echo = FALSE, fig.cap = "Log-log plot of Claim amount", out.width = "80%", fig.align = "center"}
+```{r loglog, echo = FALSE, fig.cap = "Log-log plot of Claim amount", out.width = "60%", fig.align = "center"}
 knitr::include_graphics("images/loglog.pdf")
@@
 
-```{r catprimres, echo = FALSE, fig.cap = "Distribution of observations across the Primary Residence covariate", out.width = "80%", fig.align = "center"}
+```{r catprimres, echo = FALSE, fig.cap = "Distribution of observations across the Primary Residence covariate", out.width = "60%", fig.align = "center"}
 knitr::include_graphics("images/primary_residence.pdf")
@@
 
-```{r catocc, echo = FALSE, fig.cap = "Distribution of observations across the Occupancy type covariate", out.width = "80%", fig.align = "center"}
+```{r catocc, echo = FALSE, fig.cap = "Distribution of observations across the Occupancy type covariate", out.width = "60%", fig.align = "center"}
 knitr::include_graphics("images/occupancy_type.pdf")
@@
 
-```{r catbasement, echo = FALSE, fig.cap = "Distribution of observations across the Basement Enclosure and Crawlspace covariate", out.width = "80%", fig.align = "center"}
+```{r catbasement, echo = FALSE, fig.cap = "Distribution of observations across the Basement Enclosure and Crawlspace covariate", out.width = "60%", fig.align = "center"}
 knitr::include_graphics("images/basement_enclosure_crawlspace_type.pdf")
@@
 
-```{r catfloors, echo = FALSE, fig.cap = "Distribution of observations across the Number of Floors covariate", out.width = "80%", fig.align = "center"}
+```{r catfloors, echo = FALSE, fig.cap = "Distribution of observations across the Number of Floors covariate", out.width = "60%", fig.align = "center"}
 knitr::include_graphics("images/number_of_floors_in_the_insured_building.pdf")
@@
 
-```{r catflood, echo = FALSE, fig.cap = "Distribution of observations across the Flood Zone covariate", out.width = "80%", fig.align = "center"}
+```{r catflood, echo = FALSE, fig.cap = "Distribution of observations across the Flood Zone covariate", out.width = "60%", fig.align = "center"}
 knitr::include_graphics("images/flood_zone.pdf")
@@
 
-```{r numcov, echo = FALSE, fig.cap = "Histogram of the Building Coverage covariate", out.width = "80%", fig.align = "center"}
+```{r numcov, echo = FALSE, fig.cap = "Histogram of the Building Coverage covariate", out.width = "60%", fig.align = "center"}
 knitr::include_graphics("images/total_building_insurance_coverage.pdf")
@@
 
-```{r numdisc, echo = FALSE, fig.cap = "Distribution of the Comunity Rating System Discount covariate", out.width = "80%", fig.align = "center"}
+```{r numdisc, echo = FALSE, fig.cap = "Distribution of the Comunity Rating System Discount covariate", out.width = "60%", fig.align = "center"}
 knitr::include_graphics("images/community_rating_system_discount.pdf")
@@
 
-# References {.unnumbered
+\clearpage
+
+# References {.unnumbered}

### 2021-04-07 manuscript/manuscript.Rmd
Fix formatting and bugs

@@
   - attention
-  - severity Modeling
+  - severity modeling
   - National Flood Insurance Program 
@@
 For example, when building models to price the frequency of motor insurance claims, claim experience relating to different types of motor vehicle will often be modelled by including a (single) factor within models that modifies the relative frequency predicted for each type of vehicle.
-In other cases, Modeling is performed for each category separately, thus the categorical data is used within the Modeling in an implicit manner, for example, common practice is to estimate reserves for different lines of business separately, meaning to say, with no parameters being shared across each of the reserving models.
+In other cases, modeling is performed for each category separately, thus the categorical data is used within the modeling in an implicit manner, for example, common practice is to estimate reserves for different lines of business separately, meaning to say, with no parameters being shared across each of the reserving models.
 
@@
 
-This approach to Modeling categorical data has several advantages over more traditional treatments of categorical data.
+This approach to modeling categorical data has several advantages over more traditional treatments of categorical data.
 Using categorical embeddings instead of traditional techniques has been shown to increase predictive accuracy of models, for example, see @Richman2018 in the context of pricing.
@@
 First, hyperparameter settings for embeddings, such as the dimensions of the embedding layer and the use of regularization techniques such as dropout or normalization, that achieve optimal predictive performance has not yet been studied in detail in the actuarial literature.
-In this work, we aim to study how embeddings using different settings perform in the context of a large-scale predictive Modeling problem, and give guidance on the process that can be followed to determine this in other problems.
+In this work, we aim to study how embeddings using different settings perform in the context of a large-scale predictive modeling problem, and give guidance on the process that can be followed to determine this in other problems.
 Although neural network have been shown to achieve excellent predictive accuracy on actuarial tasks, many actuaries still prefer to use GLM models for pricing tasks, thus, the issue of whether transferring embeddings to GLM models can achieve better performance is considered in this paper.
@@
 option exists to quantize numerical data and model it using embeddings, however, the results of doing so have not been investigated.
---> Finally, in the past several years, a new type of neural network architecture based on attention [@Vaswani2017] has been successfully used on embeddings in the field of natural language processing and we incorporate attention based models into our predictive Modeling example to demonstrate the use of these models for actuarial purposes.
+--> Finally, in the past several years, a new type of neural network architecture based on attention [@Vaswani2017] has been successfully used on embeddings in the field of natural language processing and we incorporate attention based models into our predictive modeling example to demonstrate the use of these models for actuarial purposes.
 
@@
 Section \ref{lit_review} reviews recent applications of embeddings in the actuarial literature.
-Section \ref{defns} provides the notation used in the paper and defines GLMs, neural networks and related Modeling concepts, including embeddings and attention.
-In Section \ref{Modeling}, we provide initial models for the NFIP dataset and consider the influence of hyperparameter choices on the results of the neural network model.
+Section \ref{defns} provides the notation used in the paper and defines GLMs, neural networks and related modeling concepts, including embeddings and attention.
+In Section \ref{modeling}, we provide initial models for the NFIP dataset and consider the influence of hyperparameter choices on the results of the neural network model.
 That section also considers how successfully the embeddings used in the neural network model can be transferred to a GLM model of the same data and how learned embeddings can be interpreted.
@@
 
-A different approach to Modeling categorical data is credibility theory (see @Buhlmann2006 for an overview), which, in the context of rating, can be applied to derive premiums that reflect the experience of a particular policyholder, by estimating premiums as a weighted average between the premium produced using the collective experience (i.e.
+A different approach to modeling categorical data is credibility theory (see @Buhlmann2006 for an overview), which, in the context of rating, can be applied to derive premiums that reflect the experience of a particular policyholder, by estimating premiums as a weighted average between the premium produced using the collective experience (i.e.
 of all policyholders) and the premium produced using the experience of the particular policyholder.
@@
 
-Generalized Linear Mixed Models (GLMMs) are an extension of GLMs that are designed for Modeling categorical data using a principle very similar to that of credibility theory [@Klinker2010].
+Generalized Linear Mixed Models (GLMMs) are an extension of GLMs that are designed for modeling categorical data using a principle very similar to that of credibility theory [@Klinker2010].
 Instead of calibrating indicator variables for each level of the category, GLMMs estimate effects for each of these levels as a combination of the overall group mean and the experience in each level of the category.
 
-Embedding layers represent a different approach to the problem of Modeling categorical data that was recently introduced in an actuarial context.
+Embedding layers represent a different approach to the problem of modeling categorical data that was recently introduced in an actuarial context.
 Note that in the next section, we reflect on similarities between the conventional approaches discussed above and embedding layers.
@@
 In that work, two applications of embedding layers were demonstrated.
-The first of these was in a Property and Casualty (P&C) pricing context, it was shown that the out-of-sample accuracy of a neural network trained to predict claims frequencies on motor third party liability was enhanced by Modeling the categorical variables within this dataset using embedding layers.
+The first of these was in a Property and Casualty (P&C) pricing context, it was shown that the out-of-sample accuracy of a neural network trained to predict claims frequencies on motor third party liability was enhanced by modeling the categorical variables within this dataset using embedding layers.
 Second, a neural network with embedding layers was used to model all of the mortality rates in the Human Mortality Database, where the differences in population mortality across countries and the differences in mortality at different ages were modelled with embedding layers, again producing more accurate out of sample performance than the other models tested.
@@
 
-In this study, we are concerned with regression Modeling, which is the task of predicting an unknown outcome $y$ on the basis of information about that outcome contained in predictor variables, or features, stored in a matrix $X$.
+In this study, we are concerned with regression modeling, which is the task of predicting an unknown outcome $y$ on the basis of information about that outcome contained in predictor variables, or features, stored in a matrix $X$.
 For simplicity, we only consider the case of univariate outcomes, i.e., $y \in \mathbb{R}^1$.
@@
 
-```{=tex}
 \begin{equation} 
@@
 \end{equation}
-```
+
 where the regression parameters (weights) for each layer $k \in [1;K+1]$ are represented by the matrices $a_k$ and the intercept terms are represented by $b_k$.
@@
 \end{equation}
-```
+
 where $q_\mathcal{P}^j$ is the dimension of the embedding for the $j$th categorical variable and $z_\mathcal{P}^j(.)$ is an implicit function that maps from the particular element of the labels $p$ to the embedding space.
@@
 
-Attention mechanisms have been widely applied within the deep learning literature to give more flexibility to RNNs [@Bahdanau2015a] and subsequently as a replacement for FCNs in the so-called Transformer architecture, which is now widely used in natural language processing [@Vaswani2017a], and, more recently, has been applied to computer vision and tabular Modeling tasks.
+Attention mechanisms have been widely applied within the deep learning literature to give more flexibility to RNNs [@Bahdanau2015a] and subsequently as a replacement for FCNs in the so-called Transformer architecture, which is now widely used in natural language processing [@Vaswani2017a], and, more recently, has been applied to computer vision and tabular modeling tasks.
 Attention mechanisms allow deep neural nets to weight the covariates entering the model in a flexible manner; these types of applications in natural language processing are demonstrated in, for example, @Vaswani2017a.
-In an actuarial context, attention mechanisms can be understood as giving greater weight to covariates that are important for the Modeling task.
+In an actuarial context, attention mechanisms can be understood as giving greater weight to covariates that are important for the modeling task.
 In this section we provide a theoretical introduction to attention mechanisms and then discuss applications of attention to modeling tabular data.
@@
 ```
-where $Q \in \mathbb{R}^{q \times d}$ is a matrix of query vectors, $K \in \mathbb{R}^{q \times d}$ is a matrix of key vectors, $X' \in \mathbb{R}^{q \times d}$ is a matrix of value vectors and $X^* \in \mathbb{R}^{q \times d}$, the output of the attention mechanism, is a new matrix of values that have been reweighted according to their importance for the Modeling problem.
+where $Q \in \mathbb{R}^{q \times d}$ is a matrix of query vectors, $K \in \mathbb{R}^{q \times d}$ is a matrix of key vectors, $X' \in \mathbb{R}^{q \times d}$ is a matrix of value vectors and $X^* \in \mathbb{R}^{q \times d}$, the output of the attention mechanism, is a new matrix of values that have been reweighted according to their importance for the modeling problem.
 As noted above, several different options for the mapping in Equation \ref{eq:attention} exist in the literature; here we describe the scaled dot-product self-attention mechanism used in @Vaswani2017a.
@@
 
-An intuitive explanation of the attention formula is as follows: we start by considering the importance of all of the covariates that we have for our Modeling problem in the context of each individual covariate.
-This is done by assigning a score between zero and one to each covariate in the Modeling problem, and we repeat this process for each of the covariates.
+An intuitive explanation of the attention formula is as follows: we start by considering the importance of all of the covariates that we have for our modeling problem in the context of each individual covariate.
+This is done by assigning a score between zero and one to each covariate in the modeling problem, and we repeat this process for each of the covariates.
 Then, we replace each of the original covariates with a new covariate that has been formed by taking a weighted average of the covariates and the scores.
@@
 
-### Attention Modeling for Tabular Data
+### Attention modeling for Tabular Data
 
-Several different approaches to applying attention within the Modeling of tabular data have been proposed in the literature.
+Several different approaches to applying attention within the modeling of tabular data have been proposed in the literature.
 Perhaps the simplest way of doing this is to insert an attention layer between the embeddings and the rest of the neural network.
@@
 Finally, a different way of incorporating attention into the modeling of tabular data has been proposed by @Ark2019, who refer to their model as TabNet.
-In summary, the main idea of the TabNet model is to try emulate the excellent performance of decision trees on tabular data Modeling using deep neural networks.
-This is done by structuring the neural networks to emulate a key aspect of decision tree Modeling, which is the efficient selection of relevant covariates for the model task.
+In summary, the main idea of the TabNet model is to try emulate the excellent performance of decision trees on tabular data modeling using deep neural networks.
+This is done by structuring the neural networks to emulate a key aspect of decision tree modeling, which is the efficient selection of relevant covariates for the model task.
 Within TabNet, an attention based model is used to select features by estimating attention scores for each covariate within $X$.
@@
 
-# Predictive Modeling with Embeddings {#Modeling}
+# Predictive Modeling with Embeddings {#modeling}
 
@@
 Because there is no way to associate records of the two datasets, we are limited to fitting severity models on the claims dataset.
-While the complete dataset contains over two million transactions, for the purposes of our experiments, we limit ourselves to data from 2000 to August 2019 and further subsample 100K data points to make experiments feasible on a CPU.
+While the complete dataset contains over two million transactions, for the purposes of our experiments, we limit ourselves to data from 2000 to 2019 and further subsample 100K data points to make experiments feasible on a CPU.
 The dataset includes a rich variety of variables, from occupancy type to flood zone.
@@
 We note that the focus of our contribution is on applications of categorical embeddings in predictive modeling, rather than on fine-tuning models in order to beat or establish a benchmark.
-To this end, we do not perform systematic hyperparameter tuning in our experiments, and the performance metrics are provided to show that reasonable models utilizing categorical embeddings.
+To this end, we do not perform systematic hyperparameter tuning in our experiments, and the performance metrics are provided to show that reasonable models utilizing categorical embeddings can be developed (note in the next section, the models achieve significantly better performance).
 However, as we describe the modeling procedure and results, we provide commentary on recommended practices in practical applications, especially with respect to the neural network models.
@@
 
-```{=tex}
 \begin{equation}
@@
 \end{equation}
-```
+
 one for the intercept, one for each numeric variable, and the numbers of levels minus one (due to dummy coding) for each categorical variable.
 
-In Table \@ref(tab:relativities), we exhibit an exerpt of the relativities, or exponentiated fitted coefficients, of a couple categorical variables.
+In Table \@ref(tab:relativities), we exhibit an exerpt of the relativities, or exponentiated fitted coefficients, of a couple of the categorical variables.
 Recall that the choice of the log link gives a multiplicative structure, so the interpretation of 1.34 for `occupancy_type = "Non-residential building"` is that, all else equal, the expected loss for a policy for a non-residential building is 1.34 times that of a policy for a single family home, which is the base, or reference, level for the factor.
@@
 
-With a single hidden layer, this architecture is relatively simple; without the hidden layer and corresponding ReLU activation, we would actually recover a logistic regression structure.
+With a single hidden layer, this architecture is relatively simple; without the hidden layer and corresponding ReLU activation, we would actually recover a type of logistic regression structure.
 The choice of one for the embedding dimension is also due to simplicity: it is easily interpretable as the representation of each factor level as a point on the real number line; also, the trained embeddings are easily incorporated into a GLM which we will see in Model 3.
@@
 : (\#tab:embeddings-occupancy-type) Learned embeddings for `occupancy_type` in Model 2.
+
+\newpage
 
@@
 (\#eq:glm2)
-\end{equation}```
+\end{equation}
 Hence, the model can be written as
 
-\newpage
-
-```{=tex}
 \begin{equation}
@@
 \end{equation}
-```
+
 where $z_{i,j}$ represents the embedding value for $i$th instance of the categorical column $X_j$.
@@
 \end{equation}
-```
+
 On the other hand, in the target space, t-SNE assumes the neighbor selection is driven by a Student t-distribution with one degree of freedom, i.e., a Cauchy distribution.
@@
 \end{equation}
-```
+
 With the similarity metrics defined for each space, we can then state the objective for "closeness" for the sets of points, which is the Kullback--Leibler divergence from Q to P:
 
-```{=tex}
 \begin{equation}
@@
 \end{equation}
-```
+
 We now circle back to Equation \@ref(eq:pji) and discuss $\sigma_i$.
@@
 
-```{=tex}
 \begin{equation}
 Perp(P_i) = 2^{H(P_i)},
-\end{equation}```
+\end{equation}
 where $H(P_i)$ denotes the entropy of $P_i$,
 
-```{=tex}
 \begin{equation}
@@
 \end{equation}
-```
+
 and $P_i$ is the Gaussian parameterized by $x_i$ and $\sigma_i$.
@@
 In addition, for our use case, which is to explore the learned embeddings, we have fewer data points than most other applications in the literature.
-Accordingly, our reaosnable range of hyperparameter values need to be adjusted down.
+Accordingly, our reasonable range of hyperparameter values need to be adjusted down.
 In Figures \@ref(fig:flood-zone-tsne), we display the t-SNE of the learned embeddings for `flood_zone` in Model 3 with various perplexity settings: 2, 3, 5, and 10; the learning rate and the number of steps are fixed at 100 and 10,000, respectively, for all plots.
@@
 Investigate approaches for using embedding layers for numeric variables, or numeric variables that were captured as 
-categorical variables (Can the Modeling of numerical variables benefit from the application of embedding layers?) How 
+categorical variables (Can the modeling of numerical variables benefit from the application of embedding layers?) How 
 should this best be done? CatBoost - cut into 256 groups smoothness Map numeric to a dense layer and use that as 
@@
 ```
-# Attention based Modeling {#attention_models}
+# Attention based modeling {#attention_models}
 
@@
 
-Compared to the models presented in the previous section, the models presented here are closer to state of the art models that might be used for tabular data Modeling problems.
+Compared to the models presented in the previous section, the models presented here are closer to state of the art models that might be used for tabular data modeling problems.
 To the best of our knowledge, this is the first analysis of these architectures within the actuarial literature.
@@
 The final model we consider in this subsection is the TabNet architecture.
-The structure of the model is quite similar to Model 6, except that a more specialized form of self-attention is used to select the most important covariates for the Modeling problem.
+The structure of the model is quite similar to Model 6, except that a more specialized form of self-attention is used to select the most important covariates for the modeling problem.
 
@@
 The results show that Model 5, which simply adds attention to Model 4, outperforms Model 4 on both the RMSE and MAE metrics.
-Thus, there is some room to argue that for tabular data Modeling that uses embeddings for categorical data, the use of attention within models should be considered.
-Disappointingly, the TabNet architecture performs poorly, perhaps due to insufficient hyperparameter tuning, but indicating that \`\`out of the box", TabNet does not appear to work well for this Modeling task.
+Thus, there is some room to argue that for tabular data modeling that uses embeddings for categorical data, the use of attention within models should be considered.
+Disappointingly, the TabNet architecture performs poorly, perhaps due to insufficient hyperparameter tuning, but indicating that \`\`out of the box", TabNet does not appear to work well for this modeling task.
 Finally, the TabTransformer model shows the best performance of all models considered in this research, beating the other models by a significant margin on both the RMSE and MAE metrics.
@@
 
-This study has focused on how embeddings can be applied within the context of actuarial Modeling, by illustrating a range of approaches: first, relatively simple neural networks with embeddings were defined, the embeddings from these models were reused within traditional GLM models and, finally, more advanced attention based models were studied.
-These models were demonstrated within the context of a claims severity Modeling problem based on data from the NFIP.
-Whereas we have only considered severity in this study, it is likely that our findings will replicate for the Modeling of claim frequency, which is usually an easier problem.
+This study has focused on how embeddings can be applied within the context of actuarial modeling, by illustrating a range of approaches: first, relatively simple neural networks with embeddings were defined, the embeddings from these models were reused within traditional GLM models and, finally, more advanced attention based models were studied.
+These models were demonstrated within the context of a claims severity modeling problem based on data from the NFIP.
+Whereas we have only considered severity in this study, it is likely that our findings will replicate for the modeling of claim frequency, which is usually an easier problem.
 Our key findings are that processing categorical variables with multi-dimensional embeddings leads to enhanced performance within simple neural networks, and that, by including these within traditional GLM models, the predictive performance of these models can be enhanced, compared to the usual encoding scheme for categorical variables.
-Some of the attention based models considered within this study performed well, in particular, the TabTransformer model of @Huang2020 appears quite promising for use in actuarial Modeling.
+Some of the attention based models considered within this study performed well, in particular, the TabTransformer model of @Huang2020 appears quite promising for use in actuarial modeling.
 The study has also illustrated how embeddings can be visualized using the PCA and t-SNE techniques.
@@
 Several avenues for future research can be considered.
-One surprising finding of our work is that the TabNet model performed quite poorly, leading us to conclude that this model appears to be less suitable for actuarial Modeling.
+One surprising finding of our work is that the TabNet model performed quite poorly, leading us to conclude that this model appears to be less suitable for actuarial modeling.
 Understanding these findings in more detail would be a valuable contribution to the literature.
-Another helpful contribution would be to investigate the optimal hyperparameters for the TabTransformer model in the context of actuarial Modeling.
+Another helpful contribution would be to investigate the optimal hyperparameters for the TabTransformer model in the context of actuarial modeling.
 Finally, extending our findings to a claims frequency example could be considered.
@@
 In this appendix we present an exploratory data analysis of the NFIP claims dataset.
-
-Figure \@ref(fig:sev) shows the distribution of the claim size that we model in this study. It can be seen that claim size varies over several orders of magnitude.
+Figure \@ref(fig:sev) shows the distribution of the claim size that we model in this study.
+It can be seen that claim size varies over several orders of magnitude.
+Figure \@ref(fig:loglog) shows the claim size seemingly follows a relatively heavy-tailed distribution.
+Figures \@ref(fig:catprimres) - \@ref(fig:catflood) illustrate the distribution of the categorical covariates within the dataset.
+Similarly, Figures \@ref(fig:numcov) - \@ref(fig:numdisc) illustrate the distribution of the continuous covariates within the dataset.
 
@@
 
-Figure \@ref(fig:loglog) shows the claim size seemingly follows a relatively heavy-tailed distribution.
-
 ```{r loglog, echo = FALSE, fig.cap = "Log-log plot of Claim amount", out.width = "60%", fig.align = "center"}
@@
 ```
-
-Figures \@ref(fig:catprimres) - \@ref(fig:catflood) illustrate the distribution of the categorical covariates within the dataset.
 
@@
 
-Similarly, Figures \@ref(fig:numcov) - \@ref(fig:numdisc) illustrate the distribution of the continuous covariates within the dataset.
-
 ```{r numcov, echo = FALSE, fig.cap = "Histogram of the Building Coverage covariate", out.width = "60%", fig.align = "center"}

### 2021-04-08 manuscript/manuscript.Rmd
bunch of edits

@@
     affiliation: RStudio and Kasa AI
-    email: kevin@kasa.ai
+    email: kevinykuo@gmail.com 
   - name: Ronald Richman
-    affiliation: QED Actuaries and Consultants
-    email: ronaldrichman@gmail.com
+    affiliation: QED Actuaries and Consultants and University of the Witwatersrand
+    email: ron@ronaldrichman.co.za
 abstract: |
-  Enter the text of your abstract here.
+  Categorical data are ubiquitous in insurance modeling. In this paper, we explore in depth how these data can be
+  processed with categorical embeddings in the context of claim severity modeling. We develop several models that range
+  in complexity from simple neural networks to state-of-the-art attention based architectures and calibrate categorical
+  embeddings using these models. We illustrate the utility of these learned embeddings as pretrained features in a
+  generalized linear model. We discuss methods for visualizing and interpreting learned embeddings. Finally, we explore
+  how attention based models can contextually augment embeddings, leading to enhanced predictive performance.
 keywords:
@@
 Although neural network have been shown to achieve excellent predictive accuracy on actuarial tasks, many actuaries still prefer to use GLM models for pricing tasks, thus, the issue of whether transferring embeddings to GLM models can achieve better performance is considered in this paper.
-<!-- Traditional actuarial techniques such as credibility theory have been used to work with some types of categorical data, but no study has been --> <!-- performed whether this can be applied within embeddings; here, we investigate whether performance is enhanced by applying credibility theory on embeddings
-relating to categorical variables with many labels. Whereas embedding layers are usually considered in the context of categorical data,the 
-option exists to quantize numerical data and model it using embeddings, however, the results of doing so have not been investigated.
---> Finally, in the past several years, a new type of neural network architecture based on attention [@Vaswani2017] has been successfully used on embeddings in the field of natural language processing and we incorporate attention based models into our predictive modeling example to demonstrate the use of these models for actuarial purposes.
+Finally, in the past several years, a new type of neural network architecture based on attention [@Vaswani2017] has been successfully used on embeddings in the field of natural language processing and we incorporate attention based models into our predictive modeling example to demonstrate the use of these models for actuarial purposes.
 
 In this work, we utilize the recently released National Flood Insurance Program (NFIP) dataset [@FederalEmergencyManagementAgency2019] which provides exposure information for policies written under the NFIP, as well as the claims data relating to these exposures.
-We refer the reader to Appendix \ref{EDA} for an exploratory analysis of this dataset.
 
@@
 Section \ref{defns} provides the notation used in the paper and defines GLMs, neural networks and related modeling concepts, including embeddings and attention.
-In Section \ref{modeling}, we provide initial models for the NFIP dataset and consider the influence of hyperparameter choices on the results of the neural network model.
-That section also considers how successfully the embeddings used in the neural network model can be transferred to a GLM model of the same data and how learned embeddings can be interpreted.
+In Section \ref{modeling}, we provide initial models for the NFIP dataset and consider how successfully the embeddings used in the neural network model can be transferred to a GLM model of the same data and how learned embeddings can be interpreted.
 We focus on attention based models in Section \ref{attention_models}.
@@
 
-Contemporaneous with that work is the DeepTriangle model of @Kuo2019, which applied recurrent neural networks to the problem of Incurred but not Reported (IBNR) loss reserving, to model jointly the paid and incurred losses in the Schedule P dataset.
+Contemporaneous with that work is the DeepTriangle model of @Kuo2019, which applied recurrent neural networks to the problem of Incurred but not Reported (IBNR) loss reserving, to model jointly the paid and incurred losses in the NAIC Schedule P dataset.
 Embedding layers were used to capture the effect of differences in reserving delays and loss ratios for each company in the Schedule P dataset.
-Evaluating the results of the DeepTriangle method showed that the out of sample performance of the model (tested against the lower triangles in the Schedule P dataset) exceeded that of traditional IBNR reserving techniques.
 
@@
 
-The predictor variables that we consider here are comprised of two types: continuous variables, taking on numerical values and represented by the matrix $X_{num}$ with $J^{num}$ columns, and categorical variables, which take on discrete values indicating one of several possible categories, represented by the matrix $X_{cat}$ with $J^{cat}$ columns, such that $J^{num} + J^{cat} = J$.
+The predictor variables that we consider here are comprised of two types: continuous variables, taking on numerical values and represented by the matrix $X_{num}$ with $|J^{num}|$ columns, and categorical variables, which take on discrete values indicating one of several possible categories, represented by the matrix $X_{cat}$ with $|J^{cat}|$ columns, such that $|J^{num}| + |J^{cat}| = J$.
 
@@
 
-A categorical variable $X_j, j \in J_{cat}$ takes as its value only one of a finite number of labels.
+A categorical variable $X_j, j \in J^{cat}$ takes as its value only one of a finite number of labels.
 Let the set of labels be $\mathcal{P}^j = \{p^j_1, p^j_2,\dots, p^j_{n_{\mathcal{P}^j}} \}$, where $n_\mathcal{P}^j = |\mathcal{P}^j|$ is the cardinality or number of levels, in $\mathcal{P}^j$.
@@
 The working example for our experiments is as follows: Given a set of claim characteristics, we predict the losses paid on the property coverage of the policy.
-The data we use comes from the National Flood Insurance Program (NFIP) and is made available by the OpenFEMA initiative of the Federal Emergency Management Agency (FEMA)[^1].
+The data we use comes from the NFIP and is made available by the OpenFEMA initiative of the Federal Emergency Management Agency (FEMA)[^1].
 Two datasets are made available by OpenFEMA: A policies dataset with exposure information, and a claims dataset with claims transactions, including paid amounts.
@@
 While the complete dataset contains over two million transactions, for the purposes of our experiments, we limit ourselves to data from 2000 to 2019 and further subsample 100K data points to make experiments feasible on a CPU.
-The dataset includes a rich variety of variables, from occupancy type to flood zone.
+The dataset includes a rich variety of variables, from occupancy type to flood zone, and a brief exploratory data analysis can be found in Appendix \ref{EDA}.
 For our models, we work with a few selected variables that represent continuous and discrete variables of low and high cardinalities, which we list in Table \@ref(tab:variables)
@@
 We note that the focus of our contribution is on applications of categorical embeddings in predictive modeling, rather than on fine-tuning models in order to beat or establish a benchmark.
-To this end, we do not perform systematic hyperparameter tuning in our experiments, and the performance metrics are provided to show that reasonable models utilizing categorical embeddings can be developed (note in the next section, the models achieve significantly better performance).
+To this end, we do not perform systematic hyperparameter tuning in our experiments, and the performance metrics are provided to show that reasonable models utilizing categorical embeddings can be developed.
 However, as we describe the modeling procedure and results, we provide commentary on recommended practices in practical applications, especially with respect to the neural network models.
@@
 ```{r occ-type, echo=FALSE, fig.cap="Learned embeddings of occupancy type visualized on a number line.", out.width = "80%", fig.align="center"}
-knitr::include_graphics("images/occupancy_type.png")
+knitr::include_graphics("images/occupancy_type_embed.png")
 ```
@@
 ```{r flood-zone, echo = FALSE, fig.cap="Learned embeddings of flood zone by prefix.", out.width = "60%", fig.align = "center"}
-knitr::include_graphics("images/flood_zone.png")
+knitr::include_graphics("images/flood_zone_embed.png")
 ```
@@
 In the first three plots, we can see the semblance of clusters forming.
-In particular, flood zone D appears in its own cluster, which implies it is far away from other levels in the embedding space.
+In particular, flood zone D appears in its own cluster, which implies it is far away from other levels in the embedding space, *as seen by the model*.
 When the perplexity is set to 10 (and beyond), however, we start to lose the geometric properties.
@@
 In terms of differences, Model 6 uses a Transformer layer in place of self-attention and a positional encoding of a single dimension, i.e.
-$d_col = 1$.
+$d_{col} = 1$.
 The TabTransformer architecture is shown in Figure \@ref(fig:nn-3).
@@
 To investigate the predictive value added by the contextual embeddings, a simple Gamma GLM was fit to these 10 000 observations, with the goal of predicting the claim amount based only on either the embeddings or the contextual embeddings.
-As shown in Table \@ref(tab:emd-vs-cembd), the performance of the latter model, as indicated by the RMSE and MAE metrics is significantly better, in other words, the contextual embeddings that incorporate information across all of the categorical variables are significantly better predictors of claim severity compared with the embeddings.
+As shown in Table \@ref(tab:emd-vs-cembd), the performance of the latter model, as indicated by the RMSE and MAE metrics is better, in other words, the contextual embeddings that incorporate information across all of the categorical variables are better predictors of claim severity compared with the embeddings.
 

### 2021-04-08 manuscript/manuscript.Rmd
final edits

@@
 ---
-title: Categorical Predictor Embeddings and Attention Based Neural Networks in Actuarial Modeling
+title: Embeddings and Attention in Predictive Modeling 
 authors:
@@
 abstract: |
-  Categorical data are ubiquitous in insurance modeling. In this paper, we explore in depth how these data can be
-  processed with categorical embeddings in the context of claim severity modeling. We develop several models that range
-  in complexity from simple neural networks to state-of-the-art attention based architectures and calibrate categorical
-  embeddings using these models. We illustrate the utility of these learned embeddings as pretrained features in a
-  generalized linear model. We discuss methods for visualizing and interpreting learned embeddings. Finally, we explore
+  We explore in depth how categorical data can be
+  processed with embeddings in the context of claim severity modeling. We develop several models that range
+  in complexity from simple neural networks to state-of-the-art attention based architectures that utilize embeddings. 
+  We illustrate the utility of learned embeddings from neural networks as pretrained features in
+  generalized linear models, and discuss methods for visualizing and interpreting embeddings. Finally, we explore
   how attention based models can contextually augment embeddings, leading to enhanced predictive performance.
@@
 
+\newpage
+
 ## Models
@@
 
-The final model we consider in this subsection is the TabNet architecture.
-The structure of the model is quite similar to Model 6, except that a more specialized form of self-attention is used to select the most important covariates for the modeling problem.
+The final model we consider in this subsection is the TabNet architecture. In TabNet, similar to decision trees which 
+it is inspired by, the input features are processed
+sequentually in a number of decision steps. In each decision step, a different subset of features are weighted more
+than the rest based on masks defined by attention modules applied to information from the previous step. The output
+of each step consists of information for the next decision step, and also an output representation that is set aside 
+then aggregated at the end, along with other decision step outputs, in order to product the final model output.
+Due to the complexity, we refer the reader to @Ark2019 for the full architectural details.
 

### 2021-04-08 manuscript/manuscript.Rmd

@@
 Thus, there is some room to argue that for tabular data modeling that uses embeddings for categorical data, the use of attention within models should be considered.
-Disappointingly, the TabNet architecture performs poorly, perhaps due to insufficient hyperparameter tuning, but indicating that \`\`out of the box", TabNet does not appear to work well for this modeling task.
+The TabNet architecture performs poorly, perhaps due to insufficient hyperparameter tuning, but indicating that *out of the box*, TabNet does not appear to work well for this modeling task.
 Finally, the TabTransformer model shows the best performance of all models considered in this research, beating the other models by a significant margin on both the RMSE and MAE metrics.
@@
 We focus on the difference between the flood embedding learned by the model, compared with the output of the Transformer layer that processes the embeddings before these enter the model.
-@Huang2020 call the latter \`\`contextual embeddings", because the attention mechanism within the TabTransformer model augments the embeddings based on the other covariates that appear for each observation $i$.
+@Huang2020 call the latter *contextual embeddings*, because the attention mechanism within the TabTransformer model augments the embeddings based on the other covariates that appear for each observation $i$.
 

### 2022-03-22 manuscript/manuscript.Rmd
fix model result table row labels

@@
 | Model 5: Simple Attention                           | 60,601 | 36,739 |
-| Model 6: TabNet                                     | 62,938 | 38,386 |
-| Model 7: TabTransformer                             | 59,900 | 36,343 |
+| Model 6: TabTransformer                             | 59,900 | 36,343 |
+| Model 7: TabNet                                     | 62,938 | 38,386 |
 | Linear regression, predictions capped below at 0.01 | 60,879 | 38,431 |

### 2022-03-27 manuscript/manuscript.Rmd
address 'nothing more than a glm' comment
add comment about being careful w/ train/validation split for embedding training -> glm

@@
 
-If $K$ is set equal to $1$, then Equation \ref{NN} reduces to nothing more than a GLM.
+If $K$ is set equal to $1$, then Equation \ref{NN} reduces to a form similar to the GLM, where $\sigma$ is analogous to the link function and $a_1X+b_1$ the linear predictor.
 A neural network with $K=2$ is called a shallow neural network and for $K \geq 2$, the network is called a deep neural network.
@@
 The modeler would need to balance the potential additional lift with overfitting and some loss of interpretability, since, with one-dimensional embeddings, our GLM structure dictates that there is a monotonic relationship between the predicted response and the input embedding, which could be desirable in certain use cases (and undesirable in others.)
+
+Regardless of the hyperparameters chosen, care needs to be taken in ensuring the integrity of the model validation process, since when we train
+the embeddings, we utilize the information from the response variables. Therefore, the holdout data must not be seen by the neural network
+training process or the GLM fitting process.
 

### 2022-03-27 manuscript/manuscript.Rmd
elaborate on glm with embeddings

@@
 Since we only have a few parameters in this model, we exhibit the full list of fitted coefficients in Table \@ref(tab:glm2). 
+For each categorical variable, there is only one coefficient estimate. This is because each categorical variable has been replaced by a
+single scalar value, so we treat it as if it were any other continuous predictor.
+
+One interesting ramification of our choice of embedding dimension of 1 in this example is that we can compute the "implied relativities"
+of the factor levels in the new GLM. Since each level corresponds to a unique scalar value, we can obtain its contribution to the
+linear predictor by multiplying by the coefficient estimate of the variable. For example, multiplying the estimate of -0.075 for `occupancy_type` in
+Table \@ref(tab:glm2) by each value in Table \@ref(tab:embeddings-flood-zone), we obtain the unnormalized contributions of each level, which can
+then be exponentiated and normalized with respect to the base level `Single family residence` in order to obtain the implied relativities,
+which could then be compared with the first GLM's output in Table \@ref(tab:relativities).
 

### 2022-03-29 manuscript/manuscript.Rmd
color changes in blue

--- 2022-03-22 manuscript/manuscript.Rmd
@@
 
-If $K$ is set equal to $1$, then Equation \ref{NN} reduces to nothing more than a GLM.
-A neural network with $K=2$ is called a shallow neural network and for $K \geq 2$, the network is called a deep neural network.
+If $K$ is set equal to $1$, then Equation \ref{NN} reduces to a \textcolor{blue}{form similar to the GLM, where $\sigma$ is analogous to the link function and $a_1X+b_1$ the linear predictor.} A neural network with $K=2$ is called a shallow neural network and for $K \geq 2$, the network is called a deep neural network.
 The matrix $X$ of data input to the network can be composed of both continuous variables as well as categorical variables, which can be pre-processed using one-hot or dummy encoding.
@@
 
-Since we only have a few parameters in this model, we exhibit the full list of fitted coefficients in Table \@ref(tab:glm2).
+\textcolor{blue}{Regardless of the hyperparameters chosen, care needs to be taken in ensuring the integrity of the model validation process, since when we train the embeddings, we utilize the information from the response variables.
+Therefore, the holdout data must not be seen by the neural network training process or the GLM fitting process.}
+
+\textcolor{blue}{Since we only have a few parameters in this model, we exhibit the full list of fitted coefficients in Table} \@ref(tab:glm2). 
+\textcolor{blue}{For each categorical variable, there is only one coefficient estimate. This is because each categorical variable has been replaced by a
+single scalar value, so we treat it as if it were any other continuous predictor.}
+
+\textcolor{blue}{One interesting ramification of our choice of embedding dimension of 1 in this example is that we can compute the "implied relativities" of the factor levels in the new GLM.
+Since each level corresponds to a unique scalar value, we can obtain its contribution to the linear predictor by multiplying by the coefficient estimate of the variable.
+For example, multiplying the estimate of -0.075 for} `occupancy_type` in Table \@ref(tab:glm2) \textcolor{blue}{by each value in Table} \@ref(tab:embeddings-flood-zone), \textcolor{blue}{we obtain the unnormalized contributions of each level, which can then be exponentiated and normalized with respect to the base level} `Single family residence` \textcolor{blue}{in order to obtain the implied relativities, which could then be compared with the first GLM's output in Table} \@ref(tab:relativities).
 
@@
 | Model 5: Simple Attention                           | 60,601 | 36,739 |
-| Model 6: TabTransformer                             | 59,900 | 36,343 |
-| Model 7: TabNet                                     | 62,938 | 38,386 |
+| \textcolor{blue}{Model 6: TabTransformer}                             | 59,900 | 36,343 |
+| \textcolor{blue}{Model 7: TabNet}                                     | 62,938 | 38,386 |
 | Linear regression, predictions capped below at 0.01 | 60,879 | 38,431 |

### 2022-03-29 manuscript/manuscript.Rmd
move pca/tsne technical stuff to appendix

@@
 Specifically, we need to reduce the dimension of the data to 2D for embeddings with more than two dimensions.
-The standard approachs for this are principal component analysis (PCA; @shlens2014tutorial) and t-distributed stochastic neighbor embedding (t-SNE; @Maaten2008a), both of which we illustrate.
-
-### Principal Component Analysis
-
-In both approaches, the overarching theme is as follows: we have a collection of points in higher dimensional space, $\mathcal{X} = \{x_1, x_2, \dots, x_n\}$ that we wish to map to some lower dimensional space, typically $\mathbb{R}^2$, obtaining $\mathcal{Y} = \{y_1, y_2, \dots, y_n\}$.
-PCA performs a linear change of coordinates on the input data so that the variance of the data is maximized along each orthogonal coordinate, also known as *principal component*, successively.
-Formally, if we denote $\mathbf{X}$ and $\mathbf{Y}$ to be the matrices whose columns are elements of $\mathcal{X}$ and $\mathcal{Y}$, respectively, this can be represented as looking for an orthonormal matrix $\mathbf{P}$ in $\mathbf{Y} = \mathbf{PX}$ such that the covariance matrix of $\mathbf{Y}$, $\frac{1}{n}\mathbf{YY^T}$, is diagonal.
-Here, the rows of $\mathbf{P}$ are the principal components that define the resulting coordinate system.
-It turns out that that these principal components are the eigenvectors of the covariance matrix of $\mathbf{X}$, i.e., $\mathbf{C_X} \equiv \frac{1}{n}\mathbf{XX^T}$.
-In practice, numerical procedures, including R's \texttt{prcomp()} which we use, utilize singular value decomposition (SVD) to compute the eigenvectors.
+The standard approaches for this are principal component analysis (PCA; @shlens2014tutorial) and t-distributed stochastic neighbor embedding (t-SNE; @Maaten2008a), both of which we illustrate.
+For a technical review of these methods, refer to Appendix \ref{dim-red].
 
@@
 
-### t-Distributed Stochastic Neighbor Embedding
-
-In contrast with PCA, t-SNE is a nonlinear technique.
-At a high level, it computes a similarity metric, in the form of conditional probabilities based on pairwise distances, among points in $\mathcal{X}$, then look for points $\mathcal{Y}$ in the lower dimensional space which have similarity metric values (for a differently defined metric) that are "close" to those of corresponding pairs of points in the original data.
-
-Let $p_{j|i}$ denote the probability that point $x_i$ picks point $x_j$ as its *neighbor*, if it picks neighbors in proportion to its density under an $n$-dimension Gaussian centered at $x_i$.
-Formally, we can write $p_{j|i}$ as
-
-\begin{equation}
-p_{j|i} = \frac{\exp(\norm{x_i - x_j}^2 / 2\sigma_i^2)}{\sum_{k\neq i} \exp(-\norm{x_i - x_k}^2 / 2\sigma_i^2)}, (\#eq:pji)
-\end{equation} where $\sigma_i^2$ denotes the variance of the Gaussian associated with $x_i$. The similarity metric for the original space symmetrizes this conditional probability and is defined as
-
-\begin{equation}
-p_{ij} = \frac{p_{j|i} + p_{i|j}}{2n}.
-\end{equation}
-
-On the other hand, in the target space, t-SNE assumes the neighbor selection is driven by a Student t-distribution with one degree of freedom, i.e., a Cauchy distribution.
-The similarity metric for a pair of points in $\mathcal{Y}$ is then defined as the joint probability
-
-\begin{equation}
-q_{ij} = \frac{(1 + \norm{y_i - y_j}^2)^{-1}}{\sum_{k \neq l} (1 + \norm{y_k - y_l}^2)^{-1}}.
-\end{equation}
-
-With the similarity metrics defined for each space, we can then state the objective for "closeness" for the sets of points, which is the Kullback--Leibler divergence from Q to P:
-
-\begin{equation}
-D_{KL}(P || Q) = \sum_{i \neq j} p_{ij} \log \frac{p_{ij}}{q_{ij}}. (\#eq:tsne-obj)
-\end{equation}
-
-We now circle back to Equation \@ref(eq:pji) and discuss $\sigma_i$.
-The variance of the Gaussian is allowed to vary depending on where the point is in the space; specifically, it should reflect the density or sparsness of surrounding points.
-To train this parameter, t-SNE introduces a hyperparameter, *perplexity*, which is a scalar value set by the user, and is defined as
-
-\begin{equation}
-Perp(P_i) = 2^{H(P_i)},
-\end{equation}
-where $H(P_i)$ denotes the entropy of $P_i$,
-
-\begin{equation}
-H(P_i) = -\sum_j p_{j|i}\log_2 p_{j|i},
-\end{equation}
-
-and $P_i$ is the Gaussian parameterized by $x_i$ and $\sigma_i$.
-During training, t-SNE looks for $P_i$ that have perpelxity corresponding to the user input.
-Finally, the objective as stated in Equation \@ref(eq:tsne-obj) is differentiable, and is trained via gradient descent.
-
-While t-SNE is a powerful visualization technique, there are a few points the modeler should be mindful of in practice.
-We refer the reader to @wattenberg2016how for a more thorough discussion, but stress here that the resulting plot can be very sensitive to the perplexity hyperparameter.
-In addition, for our use case, which is to explore the learned embeddings, we have fewer data points than most other applications in the literature.
-Accordingly, our reasonable range of hyperparameter values need to be adjusted down.
 In Figures \@ref(fig:flood-zone-tsne), we display the t-SNE of the learned embeddings for `flood_zone` in Model 3 with various perplexity settings: 2, 3, 5, and 10; the learning rate and the number of steps are fixed at 100 and 10,000, respectively, for all plots.
@@
 When the perplexity is set to 10 (and beyond), however, we start to lose the geometric properties.
+While t-SNE is a powerful visualization technique, there are a few points the modeler should be mindful of in practice.
+We refer the reader to @wattenberg2016how for a more thorough discussion, but stress here that the resulting plot can be very sensitive to the perplexity hyperparameter.
+In addition, for our use case, which is to explore the learned embeddings, we have fewer data points than most other applications in the literature.
+Accordingly, our reasonable range of hyperparameter values are adjusted down.
 
@@
 
+# Dimensionality Reduction Techniques {#dim-red}
+
+## Principal Component Analysis
+
+In both approaches, the overarching theme is as follows: we have a collection of points in higher dimensional space, $\mathcal{X} = \{x_1, x_2, \dots, x_n\}$ that we wish to map to some lower dimensional space, typically $\mathbb{R}^2$, obtaining $\mathcal{Y} = \{y_1, y_2, \dots, y_n\}$.
+PCA performs a linear change of coordinates on the input data so that the variance of the data is maximized along each orthogonal coordinate, also known as *principal component*, successively.
+Formally, if we denote $\mathbf{X}$ and $\mathbf{Y}$ to be the matrices whose columns are elements of $\mathcal{X}$ and $\mathcal{Y}$, respectively, this can be represented as looking for an orthonormal matrix $\mathbf{P}$ in $\mathbf{Y} = \mathbf{PX}$ such that the covariance matrix of $\mathbf{Y}$, $\frac{1}{n}\mathbf{YY^T}$, is diagonal.
+Here, the rows of $\mathbf{P}$ are the principal components that define the resulting coordinate system.
+It turns out that that these principal components are the eigenvectors of the covariance matrix of $\mathbf{X}$, i.e., $\mathbf{C_X} \equiv \frac{1}{n}\mathbf{XX^T}$.
+In practice, numerical procedures, including R's \texttt{prcomp()} which we use, utilize singular value decomposition (SVD) to compute the eigenvectors.
+
+## t-Distributed Stochastic Neighbor Embedding
+
+In contrast with PCA, t-SNE is a nonlinear technique.
+At a high level, it computes a similarity metric, in the form of conditional probabilities based on pairwise distances, among points in $\mathcal{X}$, then look for points $\mathcal{Y}$ in the lower dimensional space which have similarity metric values (for a differently defined metric) that are "close" to those of corresponding pairs of points in the original data.
+
+Let $p_{j|i}$ denote the probability that point $x_i$ picks point $x_j$ as its *neighbor*, if it picks neighbors in proportion to its density under an $n$-dimension Gaussian centered at $x_i$.
+Formally, we can write $p_{j|i}$ as
+
+\begin{equation}
+p_{j|i} = \frac{\exp(\norm{x_i - x_j}^2 / 2\sigma_i^2)}{\sum_{k\neq i} \exp(-\norm{x_i - x_k}^2 / 2\sigma_i^2)}, (\#eq:pji)
+\end{equation} where $\sigma_i^2$ denotes the variance of the Gaussian associated with $x_i$. The similarity metric for the original space symmetrizes this conditional probability and is defined as
+
+\begin{equation}
+p_{ij} = \frac{p_{j|i} + p_{i|j}}{2n}.
+\end{equation}
+
+On the other hand, in the target space, t-SNE assumes the neighbor selection is driven by a Student t-distribution with one degree of freedom, i.e., a Cauchy distribution.
+The similarity metric for a pair of points in $\mathcal{Y}$ is then defined as the joint probability
+
+\begin{equation}
+q_{ij} = \frac{(1 + \norm{y_i - y_j}^2)^{-1}}{\sum_{k \neq l} (1 + \norm{y_k - y_l}^2)^{-1}}.
+\end{equation}
+
+With the similarity metrics defined for each space, we can then state the objective for "closeness" for the sets of points, which is the Kullback--Leibler divergence from Q to P:
+
+\begin{equation}
+D_{KL}(P || Q) = \sum_{i \neq j} p_{ij} \log \frac{p_{ij}}{q_{ij}}. (\#eq:tsne-obj)
+\end{equation}
+
+We now circle back to Equation \@ref(eq:pji) and discuss $\sigma_i$.
+The variance of the Gaussian is allowed to vary depending on where the point is in the space; specifically, it should reflect the density or sparsness of surrounding points.
+To train this parameter, t-SNE introduces a hyperparameter, *perplexity*, which is a scalar value set by the user, and is defined as
+
+\begin{equation}
+Perp(P_i) = 2^{H(P_i)},
+\end{equation}
+where $H(P_i)$ denotes the entropy of $P_i$,
+
+\begin{equation}
+H(P_i) = -\sum_j p_{j|i}\log_2 p_{j|i},
+\end{equation}
+
+and $P_i$ is the Gaussian parameterized by $x_i$ and $\sigma_i$.
+During training, t-SNE looks for $P_i$ that have perpelxity corresponding to the user input.
+Finally, the objective as stated in Equation \@ref(eq:tsne-obj) is differentiable, and is trained via gradient descent.
+
 \clearpage

### 2022-03-31 manuscript/manuscript.Rmd
Updates for review

@@
   - name: Ronald Richman
-    affiliation: QED Actuaries and Consultants and University of the Witwatersrand
+    affiliation: Old Mutual Insure and University of the Witwatersrand
     email: ron@ronaldrichman.co.za
@@
 
+```{=tex}
 \begin{equation} 
@@
 \end{equation}
-
+```
 where the regression parameters (weights) for each layer $k \in [1;K+1]$ are represented by the matrices $a_k$ and the intercept terms are represented by $b_k$.
@@
 \end{equation}
-
+```
 where $q_\mathcal{P}^j$ is the dimension of the embedding for the $j$th categorical variable and $z_\mathcal{P}^j(.)$ is an implicit function that maps from the particular element of the labels $p$ to the embedding space.
@@
 
-We note that the focus of our contribution is on applications of categorical embeddings in predictive modeling, rather than on fine-tuning models in order to beat or establish a benchmark.
-To this end, we do not perform systematic hyperparameter tuning in our experiments, and the performance metrics are provided to show that reasonable models utilizing categorical embeddings can be developed.
-However, as we describe the modeling procedure and results, we provide commentary on recommended practices in practical applications, especially with respect to the neural network models.
+\textcolor{blue}{Whereas the main focus of our contribution} is on applications of categorical embeddings in predictive modeling, \textcolor{blue}{we have fine-tuned the neural network models in this (and the next) sections using the same 5-fold cross validation scheme described above, but applied to a separate 100k data point subsample of the FEMA data.
+The results of this fine-tuning are reported in detail in the appendix.
+The performance metrics in this, and the next, section are based on the optimal models found through this process.
+Our aim is thos show that reasonable models utilizing categorical embeddings can be developed quite easily.
+As we describe the modeling procedure and results, we provide further commentary on recommended practices in practical applications, especially with respect to the neural network models.}
 
@@
 \end{equation}
-
+```
 one for the intercept, one for each numeric variable, and the numbers of levels minus one (due to dummy coding) for each categorical variable.
@@
 The categorical inputs go through one-dimensional embedding layers where they are each mapped to a scalar.
-The embeddings are then concatenated with the numeric predictors, which have been normalized in data pre-processing, before being passed through a feedforward layer (with 8 hidden units and ReLU activation) to obtain a scalar value between 0 and 1, as constrained by a sigmoid output activation.
-This scalar output represents the proportion of coverage amount that is paid out, which we then multiply by the dollar amount of the coverage amount to obtain our prediction of the claims paid.
+The embeddings are then concatenated with the numeric predictors, which have been normalized in data pre-processing, before being passed through a feedforward layer (with 8 hidden units and ReLU activation) to \textcolor{blue}{finally} obtain a scalar value between 0 and 1, as constrained by a sigmoid output activation.
+\textcolor{blue}{Some regularization is applied within this network using the dropout technique of} @srivastava2014dropout \textcolor{blue}{and by early-stopping the fitting of the network by selecting the model weights that relate to the lowest estimated MSE score on a 5\% validation sample.} This scalar output represents the proportion of coverage amount that is paid out, which we then multiply by the dollar amount of the coverage amount to obtain our prediction of the claims paid.
 For optimization, we use the mean squared error (MSE) loss function.
@@
 (\#eq:glm2)
-\end{equation}
-Hence, the model can be written as
+\end{equation} Hence, the model can be written as
 
+```{=tex}
 \begin{equation}
@@
 \end{equation}
-
+```
 where $z_{i,j}$ represents the embedding value for $i$th instance of the categorical column $X_j$.
@@
 \textcolor{blue}{Since we only have a few parameters in this model, we exhibit the full list of fitted coefficients in Table} \@ref(tab:glm2).
-\textcolor{blue}{For each categorical variable, there is only one coefficient estimate. This is because each categorical variable has been replaced by a
+\textcolor{blue}{For each categorical variable, there is only one coefficient estimate.
+This is because each categorical variable has been replaced by a
 single scalar value, so we treat it as if it were any other continuous predictor.}
@@
 The standard approaches for this are principal component analysis (PCA; @shlens2014tutorial) and t-distributed stochastic neighbor embedding (t-SNE; @Maaten2008a), both of which we illustrate.
-For a technical review of these methods, refer to Appendix \ref{dim-red].
+For a technical review of these methods, refer to Appendix \\ref{dim-red].
 
@@
 
-The final model we consider in this subsection is the TabNet architecture. In TabNet, similar to decision trees which 
-it is inspired by, the input features are processed
-sequentually in a number of decision steps. In each decision step, a different subset of features are weighted more
-than the rest based on masks defined by attention modules applied to information from the previous step. The output
-of each step consists of information for the next decision step, and also an output representation that is set aside 
-then aggregated at the end, along with other decision step outputs, in order to product the final model output.
+The final model we consider in this subsection is the TabNet architecture.
+In TabNet, similar to decision trees which it is inspired by, the input features are processed sequentually in a number of decision steps.
+In each decision step, a different subset of features are weighted more than the rest based on masks defined by attention modules applied to information from the previous step.
+The output of each step consists of information for the next decision step, and also an output representation that is set aside then aggregated at the end, along with other decision step outputs, in order to product the final model output.
 Due to the complexity, we refer the reader to @Ark2019 for the full architectural details.
@@
 ```
+# Finetuning the Neural Network Models
+Here we describe how the neural network models presented in Sections 4 and 5 above were fine-tuned.
+
+## Models in Section 4
+\textcolor{blue}{
+As noted before, a different 100k subsample of the NFIP dataset was produced for this purpose, and a 5-fold cross-validation scheme was implemented using this data.
+Two main hyperparameters were tuned for each of Model 2 and Model 4.
+Two different activation functions (the ReLu and hyperbolic tangent activation functions) and 5 different widths of the hidden layers (8, 16, 32, 64, 128) were tested.
+The following table shows these results for each of Model 2 and Model 4.}
+
+|  | ReLU/8 | ReLu/16 | ReLu/32 | ReLu/64 | ReLu/128 | tanh/8 | tanh/16 | tanh/32 | tanh/64 | tanh/128 |
+|---|---|---|---|---|---|---|---|---|---|---|
+| Model 2 - RMSE |          60 988  |          60 561  |          60 125  |          60 147  |          59 918  |          61 728  |          60 506  |          60 130  |          59 893  |          60 065  |
+| Model 4 - RMSE |          60 535  |          60 724  |          60 311  |          60 191  |          60 114  |          60 521  |          60 658  |          60 279  |          59 892  |          59 987  |
+| Model 2 - MAE |          36 604  |          36 791  |          36 936  |          37 140  |          36 816  |          37 206  |          36 759  |          36 921  |          37 103  |          37 177  |
+| Model 4 - MAE |          36 828  |          36 824  |          36 780  |          37 054  |          36 672  |          36 528  |          36 725  |          36 483  |          36 766  |          36 394  |
+: Results of fine-tuning models in Section 4.
+
+\textcolor{blue}{It can be observed that the lowest RMSE values are produced using the tanh activation function with a hidden layer width 64 neurons.}
+
+## Models in Section 5
+
+\textcolor{blue}{Models 5 and 6 add an attention-based mechanism to derive contextual embeddings to the models in Section 4.
+To find optimal hyperparameters, the best performing variation of Model 4 (tanh/64) was taken as a baseline, and the attention mechanisms described for Models 5 and 6 were added to this baseline.
+Since the performance of the models would ideally improve as a result of adding the attention mechanisms, and, indeed, we see this is the case in the following table, we do not attempt to fine-tune Models 5 and 6 any further.}
 
@@
 \end{equation}
-
+```
 On the other hand, in the target space, t-SNE assumes the neighbor selection is driven by a Student t-distribution with one degree of freedom, i.e., a Cauchy distribution.
@@
 \end{equation}
-
+```
 With the similarity metrics defined for each space, we can then state the objective for "closeness" for the sets of points, which is the Kullback--Leibler divergence from Q to P:
 
+```{=tex}
 \begin{equation}
@@
 \end{equation}
-
+```
 We now circle back to Equation \@ref(eq:pji) and discuss $\sigma_i$.
@@
 Perp(P_i) = 2^{H(P_i)},
-\end{equation}
-where $H(P_i)$ denotes the entropy of $P_i$,
+\end{equation} where $H(P_i)$ denotes the entropy of $P_i$,
 
+```{=tex}
 \begin{equation}
@@
 \end{equation}
-
+```
 and $P_i$ is the Gaussian parameterized by $x_i$ and $\sigma_i$.

### 2022-03-31 R/cv-model-keras.R

@@ -1,0 +1,626 @@
+library(tidyverse)
+library(recipes)
+library(rsample)
+library(torch)
+library(data.table)
+library(keras)
+require(tensorflow)
+tf$compat$v1 = T
+
+source("model-utils.R")
+source("data-loading.R")
+
+source("keras_working_file.R")
+source("keras_working_file_attn.R")
+source("keras_working_file_tabtrans.R")
+
+categorical_cols <- c(
+    "primary_residence", "basement_enclosure_crawlspace_type",
+    "number_of_floors_in_the_insured_building",
+    "occupancy_type", "flood_zone"
+)
+
+numeric_cols <- c("total_building_insurance_coverage", "community_rating_system_discount")
+response_col <- "amount_paid_on_building_claim"
+
+for_cv = small_data[1:100000,]
+for_test = small_data[100000:200000,]
+
+set.seed(420)
+cvfolds <- for_cv %>%
+    rsample::vfold_cv(v = 5)
+
+# ### code to test analysis function; comment out for full CV
+#
+# splits = cvfolds$splits[[1]]
+#
+# learning_rate = 0.001
+# epochs = 10
+# batch_size = 5000
+
+### first run - Section 4 models
+
+model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_size = 5000, ...) {
+
+    env <- new.env()
+    analysis_data <- analysis(splits)
+    assessment_data <- assessment(splits)
+
+    rec_nn <- recipe(amount_paid_on_building_claim ~ .,
+        data = analysis_data %>%
+            select(-loss_proportion, -reported_zip_code)
+    ) %>%
+        step_normalize(all_numeric(), -all_outcomes()) %>%
+        step_novel(all_nominal()) %>%
+        step_integer(all_nominal(), strict = TRUE, zero_based = FALSE) %>%
+        prep(strings_as_factors = TRUE)
+
+    juiced_train_data <- juice(rec_nn)
+    baked_test_data <- bake(rec_nn, assessment_data)
+    for_card = juiced_train_data %>% data.table()
+    for_card_test = baked_test_data %>% data.table()
+
+    output_list = get_output(for_card, for_card_test)
+
+    train_dl = juiced_train_data %>% get_keras_data()
+    test_dl = baked_test_data %>% get_keras_data()
+    actuals <- assessment_data %>%
+    pull(amount_paid_on_building_claim)
+
[…]

### 2022-03-31 R/data-loading.R

@@ -7,12 +7,55 @@ small_data <- claims %>%
         amount_paid_on_building_claim > 0,
         total_building_insurance_coverage > 0
     ) %>%
-    sample_n(100000) %>%
+    sample_n(300000) %>%
     select(
         amount_paid_on_building_claim, total_building_insurance_coverage,
         reported_zip_code, primary_residence, basement_enclosure_crawlspace_type,
         number_of_floors_in_the_insured_building, occupancy_type,
         community_rating_system_discount, flood_zone
     ) %>%
-    filter(across(everything(), ~!is.na(.x))) %>% 
+    filter(across(everything(), ~!is.na(.x))) %>%
     mutate(loss_proportion = pmin(amount_paid_on_building_claim / total_building_insurance_coverage, 1))
+
+get_keras_data = function(dat){
+  dat = dat %>% data.table
+  dat_list = list()
+  for (column in categorical_cols) dat_list[[column]] = as.matrix(dat[, get(column)])
+  dat_list[["num_input"]] = as.matrix(dat[, c(numeric_cols), with = F]) %>% unname
+
+  ### add column identifiers for TabTransformer
+
+  dat_list[["col_idx"]] = unname(as.matrix(reshape::untable(data.table(t(1:5)),dat[,.N])))
+  dat_list
+}
+
+get_embed_map = function(analysis_data, model, layer_start){
+  dat_list = list()
+  analysis_data = analysis_data %>% data.table
+  i = layer_start - 1
+  for (column in categorical_cols) {
+
+    i = i + 1
+    temp_lookup = data.table(cbind(analysis_data[, get(column)], analysis_data[, as.integer(as.factor(get(column)))])) %>% unique()
+    temp_lookup %>% setnames(temp_lookup %>% names, c(column, paste0(column, "int")))%>% setkeyv(eval(column))
+    embeds = data.table((model$layers[[i]] %>% get_weights())[[1]])
+    embeds=embeds[2:((analysis_data[, as.integer(as.factor(get(column)))] %>% max())+1)]
+    embeds_dim = ((model$layers[[i]] %>% get_weights())[[1]] %>% dim)[2]
+    temp_lookup[,  paste0(column, "_embed", "_", 1:embeds_dim) := data.table(as.matrix(embeds))]
+
+    dat_list[[column]] = temp_lookup %>% copy
+
+  }
+
+  dat_list
+
+}
+
+get_output = function(train, test, column = "amount_paid_on_building_claim"){
[…]

### 2022-03-31 R/keras_working_file.R

@@ -1,0 +1,80 @@
+get_keras_model = function(hidden_layer_units = 64, hidden_layer_activations = "relu",
+                           embed = 1, for_card, train_dl, test_dl, output_list) {
+
+k_clear_session()
+
+input_list = list()
+embedding_list = list()
+cardinalities = list()
+count = 0
+
+get_embed_dim = function(cards, embed){
+  if (embed == 1) {1}
+  else{
+  (trunc(cards/2)+1)
+  }
+}
+
+for (column in categorical_cols){
+  count = count + 1
+  cardinalities[[column]] = for_card[, max(get(column))]
+  input_list[[count]] = layer_input(shape = 1, dtype = "int32", name = column)
+  embed_dim = get_embed_dim(cardinalities[[column]], embed)
+  embedding_list[[count]] = input_list[[count]] %>%
+    layer_embedding(input_dim = cardinalities[[column]]*2+1, output_dim =embed_dim)  %>%
+    layer_flatten(name = paste0(column, "_embed"))
+}
+
+input_list[[count+1]] = layer_input(shape = numeric_cols %>% length, dtype = "float32", name = "num_input")
+
+embeddings = embedding_list %>% layer_concatenate()
+main = list(embeddings, input_list[[count+1]]) %>% layer_concatenate() %>%
+  layer_dense(units = hidden_layer_units, activation = "relu") %>%
+  layer_dropout(rate = 0.025)
+
+output = main %>%
+  layer_dense(units = 1, activation = "sigmoid", name = "output")
+
+model <- keras_model(
+  inputs = input_list,
+  outputs = c(output))
+
+adam = optimizer_adam(lr=0.001)
+
+model %>% compile(
+  loss = 'mean_squared_error',
+  optimizer = adam
+)
+
+lr_call = callback_reduce_lr_on_plateau(monitor = "val_loss", patience = 50, verbose = 1, cooldown = 5,
+                                        factor = 0.9, min_lr = 0.0001)
+mod_save = callback_model_checkpoint(filepath = paste0("c:/r/keras_mod.h5"), verbose = T, save_best_only = T)
+
+fit <- model %>% fit(x = train_dl,
+                     y= list(output = as.matrix(output_list$y_train)),
+                     epochs=150,
+                     batch_size=1024,
+                     verbose=2,
+                     validation_split = 0.05,
+                     shuffle=T,
[…]

### 2022-03-31 R/keras_working_file_attn.R

@@ -1,0 +1,78 @@
+get_keras_model_attn = function(hidden_layer_units = 64, embed = 1, for_card, train_dl, test_dl, output_list) {
+
+  k_clear_session()
+
+  input_list = list()
+  embedding_list = list()
+  cardinalities = list()
+  count = 0
+
+  get_embed_dim = function(cards, embed){
+    if (embed == 1) {1}
+    else{
+      if(embed ==0) {16}
+      else {(trunc(cards/2)+1)}
+    }
+  }
+
+  for (column in categorical_cols){
+    count = count + 1
+    cardinalities[[column]] = for_card[, max(get(column))]
+    input_list[[count]] = layer_input(shape = 1, dtype = "int32", name = column)
+    embed_dim = get_embed_dim(cardinalities[[column]], embed)
+    embedding_list[[count]] = input_list[[count]] %>%
+      layer_embedding(input_dim = cardinalities[[column]]*2+1, output_dim =embed_dim,name = paste0(column, "_embed"))
+  }
+
+  input_list[[count+1]] = layer_input(shape = numeric_cols %>% length, dtype = "float32", name = "num_input")
+
+  embeddings = embedding_list %>% layer_concatenate(axis = 1)
+  key = embeddings %>% (layer = layer_dense(units = 16))
+  query = embeddings %>% (layer = layer_dense(units = 16))
+  value = embeddings %>% (layer = layer_dense(units = 16))
+
+  attn = layer_attention(list(key, query, value), use_scale = T)
+  attn_flat = attn %>% layer_flatten() %>% layer_dropout(rate = 0.025)
+
+  main = list(attn_flat, input_list[[count+1]]) %>% layer_concatenate() %>%
+    layer_dense(units = 64, activation = "tanh") %>%
+    layer_dropout(rate = 0.025)
+
+  output = main %>%
+    layer_dense(units = 1, activation = "sigmoid", name = "output")
+
+  model <- keras_model(
+    inputs = input_list,
+    outputs = c(output))
+
+  adam = optimizer_adam(lr=0.001)
+
+  model %>% compile(
+    loss = 'mean_squared_error',
+    optimizer = adam
+  )
+
+  lr_call = callback_reduce_lr_on_plateau(monitor = "val_loss", patience = 50, verbose = 1, cooldown = 5,
+                                          factor = 0.9, min_lr = 0.0001)
+  mod_save = callback_model_checkpoint(filepath = paste0("c:/r/keras_mod.h5"), verbose = T, save_best_only = T)
+
[…]

### 2022-03-31 R/keras_working_file_tabtrans.R

@@ -1,0 +1,100 @@
+get_keras_model_tabtrans = function(hidden_layer_units = 64, embed = 0, for_card, train_dl, test_dl, output_list) {
+
+  k_clear_session()
+
+  input_list = list()
+  embedding_list = list()
+  cardinalities = list()
+  count = 0
+
+  get_embed_dim = function(cards, embed){
+    if (embed == 1) {1}
+    else{
+      if(embed ==0) {16}
+      else {(trunc(cards/2)+1)}
+    }
+  }
+
+  for (column in categorical_cols){
+    count = count + 1
+    cardinalities[[column]] = for_card[, max(get(column))]
+    input_list[[count]] = layer_input(shape = 1, dtype = "int32", name = column)
+    embed_dim = get_embed_dim(cardinalities[[column]], embed)
+    embedding_list[[count]] = input_list[[count]] %>%
+      layer_embedding(input_dim = cardinalities[[column]]*2+1, output_dim =embed_dim,name = paste0(column, "_embed"))
+  }
+
+  input_list[[count+1]] = layer_input(shape = numeric_cols %>% length, dtype = "float32", name = "num_input")
+  input_list[[count+2]] = layer_input(shape = 5, dtype = "int32", name = "col_idx")
+
+  col_idx_int = input_list[[count+2]] %>%
+    layer_reshape(c(5,1), name = "col_idx_int")
+
+  embeddings = embedding_list %>% layer_concatenate(axis = 1)
+  col_embed = layer_embedding(input_dim = 6, output_dim = 16)
+  col_embeds = col_idx_int %>% time_distributed(col_embed) %>% layer_reshape(c(5,16), name = "col_embeds")
+  all_embeds = list(embeddings, col_embeds) %>% layer_add()%>% layer_layer_normalization()
+
+  attn_heads = list()
+
+  for (i in 1:2){
+    key = all_embeds %>% (layer = layer_dense(units = 16))
+    query = all_embeds %>% (layer = layer_dense(units = 16))
+    value = all_embeds %>% (layer = layer_dense(units = 16))
+    attn = layer_attention(list(key, query, value), use_scale = T)
+    attn_heads[[i]] = attn
+  }
+
+  multi_head_attn = attn_heads %>% layer_concatenate(axis=2) %>% layer_dense(units = 16)
+  stage1 = list(all_embeds, multi_head_attn) %>% layer_add()
+
[…]

### 2022-03-31 R/results.R

@@ -1,0 +1,18 @@
+library(recipes)
+library(rsample)
+library(data.table)
+library(dplyr)
+
+dirs = "C:\\R\\embed-actuarial\\results\\"
+
+files = list.files(dirs)
+
+all_res = lapply(files, function (x) fread(paste0(dirs, x))) %>% rbindlist(fill = T) %>% data.table()
+
+all_res = all_res %>% melt.data.table(id.vars = c("run", "id"))
+melted = all_res[, mean(value), keyby = .(run, variable)] 
+melted = melted[order(run)]%>% 
+  dcast.data.table(variable~run) 
+
+melted[variable %in% c("rmse_nn", "rmse_nn2", "mae_nn", "mae_nn2")] %>% 
+  fwrite("c:/r/finetune_sect4.csv")

### 2022-04-10 manuscript/manuscript.Rmd
Ron final changes

@@
 The performance metrics in this, and the next, section are based on the optimal models found through this process.
-Our aim is thos show that reasonable models utilizing categorical embeddings can be developed quite easily.
+Our aim is to show that performant predictive models utilizing categorical embeddings can be developed quite easily, and that these models can be enhanced using suitable architectures utilizing attention mechanisms.
 As we describe the modeling procedure and results, we provide further commentary on recommended practices in practical applications, especially with respect to the neural network models.}
@@
 In Table \@ref(tab:relativities), we exhibit an exerpt of the relativities, or exponentiated fitted coefficients, of a couple of the categorical variables.
-Recall that the choice of the log link gives a multiplicative structure, so the interpretation of 1.34 for `occupancy_type = "Non-residential building"` is that, all else equal, the expected loss for a policy for a non-residential building is 1.34 times that of a policy for a single family home, which is the base, or reference, level for the factor.
+Recall that the choice of the log link gives a multiplicative structure, so the interpretation of 1.35 for `occupancy_type = "Non-residential building"` is that, all else equal, the expected loss for a policy for a non-residential building is 1.35 times that of a policy for a single family home, which is the base, or reference, level for the factor.
 
-| variable       | label                                       | relativity |
-|:---------------|:--------------------------------------------|-----------:|
-| occupancy_type | Single family residence                     |       1.00 |
-| occupancy_type | 2 to 4 unit residential buidling            |       1.10 |
-| occupancy_type | Non-residential building                    |       1.34 |
-| occupancy_type | Residential building with more than 4 units |       1.59 |
-| flood_zone     | C                                           |       1.00 |
-| flood_zone     | A                                           |       1.42 |
-| flood_zone     | X                                           |       1.18 |
-| flood_zone     | B                                           |       1.65 |
-| flood_zone     | V                                           |       1.38 |
-| flood_zone     | D                                           |       1.45 |
+|variable       |label                                       | relativity|
+|:--------------|:-------------------------------------------|----------:|
+|occupancy_type |Single family residence                     |       1.00|
+|occupancy_type |2 to 4 unit residential buidling            |       1.11|
+|occupancy_type |Non-residential building                    |       1.35|
+|occupancy_type |Residential building with more than 4 units |       1.57|
+|flood_zone     |C                                           |       1.00|
+|flood_zone     |A                                           |       1.37|
+|flood_zone     |X                                           |       1.15|
+|flood_zone     |B                                           |       1.64|
+|flood_zone     |V                                           |       1.35|
+|flood_zone     |D                                           |       1.50|
 
@@
 The embeddings are then concatenated with the numeric predictors, which have been normalized in data pre-processing, before being passed through a feedforward layer (with 8 hidden units and ReLU activation) to \textcolor{blue}{finally} obtain a scalar value between 0 and 1, as constrained by a sigmoid output activation.
-\textcolor{blue}{Some regularization is applied within this network using the dropout technique of} @srivastava2014dropout \textcolor{blue}{and by early-stopping the fitting of the network by selecting the model weights that relate to the lowest estimated MSE score on a 5\% validation sample.} This scalar output represents the proportion of coverage amount that is paid out, which we then multiply by the dollar amount of the coverage amount to obtain our prediction of the claims paid.
+\textcolor{blue}{Some regularization is applied within this network using the dropout technique of} @srivastava2014dropout \textcolor{blue}{ with a dropout rate of 2.5\% and by early-stopping the fitting of the network by selecting the model weights that relate to the lowest estimated MSE score on a 5\% validation sample.} \textcolor{blue}{Dropout functions by setting some components of the network randomly to zero during each epoch of training.
+This forces each component of the network to learn a somewhat independent representation of the data, thus helping to avoid overfitting by preventing components of the network from becoming too specialized.} This scalar output represents the proportion of coverage amount that is paid out, which we then multiply by the dollar amount of the coverage amount to obtain our prediction of the claims paid.
 For optimization, we use the mean squared error (MSE) loss function.
@@
 
-| level                                       | embedding |
-|:--------------------------------------------|----------:|
-| 2 to 4 unit residential buidling            |      1.46 |
-| Non-residential building                    |     -1.04 |
-| Residential building with more than 4 units |      0.12 |
-| Single family residence                     |      0.36 |
+|level                                       | embedding|
+|:-------------------------------------------|---------:|
+|2 to 4 unit residential buidling            |     -0.20|
+|Non-residential building                    |     -0.02|
+|Residential building with more than 4 units |     -0.03|
+|Single family residence                     |     -0.16|
 
@@
 
-| level | embedding | level | embedding | level | embedding | level | embedding | level | embedding |
-|:------|----------:|:------|----------:|:------|----------:|:------|----------:|:------|----------:|
-| A     |      1.48 | A09   |     -0.48 | A18   |      0.39 | A28   |      1.19 | C     |      1.73 |
-| A00   |     -1.05 | A0B   |      1.47 | A19   |     -1.06 | A30   |     -0.01 | D     |     -1.15 |
-| A01   |     -0.18 | A10   |     -0.25 | A20   |     -1.01 | A99   |     -0.44 | V     |     -1.85 |
-| A02   |     -0.06 | A11   |      0.35 | A21   |      2.08 | AE    |      1.12 | V01   |      0.02 |
-| A03   |     -0.01 | A12   |     -0.38 | A22   |     -0.15 | AH    |      2.19 | V02   |     -1.55 |
-| A04   |      0.05 | A13   |      2.81 | A23   |     -0.76 | AHB   |     -0.68 | V03   |     -0.98 |
-| A05   |      1.30 | A14   |      0.58 | A24   |     -0.87 | AO    |      0.55 | V04   |      1.73 |
-| A06   |     -0.76 | A15   |     -0.91 | A25   |      0.02 | AOB   |      0.08 | V05   |     -1.97 |
-| A07   |     -0.62 | A16   |      0.79 | A26   |      0.00 | AR    |      2.93 | V06   |      0.43 |
-| A08   |     -0.53 | A17   |      1.35 | A27   |      0.80 | B     |      0.33 | V07   |      1.91 |
+|level | embedding|level | embedding|level | embedding|level | embedding|level | embedding|
+|:-----|---------:|:-----|---------:|:-----|---------:|:-----|---------:|:-----|---------:|
+|A     |     -0.20|A09   |     -0.11|A18   |     -0.26|A30   |     -0.25|D     |     -0.26|
+|A00   |     -0.31|A0B   |     -0.30|A19   |     -0.19|A99   |     -0.11|V     |     -0.44|
+|A01   |     -0.09|A10   |     -0.09|A20   |     -0.26|AE    |     -0.15|V01   |     -0.33|
+|A02   |     -0.05|A11   |     -0.07|A21   |     -0.51|AH    |     -0.18|V02   |     -0.47|
+|A03   |      0.01|A12   |     -0.06|A22   |     -0.21|AHB   |     -0.30|V03   |     -0.32|
+|A04   |     -0.05|A13   |     -0.36|A23   |     -0.31|AO    |     -0.11|V04   |     -0.37|
+|A05   |     -0.17|A14   |     -0.04|A24   |      0.15|AOB   |     -0.09|V05   |     -0.52|
+|A06   |     -0.17|A15   |     -0.26|A25   |     -0.30|AR    |     -0.36|V06   |     -0.02|
+|A07   |     -0.26|A16   |     -0.22|A26   |      0.09|B     |     -0.07|V07   |     -0.16|
+|A08   |     -0.19|A17   |     -0.29|A27   |     -0.07|C     |     -0.20|V08   |     -0.13|
 
@@
 Since each level corresponds to a unique scalar value, we can obtain its contribution to the linear predictor by multiplying by the coefficient estimate of the variable.
-For example, multiplying the estimate of -0.075 for} `occupancy_type` in Table \@ref(tab:glm2) \textcolor{blue}{by each value in Table} \@ref(tab:embeddings-flood-zone), \textcolor{blue}{we obtain the unnormalized contributions of each level, which can then be exponentiated and normalized with respect to the base level} `Single family residence` \textcolor{blue}{in order to obtain the implied relativities, which could then be compared with the first GLM's output in Table} \@ref(tab:relativities).
+For example, multiplying the estimate of 2 for} `occupancy_type` in Table \@ref(tab:glm2) \textcolor{blue}{by each value in Table} \@ref(tab:embeddings-flood-zone), \textcolor{blue}{we obtain the unnormalized contributions of each level, which can then be exponentiated and normalized with respect to the base level} `Single family residence` \textcolor{blue}{in order to obtain the implied relativities, which could then be compared with the first GLM's output in Table} \@ref(tab:relativities).
 
-| term                                     | estimate |
-|:-----------------------------------------|---------:|
-| (Intercept)                              |    3.371 |
-| total_building_insurance_coverage        |    0.586 |
-| basement_enclosure_crawlspace_type       |    0.597 |
-| number_of_floors_in_the_insured_building |   -0.278 |
-| occupancy_type                           |   -0.075 |
-| flood_zone                               |   -0.007 |
-| primary_residence                        |   -0.062 |
-| community_rating_system_discount         |    0.706 |
+|term        | estimate|
+|:------------------------------------------|--------:|
+|(Intercept)                                |    5.579|
+|total_building_insurance_coverage          |    0.959|
+|basement_enclosure_crawlspace_type         |   -2.243|
+|number_of_floors_in_the_insured_building   |    1.254|
+|occupancy_type                             |    2.000|
+|flood_zone                                 |    2.552|
+|primary_residence                          |    0.552|
+|community_rating_system_discount           |    0.042|
 
@@
 
-| level                                       |    e1 |    e2 |    e3 |
-|:--------------------------------------------|------:|------:|------:|
-| 2 to 4 unit residential buidling            |  0.37 | -1.76 |  1.36 |
-| Non-residential building                    |  0.13 |  1.47 |  1.77 |
-| Residential building with more than 4 units | -1.12 | -0.15 | -1.43 |
-| Single family residence                     |  0.85 |  0.16 | -0.99 |
+|level                                       |    e1|    e2|    e3|
+|:-------------------------------------------|-----:|-----:|-----:|
+|2 to 4 unit residential buidling            |  0.14| -0.01|  0.11|
+|Non-residential building                    | -0.10|  0.06| -0.08|
+|Residential building with more than 4 units | -0.05|  0.20|  0.04|
+|Single family residence                     |  0.09| -0.04|  0.10|
 
@@
 
-| dimension | value  | dimension | value  | dimension | value  | dimension | value  |
-|:----------|:-------|:----------|:-------|:----------|:-------|:----------|:-------|
-| e1        | -0.167 | e11       | -0.810 | e21       | -0.300 | e31       | -0.421 |
-| e2        | -0.363 | e12       | 1.380  | e22       | -0.194 | e32       | 0.594  |
-| e3        | -0.893 | e13       | -0.180 | e23       | -0.320 | e33       | 1.681  |
-| e4        | 0.130  | e14       | -1.612 | e24       | -0.035 | e34       | 1.668  |
-| e5        | -1.588 | e15       | -1.327 | e25       | -1.128 |           |        |
-| e6        | -0.123 | e16       | -0.965 | e26       | 0.168  |           |        |
-| e7        | -0.259 | e17       | -1.356 | e27       | -1.022 |           |        |
-| e8        | 0.324  | e18       | -0.061 | e28       | 1.011  |           |        |
-| e9        | -1.430 | e19       | -0.120 | e29       | -0.843 |           |        |
-| e10       | -1.598 | e20       | -0.488 | e30       | -0.743 |           |        |
+|dimension |value   |dimension |value   |dimension |value   |dimension |value   |
+|:---------|:-------|:---------|:-------|:---------|:-------|:---------|:-------|
+|e1        |0.1605  |e11       |0.0439  |e21       |-0.1335 |e31       |-0.0847 |
+|e2        |0.0783  |e12       |0.1183  |e22       |0.0075  |e32       |0.0115  |
+|e3        |0.0716  |e13       |-0.1515 |e23       |0.1771  |e33       |0.1238  |
+|e4        |-0.0420 |e14       |-0.0875 |e24       |-0.1250 |e34       |-0.1007 |
+|e5        |-0.1034 |e15       |0.0427  |e25       |0.1037  |          |        |
+|e6        |-0.0892 |e16       |-0.0302 |e26       |0.1054  |          |        |
+|e7        |0.1485  |e17       |-0.1293 |e27       |-0.0525 |          |        |
+|e8        |-0.0633 |e18       |0.1022  |e28       |-0.0650 |          |        |
+|e9        |0.0680  |e19       |0.1327  |e29       |-0.0313 |          |        |
+|e10       |-0.1160 |e20       |-0.0708 |e30       |0.0709  |          |        |
 
@@
 The standard approaches for this are principal component analysis (PCA; @shlens2014tutorial) and t-distributed stochastic neighbor embedding (t-SNE; @Maaten2008a), both of which we illustrate.
-For a technical review of these methods, refer to Appendix \\ref{dim-red].
+For a technical review of these methods, refer to Appendix \\ref{dim-red}.
 
@@
 In our case, however, we are not able to identify discernable clusters in the plot.
-From inspecting the matrix decomposition results, we see that the cumulative proportion of variance for the first two principal components are just 0.18, which may suggest that perhaps PCA is not the most appropriate dimensionality reduction technique in this case.
+From inspecting the matrix decomposition results, we see that the cumulative proportion of variance for the first two principal components are just \textcolor{blue}{0.38, which is a relatively low proportion,} suggesting that perhaps PCA is not the most appropriate dimensionality reduction technique in this case.
 
@@
 In the first three plots, we can see the semblance of clusters forming.
-In particular, flood zone D appears in its own cluster, which implies it is far away from other levels in the embedding space, *as seen by the model*.
-When the perplexity is set to 10 (and beyond), however, we start to lose the geometric properties.
-While t-SNE is a powerful visualization technique, there are a few points the modeler should be mindful of in practice.
+In particular, flood zone \textcolor{blue}{B appears at the extreme of the plot, which implies it is relatively} far away from other levels in the embedding space, *as seen by the model*.
+\textcolor{blue}{We also observe that flood zones C and X lie close to each other, regardless of the perplexity parameter, and a similar observation can be made for flood zones B and D.
+Using these two sets of points as anchors within these plots, we can finally observe that the learned embeddings for flood zones A and V appear to be divided into two main groups.} While t-SNE is a powerful visualization technique, there are a few points the modeler should be mindful of in practice.
 We refer the reader to @wattenberg2016how for a more thorough discussion, but stress here that the resulting plot can be very sensitive to the perplexity hyperparameter.
@@
 For the GLMs, Models 1 and 3, we follow the standard optimization procedure using iteratively reweighted least squares (IWLS) without regularization.
-For the neural networks, Models 2 and 4, we utilize the \texttt{Adam} optimizer [@Kingma2014] with a learning rate of 0.01 and a minibatch size of 1000.
-We split the training set into analysis and assessment sets, containing 80% and 20% of the rows, respectively.
-We train on the analysis set for a maximum of 15 epochs, and stop early if the loss on the assessment set does not improve for 5 epochs.
+For the neural networks, Models 2 and 4, we utilize the \texttt{Adam} optimizer [@Kingma2014] with a learning rate of \textcolor{blue}{0.001 and a minibatch size of 1024.
+We split the training set into analysis and assessment sets, containing} 80% and 20% \textcolor{blue}{of the rows, respectively, and further select a} 5% \textcolor{blue}{sample of the training set as a validation set to estimate the out of sample performance of each model.
+We train on the analysis set for a maximum of 150 epochs, and select the best model from the 150 epochs as measured by the validation.
+Finally, as mentioned above, in addition to this form of early stopping, we also apply the sropout technique with a rate of dropout of} 2.5\%.
 
@@
 
-We see that the neural networks generally outperform the GLMs; however, what is more interesting is that using learned embeddings in place of categorical levels improves the GLM, at least from the RMSE perspective.
+We see that the neural networks \textcolor{blue}{outperform the GLMs in all cases, as would be expected; however, what is more interesting is that using learned embeddings in place of categorical levels improves the GLM, at least from the RMSE perspective.
+This indicates that using neural networks to derive embeddings for categorical variables for subsequent use in GLMs is a strategy that should be considered when building GLM models for ratemaking.}
 
@@
 Since it is possible for a linear regression to output negative values, we cap the predictions below by 0.01 during scoring.
-Somewhat surprisingly, in the problem we are considering, it performs similarly to the more complex neural network models in the RMSE metric (which it optimizes for, as the unit deviance of the normal distribution correspond to MSE.) On the other hand, the performance of the linear model is quite significantly worse on the MAE metric.
-Of course, this is not to discredit neural networks or GLMs, as the experiments are performed without extensive hyperparameter tuning or feature engineering.
+Somewhat surprisingly, in the problem we are considering, it performs \textcolor{blue}{slightly worse than the more complex neural network models in the RMSE metric but significantly better than the other GLM models.
+This may be because this model optimizes for the RMSE metric, as the unit deviance of the normal distribution corresponds to MSE.} On the other hand, the performance of the linear model is quite significantly worse on the MAE metric.
+\textcolor{blue}{Another observation is that Model 4 performs slighlty worse than Model 2, perhaps as a result of some overfitting resulting from the multidimensional embeddings in Model 4.
+If further tuning were to be applied, it would be sensible to apply extra regularization to Model 4, however, we refrain from doing so here.}
 
 | Model                                                                             | RMSE             | MAE           |
-|:------------------------------------------------------------------------------|-------:|-------:|
-| Model 1: GLM (gamma/log link)                                                 | 65,138 | 38,367 |
-| Model 2: MLP with 1-dimensional embeddings                                    | 60,979 | 37,605 |
-| Model 3: GLM (gamma/log link), categorical variables replaced with embeddings | 63,170 | 38,360 |
-| Model 4: MLP with multidimensional embeddings                                 | 60,973 | 37,574 |
-| Linear regression, predictions capped below at 0.01                           | 60,879 | 38,431 |
+|-----------------------------------------------------------------------------------|------------------|---------------|
+|  Model 1: GLM (gamma/log link)                                                    |          65 676  |       38 431  |
+|  Model 2: MLP with 1-dimensional   embeddings                                     |          60 214  |       37 392  |
+|  Model 3: GLM (gamma/log link), categorical   variables replaced with embeddings  |          63 733  |       37 987  |
+|  Model 4: MLP with multidimensional   embeddings                                  |          60 772  |       37 587  |
+|  Linear regression, predictions capped below   at 0.01                            |          61 285  |       38 962  |
 
@@
 We follow a similar training setup for the three attention based models, to the neural networks discussed in the previous section.
-For Models 5 and 6, we utilize the \texttt{Adam} optimizer as before, however, due to the increased complexity of the models in this section, we use learning rate of 0.001 (compared to 0.01 for the simpler models).
-Reflecting this reduced learning rate, we train on the analysis set for a maximum of 150 epochs, and select the best model based on the lowest loss achieved on the assessment.
-Moreover, since these models are significantly more complex than those tested in the previous section, we also add some minimal regularization using dropout [@srivastava2014dropout] to the attention layers and the last layer of the network, to prevent overfitting.
-Dropout functions by setting some components of the network randomly to zero during each epoch of training.
-This forces each component of the network to learn a somewhat independent representation of the data, thus helping to avoid overfitting by preventing components of the network from becoming too specialized.
-In this section, we drop out components with a probability of 2.5%.
+For Models 5 and 6, we utilize the \texttt{Adam} optimizer as before \textcolor{blue}{and similar to the model in the previous section, we use learning rate of 0.001}.
+\textcolor{blue}{Similarly,} we train on the analysis set for a maximum of 150 epochs, and select the best model based on the lowest loss achieved on the assessment.
+Moreover, since these models are significantly more complex than those tested in the previous section, we also add \textcolor{blue}{extra} regularization using dropout  to the attention layers, to prevent overfitting.In this section, we drop out components with a probability of 2.5%.
 A final detail is that, for both of these models, we use an embedding dimension of size 16 for each of the categorical covariates, since the attention mechanism requires that the embeddings be of a common length.
@@
 Finally, the TabTransformer model shows the best performance of all models considered in this research, beating the other models by a significant margin on both the RMSE and MAE metrics.
+\textcolor{blue}{We conclude that the more complex Transformer style attention applied in the TabTransformer model appears to lead to a relatively significant improvement in performance over all other models considered here.}
 
 | Model                                                                            | RMSE             | MAE              |
-|:----------------------------------------------------|-------:|-------:|
-| Model 4: MLP with multidimensional embeddings       | 60,973 | 37,574 |
-| Model 5: Simple Attention                           | 60,601 | 36,739 |
-| \textcolor{blue}{Model 6: TabTransformer}           | 59,900 | 36,343 |
-| \textcolor{blue}{Model 7: TabNet}                   | 62,938 | 38,386 |
-| Linear regression, predictions capped below at 0.01 | 60,879 | 38,431 |
+|----------------------------------------------------------------------------------|------------------|------------------|
+| Model 2: MLP with 1-dimensional   embeddings                                     |          60 214  |          37 392  |
+| Model 5: Simple Attention                                                        |          60 367  |          37 527  |
+| Model 6: TabTransformer                                                          |          59 908  |          36 501  |
+| Model 7: TabNet                                                                  |          63 619  |          39 668  |
+| Linear regression, predictions capped below at 0.01                              |          61 285  |          38 962  |
 
@@
 
-| Embedding Type       |     RMSE |      MAE |
-|:---------------------|---------:|---------:|
-| Embedding            | 62596.84 | 40323.82 |
-| Contextual embedding | 62027.85 | 39450.45 |
+|Embedding Type       |  RMSE|   MAE|
+|:--------------------|------:|------:|
+|Embedding            | 68 444| 41 557|
+|Contextual embedding | 67 905| 40 559|
 
@@
 ```
+
 # Finetuning the Neural Network Models
+
 Here we describe how the neural network models presented in Sections 4 and 5 above were fine-tuned.
@@
 ## Models in Section 4
+
+```{=tex}
 \textcolor{blue}{
@@
 The following table shows these results for each of Model 2 and Model 4.}
+```
+\tiny
 
 |                | ReLU/8 | ReLu/16 | ReLu/32 | ReLu/64 | ReLu/128 | tanh/8 | tanh/16 | tanh/32 | tanh/64 | tanh/128 |
-|---|---|---|---|---|---|---|---|---|---|---|
+|----------------|--------|---------|---------|---------|----------|--------|---------|---------|---------|----------|
 | Model 2 - RMSE | 60 988 | 60 561  | 60 125  | 60 147  | 59 918   | 61 728 | 60 506  | 60 130  | 59 893  | 60 065   |
@@
 
+\normalsize
+
 \textcolor{blue}{It can be observed that the lowest RMSE values are produced using the tanh activation function with a hidden layer width 64 neurons.}
+
+\newpage
 
@@
 \textcolor{blue}{Models 5 and 6 add an attention-based mechanism to derive contextual embeddings to the models in Section 4.
-To find optimal hyperparameters, the best performing variation of Model 4 (tanh/64) was taken as a baseline, and the attention mechanisms described for Models 5 and 6 were added to this baseline.
-Since the performance of the models would ideally improve as a result of adding the attention mechanisms, and, indeed, we see this is the case in the following table, we do not attempt to fine-tune Models 5 and 6 any further.}
+To find optimal hyperparameters, the best performing variation of Model 4 (tanh/64) was taken as a baseline, and the attention mechanisms described for Models 5 and 6 were then added to this baseline model.
+It was found that the performance of Model 6 improved as a result of adding the Tab Transformer attention mechanism, and, thus, no further fintetuning was performed on this model.
+However, despite several attempts at optimizing the hyperparameters of Models 5 (which included modifying the size of the embeddings and the amount of dropout applied), significant improvements beyond those shown in the table below were not achieved.}
+
+\tiny
+
+|                | Scores |
+|----------------|--------|
+| Model 5 - RMSE | 60 382 |
+| Model 5 - MAE  | 37 426 |
+| Model 6 - RMSE | 59 821 |
+| Model 6 - MAE  | 36 474 |
+: Results of fine-tuning models in Section 5.
+
+\normalsize
+
+\textcolor{blue}{Finally, several of the recommended default hyperparamter settings for the TabNet model were tried, however, significant improvements over the results shown in Section 5 were not achieved.}
 

### 2022-04-10 R/cv-model-keras.R

@@ -5,6 +5,7 @@ library(torch)
 library(data.table)
 library(keras)
 require(tensorflow)
+require(tabnet)
 tf$compat$v1 = T
 
 source("model-utils.R")
@@ -23,8 +24,10 @@ categorical_cols <- c(
 numeric_cols <- c("total_building_insurance_coverage", "community_rating_system_discount")
 response_col <- "amount_paid_on_building_claim"
 
+### for finetuning use first 100k
 for_cv = small_data[1:100000,]
-for_test = small_data[100000:200000,]
+### for test use second 100k
+#for_test = small_data[100000:200000,]
 
 set.seed(420)
 cvfolds <- for_cv %>%
@@ -125,53 +128,68 @@ model_analyze_assess <- function(splits, learning_rate = 1, epochs = 10, batch_s
 
     ### glm - replace with unidimensional embeddings
 
-    analysis_data = analysis_data %>% data.table()
-    embed_map = get_embed_map(analysis_data, simple_nn$model, 6)
-    #
-    # temp = embed_map[["flood_zone"]]
-    # temp[, flood_zone_long := flood_zone]
-    # temp[, flood_zone := str_sub(flood_zone_long,1,1)]
-    # temp =     temp[, .(flood_zone_embed_1 = mean(flood_zone_embed_1)), keyby = flood_zone]
-    # embed_map[["flood_zone"]] =temp %>% copy
-
-    train_glm = juice(rec_glm) %>% data.table()
-    train_glm[, set := "train"]
-    test_glm = bake(rec_glm, assessment_data) %>% data.table()
-    test_glm[, set := "test"]
-
-    train_glm = rbind(train_glm, test_glm)
-
-    # train_glm[, flood_zone_long := flood_zone]
-    # train_glm[, flood_zone := str_sub(flood_zone_long,1,1)]
-    # train_glm$flood_zone_long = NULL
-
-    train_glm_cat = train_glm[, c(categorical_cols), with=F]
-
-    glm_cols = c( "total_building_insurance_coverage" ,
-                  "basement_enclosure_crawlspace_type" , "number_of_floors_in_the_insured_building" ,
-                  "occupancy_type" , "flood_zone" , "primary_residence" , "community_rating_system_discount")
-
-    for (column in categorical_cols){
-      train_glm %>% setkeyv(eval(column))
-      train_glm_cat %>% setkeyv(eval(column))
[…]

### 2022-04-10 R/keras_working_file.R

@@ -29,7 +29,7 @@ input_list[[count+1]] = layer_input(shape = numeric_cols %>% length, dtype = "fl
 
 embeddings = embedding_list %>% layer_concatenate()
 main = list(embeddings, input_list[[count+1]]) %>% layer_concatenate() %>%
-  layer_dense(units = hidden_layer_units, activation = "relu") %>%
+  layer_dense(units = hidden_layer_units, activation = hidden_layer_activations) %>%
   layer_dropout(rate = 0.025)
 
 output = main %>%

### 2022-04-10 R/keras_working_file_tabtrans_48.R

@@ -10,7 +10,7 @@ get_keras_model_tabtrans = function(hidden_layer_units = 64, embed = 0, for_card
   get_embed_dim = function(cards, embed){
     if (embed == 1) {1}
     else{
-      if(embed ==0) {12}
+      if(embed ==0) {44}
       else {(trunc(cards/2)+1)}
     }
   }
@@ -37,29 +37,29 @@ get_keras_model_tabtrans = function(hidden_layer_units = 64, embed = 0, for_card
 
   attn_heads = list()
 
-  for (i in 1:2){
-    key = all_embeds %>% (layer = layer_dense(units = 16))
-    query = all_embeds %>% (layer = layer_dense(units = 16))
-    value = all_embeds %>% (layer = layer_dense(units = 16))
-    attn = layer_attention(list(key, query, value), use_scale = T)%>%
-      layer_dropout(rate = 0.5)
+  for (i in 1:4){
+    key = all_embeds %>% (layer = layer_dense(units = 12))
+    query = all_embeds %>% (layer = layer_dense(units = 12))
+    value = all_embeds %>% (layer = layer_dense(units = 12))
+    attn = layer_attention(list(key, query, value), use_scale = T) %>%
+      layer_dropout(rate = 0.075)
     attn_heads[[i]] = attn
   }
 
-  multi_head_attn = attn_heads %>% layer_concatenate(axis=2) %>% layer_dense(units = 16)
+  multi_head_attn = attn_heads %>% layer_concatenate(axis=2) %>% layer_dense(units = 48)
   stage1 = list(all_embeds, multi_head_attn) %>% layer_add()%>% layer_layer_normalization()
 
-  stage2 = stage1  %>% layer_dense(units = 16*4, activation = "linear") %>%
+  stage2 = stage1  %>% layer_dense(units = 48*4, activation = "linear") %>%
     layer_activation_leaky_relu() %>%
-    layer_dropout(rate = 0.5) %>% layer_dense(units = 16)
+    layer_dropout(rate = 0.15) %>% layer_dense(units = 48)
 
   stage3 = list(stage1, stage2) %>% layer_add() %>% layer_layer_normalization()
 
-  attn_flat = stage3 %>% layer_flatten() %>% layer_dropout(rate = 0.05)
+  attn_flat = stage3 %>% layer_flatten() %>% layer_dropout(rate = 0.15)
 
   main = list(attn_flat, input_list[[count+1]]) %>% layer_concatenate() %>%
[…]

### 2022-04-10 R/keras_working_file_tabtrans_inc_doattn.R

@@ -10,7 +10,7 @@ get_keras_model_tabtrans = function(hidden_layer_units = 64, embed = 0, for_card
   get_embed_dim = function(cards, embed){
     if (embed == 1) {1}
     else{
-      if(embed ==0) {12}
+      if(embed ==0) {8}
       else {(trunc(cards/2)+1)}
     }
   }
@@ -38,20 +38,20 @@ get_keras_model_tabtrans = function(hidden_layer_units = 64, embed = 0, for_card
   attn_heads = list()
 
   for (i in 1:2){
-    key = all_embeds %>% (layer = layer_dense(units = 16))
-    query = all_embeds %>% (layer = layer_dense(units = 16))
-    value = all_embeds %>% (layer = layer_dense(units = 16))
+    key = all_embeds %>% (layer = layer_dense(units = 12))
+    query = all_embeds %>% (layer = layer_dense(units = 12))
+    value = all_embeds %>% (layer = layer_dense(units = 12))
     attn = layer_attention(list(key, query, value), use_scale = T)%>%
-      layer_dropout(rate = 0.5)
+      layer_dropout(rate = 0.025)
     attn_heads[[i]] = attn
   }
 
-  multi_head_attn = attn_heads %>% layer_concatenate(axis=2) %>% layer_dense(units = 16)
+  multi_head_attn = attn_heads %>% layer_concatenate(axis=2) %>% layer_dense(units = 12)
   stage1 = list(all_embeds, multi_head_attn) %>% layer_add()%>% layer_layer_normalization()
 
-  stage2 = stage1  %>% layer_dense(units = 16*4, activation = "linear") %>%
+  stage2 = stage1  %>% layer_dense(units = 12*4, activation = "linear") %>%
     layer_activation_leaky_relu() %>%
-    layer_dropout(rate = 0.5) %>% layer_dense(units = 16)
+    layer_dropout(rate = 0.05) %>% layer_dense(units = 12)
 
   stage3 = list(stage1, stage2) %>% layer_add() %>% layer_layer_normalization()
 
@@ -75,7 +75,7 @@ get_keras_model_tabtrans = function(hidden_layer_units = 64, embed = 0, for_card
     optimizer = adam
   )
 
-  lr_call = callback_reduce_lr_on_plateau(monitor = "val_loss", patience = 50, verbose = 1, cooldown = 1,
[…]

### 2022-04-10 R/keras_working_file_tabtrans_inc_doattn_16.R

@@ -10,7 +10,7 @@ get_keras_model_tabtrans = function(hidden_layer_units = 64, embed = 0, for_card
   get_embed_dim = function(cards, embed){
     if (embed == 1) {1}
     else{
-      if(embed ==0) {12}
+      if(embed ==0) {4}
       else {(trunc(cards/2)+1)}
     }
   }
@@ -38,24 +38,24 @@ get_keras_model_tabtrans = function(hidden_layer_units = 64, embed = 0, for_card
   attn_heads = list()
 
   for (i in 1:2){
-    key = all_embeds %>% (layer = layer_dense(units = 16))
-    query = all_embeds %>% (layer = layer_dense(units = 16))
-    value = all_embeds %>% (layer = layer_dense(units = 16))
+    key = all_embeds %>% (layer = layer_dense(units = 8))
+    query = all_embeds %>% (layer = layer_dense(units = 8))
+    value = all_embeds %>% (layer = layer_dense(units = 8))
     attn = layer_attention(list(key, query, value), use_scale = T)%>%
-      layer_dropout(rate = 0.5)
+      layer_dropout(rate = 0.025)
     attn_heads[[i]] = attn
   }
 
-  multi_head_attn = attn_heads %>% layer_concatenate(axis=2) %>% layer_dense(units = 16)
+  multi_head_attn = attn_heads %>% layer_concatenate(axis=2) %>% layer_dense(units = 8)
   stage1 = list(all_embeds, multi_head_attn) %>% layer_add()%>% layer_layer_normalization()
 
-  stage2 = stage1  %>% layer_dense(units = 16*4, activation = "linear") %>%
+  stage2 = stage1  %>% layer_dense(units = 8*4, activation = "linear") %>%
     layer_activation_leaky_relu() %>%
-    layer_dropout(rate = 0.5) %>% layer_dense(units = 16)
+    layer_dropout(rate = 0.025) %>% layer_dense(units = 8)
 
   stage3 = list(stage1, stage2) %>% layer_add() %>% layer_layer_normalization()
 
-  attn_flat = stage3 %>% layer_flatten() %>% layer_dropout(rate = 0.05)
+  attn_flat = stage3 %>% layer_flatten() %>% layer_dropout(rate = 0.025)
 
   main = list(attn_flat, input_list[[count+1]]) %>% layer_concatenate() %>%
     layer_dense(units = 64, activation = "tanh") %>%
[…]

### 2022-04-10 R/results.R

@@ -10,9 +10,32 @@ files = list.files(dirs)
 all_res = lapply(files, function (x) fread(paste0(dirs, x))) %>% rbindlist(fill = T) %>% data.table()
 
 all_res = all_res %>% melt.data.table(id.vars = c("run", "id"))
-melted = all_res[, mean(value), keyby = .(run, variable)] 
-melted = melted[order(run)]%>% 
-  dcast.data.table(variable~run) 
+melted = all_res[, mean(value), keyby = .(run, variable)]
+melted = melted[order(run)]%>%
+  dcast.data.table(variable~run)
 
-melted[variable %in% c("rmse_nn", "rmse_nn2", "mae_nn", "mae_nn2")] %>% 
+melted[variable %in% c("rmse_nn", "rmse_nn2", "mae_nn", "mae_nn2")] %>%
   fwrite("c:/r/finetune_sect4.csv")
+
+all_res = fread(paste0(dirs, "sect5.csv"))
+
+all_res = all_res %>% melt.data.table(id.vars = c("run", "id"))
+melted = all_res[, mean(value), keyby = .(run, variable)]
+melted = melted[order(run)]%>%
+  dcast.data.table(variable~run)
+
+melted %>%
+fwrite("c:/r/finetune_sect5.csv")
+
+
+
+
+all_res = res
+
+all_res = all_res %>% melt.data.table(id.vars = c("run", "id"))
+melted = all_res[, mean(value), keyby = .(run, variable)]
+melted = melted[order(run)]%>%
+  dcast.data.table(variable~run)
+
+melted %>%
+  fwrite("c:/r/finetune_sect5.csv")

### 2022-04-11 manuscript/manuscript.Rmd
Spelling corrections

@@
 The standard approaches for this are principal component analysis (PCA; @shlens2014tutorial) and t-distributed stochastic neighbor embedding (t-SNE; @Maaten2008a), both of which we illustrate.
-For a technical review of these methods, refer to Appendix \\ref{dim-red}.
+For a technical review of these methods, refer to Appendix \ref{dim-red}.
 
@@
 |-----------------------------------------------------------------------------------|------------------|---------------|
-|  Model 1: GLM (gamma/log link)                                                    |          65 676  |       38 431  |
-|  Model 2: MLP with 1-dimensional   embeddings                                     |          60 214  |       37 392  |
-|  Model 3: GLM (gamma/log link), categorical   variables replaced with embeddings  |          63 733  |       37 987  |
-|  Model 4: MLP with multidimensional   embeddings                                  |          60 772  |       37 587  |
-|  Linear regression, predictions capped below   at 0.01                            |          61 285  |       38 962  |
+|  Model 1: GLM (gamma/log link)                                                    |          65,676  |       38,431  |
+|  Model 2: MLP with 1-dimensional   embeddings                                     |          60,214  |       37,392  |
+|  Model 3: GLM (gamma/log link), categorical   variables replaced with embeddings  |          63,733  |       37,987  |
+|  Model 4: MLP with multidimensional   embeddings                                  |          60,772  |       37,587  |
+|  Linear regression, predictions capped below   at 0.01                            |          61,285  |       38,962  |
 
@@
 |----------------------------------------------------------------------------------|------------------|------------------|
-| Model 2: MLP with 1-dimensional   embeddings                                     |          60 214  |          37 392  |
-| Model 5: Simple Attention                                                        |          60 367  |          37 527  |
-| Model 6: TabTransformer                                                          |          59 908  |          36 501  |
-| Model 7: TabNet                                                                  |          63 619  |          39 668  |
-| Linear regression, predictions capped below at 0.01                              |          61 285  |          38 962  |
+| Model 2: MLP with 1-dimensional   embeddings                                     |          60,214  |          37,392  |
+| Model 5: Simple Attention                                                        |          60,367  |          37,527  |
+| Model 6: TabTransformer                                                          |          59,908  |          36,501  |
+| Model 7: TabNet                                                                  |          63,619  |          39,668  |
+| Linear regression, predictions capped below at 0.01                              |          61,285  |          38,962  |
 
@@
 |:--------------------|------:|------:|
-|Embedding            | 68 444| 41 557|
-|Contextual embedding | 67 905| 40 559|
+|Embedding            | 68,444| 41,557|
+|Contextual embedding | 67,905| 40,559|
 
@@
 
-# Finetuning the Neural Network Models
+# Fine-tuning the Neural Network Models
 
@@
 |----------------|--------|---------|---------|---------|----------|--------|---------|---------|---------|----------|
-| Model 2 - RMSE | 60 988 | 60 561  | 60 125  | 60 147  | 59 918   | 61 728 | 60 506  | 60 130  | 59 893  | 60 065   |
-| Model 4 - RMSE | 60 535 | 60 724  | 60 311  | 60 191  | 60 114   | 60 521 | 60 658  | 60 279  | 59 892  | 59 987   |
-| Model 2 - MAE  | 36 604 | 36 791  | 36 936  | 37 140  | 36 816   | 37 206 | 36 759  | 36 921  | 37 103  | 37 177   |
-| Model 4 - MAE  | 36 828 | 36 824  | 36 780  | 37 054  | 36 672   | 36 528 | 36 725  | 36 483  | 36 766  | 36 394   |
+| Model 2 - RMSE | 60,988 | 60,561  | 60,125  | 60,147  | 59,918   | 61,728 | 60,506  | 60,130  | 59,893  | 60,065   |
+| Model 4 - RMSE | 60,535 | 60,724  | 60,311  | 60,191  | 60,114   | 60,521 | 60,658  | 60,279  | 59,892  | 59,987   |
+| Model 2 - MAE  | 36,604 | 36,791  | 36,936  | 37,140  | 36,816   | 37,206 | 36,759  | 36,921  | 37,103  | 37,177   |
+| Model 4 - MAE  | 36,828 | 36,824  | 36,780  | 37,054  | 36,672   | 36,528 | 36,725  | 36,483  | 36,766  | 36,394   |
 : Results of fine-tuning models in Section 4.
@@
 To find optimal hyperparameters, the best performing variation of Model 4 (tanh/64) was taken as a baseline, and the attention mechanisms described for Models 5 and 6 were then added to this baseline model.
-It was found that the performance of Model 6 improved as a result of adding the Tab Transformer attention mechanism, and, thus, no further fintetuning was performed on this model.
+It was found that the performance of Model 6 improved as a result of adding the TabTransformer attention mechanism, and, thus, no further fintetuning was performed on this model.
 However, despite several attempts at optimizing the hyperparameters of Models 5 (which included modifying the size of the embeddings and the amount of dropout applied), significant improvements beyond those shown in the table below were not achieved.}
@@
 |----------------|--------|
-| Model 5 - RMSE | 60 382 |
-| Model 5 - MAE  | 37 426 |
-| Model 6 - RMSE | 59 821 |
-| Model 6 - MAE  | 36 474 |
+| Model 5 - RMSE | 60,382 |
+| Model 5 - MAE  | 37,426 |
+| Model 6 - RMSE | 59,821 |
+| Model 6 - MAE  | 36,474 |
 : Results of fine-tuning models in Section 5.

### 2022-04-11 manuscript/manuscript.Rmd
Finalize manuscript

@@
 We compare the results of the TabTransformer model to the other models tested below.
+\textcolor{blue}{We refer the reader to Section \ref{attention_models} below where the TabTransformer model is shown diagramatically.}
 
@@
 
-For our experiments, we set up a 5-fold cross validation scheme that is applied to each of the models we introduce.
+For our experiments, we set up a 5-fold cross-validation scheme that is applied to each of the models we introduce.
 In Sections \ref{models} and \ref{interpretation}, the tables and figures are based on a single fold of the cross validation split.
@@
 
-\textcolor{blue}{Whereas the main focus of our contribution} is on applications of categorical embeddings in predictive modeling, \textcolor{blue}{we have fine-tuned the neural network models in this (and the next) sections using the same 5-fold cross validation scheme described above, but applied to a separate 100k data point subsample of the FEMA data.
-The results of this fine-tuning are reported in detail in the appendix.
+\textcolor{blue}{Whereas the main focus of our contribution} is on applications of categorical embeddings in predictive modeling, \textcolor{blue}{we have fine-tuned the neural network models in this (and the next) sections using the same 5-fold cross validation scheme described above, but applied to a separate 100k data point subsample of the NFIP data.
+The results of this fine-tuning are reported in detail in the appendix and this separate subsample of the NFIP data is not used for any other purpose in this study.
 The performance metrics in this, and the next, section are based on the optimal models found through this process.
@@
 From inspecting the matrix decomposition results, we see that the cumulative proportion of variance for the first two principal components are just \textcolor{blue}{0.38, which is a relatively low proportion,} suggesting that perhaps PCA is not the most appropriate dimensionality reduction technique in this case.
+\textcolor{blue}{Additionally, this indicates that each of the dimensions of the calibrated embeddings are important, implying that the embedding has been well calibrated.}
 
@@
 For the neural networks, Models 2 and 4, we utilize the \texttt{Adam} optimizer [@Kingma2014] with a learning rate of \textcolor{blue}{0.001 and a minibatch size of 1024.
-We split the training set into analysis and assessment sets, containing} 80% and 20% \textcolor{blue}{of the rows, respectively, and further select a} 5% \textcolor{blue}{sample of the training set as a validation set to estimate the out of sample performance of each model.
-We train on the analysis set for a maximum of 150 epochs, and select the best model from the 150 epochs as measured by the validation.
-Finally, as mentioned above, in addition to this form of early stopping, we also apply the sropout technique with a rate of dropout of} 2.5\%.
+Using a five-fold cross-validation approach, we split the dateset into analysis and assessment sets, containing} 80% and 20% \textcolor{blue}{of the rows, respectively, and further select a} 5% \textcolor{blue}{sample of the analysis set as a validation set to estimate the out of sample performance of each model.
+This is repeated five times on non-overlapping subsets of the dataset.
+For each of these five splits of the data, we train on the analysis set for a maximum of 150 epochs, and select the best model from the 150 epochs as measured by the validation set.
+Finally, as mentioned above, in addition to this form of early stopping, we also apply the dropout technique with a rate of dropout of} 2.5\%.
 
@@
 
+Acknowledgments {.unnumbered}
+==========
+
+We thank the two anonymous reviewers for their helpful comments which significantly improved the manuscript.
+
 \clearpage
